### 2013-04-04 Sunpy_paper_0.3.tex
Added template for IOP CSD.
This is the jouranl to which scipy 2013 are submitting, however
if we want to / need to at a later date this can be changed.

\documentclass[12pt]{iopart}

%Uncomment next line if AMS fonts required
%\usepackage{iopams}

\begin{document}

\title{SunPy - Python for Solar Physicists}

\author{SunPy Developers}

\address{The Internet}
\ead{sunpy@googlegroups.com}
\begin{abstract}

SunPy contains too much awesome.

\end{abstract}

\maketitle

\section{Introduction}

\section*{References}
\begin{thebibliography}{10}
\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{thebibliography}

\end{document}

### 2014-01-08 Sunpy_paper_0.4.tex
Rename tex source
Add draft TOC and bib

--- 2013-04-04 Sunpy_paper_0.3.tex
@@
 
-\title{SunPy - Python for Solar Physicists}
+\title{SunPy - Python for Solar Physics}
 
-\author{SunPy Developers}
+\author{S J Mumford}
+\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield, S3 7RH U.K.}
 
-\address{The Internet}
+\author{J Bloggs}
+\address{Wibble wiblle wiblle}
+
 \ead{sunpy@googlegroups.com}
+
 \begin{abstract}
-
-SunPy contains too much awesome.
+This paper presents version 0.4 of SunPy a community developed Python package.
+SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.
 
@@
 
-\section*{References}
-\begin{thebibliography}{10}
-\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
-(Reading, MA: Addison-Wesley)
-\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
-\end{thebibliography}
+\section{Core Data Types}
+
+	\subsection{Map}
+
+	\subsection{Lightcurve}
+
+	\subsection{Spectra}
+
+\section{Solar Data Retrieval}
+
+	\subsection{VSO}
+
+	\subsection{HEK}
+
+	\subsection{HELIO}
+
+\section{Visualisation}
+
+\section{Coordinates}
+
+\section{Development and Community}
+
+\section{Future of SunPy}
+
+%%% References
+\bibliography{sunpy_paper_0.4}{}
 

### 2014-01-09 Sunpy_paper_0.4.tex
Add some introduction

@@
 \author{S J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield, S3 7RH U.K.}
+\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
+Mathematics and Statistics, The University of Sheffield, Hicks Building, 
+Hounsfield Road, Sheffield, S3 7RH U.K.}
 
@@
 \begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package.
-SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.
+This paper presents version 0.4 of SunPy a community developed Python package 
+for solar physics.
 
@@
 \section{Introduction}
+SunPy is a project dedicated to providing the tools to process and analyse 
+solar data in Python.
+The Python programming language has gained much traction as a scientific 
+programming language in the last decade.
+Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
+the core tools 
+needed 
+for 
+scientific analsysis and visualisation, while other packages such as pandas, 
+Astropy or scikit-image provide more domain specific functionality.
+SunPy aims to provide such domain specific functionality to the solar physics 
+community.
+
+The goal of SunPy is to provide a clean, simple to use and well structured 
+package that provides the \textit{core} tools for solar physics.
+The primary focus of SunPy's development is current providing specialised, 
+linked, datatypes that allow the import, processing and visualisation of solar 
+data. Currently the datatypes implemented are \texttt{Map}, \texttt{LightCurve} 
+and \texttt{Spectrum}, LLthese cover spatial, timeseries and spectral data 
+respectively.
+
+In this paper we will provide an overview of the current functionality of the 
+\texttt{sunpy} library as well as giving details on the development model and 
+community aspects of the SunPy project.
 
@@
 
-\section{Solar Data Retrieval}
+\section{Solar Data Search and Retrieval}
 
@@
 	\subsection{HELIO}
+
+	\subsection{The SunPy Database}
 

### 2014-01-13 Sunpy_paper_0.4.tex

@@
 data. Currently the datatypes implemented are \texttt{Map}, \texttt{LightCurve} 
-and \texttt{Spectrum}, LLthese cover spatial, timeseries and spectral data 
+and \texttt{Spectrum}, these cover spatial, timeseries and spectral data 
 respectively.
@@
 \section{Core Data Types}
+One of the primary focus' of the SunPy library is to provide data structures 
+that are 
+specifically designed for the various types of data generally processed for 
+solar physics. Currently \texttt{SunPy} provides three datatypes, each separate 
+from one another to process 2D spatial data (Map), 1D temporal series 
+(LightCurve) and 1 and 2D spectra (Spectrum and Spectra).
+
+This section will give a brief overview of the \textit{current} functionality 
+of each of these modules and then describe the development plan for future 
+improvements to these submodules.
 
 	\subsection{Map}
+	Map is a 2D spatial data type, primarily used for images of the Sun and 
+	inner heliosphere. It provides a wrapper around a data array (numpy 
+	ndarray) and gives easy access to standard meta data in the header of the 
+	image.
+	The \texttt{Map} datatype provides convenience methods for many functions 
+	such as, rotation and re-sampling as well as convenience visualisation 
+	functions.
+	The design of the map submodule is such that each instrument or 
+	detector can subclass the parent \texttt{GenericMap} class to implement 
+	special meta data handling or other data specific functions. Each subclass 
+	of \texttt{GenericMap} can register with the \texttt{Map} factory class and 
+	by implementing a method that returns \texttt{True} if the meta data 
+	matches meta data for that instrument or detector, the \texttt{Map} factory 
+	will automatically return an instance of the specific \texttt{GenericMap} 
+	subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
+	following instruments: \textit{IRIS} SJI frames, \textit{SDO/AIA} and 
+	\textit{HMI}, \textit{SOHO/EIT} and 	\textit{LASCO}, 
+	\textit{STEREO/EUVI} 	and \textit{COR}, \textit{YOHKOH/SXT}, 
+	\textit{RHESSI}, \textit{PROBA2/SWAP} and\textit{HINODE/XRT}.
+	As well as providing the base classes the map submodule provides two 
+	collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
+	temporally and spatially aligned data respectively. \texttt{MapCube} 
+	provides methods for animation of its series of \texttt{Map} objects. 
+	\texttt{CompositeMap} provides methods for overlaying spatially aligned 
+	data, with support for visualisation of images and contour lines overlaid 
+	upon each other.
 

### 2014-01-13 1-Introduction.tex

--- 2014-01-09 Sunpy_paper_0.4.tex
@@
-\documentclass[12pt]{iopart}
-
-%Uncomment next line if AMS fonts required
-%\usepackage{iopams}
-
-\begin{document}
-
-\title{SunPy - Python for Solar Physics}
-
-\author{S J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
-Mathematics and Statistics, The University of Sheffield, Hicks Building, 
-Hounsfield Road, Sheffield, S3 7RH U.K.}
-
-\author{J Bloggs}
-\address{Wibble wiblle wiblle}
-
-\ead{sunpy@googlegroups.com}
-
-\begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package 
-for solar physics.
-
-\end{abstract}
-
-\maketitle
-
 \section{Introduction}
@@
 Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
-the core tools 
-needed 
-for 
-scientific analsysis and visualisation, while other packages such as pandas, 
-Astropy or scikit-image provide more domain specific functionality.
-SunPy aims to provide such domain specific functionality to the solar physics 
-community.
+the core tools needed for scientific analsysis and visualisation, while other 
+packages such as pandas, Astropy or scikit-image provide more domain specific 
+functionality. SunPy aims to provide such domain specific functionality to the 
+solar physics community.
 
@@
 community aspects of the SunPy project.
-
-\section{Core Data Types}
-
-	\subsection{Map}
-
-	\subsection{Lightcurve}
-
-	\subsection{Spectra}
-
-\section{Solar Data Search and Retrieval}
-
-	\subsection{VSO}
-
-	\subsection{HEK}
-
-	\subsection{HELIO}
-
-	\subsection{The SunPy Database}
-
-\section{Visualisation}
-
-\section{Coordinates}
-
-\section{Development and Community}
-
-\section{Future of SunPy}
-
-%%% References
-\bibliography{sunpy_paper_0.4}{}
-
-\end{document}

### 2014-01-13 2-Data_Types.tex

--- 2014-01-08 Sunpy_paper_0.4.tex
@@
-\documentclass[12pt]{iopart}
+\section{Core Data Types}
+One of the primary focus' of the SunPy library is to provide data structures 
+that are 
+specifically designed for the various types of data generally processed for 
+solar physics. Currently \texttt{SunPy} provides three datatypes, each separate 
+from one another to process 2D spatial data (Map), 1D temporal series 
+(LightCurve) and 1 and 2D spectra (Spectrum and Spectra).
 
-%Uncomment next line if AMS fonts required
-%\usepackage{iopams}
+This section will give a brief overview of the \textit{current} functionality 
+of each of these modules and then describe the development plan for future 
+improvements to these submodules.
 
-\begin{document}
-
-\title{SunPy - Python for Solar Physics}
-
-\author{S J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield, S3 7RH U.K.}
-
-\author{J Bloggs}
-\address{Wibble wiblle wiblle}
-
-\ead{sunpy@googlegroups.com}
-
-\begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package.
-SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.
-
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-\section{Core Data Types}
-
-	\subsection{Map}
-
-	\subsection{Lightcurve}
-
-	\subsection{Spectra}
-
-\section{Solar Data Retrieval}
-
-	\subsection{VSO}
-
-	\subsection{HEK}
-
-	\subsection{HELIO}
-
-\section{Visualisation}
-
-\section{Coordinates}
-
-\section{Development and Community}
-
-\section{Future of SunPy}
-
-%%% References
-\bibliography{sunpy_paper_0.4}{}
-
-\end{document}
+\input{2-1-Map}
+\input{2-2-Lightcurve}
+\input{2-3-Spectra}

### 2014-01-13 3-Retrieval.tex

\section{Solar Data Search and Retrieval}

\input{3-1-VSO}
\input{3-2-HEK}
\input{3-3-HELIO}
\input{3-4-Helioviewer}
\input{3-5-Database}

### 2014-01-13 4-Util.tex

\section{Utilities}

	\subsection{Coordinates}

	\subsection{Constants}

	\subsection{Sun}

	\subsection{General}

### 2014-01-13 2-1-Map.tex
Split tex file into parts @ehsteve You can do util ;)

--- 2014-01-08 Sunpy_paper_0.4.tex
@@
-\documentclass[12pt]{iopart}
-
-%Uncomment next line if AMS fonts required
-%\usepackage{iopams}
-
-\begin{document}
-
-\title{SunPy - Python for Solar Physics}
-
-\author{S J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield, S3 7RH U.K.}
-
-\author{J Bloggs}
-\address{Wibble wiblle wiblle}
-
-\ead{sunpy@googlegroups.com}
-
-\begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package.
-SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.
-
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-\section{Core Data Types}
-
 	\subsection{Map}
-
-	\subsection{Lightcurve}
-
-	\subsection{Spectra}
-
-\section{Solar Data Retrieval}
-
-	\subsection{VSO}
-
-	\subsection{HEK}
-
-	\subsection{HELIO}
-
-\section{Visualisation}
-
-\section{Coordinates}
-
-\section{Development and Community}
-
-\section{Future of SunPy}
-
-%%% References
-\bibliography{sunpy_paper_0.4}{}
-
-\end{document}
+	Map is a 2D spatial data type, primarily used for images of the Sun and 
+	inner heliosphere. It provides a wrapper around a data array (numpy 
+	ndarray) and gives easy access to standard meta data in the header of the 
+	image.
+	The \texttt{Map} datatype provides convenience methods for many functions 
+	such as, rotation and re-sampling as well as convenience visualisation 
+	functions.
+	The design of the map submodule is such that each instrument or 
+	detector can subclass the parent \texttt{GenericMap} class to implement 
+	special meta data handling or other data specific functions. Each subclass 
+	of \texttt{GenericMap} can register with the \texttt{Map} factory class and 
+	by implementing a method that returns \texttt{True} if the meta data 
+	matches meta data for that instrument or detector, the \texttt{Map} factory 
+	will automatically return an instance of the specific \texttt{GenericMap} 
+	subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
+	following instruments: \textit{IRIS} SJI frames, \textit{SDO/AIA} and 
+	\textit{HMI}, \textit{SOHO/EIT} and 	\textit{LASCO}, 
+	\textit{STEREO/EUVI} 	and \textit{COR}, \textit{YOHKOH/SXT}, 
+	\textit{RHESSI}, \textit{PROBA2/SWAP} and\textit{HINODE/XRT}.
+	As well as providing the base classes the map submodule provides two 
+	collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
+	temporally and spatially aligned data respectively. \texttt{MapCube} 
+	provides methods for animation of its series of \texttt{Map} objects. 
+	\texttt{CompositeMap} provides methods for overlaying spatially aligned 
+	data, with support for visualisation of images and contour lines overlaid 
+	upon each other.

### 2014-01-13 Sunpy_paper_0.4.tex
Split tex file into parts @ehsteve You can do util ;)

--- 2014-01-08 Sunpy_paper_0.4.tex
@@
 
-\section{Introduction}
+\input{1-Introduction}
 
-\section{Core Data Types}
+\input{2-Data_Types}
 
-	\subsection{Map}
+\input{3-Retrieval}
 
-	\subsection{Lightcurve}
+\input{4-Util}
 
-	\subsection{Spectra}
+\input{5-Dev}
 
-\section{Solar Data Retrieval}
-
-	\subsection{VSO}
-
-	\subsection{HEK}
-
-	\subsection{HELIO}
-
-\section{Visualisation}
-
-\section{Coordinates}
-
-\section{Development and Community}
-
-\section{Future of SunPy}
+\input{6-Future}
 

### 2014-01-14 2-1-Map.tex
Add some examples to the Map section.
This uses minted, see readme.

@@
 \textit{RHESSI}, \textit{PROBA2/SWAP} and\textit{HINODE/XRT}.
+
+\begin{listing}
+\begin{minted}{python}
+
+import sunpy.map
+
+aiamap = sunpy.map.Map('aia_file.fits')
+aia.peek()
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{aia_map_example}
+\caption{Demonstration of the \textit{AIA} map quick view plotting method.}
+\label{code:aia_1}
+\end{listing}
+
+\begin{listing}
+\begin{minted}{pycon}
+
+>>> import sunpy.map
+
+>>> aiamap = sunpy.map.Map('aia_file.fits')
+>>> aia
+SunPy AIAMap
+---------
+Observatory: SDO
+Instrument:  AIA_3
+Detector:    AIA
+Measurement: 171
+Obs Date:    2011-03-19T10:54:00.34
+dt:          1.999601
+Dimension:   [1024, 1024]
+[dx, dy] =   [2.400000, 2.400000]
+
+array([[ 0.3125, -0.0625, -0.125 , ...,  0.625 , -0.625 ,  0.    ],
+       [ 1.    ,  0.1875, -0.8125, ...,  0.625 , -0.625 ,  0.    ],
+       [-1.1875,  0.375 , -0.5   , ..., -0.125 , -0.625 , -1.1875],
+       ..., 
+       [-0.625 ,  0.0625, -0.3125, ...,  0.125 ,  0.125 ,  0.125 ],
+       [ 0.5625,  0.0625,  0.5625, ..., -0.0625, -0.0625,  0.    ],
+       [ 0.5   , -0.125 ,  0.4375, ...,  0.6875,  0.6875,  0.6875]])
+
+\end{minted}
+\caption{Example of printing information about a map at a Python interactive 
+prompt.}
+\label{code:aia_2}
+\end{listing}
+
+As can been seen in Listing \ref{code:aia_1} \& \ref{code:aia_2} the map 
+datatype parses header information for many purposes including visualisation on 
+correct physical axes and limb plotting as well as making this information 
+easily available to the user.
+
 As well as providing the base classes the map submodule provides two 

### 2014-01-16 2-2-Lightcurve.tex
adding to first draft of Lightcurve section

\subsection{Lightcurve}

Time series data and analyses are a fundamental aspect of solar physics for which many data sources are available. In recognition of this fact, SunPy provides a \textit{Lightcurve} object designed to provide a convenient and consistent interface for handling solar time series data. The main engine behind the \textit{Lightcurve} object is the \textit{pandas} data analysis library. This library contains a large amount of functionality for manipulating and analysing time series data, making it an ideal basis for \textit{Lightcurve}.  Like all other SunPy objects, \textit{Lightcurve} is a wrapper around a data object, which in this case is the \textit{pandas} object.

Currently, the \textit{Lightcurve} object is compatible with the following data sources; the GOES X-ray Sensor (XRS), the SDO EUV Variability Experiment (EVE), and PROBA2/LYRA. For each of these instruments, a sub-class of the \textit{Lightcurve} object is initialized (e.g. \textit{GOESLightCurve, LYRALightCurve}) which inherits from \textit{Lightcurve} but allows instrument-specific functionality to be included. Future developments will introduce support for additional instruments and data products. 
Since time series data is generally relatively small and there is no established standard as to how it should be stored and distributed, each SunPy \textit{Lightcurve} object provides the ability to download its own data in its constructor.

A \textit{Lightcurve} object may be created using a range of different methods. Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see example below). In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object.

\begin{lstlisting}[language=Python]
from sunpy import lightcurve
goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
`2011-06-07 08:00')
goes.peek()

\end{lstlisting}

Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see example below).

\begin{lstlisting}[language=Python]
from sunpy import lightcurve
file=`lyra_20110607-000000_lev2_std.fits'
lyra=lightcurve.LYRALightCurve.create(file)
lyra.peek()

\end{lstlisting}

### 2014-01-17 4-Util.tex
hacking at utilities section

@@
 \section{Utilities}
+SunPy is meant to provide a consistent environment for solar data analysis. In order to
+achieve this goal SunPy provides a number of utility functions which are used by the other
+SunPy modules and are made available to the user. Two modules are described in this Section, 
+namely, solar coordinates (coords), and the Sun module (sun).
 
 \subsection{Coordinates}
+Coordinate transformations are frequently a necessary task within the solar data analysis
+workflow. Likely the most often used transformation is from observer coordinates (e.g. 
+sky coordinates) to a coordinate system which is mapped onto the solar surface (e.g.
+latitude and longitude). This transformation is necessary to compare the true physical
+distance between different solar features. This type of transformation is not unique
+to solar observations (e.g. planetary) but it is not provided by Astropy coordinates 
+package.
 
-	\subsection{Constants}
+\subsubsection{Sun}
+The purpose of this module is to provide solar-specific data
 
-	\subsection{Sun}
-
-	\subsection{General}
+\subsubsection{constants}
+The purpose of the constants package is to provide a number of solar-related constants 
+in order to provide consistency in the calculations of derived solar values both within the
+SunPy code base but also to the user. Every solar constants is provided as a Constant objects as defined by Astropy. 
+Each Constant object defines a Quantity, a number associated with a unit, along with the constant's provenance
+(i.e. reference) as well as its uncertainty. Using Astropy's Quantities, any solar constant
+can easily be converted between different units as can be seen in Figure~\ref{fig:constants_code} as well
+as between SI or cgs with a single command.  As these objects inherit from Numpy's ndarray,
+they work well with standard representations of numbers.
+For convenience a number shortcuts to frequently used constants are provided directly when importing
+the module. A larger list of constants can be accessed through an interface modelled 
+on that provided by the SciPy constants package. To view all of the available constants
+a print_all() function can be used.

### 2014-01-19 2-Data_Types.tex
changes and images

@@
 \input{2-3-Spectra}
+
+\subsection{Visualisation}
+As has been demonstrated in this section, the core SunPy datatypes include 
+visualisation code that is specialised to that data type. These visualisation 
+methods all currently utilise the matplotlib package, and are designed in such 
+a way that they integrate well with the pyplot functional interface of 
+matplotlib, as demonstrated in Listing \ref{code:mpl_1}.
+
+\begin{listing}[h]
+\begin{minipage}{0.49\columnwidth}
+\begin{minted}{python}
+import sunpy.map
+import matplotlib.pyplot as plt
+
+#Read in a aia file using SunPy
+aiamap = sunpy.map.Map('aia.fits')
+
+#Create the figure and axis 
+#explicitly
+fig = plt.figure()
+ax = plt.subplot()
+
+#Create a image plot with raw data
+im = ax.imshow(aiamap.data,...)
+#add a colour bar
+plt.colorbar(im,ax=ax)
+
+#Add a title
+plt.title("My AIA plot")
+plt.show()
+\end{minted}
+\end{minipage}
+\begin{minipage}{0.49\columnwidth}
+\begin{minted}{python}
+import sunpy.map
+import matplotlib.pyplot as plt
+
+#Read in a aia file using SunPy
+aiamap = sunpy.map.Map('aia.fits')
+
+#Create the figure and axis 
+#explicitly
+fig = plt.figure()
+ax = plt.subplot()
+
+#Plot the AIA map
+im = aiamap.plot(axes=ax)
+#add a colour bar
+plt.colorbar(im,ax=ax)
+
+#Add a title
+plt.title("My AIA plot")
+plt.show()
+\end{minted}
+\end{minipage}
+\caption{A simple example of how SunPy's plotting functions provide similar 
+behaviour to matplotlib's pyplot interface.}
+\label{code:mpl_1}
+\end{listing}
+
+This design philosophy makes the behaviour of SunPy's visualisation routines 
+intuitive to those who already understand how matplotlib's interface is 
+designed as well as allowing the use of the standard matplotlib commands to 
+change the plot, \textit{e.g.} set the title.

### 2014-01-19 2-1-Map.tex

@@
 
-\begin{listing}
-\begin{minted}{python}
-
-import sunpy.map
-
-aiamap = sunpy.map.Map('aia_file.fits')
-aia.peek()
-\end{minted}
-\includegraphics[width=0.8\columnwidth]{aia_map_example}
-\caption{Demonstration of the \textit{AIA} map quick view plotting method.}
-\label{code:aia_1}
-\end{listing}
-
-\begin{listing}
+\begin{listing}[h]
 \begin{minted}{pycon}
@@
 
+\begin{listing}[h]
+\begin{minted}{python}
+
+import sunpy.map
+
+aiamap = sunpy.map.Map('aia_file.fits')
+aia.peek()
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{aia_map_example}
+\caption{Demonstration of the \textit{AIA} map quick view plotting method.}
+\label{code:aia_1}
+\end{listing}
+
 As can been seen in Listing \ref{code:aia_1} \& \ref{code:aia_2} the map 
@@
 upon each other.
+
+\begin{listing}[h]
+\begin{minted}{python}
+import matplotlib.pyplot as plt
+import sunpy.map
+
+#Create a composite map from two files
+compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
+composite=True)
+
+#Set the RHESSI image (index 1) to have contour levels and a red colour map.
+compmap.set_levels(1,range(0,50,5),percent=True)
+compmap.set_colors(1,'Reds_r')
+
+#Plot the result and crop
+ax = plt.subplot()
+compmap.plot()
+ax.axis([200,600,-600,-200])
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{comp_map_example}
+\caption{Example demonstrating a CompositeMap plot, using contours and how 
+SunPy integrates with matplotlib's pyplot functional interface.}
+\label{code:compmap_1}
+\end{listing}
+
+\begin{listing}[h]
+\begin{minted}{python}
+import sunpy.map
+
+compmap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+compmap.peek()
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
+\caption{An example showing creation of a MapCube from a glob file search. The 
+resultant plot makes use of matplotlib's interactive widgets to allow scrolling 
+through the MapCube.}
+\label{code:mapcube_1}
+\end{listing}
+
+\begin{listing}[h]
+\begin{minted}{python}
+import sunpy.map
+from matplotlib import animation
+
+mapc = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+anim = mapc.plot()
+Writer = animation.writers['ffmpeg']
+writer = Writer(fps=10, metadata=dict(artist='SunPy'), bitrate=1800)
+anim.save('aia_cube.ogv')
+\end{minted}
+\caption{Example showing how to save a video animation from a MapCube, using 
+matplotlib's animation framework.}
+\label{code:mapcube_2}
+\end{listing}

### 2014-01-19 1-Introduction.tex
big expansion of intro text

@@
 \section{Introduction}
-SunPy is a project dedicated to providing the tools to process and analyse 
-solar data in Python.
-The Python programming language has gained much traction as a scientific 
-programming language in the last decade.
-Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
-the core tools needed for scientific analsysis and visualisation, while other 
-packages such as pandas, Astropy or scikit-image provide more domain specific 
-functionality. SunPy aims to provide such domain specific functionality to the 
-solar physics community.
+Modern solar physics, similar to astrophysics, requires increasingly complex software 
+tools both for the retrieval as well as the analysis of data. The Sun is the most well-observed 
+star. As such, solar physics is unique in its ability to access large amounts of high 
+resolution ground- and space-based observations of the Sun at many different wavelengths 
+and spatial scales with high time cadence. Modern solar physics, similar to astrophysics, 
+therefore requires increasingly complex software tools, both for the retrieval and the 
+analysis of data. For example, NASA's Solar Dynamics Observatory (SDO) satellite records 
+over 1 TB of data per day all of which is telemetered to the ground and available for 
+analysis. As a result, scientists have to process large volumes of complex data products. 
+In order to make meaningful advances in solar physics, it is important for the software 
+tools to be standardized, easy to use, and transparent, so that the community can build 
+upon a common foundation.
 
-The goal of SunPy is to provide a clean, simple to use and well structured 
+Currently, most solar data analysis is performed with a large library of routines called 
+SolarSoft [SSW]. SolarSoft is a set of integrated software libraries, databases, and 
+system utilities which provide a common programming and data analysis environment for
+solar physics. It is overwhelmingly an environment which relies upon IDL (Interactive Data Language),
+a commercial and closed-source interactive data analysis environment sold by 
+Exelis a global aerospace, defense, information and services company. The SSW gen package
+provides the base analysis capabilities such as time series analysis, time conversions,
+spectral fitting, image display, and file I/O. It is composed of 89\% IDL code while the remainder
+is mostly perl (5.4\%) and csh scripts (3.8\%). According to data generated using 
+David A. Wheeler's 'SLOCCount', SSW/gen is composed of 289,724 lines of code with a total approximate
+value of \$10.4M (based on the Basic COCOMO model). 
+Individual missions and instruments provide additional optional packages. For example, 
+the SDO package is 100\% IDL code and is 11k lines of code (\$360k) and the SOHO package is
+100k lines of code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
+Lockheed Martin Solar and Astrophysics Laboratory.
+
+%The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
+
+While SSW is open-source and freely available, the IDL core is not. In addition, the development
+of SolarSoft is neither open nor transparent to the public. Also IDL is fairly limited in 
+its ability to interact with other languages. One of SunPy's key aims is to 
+provide a free and modern alternative to the SolarSoft (gen) library. This is made possible
+by the recent rise of the scientific Python community. Python is general purpose 
+high-level programming language. It is free to use, cross-platform, and has a strong
+emphasis on readability a concept which is well-aligned with the scientific endeavor.
+Python has a very large user community which extends far outside of the solar physics
+or astronomy communities. It is very extensible with C, C++, Fortran or even IDL. It is 
+easy to learn. Many books and on-line documentation is available. For example at the time
+of this writing a search on Amazon for books on IDL programming generated 189 results while a search
+for Python yielded 1,788 results. Additionally, students may already have learned Python during their 
+undergraduate which means that research projects can begin quickly without the need for 
+the student to learn a new (and relatively niche) language. Finally, knowledge of Python is a skill which is useful
+and well compensated outside of the scientific community (average salary of \$110k in Washington DC area according
+to indeed.com at the time of writing). Finally, the astronomy community has begun to
+move away from IDL to Python. For all of these reasons, Python is an ideal platform for
+the generation of solar physics data analysis environment.
+
+SunPy is built on top of the core scientific Python packages namely \texttt{NumPy}, \texttt{SciPy}, 
+\texttt{matplotlib}, and \texttt{Pandas}. As of the release 0.4, SunPy is also leveraging the 
+newly release \texttt{Astropy} package (0.3). Leveraging all of these packages has allowed 
+the development of SunPy to provide many capabilities without very much effort. The design
+philosophy of SunPy is to provide a clean, simple to use and well structured 
 package that provides the \textit{core} tools for solar physics.
-The primary focus of SunPy's development is current providing specialised, 
+The primary focus of SunPy's development early development is to providing specialised, 
 linked, datatypes that allow the import, processing and visualisation of solar 
@@
 
-In this paper we will provide an overview of the current functionality of the 
-\texttt{sunpy} library as well as giving details on the development model and 
-community aspects of the SunPy project.
+The purpose of this paper is to provide an overview of SunPy's current capabilities, an 
+overview of the development model and community aspects of the SunPy project
+as well as future plans. The latest release of SunPy is available in 
+PyPI and can be installed in the usual manner.

### 2014-01-19 4-Util.tex
big expansion of intro text

@@
 distance between different solar features. This type of transformation is not unique
-to solar observations (e.g. planetary) but it is not provided by Astropy coordinates 
-package.
+to solar observations (e.g. planetary) but it is not provided by the Astropy coordinates 
+package. The coordinates package implements the World Coordinate System (WCS) for solar
+coordinates as described by \cite{Thompson2000}. The coordinate system transformations
+currently implemented as those most useful for most solar data analysis, namely 
+converting from Helioprojective-Cartesian (HPC) to Heliographic coordinates (HG). HPC 
+which describes the positions on the Sun as angles measured from the center of the solar 
+disk (usually in arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
+most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). HG
+coordinates express positions on the Sun using longitude and latitude on the solar 
+sphere. There are two standards for this coordinate system, Stonyhurst-Heliographic 
+where the origin is at the intersection of the solar equator and 
+the central meridian as seen from Earth and Carrington-Heliographic is a system which is
+fixed to the Sun and does not depend on Earth. The implementation of these transformations
+pass through common coordinate system called Heliocentric-Cartesian (HCC) where positions 
+are expressed in true (deprojected) physical distances instead of angles on the celestial sphere.
+These transformations require some knowledge of the location of the observer which is
+usually provided by the image header information. In case where it is not, the observer
+is assumed to be at Earth.
 

### 2014-01-19 3-5-Database.tex
added first draft of database section

\subsection{The SunPy Database}
% TODO: reference / footnote to Summer of Code website?
The database package has been added as a Google Summer of Code (GSoC) project
in 2013. Its purpose is to offer a database interface to store and manage data
that has been retrieved via packages from the net package. Note that currently
only the VSO package is supported, not the HEK package.

The need for a database package arose because using VSO alone lead to two major
problems:
\begin{enumerate}
  \item downloaded data cannot be queried or browsed
  \item to fetch data that has already been saved on the local hard drive,
    the VSO has to be queried again
\end{enumerate}

Here is a list of the main features:
\begin{itemize}
  \item detects if certain query has already been used before and queries
    the database then instead of the VSO
  % TODO: reference to SA docs? or list all currently supported SQL dialects here?
  \item many supported SQL dialects
  % TODO: footnotes for LRU/LFU or some explanation in parens behind them?
  \item database may act as a Cache (algorithm may be LRU, LFU or a custom one)
  \item all writing operations can be undone and redone
\end{itemize}

Using the database package, one uses the Database class to connect with a
database and perform operations on it.

\begin{listing}
\begin{minted}{python}
>>> from sunpy.net import vso
>>> from sunpy.database import Database
>>> database = Database('sqlite:///')
>>> database.download(
...     vso.attrs.Time((2011, 9, 20, 1), (2011, 9, 20, 2)),
...     vso.attrs.Instrument('RHESSI'))
>>> len(database)
6
\end{minted}
\caption{Connecting to a database and adding new entries.}
\label{code:db_1}
\end{listing}

In the code listing \ref{code:db_1}, a connection to new SQLite in-memory
database is established. After that, the attributes from the \textsc{VSO}
package are used to query the \textsc{VSO} and download the corresponding
files. The function \texttt{len} can be used to get the number of all database
records.

Note that the number of new database entries does not depend on the
number of files being downloaded but on the total number of \textsc{FITS}
headers in the files! If the used query had been used to query the \textsc{VSO}
directly, the number of query results would have been 2. You can see in the
following code example, listing \ref{code:db_2}, that indeed the entries can
be grouped to two results.

The function \texttt{display\_entries} displays an iterable of database entries
in a nicely-formatted \textsc{ASCII} table. The headlines correspond to the
attributes of the respective database entries.

\begin{listing}
\begin{minted}{python}
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
id observation_time_start wavemin        wavemax           download_time             
-- ---------------------- -------        -------           -------------             
1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525397
2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525469
3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525532
4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429665
5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429731
6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429792
\end{minted}
\caption{Displaying database entries in a table.}
\label{code:db_2}
\end{listing}

As said before, the database can be used as a cache. By default, the size of
the cache is not limited which in other words means that caching is disabled.
To limit the number of database entries to a certain number a posteriori, use
the method \texttt{set\_cache\_size} and pass it the number of maximum entries.
The default algorithm to remove entries from the cache is \textsc{LRU}
(least recently used), i.e. the item whose usage is farthest away is removed
first.  % FIXME is 'whose' correct here? ^

\begin{listing}
\begin{minted}{python}
>>> database.set_cache_size(3)
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
id observation_time_start wavemin        wavemax           download_time             
-- ---------------------- -------        -------           -------------             
4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429665
5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429731
6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429792
\end{minted}
\caption{Displaying database entries in a table.}
\label{code:db_3}
\end{listing}

In code listing \ref{code:db_3} the entries with the IDs \#1 -- \#3 have been
removed because they have been added first and are therefore the entries that
have been used least recently. To undo this operation, the \texttt{undo} method
is used in code listing \ref{code:db_4} to add the 3 removed entries back to
the database. The \texttt{redo} method removes them again.

\begin{listing}
\begin{minted}{python}
>>> database.undo()
>>> len(database)
6
>>> database.redo()
>>> len(database)
3
\end{minted}
\caption{Undoing and redoing operations.}
\label{code:db_4}
\end{listing}

% TODO: 'clever fetching'

### 2014-01-20 4-Util.tex
work on sun module

--- 2014-01-17 4-Util.tex
@@
 distance between different solar features. This type of transformation is not unique
-to solar observations (e.g. planetary) but it is not provided by Astropy coordinates 
-package.
+to solar observations (e.g. planetary) but it is not provided by the Astropy coordinates 
+package. SunPy implements the World Coordinate System (WCS) for solar
+coordinates as described by \cite{Thompson2000}. The coordinate system transformations
+currently implemented as those most useful for most solar data analysis, namely 
+converting from Helioprojective-Cartesian (HPC) to Heliographic coordinates (HG). HPC 
+which describes the positions on the Sun as angles measured from the center of the solar 
+disk (usually in arcseconds) using cartesian coordinates (X, Y). These are the coordinates 
+most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). HG
+coordinates express positions on the Sun using longitude and latitude on the solar 
+sphere. There are two standards for this coordinate system, Stonyhurst-Heliographic 
+where the origin is at the intersection of the solar equator and 
+the central meridian as seen from Earth. Carrington-Heliographic is a system which is
+fixed to the Sun and does not depend on Earth. The implementation of these transformations
+pass through a common coordinate system called Heliocentric-Cartesian (HCC) where positions 
+are expressed in true (deprojected) physical distances instead of angles on the celestial sphere.
+These transformations require some knowledge of the location of the observer which is
+usually provided by the image header information. In cases where it is not, the observer
+is assumed to be at Earth. The current implementation is function-based and is used mostly
+by the SunPy map object. A refactor to a more object-oriented API is planned for a future
+release of SunPy.
 
 \subsubsection{Sun}
-The purpose of this module is to provide solar-specific data
+The purpose of this module is to provide solar-specific data for example ephemeris and
+solar constants. The main namespace contains a number of functions which provide solar
+ephemeris such as sun to earth distance, solar cycle number, the mean anomaly, etc.
+All of these functions take a time as their input which can be provided in any parse_time
+compatible format. A future version of SunPy will integrate with the AstroPy coordinates package.
 
@@
 For convenience a number shortcuts to frequently used constants are provided directly when importing
-the module. A larger list of constants can be accessed through an interface modelled 
-on that provided by the SciPy constants package. To view all of the available constants
-a print_all() function can be used.
+the sub-package. A larger list of constants can be accessed through an interface modelled 
+on that provided by the SciPy constants package and are available as a dictionary called
+physical_constants. To view all quickly a print_all() function is available.
+
+\begin{listing}[h]
+\begin{minted}{pycon}
+
+>>> from sunpy.sun import constants as sun
+>>> print(sun.mass)
+  Name   = Solar mass
+  Value  = 1.9891e+30
+  Error  = 5e+25
+  Units  = kg
+  Reference = Allen's Astrophysical Quantities 4th Ed.
+Verify the average density of the Sun and convert to cgs
+>>> (sun.mass/sun.volume).cgs
+<Quantity 1.40851154227 g / (cm3)>
+Check to see if the age of the Sun is available and grab the unit and value separately
+>>> sun.find('age')
+['age', 'average angular size', 'average density', 'average intensity']
+>>> sun.value('age'), sun.unit('age')
+
+\end{minted}
+\caption{Using sunpy.sun.constants sub-package.}
+\label{code:constants_code}
+\end{listing}

### 2014-01-20 3-4-Helioviewer.tex
first edits for Helioviewer

\subsection{Helioviewer}

SunPy provides the ability to download images from Helioviewer Project
servers.  The aim of the Helioviewer Project is to enable the
exploration of solar and heliospheric data from multiple data sources
(such as instrumentation and feature/event catalogs) via easy-to-use
visual interfaces.  The primary data provided by the Helioviewer
Project are images in the JPEG2000 format (for further details on the
Helioviewer Project see \cite{}\footnote{SunPy is used in Helioviewer
  production servers to manage the download and ingestion of JPEG2000
  files from remote servers.}.)

In

Suppose we next want to download a PNG image of the latest AIA 304
image available on Helioviewer.org. We could use the explicit
approach:

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
\end{minted}
\caption{Acquisition of the latest AIA 304\AA\ image available at www.helioviewer.org.}
\label{code:downloadlatestpng}
\end{listing}

Where 4.8 refers to the image resolution in arcseconds per pixel
(larger values mean lower resolution), the “1” and “100” in the layer
string refer to the visibility (visible/hidden) and opacity, x0 and y0
are the center points about which to focus and the width and height
are the pixel values for the image dimensions.

The result is:

The filename of the returned file has the date and time of the
requested time, which is not the time of the observation shown in the
PNG image.  This is because of the Helioviewer API.  The API request
finds images closest to the requested time. But since the user may ask
for images from multiple sources, and each of them may have a
different observation time, it is unclear which time is the most
appropriate to associate with the resultant image.  The Helioviewer
API does not select between any of the image observation times, but
instead returns an image filename based on the request time, resulting
in predictable filenames.

The Helioviewer API allows composition and overlay of images from
multiple sources, based on the positioning metadata in the source FITS
file. This ability takes advantage of the fact that the JPEG2000 file
format contains an arbitrary XML box that can be used to store image
metadata.  Helioviewer Project JPEG2000 file metadata are based (in
part) on the original FITS header information, and carry sufficient
metadata to permit overlay with other Helioviewer JPEG2000 files.

SunPy accesses this overlay/composition capability through the
\texttt{download_png} method of the Helioviewer client.

This functionality makes it simple for SunPy users to generate complex
images from multiple, correctly overlaid, image datasources.

To read a JPEG2000 file into a SunPy session requires installing two
other pieces of software. The first, \texttt{OpenJPEG}, is an open
source library for reading and writing JPEG2000 files
(http://www.openjpeg.org).  The other package required is
\texttt{glymur}, (https://github.com/quintusdias/glymur), an interface
between Python and the OpenJPEG libraries (note that these packages
are {\it not} required to use the functionality described above).

Example \ref{code:downloadjp2} demonstrates the querying, reading and
conversion of a Helioviewer JPEG2000 file into a SunPy Map object.
This functionality allows users to visualize and manipulate
Helioviewer-supplied image data in an identical fashion to a SunPy map
object generated from FITS data (see Section \ref{{}).

\begin{listing}
\begin{minted}{python}
filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO', instrument='HMI', detector='HMI', measurement='continuum')
from sunpy.map import Map
hmi = Map(filepath)
hmi.submap([200,550],[-400,-200]).peek()
\end{minted}
\caption{Acquisition and display of a Helioviewer JPEG2000 file.}
\label{code:downloadjp2}
\end{listing}

### 2014-01-20 2-3-Spectra.tex
Introduction to spectra

\subsection{Spectra}\label{sec:spectra}

Spectroscopy consists in the study of the radiative energy related to the its wavelength.
An spectrum is normally obtained by observing a range of frequencies at the same time; 
this can be done either for example in radio wavelengths by swiping over different frequencies - e.g., with radio receiver - 
or in visible and ultraviolet by the dispersion of the incident light through a diffraction grating or prism.
By analysing the resultant spectrum properties such temperature, density, speed and other kinematics can be obtained. Therefore, spectroscopy provides to the solar physicists invaluable information about the composition and the physical properties of the Sun.

Sunpy intents to provide support to most of solar spectroscopy instrument, however the complexity of this kind of datasets makes very challenging to add support to them all in a general way.  
Nevertheless, the design of the \textit{Spectra} object is consistent with the other data types available in Sunpy.
As yet, Sunpy offers a \textit{Spectrogram} object that supports radio spectra from the e-Callisto 
network\footnote{e-Callisto is an international network of solar radio spectrometers, all the data is available at: \url{http://www.e-callisto.org/} } 
and STEREO/SWAVES spectrograms.
These radio spectrograms are consecutive 1D frequency spectra measured over time.  
However, the study of this type of spectrograms is normally driven by the variation of the spectra through time, therefore the data files normally contains a 2D array, with one axis for frequency and another for time, providing an image as the one shown in figure \ref{spectrogram:example}.
The Spectrogram object offers some common functionality to both type of instruments to help its analysis, this includes:
read the data (fits format for e-Callisto, ASCII for STEREO/SWAVES); 
join different time ranges and frequencies; 
frequency dependent background subtraction;  
linearise of frequency axis and automated downsample for proper visualisation on a normal computer screen;  
and point-and-click functionality to save pixels of interest for further analysis.
In addition, this object is equipped with a download data interface for e-Callisto that only requires the observatory name and the desired time-range. STEREO/SWAVES can be obtained via the virtual solar observatory (see \s\ref{sec:vso}).

% Download Callisto
% Merge multiple time-ranges / frequencies (just work from downlad!)
% Merge callisto with swaves

### 2014-01-20 3-4-Helioviewer.tex
added in EPS images for helioviewer section

@@
-\subsection{Helioviewer}
+\subsection{Helioviewer}\label{ssec:hv}
 
@@
 \end{minted}
-\caption{Acquisition of the latest AIA 304\AA\ image available at www.helioviewer.org.}
+\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
+\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image available at
+  www.helioviewer.org.}
 \label{code:downloadlatestpng}
@@
 are the pixel values for the image dimensions.
-
-The result is:
 
@@
 
+\begin{listing}
+\begin{minted}{python}
+hv.download_png('2099/01/01', 6, "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
+\caption{Acquisition of a PNG image composed from data from three
+  separate sources.}
+\label{code:downloadjp2}
+\end{listing}
+
 This functionality makes it simple for SunPy users to generate complex
@@
 
-Example \ref{code:downloadjp2} demonstrates the querying, reading and
+Listing \ref{code:downloadjp2} demonstrates the querying, reading and
 conversion of a Helioviewer JPEG2000 file into a SunPy Map object.
@@
 Helioviewer-supplied image data in an identical fashion to a SunPy map
-object generated from FITS data (see Section \ref{{}).
+object generated from FITS data (see Section \ref{sec:maps}).
 
@@
 \end{minted}
-\caption{Acquisition and display of a Helioviewer JPEG2000 file.}
+\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map.eps}
+\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
+  SunPy map object.}
 \label{code:downloadjp2}

### 2014-01-20 2-2-Lightcurve.tex

@@
 \subsection{Lightcurve}
+\lstset{frame=single}
 
@@
 
+\subsubsection{Creating and using Lightcurves}
+
 A \textit{Lightcurve} object may be created using a range of different methods.
-Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see example below).
-In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object.
+Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see Listing \ref{goes_lc_code} below).
+In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object (see also Figure \ref{goes_lc}).
 
-\begin{lstlisting}[language=Python]
-from sunpy import lightcurve
-goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
+\begin{lstlisting}[language=Python,caption = Creating a GOES lightcurve using a time range.,label=goes_lc_code]
+>>> from sunpy import lightcurve
+>>> goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
 `2011-06-07 08:00')
-goes.peek()
+>>> goes.peek()
 
@@
 
-Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see example below).
+\begin{figure}
+\begin{center}
+\includegraphics[width=14cm]{goes_lightcurve.pdf}
+\caption{GOES lightcurve for the time interval 06:00 - 08:00 UT on 2011 June 7, plotted with the default parameters using the peek command (see Listing 1).}
+\label{goes_lc}
+\end{center}
+\end{figure}
 
-\begin{lstlisting}[language=Python]
-from sunpy import lightcurve
-file=`lyra_20110607-000000_lev2_std.fits'
-lyra=lightcurve.LYRALightCurve.create(file)
-lyra.peek()
+Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see Listing \ref{lyra_lc_code} below and Figure \ref{lyra_lc}).
+
+\begin{lstlisting}[language=Python, caption = Creating a LYRA lightcurve using an existing data file.,label=lyra_lc_code]
+>>> from sunpy import lightcurve
+>>> file=`lyra_20110607-000000_lev2_std.fits'
+>>> lyra=lightcurve.LYRALightCurve.create(file)
+>>> lyra.peek()
 
 \end{lstlisting}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=14cm]{lyra_lightcurve.pdf}
+\caption{LYRA lightcurve for the full day of 2011 June 7, plotted with the default parameters using the peek command (see Listing 2).}
+\label{lyra_lc}
+\end{center}
+\end{figure}
+
+Once the \textit{Lightcurve} has been created it may be manipulated in a variety of ways in order to perform time series analysis.
+Continuing from the above, we show a few simple examples of using a LYRA lightcurve.
+
+In the above case (Listing \ref{lyra_lc_code}), we created a LYRA Lightcurve spanning the full day of 2011 June 7.
+To extract the sub-interval 06:00 - 07:00 UT into a new \textit{Lightcurve} called \verb|lyra_zoom| we simply do the following:
+
+\begin{lstlisting}[language=Python, ,caption = Extracting a sub-interval from a Lightcurve., label=lyra_truncate]
+>>> from sunpy.time import TimeRange
+>>> tran=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+>>> lyra_zoom = lyra.truncate(tran)
+
+\end{lstlisting}
+
+Also in the example shown in Listing \ref{lyra_lc_code}, direct access to the data and time information in the object is available through \verb|lyra.data| and \verb|lyra.data.index| respectively.
+
+\begin{lstlisting}[language=Python, caption = Accessing the data and time axis in a Lightcurve]
+>>> print lyra.data
+<class 'pandas.core.frame.DataFrame'>
+DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
+2011-01-28 23:59:59.983993
+Data columns (total 4 columns):
+CHANNEL1    1496629  non-null values
+CHANNEL2    1496629  non-null values
+CHANNEL3    1496629  non-null values
+CHANNEL4    1496629  non-null values
+dtypes: float64(4)
+
+>>> print lyra.data.index
+<class 'pandas.tseries.index.DatetimeIndex'>
+[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
+Length: 1496629, Freq: None, Timezone: None
+\end{lstlisting}

### 2014-01-20 1-Introduction.tex
First draft for Dev and Future as well lc tweaks.
Changed to minted typesetting for code examples in lc section.

--- 2014-01-13 1-Introduction.tex
@@
 Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
-the core tools needed for scientific analsysis and visualisation, while other 
+the core tools needed for scientific analysis and visualisation, while other 
 packages such as pandas, Astropy or scikit-image provide more domain specific 

### 2014-01-20 5-Dev.tex
First draft for Dev and Future as well lc tweaks.
Changed to minted typesetting for code examples in lc section.

\section{Development and Community}
SunPy is a community developed library, it is designed and developed for and by 
the solar physics community. Not only is all the source code publicly available 
online under the permissive 2-clause BSD licence 
\footnote{\url{http://opensource.org/licenses/BSD-2-Clause}}, the whole 
development 
process is also online and open for anyone to contribute to.
The primary media by which SunPy's development is facilitated is the online 
service GitHub \footnote{\url{http://github.com}} which makes use of the 
distributed 
version control software git. \footnote{\url{http://git-scm.com/}}

The development workflow that GitHub enables is simple and transparent. The 
primary source code repository \url{http://github.com/sunpy/sunpy} can be 
`forked' by anyone with a GitHub account who can then modify their fork as they 
wish. Upon completion of any modifications it is possible for a user to create 
a 'Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
repository where it can be reviewed by anyone and then accepted by one of the 
development team who have commit rights to the main SunPy repository.

Pull requests are a very powerful tool to maintain code quality, as each line 
of code that has been modified is highlighted for review. For code to be 
accepted into the SunPy repository three primary things have to have been 
completed:

\begin{enumerate}
	\item  The code has to follow 	
	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
	guidelines, this keeps all the code in SunPy (and 99\% of all other Python 
	code) styled in a consistent manner and easy to read.

	\item The code must be documented. SunPy's documentation is generated by 
	the Sphinx package, which is automatically run and hosted by 
	\url{http://readthedocs.org}.

	\item The code must contain full unit test coverage. SunPy code is well 
	tested and coverage is increasing all the time. All SunPy's tests are 
	automatically run for each `Pull Request' and branch by the 
	\href{http://travis-ci.org/sunpy/sunpy}{Travis-CI }	service, and a test 
	coverage record is kept by 
	\href{http://coveralls.io/r/sunpy/sunpy}{Coveralls}
\end{enumerate}

This kind of development model is widely used within the scientific Python 
community as well as buy a wide variety of other projects both open and closed 
source.

As well as having a open source and open development model SunPy has a active 
community, with lots of both on-topic and off-topic chat on the \#SunPy IRC 
channel on freenode.net and on the mailing lists. The project always welcomes 
new contributions of any scale.

Many of the larger features added to SunPy during it's life have been added 
with the aid of both ESA's Summer Of Code In Space (SOCIS) program and Google's 
Summer of Code (GSOC) program. Initial development of SunPy's VSO and HEK 
implementations were funded by the SOCIS program as well as a prototyped GUI 
and N-Dimensional datatype implementations. 2013 was the first year that SunPy 
obtained GSOC funding, through the Python Software Foundation (PSF). The two 
projects that were undertaken was the development of a HELIO package and a 
package for integration between the HEK and VSO, allowing the download of data 
from VSO relating to a HEK query. As well as the Database module, which 
provides a single query-able interface between local data and the VSO.

### 2014-01-20 6-Future.tex

\section{Future of SunPy}
SunPy as a project has existed for roughly three years. In this time the code 
base has grown to over $110,000$ lines. SunPy in it's current form is a useful 
package for the analysis of calibrated solar data, however, the code base is 
still very changeable from release to release.

The near-term future of the SunPy library is likely to continue this changeable 
nature with re-factoring and restructuring planned, especially within the 
core data types. The main focus upon the data types defined inside sunpy is to 
improve the interoperability and to redesign them in a more consistent manner.

In the past 12 months the collaboration with the Astropy project 
\cite{theastropycollaboration2013} has grown. The future of SunPy 
will continue this collaboration as the Astropy package provides many core 
tools that are applicable to all types of astronomy. For example the 
\texttt{astropy.units} submodule provides a simple and efficient way of 
representing physical units in Python data types, there are plans to 
incorporate this widely in the SunPy code-base.

### 2014-01-20 1-Introduction.tex

--- 2014-01-19 1-Introduction.tex
@@
 SunPy is built on top of the core scientific Python packages namely \texttt{NumPy}, \texttt{SciPy}, 
-\texttt{matplotlib}, and \texttt{Pandas}. As of the release 0.4, SunPy is also leveraging the 
+\texttt{matplotlib}, and \texttt{Pandas}. As of the release 0.4, SunPy is also using the 
 newly release \texttt{Astropy} package (0.3). Leveraging all of these packages has allowed 
-the development of SunPy to provide many capabilities without very much effort. The design
-philosophy of SunPy is to provide a clean, simple to use and well structured 
+the development of SunPy to provide many capabilities without much effort. The design
+philosophy of SunPy is to provide a clean, simple to use, and well structured 
 package that provides the \textit{core} tools for solar physics.

### 2014-01-20 3-3-HELIO.tex

\subsection{HELIO}\label{ssec:helio}

The HELiophysics Integrated Observatory (HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web services which allows the scientist to query them in order to discover data in the heliosphere (\eg, solar, planetary, inter-planetary data, \cdots)\citep{dps2012}. 
HELIO has been built with a Service-Oriented Architecture, 
\ie HELIO capabilities are split into a number of tasks that are implemented as separate services. 
HELIO counts with up to nine different public services, which allows to the scientist to look up in different catalogues of registered events, features on the sun and data from instruments in the heliosphere. 
Additionally, HELIO provides of a service that uses a propagation model to link the data in different points of the solar system by its original nature 
(\eg., Earth auroras are a signature of magnetic field disturbances produced few days before on the Sun).
The main interface to acccess to HELIO is through its front-end\footnote{
\url{http://hfe.helio-vo.eu}},
but since the system is based in webservices they can be accessed from many different tools.

The current version of Sunpy has implemented an interface to access the \textit{HELIO Event Catalogue} service.  
HELIO results are provided as VOTable format\footnote{\bf{info about votables IVOAA standard!}} 
which reader have been integrated within Astropy, this has an additional advantage of getting metadata with information as data provenance and the performed query.

%example on how to use it

%In the future, when the rest of services are implemented HELIO tools could interact with other services like database or data visualisation in a seemlessly way.

### 2014-01-20 3-4-Helioviewer.tex
added full bibtex reference for Helioviewer paper

@@
   production servers to manage the download and ingestion of JPEG2000
-  files from remote servers.}.)
+  files from remote servers.}.)  The JPEG2000 files are typically
+highly compressed compared to the source FITS files they are generated
+from, and so can be a used as a shortcut to visualize large amounts of
+data from multiple sources.
 
-In
+The Helioviewer Project categorizes image data based on the physical
+construction of the source instrument, using the following hierarchy:
+observatory $\rightarrow$ instrument $\rightarrow$ detector
+$\rightarrow$ measurement, where '$\rightarrow$' means 'provides
+(possibly multiple)'.  The full list of image data sources available
+can be found through the code snippet, Example
+\ref{code:hv:datasources}.
 
-Suppose we next want to download a PNG image of the latest AIA 304
-image available on Helioviewer.org. We could use the explicit
-approach:
+\begin{listing}
+\begin{minted}{python}
+from sunpy.net.helioviewer import HelioviewerClient
+
+hv = HelioviewerClient()
+datasources = hv.get_data_sources()
+
+# print a list of datasources and their associated ids
+for observatory, instruments in datasources.items():
+    for inst, detectors in instruments.items():
+        for det, measurements in detectors.items():
+            for meas, params in measurements.items():
+                print("%s %s: %d" % (observatory, params['nickname'], params['sourceId']))
+\caption{Initializing the Helioviewer client and listing the full
+  range of image data available.}
+\label{code:hv:datasources}
+\end{listing}
+
+Each Helioviewer Project JPEG2000 file contains metadata which are
+based (in part) on the original FITS header information, and carry
+sufficient information to permit overlay with other Helioviewer
+JPEG2000 files. Images can be accessed either as PNGs (Section
+\ref{sssec:hv:png} or as JPEG2000 files (Section \ref{sssec:hv:jp}).
+
+\subsubsection{Download a PNG file}\label{sssec:hv:png}
+
+Example \ref{code:hv:downloadlatestpng} demonstrates how to download a
+PNG image of the latest AIA 304\AA\ image available on
+Helioviewer.org.
 
@@
   www.helioviewer.org.}
-\label{code:downloadlatestpng}
+\label{code:hv:downloadlatestpng}
 \end{listing}
 
-Where 4.8 refers to the image resolution in arcseconds per pixel
-(larger values mean lower resolution), the “1” and “100” in the layer
-string refer to the visibility (visible/hidden) and opacity, x0 and y0
-are the center points about which to focus and the width and height
-are the pixel values for the image dimensions.
+The first argument is the requested time of the image.  Helioviewer
+selects images closest to the requested time.  In this case, the
+requested time is in the future and so Helioviewer will find the most
+recent available image.  The second argument refers to the image
+resolution in arcseconds per pixel (larger values mean lower
+resolution).  The third argument is a string detailing the requested
+observatory $\rightarrow$ instrument $\rightarrow$ detector
+$\rightarrow$ measurement combination.  The final two numbers in this
+string are the visibility and the opacity of the this image layer (1/0
+is visible/invisible with opacity in the range $0\rightarrow100$, with
+$100$ meaning fully opaque).  The quantities $x0$ and $y0$ are the $x$
+and $y$ center points about which to center the image (measured in
+helio-projective cartesian co-ordinates) and the \texttt{width} and
+\texttt{height} are the pixel values for the image dimensions.
 
-The filename of the returned file has the date and time of the
-requested time, which is not the time of the observation shown in the
-PNG image.  This is because of the Helioviewer API.  The API request
-finds images closest to the requested time. But since the user may ask
-for images from multiple sources, and each of them may have a
-different observation time, it is unclear which time is the most
-appropriate to associate with the resultant image.  The Helioviewer
-API does not select between any of the image observation times, but
-instead returns an image filename based on the request time, resulting
-in predictable filenames.
+It should be noted that the filename of the returned file has the date
+and time of the requested time, which is not the time of the
+observation shown in the PNG image.  This is because of the
+Helioviewer API.  The API request finds images closest to the
+requested time. But since the user may ask for images from multiple
+sources, and each of them may have a different observation time, it is
+unclear which time is the most appropriate to associate with the
+resultant image.  The Helioviewer API does not select between any of
+the image observation times, but instead returns an image filename
+based on the request time, resulting in predictable filenames.
 
@@
 multiple sources, based on the positioning metadata in the source FITS
-file. This ability takes advantage of the fact that the JPEG2000 file
-format contains an arbitrary XML box that can be used to store image
-metadata.  Helioviewer Project JPEG2000 file metadata are based (in
-part) on the original FITS header information, and carry sufficient
-metadata to permit overlay with other Helioviewer JPEG2000 files.
-
-SunPy accesses this overlay/composition capability through the
-\texttt{download_png} method of the Helioviewer client.
+file.  SunPy accesses this overlay/composition capability through the
+\texttt{download_png} method of the Helioviewer client.  Example
+\ref{code:hv:overlaid} gives an example of the composition of three
+separate images in to a single image.
 
@@
   separate sources.}
-\label{code:downloadjp2}
+\label{code:hv:overlaid}
 \end{listing}
 
+The principle difference between this code snippet and Example
+\ref{code:hv:downloadlatestpng} is in the layer string (the third
+argument).  The layer string has three separate comma separated
+entries detailing the data source, its visibility and its opacity.
 This functionality makes it simple for SunPy users to generate complex
-images from multiple, correctly overlaid, image datasources.
+images from multiple, correctly overlaid, image data sources.
 
-To read a JPEG2000 file into a SunPy session requires installing two
+\subsubsection{Download a JPEG2000 file}\label{sssec:hv:jp}
+
+As noted above, Helioviewer JPEG2000 files contain metadata that allow
+positioning of the image data.  There is sufficient metadata in each
+file to permit the creation of a SunPy map object (see Section
+\ref{ssec:maps}) from a Helioviewer JPEG2000 file.  This allows image
+data to be manipulated in the same way as any other map object.
+
+Reading JPEG2000 file into a SunPy session requires installing two
 other pieces of software. The first, \texttt{OpenJPEG}, is an open
@@
 between Python and the OpenJPEG libraries (note that these packages
-are {\it not} required to use the functionality described above).
+are {\it not} required to use the functionality described in Section
+\ref{sssec:hv:png}).
 
-Listing \ref{code:downloadjp2} demonstrates the querying, reading and
-conversion of a Helioviewer JPEG2000 file into a SunPy Map object.
-This functionality allows users to visualize and manipulate
+Listing \ref{code:downloadjp2} demonstrates the querying, downloading,
+reading and conversion of a Helioviewer JPEG2000 file into a SunPy Map
+object.  This functionality allows users to visualize and manipulate
 Helioviewer-supplied image data in an identical fashion to a SunPy map
@@
 \end{listing}
+
+%
+% Helioviewer article citation
+%
+%@article{Muller:2009:JVL:2220073.2220164,
+% author = {Muller, D. and Fleck, B. and Dimitoglou, G. and Caplins, B. W. and Amadigwe, D. E. and Ortiz, J. P.G. and Wamsler, B. and Alexanderian, A. and Hughitt, V. K. and Ireland, J.},
+% title = {JHelioviewer: Visualizing Large Sets of Solar Images Using JPEG 2000},
+% journal = {Computing in Science and Engg.},
+% issue_date = {September 2009},
+% volume = {11},
+% number = {5},
+% month = sep,
+% year = {2009},
+% issn = {1521-9615},
+% pages = {38--47},
+% numpages = {10},
+% url = {http://dx.doi.org/10.1109/MCSE.2009.142},
+% doi = {10.1109/MCSE.2009.142},
+% acmid = {2220164},
+% publisher = {IEEE Educational Activities Department},
+% address = {Piscataway, NJ, USA},
+% keywords = {data visualization},
+%}

### 2014-01-20 3-3-HELIO.tex
Fix merge related issues

@@
 
-The HELiophysics Integrated Observatory (HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web services which allows the scientist to query them in order to discover data in the heliosphere (\eg, solar, planetary, inter-planetary data, \cdots)\citep{dps2012}.
+The HELiophysics Integrated Observatory 
+(HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web 
+services which allows the scientist to query them in order to discover data in 
+the heliosphere (\textit{e.g.}, solar, planetary, inter-planetary data, 
+...)\cite{dps2012}. 
 HELIO has been built with a Service-Oriented Architecture, 
-\ie HELIO capabilities are split into a number of tasks that are implemented as separate services. 
+\textit{i.e.} HELIO capabilities are split into a number of tasks that are 
+implemented as separate services. 
 HELIO counts with up to nine different public services, which allows to the scientist to look up in different catalogues of registered events, features on the sun and data from instruments in the heliosphere.
 Additionally, HELIO provides of a service that uses a propagation model to link the data in different points of the solar system by its original nature 
-(\eg., Earth auroras are a signature of magnetic field disturbances produced few days before on the Sun).
+(\textit{e.g.}, Earth auroras are a signature of magnetic field disturbances 
+produced few days before on the Sun).
 The main interface to acccess to HELIO is through its front-end\footnote{

### 2014-01-20 3-4-Helioviewer.tex
Fix merge related issues

@@
             for meas, params in measurements.items():
-                print("%s %s: %d" % (observatory, params['nickname'], params['sourceId']))
+                print("%s %s: %d" % (observatory, params['nickname'], 
+                %%%%params['sourceId']))
+\end{minted}
 \caption{Initializing the Helioviewer client and listing the full
@@
 \includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
-\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image available at
-  www.helioviewer.org.}
+\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
+available at \url{www.helioviewer.org}.}
 \label{code:hv:downloadlatestpng}
@@
 file.  SunPy accesses this overlay/composition capability through the
-\texttt{download_png} method of the Helioviewer client.  Example
+\texttt{download\_png} method of the Helioviewer client.  Example
 \ref{code:hv:overlaid} gives an example of the composition of three

### 2014-01-20 4-Util.tex
Fix merge related issues

@@
 \section{Utilities}
-SunPy is meant to provide a consistent environment for solar data analysis. In order to
-achieve this goal SunPy provides a number of utility functions which are used by the other
-SunPy modules and are made available to the user. Two modules are described in this Section, 
-namely, solar coordinates (coords), and the Sun module (sun).
+SunPy is meant to provide a consistent environment for solar data analysis. In 
+order to achieve this goal SunPy provides a number of utility functions which 
+are used by the other SunPy modules and are made available to the user. Two 
+modules are described in this Section, namely, solar coordinates (coords), and 
+the Sun module (sun).
 
 \subsection{Coordinates}
-Coordinate transformations are frequently a necessary task within the solar data analysis
-workflow. Likely the most often used transformation is from observer coordinates (e.g. 
-sky coordinates) to a coordinate system which is mapped onto the solar surface (e.g.
-latitude and longitude). This transformation is necessary to compare the true physical
-distance between different solar features. This type of transformation is not unique
-to solar observations (e.g. planetary) but it is not provided by the Astropy coordinates 
-package. The coordinates package implements the World Coordinate System (WCS) for solar
-coordinates as described by \cite{Thompson2000}. The coordinate system transformations
-currently implemented as those most useful for most solar data analysis, namely 
-converting from Helioprojective-Cartesian (HPC) to Heliographic coordinates (HG). HPC 
-which describes the positions on the Sun as angles measured from the center of the solar 
-disk (usually in arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
-most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). HG
-coordinates express positions on the Sun using longitude and latitude on the solar 
-sphere. There are two standards for this coordinate system, Stonyhurst-Heliographic 
-where the origin is at the intersection of the solar equator and 
-the central meridian as seen from Earth and Carrington-Heliographic is a system which is
-fixed to the Sun and does not depend on Earth. The implementation of these transformations
-pass through common coordinate system called Heliocentric-Cartesian (HCC) where positions 
-are expressed in true (deprojected) physical distances instead of angles on the celestial sphere.
-These transformations require some knowledge of the location of the observer which is
-usually provided by the image header information. In case where it is not, the observer
-is assumed to be at Earth.
+Coordinate transformations are frequently a necessary task within the solar 
+data analysis workflow. Likely the most often used transformation is from 
+observer coordinates (e.g. sky coordinates) to a coordinate system which is 
+mapped onto the solar surface (e.g. latitude and longitude). This 
+transformation is necessary to compare the true physical distance between 
+different solar features. This type of transformation is not unique
+to solar observations (e.g. planetary) but it is not provided by the Astropy 
+coordinates package. The coordinates package implements the World Coordinate 
+System (WCS) for solarcoordinates as described by \cite{Thompson2000}. The 
+coordinate system transformations currently implemented as those most useful 
+for most solar data analysis, namely converting from Helioprojective-Cartesian 
+(HPC) to Heliographic coordinates (HG). HPC which describes the positions on 
+the Sun as angles measured from the center of the solar disk (usually in 
+arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
+most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). 
+HG coordinates express positions on the Sun using longitude and latitude on 
+the 
+solar sphere. There are two standards for this coordinate system, 
+Stonyhurst-Heliographic where the origin is at the intersection of the solar 
+equator and the central meridian as seen from Earth and 
+Carrington-Heliographic 
+is a system which is fixed to the Sun and does not depend on Earth. The 
+implementation of these transformations pass through common coordinate system 
+called Heliocentric-Cartesian (HCC) where positions are expressed in true 
+(deprojected) physical distances instead of angles on the celestial sphere.
+These transformations require some knowledge of the location of the observer 
+which is usually provided by the image header information. In case where it is 
+not, the observer is assumed to be at Earth.
 
@@
 \subsubsection{constants}
-The purpose of the constants package is to provide a number of solar-related constants 
-in order to provide consistency in the calculations of derived solar values both within the
-SunPy code base but also to the user. Every solar constants is provided as a Constant objects as defined by Astropy. 
-Each Constant object defines a Quantity, a number associated with a unit, along with the constant's provenance
-(i.e. reference) as well as its uncertainty. Using Astropy's Quantities, any solar constant
-can easily be converted between different units as can be seen in Figure~\ref{fig:constants_code} as well
-as between SI or cgs with a single command.  As these objects inherit from Numpy's ndarray,
-they work well with standard representations of numbers.
-For convenience a number shortcuts to frequently used constants are provided directly when importing
-the sub-package. A larger list of constants can be accessed through an interface modelled 
-on that provided by the SciPy constants package and are available as a dictionary called
-physical_constants. To view all quickly a print_all() function is available.
+The purpose of the constants package is to provide a number of solar-related 
+constants in order to provide consistency in the calculations of derived solar 
+values both within the SunPy code base but also to the user. Every solar 
+constants is provided as a Constant objects as defined by Astropy. Each 
+Constant object defines a Quantity, a number associated with a unit, along with 
+the constant's provenance (i.e. reference) as well as its uncertainty. Using 
+Astropy's Quantities, any solar constant can easily be converted between 
+different units as can be seen in Figure~\ref{fig:constants_code} as well
+as between SI or cgs with a single command.  As these objects inherit from 
+Numpy's ndarray, they work well with standard representations of numbers.
+For convenience a number shortcuts to frequently used constants are provided 
+directly when importing the sub-package. A larger list of constants can be 
+accessed through an interface modelled on that provided by the SciPy constants 
+package and are available as a dictionary called \texttt{physical\_constants}. 
+To view all quickly a \texttt{print\_all()} function is available.
 

### 2014-01-20 1-Introduction.tex
More post-merge changes

@@
 \section{Introduction}
-Modern solar physics, similar to astrophysics, requires increasingly complex software 
-tools both for the retrieval as well as the analysis of data. The Sun is the most well-observed 
-star. As such, solar physics is unique in its ability to access large amounts of high 
-resolution ground- and space-based observations of the Sun at many different wavelengths 
-and spatial scales with high time cadence. Modern solar physics, similar to astrophysics, 
-therefore requires increasingly complex software tools, both for the retrieval and the 
-analysis of data. For example, NASA's Solar Dynamics Observatory (SDO) satellite records 
-over 1 TB of data per day all of which is telemetered to the ground and available for 
-analysis. As a result, scientists have to process large volumes of complex data products. 
-In order to make meaningful advances in solar physics, it is important for the software 
-tools to be standardized, easy to use, and transparent, so that the community can build 
-upon a common foundation.
+Modern solar physics, similar to astrophysics, requires increasingly complex 
+software tools both for the retrieval as well as the analysis of data. The Sun 
+is the most well-observed star. As such, solar physics is unique in its ability 
+to access large amounts of high resolution ground- and space-based observations 
+of the Sun at many different wavelengths and spatial scales with high time 
+cadence. Modern solar physics, similar to astrophysics, therefore requires 
+increasingly complex software tools, both for the retrieval and the analysis of 
+data. For example, NASA's Solar Dynamics Observatory (SDO) satellite records 
+over 1 TB of data per day all of which is telemetered to the ground and 
+available for analysis. As a result, scientists have to process large volumes 
+of complex data products. In order to make meaningful advances in solar 
+physics, it is important for the software tools to be standardized, easy to 
+use, and transparent, so that the community can build upon a common foundation.
 
-Currently, most solar data analysis is performed with a large library of routines called 
-SolarSoft [SSW]. SolarSoft is a set of integrated software libraries, databases, and 
-system utilities which provide a common programming and data analysis environment for
-solar physics. It is overwhelmingly an environment which relies upon IDL (Interactive Data Language),
-a commercial and closed-source interactive data analysis environment sold by 
-Exelis a global aerospace, defense, information and services company. The SSW gen package
-provides the base analysis capabilities such as time series analysis, time conversions,
-spectral fitting, image display, and file I/O. It is composed of 89\% IDL code while the remainder
-is mostly perl (5.4\%) and csh scripts (3.8\%). According to data generated using 
-David A. Wheeler's 'SLOCCount', SSW/gen is composed of 289,724 lines of code with a total approximate
-value of \$10.4M (based on the Basic COCOMO model). 
-Individual missions and instruments provide additional optional packages. For example, 
-the SDO package is 100\% IDL code and is 11k lines of code (\$360k) and the SOHO package is
-100k lines of code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
+Currently, most solar data analysis is performed with a large library of 
+routines called SolarSoft [SSW]. SolarSoft is a set of integrated software 
+libraries, databases, and system utilities which provide a common programming 
+and data analysis environment for solar physics. It is overwhelmingly an 
+environment which relies upon IDL (Interactive Data Language), a commercial and 
+closed-source interactive data analysis environment sold by Exelis a global 
+aerospace, defense, information and services company. The SSW gen package
+provides the base analysis capabilities such as time series analysis, time 
+conversions, spectral fitting, image display, and file I/O. It is composed of 
+89\% IDL code while the remainder is mostly perl (5.4\%) and csh scripts 
+(3.8\%). According to data generated using David A. Wheeler's 'SLOCCount', 
+SSW/gen is composed of 289,724 lines of code with a total approximate value of 
+\$10.4M (based on the Basic COCOMO model). Individual missions and instruments 
+provide additional optional packages. For example, the SDO package is 100\% IDL 
+code and is 11k lines of code (\$360k) and the SOHO package is 100k lines of 
+code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
 Lockheed Martin Solar and Astrophysics Laboratory.
@@
 
-While SSW is open-source and freely available, the IDL core is not. In addition, the development
-of SolarSoft is neither open nor transparent to the public. Also IDL is fairly limited in 
-its ability to interact with other languages. One of SunPy's key aims is to 
-provide a free and modern alternative to the SolarSoft (gen) library. This is made possible
-by the recent rise of the scientific Python community. Python is general purpose 
-high-level programming language. It is free to use, cross-platform, and has a strong
-emphasis on readability a concept which is well-aligned with the scientific endeavor.
-Python has a very large user community which extends far outside of the solar physics
-or astronomy communities. It is very extensible with C, C++, Fortran or even IDL. It is 
-easy to learn. Many books and on-line documentation is available. For example at the time
-of this writing a search on Amazon for books on IDL programming generated 189 results while a search
-for Python yielded 1,788 results. Additionally, students may already have learned Python during their 
-undergraduate which means that research projects can begin quickly without the need for 
-the student to learn a new (and relatively niche) language. Finally, knowledge of Python is a skill which is useful
-and well compensated outside of the scientific community (average salary of \$110k in Washington DC area according
-to indeed.com at the time of writing). Finally, the astronomy community has begun to
-move away from IDL to Python. For all of these reasons, Python is an ideal platform for
-the generation of solar physics data analysis environment.
+While SSW is open-source and freely available, the IDL core is not. In 
+addition, the development of SolarSoft is neither open nor transparent to the 
+public. Also IDL is fairly limited in its ability to interact with other 
+languages. One of SunPy's key aims is to provide a free and modern alternative 
+to the SolarSoft (gen) library. This is made possible by the recent rise of the 
+scientific Python community. Python is general purpose high-level programming 
+language. It is free to use, cross-platform, and has a strong emphasis on 
+readability a concept which is well-aligned with the scientific endeavor.
+Python has a very large user community which extends far outside of the solar 
+physics or astronomy communities. It is very extensible with C, C++, Fortran or 
+even IDL. It is easy to learn. Many books and on-line documentation is 
+available. For example at the time of this writing a search on Amazon for books 
+on IDL programming generated $189$ results while a search for Python yielded 
+$1,788$ results. Additionally, students may already have learned Python during 
+their  undergraduate which means that research projects can begin quickly 
+without the need for the student to learn a new (and relatively niche) 
+language. Finally, knowledge of Python is a skill which is useful and well 
+compensated outside of the scientific community (average salary of \$110k in 
+Washington DC area according to indeed.com at the time of writing). Finally, 
+the astronomy community has begun to move away from IDL to Python. For all of 
+these reasons, Python is an ideal platform for the generation of solar physics 
+data analysis environment.
 
-SunPy is built on top of the core scientific Python packages namely \texttt{NumPy}, \texttt{SciPy}, 
-\texttt{matplotlib}, and \texttt{Pandas}. As of the release 0.4, SunPy is also using the 
-newly release \texttt{Astropy} package (0.3). Leveraging all of these packages has allowed 
-the development of SunPy to provide many capabilities without much effort. The design
-philosophy of SunPy is to provide a clean, simple to use, and well structured 
-package that provides the \textit{core} tools for solar physics.
-The primary focus of SunPy's development early development is to providing specialised, 
-linked, datatypes that allow the import, processing and visualisation of solar 
-data. Currently the datatypes implemented are \texttt{Map}, \texttt{LightCurve} 
-and \texttt{Spectrum}, these cover spatial, timeseries and spectral data 
+SunPy is built on top of the core scientific Python packages namely 
+\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}, and \texttt{Pandas}. As of 
+the release 0.4, SunPy is also using the newly release \texttt{Astropy} package 
+(0.3). Leveraging all of these packages has allowed the development of SunPy to 
+provide many capabilities without much effort. The design philosophy of SunPy 
+is to provide a clean, simple to use, and well structured package that provides 
+the \textit{core} tools for solar physics. The primary focus of SunPy's 
+development early development is to providing specialised,  linked, datatypes 
+that allow the import, processing and visualisation of solar  data. Currently 
+the datatypes implemented are \texttt{Map}, \texttt{LightCurve} and 
+\texttt{Spectrum}, these cover spatial, timeseries and spectral data  
 respectively.
 
-The purpose of this paper is to provide an overview of SunPy's current capabilities, an 
-overview of the development model and community aspects of the SunPy project
-as well as future plans. The latest release of SunPy is available in 
-PyPI and can be installed in the usual manner.
+The purpose of this paper is to provide an overview of SunPy's current 
+capabilities, an overview of the development model and community aspects of the 
+SunPy project as well as future plans. The latest release of SunPy is available 
+in PyPI and can be installed in the usual manner.

### 2014-01-20 3-4-Helioviewer.tex
More post-merge changes

@@
 Project are images in the JPEG2000 format (for further details on the
-Helioviewer Project see \cite{}\footnote{SunPy is used in Helioviewer
+Helioviewer Project see \cite{muller2009}\footnote{SunPy is used in Helioviewer 
 production servers to manage the download and ingestion of JPEG2000
@@
 \begin{minted}{python}
-hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
+hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0,
+ width=512, height=512)
 \end{minted}
@@
 \begin{minted}{python}
-hv.download_png('2099/01/01', 6, "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
+hv.download_png('2099/01/01', 6, 
+"[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50], \
+[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
 \end{minted}
@@
 \begin{minted}{python}
-filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO', instrument='HMI', detector='HMI', measurement='continuum')
+filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
+ instrument='HMI', detector='HMI', measurement='continuum')
 from sunpy.map import Map
@@
 \end{listing}
-
-%
-% Helioviewer article citation
-%
-%@article{Muller:2009:JVL:2220073.2220164,
-% author = {Muller, D. and Fleck, B. and Dimitoglou, G. and Caplins, B. W. and Amadigwe, D. E. and Ortiz, J. P.G. and Wamsler, B. and Alexanderian, A. and Hughitt, V. K. and Ireland, J.},
-% title = {JHelioviewer: Visualizing Large Sets of Solar Images Using JPEG 2000},
-% journal = {Computing in Science and Engg.},
-% issue_date = {September 2009},
-% volume = {11},
-% number = {5},
-% month = sep,
-% year = {2009},
-% issn = {1521-9615},
-% pages = {38--47},
-% numpages = {10},
-% url = {http://dx.doi.org/10.1109/MCSE.2009.142},
-% doi = {10.1109/MCSE.2009.142},
-% acmid = {2220164},
-% publisher = {IEEE Educational Activities Department},
-% address = {Piscataway, NJ, USA},
-% keywords = {data visualization},
-%}

### 2014-01-20 3-2-HEK.tex
first edit on HEK

\subsection{HEK}\label{ssec:hek}

The Sun is an active star and exhibits a wide range of phenomena on
many different time-scales, length-scales and wavelengths.
Observations and metadata concerning these phenomena are collected at
the Heliophysics Event Knowledgebase (HEK).  Entries are generated
both by automated algorithms and human observers.  Some of the
information in the HEK reproduces feature/event data elsewhere (for
example, the GOES flare catalog), and some is generated by the Solar
Dynamics Observatory Feature Finding Team \cite{???} to populate the
HEK.  The advantage of the HEK to SunPy is that it is a single service
that provides a homogeneous and well-described interface to a large
amount of feature/event information of interest to the solar physics
community.

SunPy accesses this information through the \texttt{hek} module, which
was developed through support from the European Space Agency Summer of
Code in Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of
the HEK API
(http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print).
Every event type has required and optional properties; the current
list of events maintained by the HEK and their properties can be found
at http://www.lmsal.com/hek/VOEvent_Spec.html.

Simple HEK queries consist of start time, an end time, and an event
type (Example \ref{code:hek:simple}). Times can be specified in any
SunPy-acceptable format. Event types are specified as upper case, two
letter strings, and are identical to the two letter abbreviations
found at the HEK website, http://www.lmsal.com/hek/VOEvent_Spec.html.

\begin{listing}
\begin{minted}{python}
from sunpy.net import hek
client = hek.HEKClient()
tstart = '2011/08/09 07:23:56'
tend = '2011/08/09 12:40:29'
event_type = 'FL'
result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type))
\end{minted}
\caption{Simple HEK query, returning 19 entries.}
\label{code:hek:simple}
\end{listing}

The module \texttt{hek.attrs} contains attributes of the HEK that can be used to
construct HEK queries.  For example, a flare is an attribute of the
HEK, and so instead of specifying \texttt{hek.attrs.EventType('FL')}
in Example \ref{code:hek:simple}, this can also be expressed as
\texttt{hek.attrs.FL}.

HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in
that many of them are wrappers that conveniently expose
comparisions by overloading Python operators.  This allows filtering
of the HEK entries by the properties of the event.  As was mentioned
above, the HEK stores feature/event metadata obtained in different
ways, known generally as {\it feature recognition methods}, or FRMs.
Example \ref{code:hek:frm} filters the results of the previous result
to return only those events that have the FRM 'SSW Latest Events'.
\begin{listing}
\begin{minted}{python}
result = client.query( hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), hek.attrs.FRM.Name == 'SSW Latest Events')
\end{minted}
\caption{An HEK query that returns only those flares that were
  detected by the 'SSW Latest Events' feature recognition method.}
\label{code:hek:frm}
\end{listing}

For example you are able
to say AR & AR.NumSpots < 5 to find all active regions with less than
5 spots.

As with the VSO query, you can use the fundamental logic
operators AND and OR to construct queries of almost arbitrary
complexity. Note that complex queries result in multiple requests to
the server which might make them less efficient.

### 2014-01-20 3-2-HEK.tex
finished first draft of HEK section

@@
 example, the GOES flare catalog), and some is generated by the Solar
-Dynamics Observatory Feature Finding Team \cite{???} to populate the
-HEK.  The advantage of the HEK to SunPy is that it is a single service
-that provides a homogeneous and well-described interface to a large
-amount of feature/event information of interest to the solar physics
-community.
+Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
+populate the HEK.  The advantage of the HEK to SunPy is that it is a
+single service that provides a homogeneous and well-described
+interface to a large amount of feature/event information of interest
+to the solar physics community.
 
@@
 \begin{minted}{python}
-result = client.query( hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), hek.attrs.FRM.Name == 'SSW Latest Events')
+result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), hek.attrs.FRM.Name == 'SSW Latest Events')
 \end{minted}
@@
 \end{listing}
+Multiple comparisons can be made by including more comma-separated
+conditions on the attributes in the call to the HEK query method.
 
-For example you are able
-to say AR & AR.NumSpots < 5 to find all active regions with less than
-5 spots.
+HEK comparisons can be combined using Python’s logical operators AND
+and OR. This makes complex queries easy to create: example
+\ref{code:hek:or} returns flares west of 50 arcseconds or those that
+have a peak flux above 1000.0 (the units of the flux are FRM dependent
+and are described at the HEK website).
+\begin{listing}
+\begin{minted}{python}
+result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), (hek.attrs.Event.Coord1 > 50) or (hek.attrs.FL.PeakFlux > 1000.0) )
+\caption{HEK query using the 'or' operator.}
+\label{code:hek:or}
+\end{listing}
+All FRMs report the required feature attributes (as described at
+http://www.lmsal.com/hek/VOEvent_Spec.html), but the optional
+attributes are FRM dependent.  If a FRM does not have one of the
+optional attribute, a 'None' is returned by the \texttt{hek} module.
 
-As with the VSO query, you can use the fundamental logic
-operators AND and OR to construct queries of almost arbitrary
-complexity. Note that complex queries result in multiple requests to
-the server which might make them less efficient.
+The ability to use comparison and logical operators on HEK attributes
+allows the construction of queries of almost arbitrary complexity,
+bringing powerful feature/event search capabilities to SunPy.

### 2014-01-21 2-1-Map.tex
add stuff to dataypes

@@
 Map is a 2D spatial data type, primarily used for images of the Sun and 
-inner heliosphere. It provides a wrapper around a data array (numpy 
-ndarray) and gives easy access to standard meta data in the header of the 
-image.
-The \texttt{Map} datatype provides convenience methods for many functions 
+inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
+\texttt{ndarray}) and gives easy access to standard meta data in the header of 
+the image, via the \texttt{.meta} attribute as well as some convienience 
+properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
+\texttt{.wavelength} or \texttt{.coordinate\_system}.
+The \texttt{Map} data type provides convenience methods for many functions 
 such as, rotation and re-sampling as well as convenience visualisation 
-functions.
+functions, providing a easy to use as well as powerful interface.
+
 The design of the map submodule is such that each instrument or 
@@
 following instruments: \textit{IRIS} SJI frames, \textit{SDO/AIA} and 
-\textit{HMI}, \textit{SOHO/EIT} and 	\textit{LASCO}, 
-\textit{STEREO/EUVI} 	and \textit{COR}, \textit{YOHKOH/SXT}, 
-\textit{RHESSI}, \textit{PROBA2/SWAP} and\textit{HINODE/XRT}.
+\textit{HMI}, \textit{SOHO/EIT} and	\textit{LASCO}, \textit{STEREO/EUVI} and 
+\textit{COR}, \textit{YOHKOH/SXT}, \textit{RHESSI}, \textit{PROBA2/SWAP} and 
+\textit{HINODE/XRT}.
 
-\begin{listing}[h]
+As can been seen in Listing \ref{code:aia_1} the map datatype parses header 
+information for many purposes including visualisation on correct physical axes 
+and limb plotting as well as making this information easily available to the 
+user.
+
+\begin{listing}[H]
 \begin{minted}{pycon}
@@
 >>> aiamap = sunpy.map.Map('aia_file.fits')
->>> aia
+>>> aiamap
 SunPy AIAMap
@@
 Observatory: SDO
-Instrument:  AIA_3
+Instrument:  AIA
 Detector:    AIA
@@
 
-\end{minted}
-\caption{Example of printing information about a map at a Python interactive 
-prompt.}
-\label{code:aia_2}
-\end{listing}
-
-\begin{listing}[h]
-\begin{minted}{python}
-
-import sunpy.map
-
-aiamap = sunpy.map.Map('aia_file.fits')
-aia.peek()
+>>> aia.peek()
 \end{minted}
 \includegraphics[width=0.8\columnwidth]{aia_map_example}
-\caption{Demonstration of the \textit{AIA} map quick view plotting method.}
+\caption{Demonstration of the \texttt{AIAMap} specilisation of 
+\texttt{GenericMap}. The Map is created from a \textit{AIA} FITS file and the 
+key meta data and array overview is printed. Then a quick view plot is created 
+by using the \texttt{.peek()} method.}
 \label{code:aia_1}
 \end{listing}
-
-As can been seen in Listing \ref{code:aia_1} \& \ref{code:aia_2} the map 
-datatype parses header information for many purposes including visualisation on 
-correct physical axes and limb plotting as well as making this information 
-easily available to the user.
 
@@
 
-\begin{listing}[h]
+\begin{listing}[H]
 \begin{minted}{python}

### 2014-01-21 2-2-Lightcurve.tex
add stuff to dataypes

--- 2014-01-16 2-2-Lightcurve.tex
@@
 
+\subsubsection{Creating and using Lightcurves}
+
 A \textit{Lightcurve} object may be created using a range of different methods. 
-Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see example below).
-In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object.
+Firstly, a \textit{Lightcurve} may be created for a specific instrument based 
+on an input time range (see Listing \ref{goes_lc_code} below). In this example, 
+the Lightcurve constructor searches remote sites for the GOES X-ray data 
+specified by the time interval, downloads the required files and subsequently 
+creates the object (see also Listing \ref{goes_lc_code}).
 
-\begin{lstlisting}[language=Python]
-from sunpy import lightcurve
-goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
-`2011-06-07 08:00')
-goes.peek()
+\begin{listing}[H]
+\begin{minted}{python}
+>>> from sunpy import lightcurve
+>>> goes=lightcurve.GOESLightCurve.create('2011-06-07 06:00',
+'2011-06-07 08:00')
+>>> goes.peek()
+\end{minted}
+\includegraphics[width=14cm]{goes_lightcurve.pdf}
+\label{goes_lc_code}
+\caption{Creating a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
+2011 June 7 using a time range, and the result of the \texttt{peek()} command.}
+\end{listing}
 
-\end{lstlisting}
+Alternatively, if the data file already exists on the local system, the 
+\textit{Lightcurve} object may instead be initialized using that file as input 
+(see Listing \ref{lyra_lc_code}).
 
-Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see example below).
+\begin{listing}[H]
+\begin{minted}{python}
+>>> from sunpy import lightcurve
+>>> file='lyra_20110607-000000_lev2_std.fits'
+>>> lyra=lightcurve.LYRALightCurve.create(file)
+>>> lyra.peek()
+\end{minted}
+\includegraphics[width=14cm]{lyra_lightcurve.pdf}
+\label{lyra_lc_code}
+\caption{Creating a LYRA lightcurve for the full day of 2011 June 7 using an 
+existing data file, and the result of the \texttt{peek()} command}
+\end{listing}
 
-\begin{lstlisting}[language=Python]
-from sunpy import lightcurve
-file=`lyra_20110607-000000_lev2_std.fits'
-lyra=lightcurve.LYRALightCurve.create(file)
-lyra.peek()
+Once the \textit{Lightcurve} has been created it may be manipulated in a variety of ways in order to perform time series analysis.
+Continuing from the above, we show a few simple examples of using a LYRA lightcurve.
 
-\end{lstlisting}
+In the above case (Listing \ref{lyra_lc_code}), we created a LYRA Lightcurve spanning the full day of 2011 June 7.
+To extract the sub-interval 06:00 - 07:00 UT into a new \textit{Lightcurve} called \verb|lyra_zoom| we simply do the following:
+
+\begin{listing}[H]
+\begin{minted}{python}
+>>> from sunpy.time import TimeRange
+>>> tran=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+>>> lyra_zoom = lyra.truncate(tran)
+\end{minted}
+\label{lyra_truncate}
+\caption{Extracting a sub-interval from a Lightcurve.}
+\end{listing}
+
+Also in the example shown in Listing \ref{lyra_lc_code}, direct access to the data and time information in the object is available through \verb|lyra.data| and \verb|lyra.data.index| respectively.
+
+\begin{listing}[H]
+\begin{minted}{python}
+>>> print lyra.data
+<class 'pandas.core.frame.DataFrame'>
+DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
+2011-01-28 23:59:59.983993
+Data columns (total 4 columns):
+CHANNEL1    1496629  non-null values
+CHANNEL2    1496629  non-null values
+CHANNEL3    1496629  non-null values
+CHANNEL4    1496629  non-null values
+dtypes: float64(4)
+
+>>> print lyra.data.index
+<class 'pandas.tseries.index.DatetimeIndex'>
+[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
+Length: 1496629, Freq: None, Timezone: None
+\end{minted}
+\label{lyra_pandas}
+\caption{Accessing the data and time axis in a Lightcurve}
+\end{listing}

### 2014-01-21 2-Data_Types.tex
add stuff to dataypes

@@
 One of the primary focus' of the SunPy library is to provide data structures 
-that are 
-specifically designed for the various types of data generally processed for 
-solar physics. Currently \texttt{SunPy} provides three datatypes, each separate 
-from one another to process 2D spatial data (Map), 1D temporal series 
-(LightCurve) and 1 and 2D spectra (Spectrum and Spectra).
+that are specifically designed for the various types of data generally 
+processed for solar physics. Currently SunPy provides three data 
+types, each separate from one another to process 2D spatial data 
+(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
+(\texttt{Spectrum} and \texttt{Spectra}).
+
+The design of SunPy's core data types is as a wrapper around a data object, 
+either a \texttt{numpy} \texttt{ndarray} or a \texttt{pandas} 
+\texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
+\texttt{LightCurve} respectively. Each data type has a \texttt{.data} attribute 
+where this data object is located and some meta data. It is possible to 
+instantiate the data types from various different sources, \textit{e.g.} files, 
+urls, arrays or time ranges. The specific sources supported is dependant upon 
+which data type and which instrument. All the SunPy data types support 
+specialisation on a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
+\texttt{AIAMap} sub-type. This design allows simple extensions to cope with the 
+diversity of data from different sources in solar physics. As well as support 
+for different instruments and data sources each data type supports different 
+visualisation wrappers that allow both quick view plotting (the peek command) 
+and more fine-grained control plotting that integrates well with 
+\texttt{matplotlib} (the plot command).
 
 This section will give a brief overview of the \textit{current} functionality 
-of each of these modules and then describe the development plan for future 
-improvements to these submodules.
+of each of these modules.
 
@@
 change the plot, \textit{e.g.} set the title. 
+More technically what is done in the plotting routines is firstly, to make sure 
+that the current state of the figure and axes is mantined in the same way as it 
+is inside the \texttt{pyplot} functions. For \texttt{Map} this means setting 
+\texttt{pyplot.sci()} or set current image, so that \texttt{plt.colorbar()} 
+automatically detects the plotted \texttt{AxesImage} object. Secondly, it also 
+means returning the same type of object as the \texttt{pyplot} interfaces 
+function, \textit{i.e.} for \texttt{Map} it returns the \texttt{AxesImage} 
+instance which is the same type of return as \texttt{pyplot.imshow}.

### 2014-01-22 1-Introduction.tex

@@
 Currently, most solar data analysis is performed with a large library of 
-routines called SolarSoft [SSW]. SolarSoft is a set of integrated software 
+routines called SolarSoft, also referred to as SSW \cite{ssw_ref}. SolarSoft is a set of integrated software 
 libraries, databases, and system utilities which provide a common programming 
@@
 environment which relies upon IDL (Interactive Data Language), a commercial and 
-closed-source interactive data analysis environment sold by Exelis a global 
+closed-source interactive data analysis environment sold by Exelis, a global 
 aerospace, defense, information and services company. The SSW gen package
@@
 \$10.4M (based on the Basic COCOMO model). Individual missions and instruments 
-provide additional optional packages. For example, the SDO package is 100\% IDL 
-code and is 11k lines of code (\$360k) and the SOHO package is 100k lines of 
+provide additional optional packages to support and process their data. 
+For example, the SDO package \cite{sdo} is 100\% IDL code and is 11k lines of code (\$360k) 
+and the SOHO package \cite{soho} is 100k lines of 
 code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
@@
 
-While SSW is open-source and freely available, the IDL core is not. In 
-addition, the development of SolarSoft is neither open nor transparent to the 
-public. Also IDL is fairly limited in its ability to interact with other 
-languages. One of SunPy's key aims is to provide a free and modern alternative 
+While SSW is open-source and freely available, the IDL core. The cost of IDL is prohibitive
+for many undergraduates as well as institutions with limited means.
+
+One of SunPy's key aims is to provide a free and modern alternative 
 to the SolarSoft (gen) library. This is made possible by the recent rise of the 
-scientific Python community. Python is general purpose high-level programming 
-language. It is free to use, cross-platform, and has a strong emphasis on 
+scientific Python community. Python is a general purpose high-level programming 
+language. It is free to use, cross-platform and is both an accessible and powerful
+programming language. Python is one of the top ten most popular programming languages 
+in the world according to the 2014 TIOBE Index\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
+It therefore has a very large user community which extends far outside of the solar 
+physics or astronomy communities. It is very extensible with C, C++, Fortran or 
+even IDL. Many books and on-line documentation is 
+available. For example at the time writing a search on Amazon for books 
+on IDL programming generated $189$ results while a search for Python yielded 
+$1,788$ results. Python has a strong emphasis on 
 readability a concept which is well-aligned with the scientific endeavor.
-Python has a very large user community which extends far outside of the solar 
-physics or astronomy communities. It is very extensible with C, C++, Fortran or 
-even IDL. It is easy to learn. Many books and on-line documentation is 
-available. For example at the time of this writing a search on Amazon for books 
-on IDL programming generated $189$ results while a search for Python yielded 
-$1,788$ results. Additionally, students may already have learned Python during 
-their  undergraduate which means that research projects can begin quickly 
-without the need for the student to learn a new (and relatively niche) 
+Additionally, Python is increasingly being taught in universities,
+which means that research projects can begin quickly 
+without the need for students to learn a new (and relatively niche) 
 language. Finally, knowledge of Python is a skill which is useful and well 
 compensated outside of the scientific community (average salary of \$110k in 
-Washington DC area according to indeed.com at the time of writing). Finally, 
-the astronomy community has begun to move away from IDL to Python. For all of 
-these reasons, Python is an ideal platform for the generation of solar physics 
+the Washington DC area according to indeed.com at the time of writing).
+Python continues to see increased use in the astronomy community 
+\cite{2011ASPC..442..425G} which has similar goals and requirements as the solar physics
+community. Finally, Python plays well with many technologies such as web servers \cite{2008JPhCS.119d2011D}, 
+SQL databases, interactive and shareable notebook-based computing \cite{PER-GRA:2007}.
+For all of these reasons, Python is an ideal platform for a modern solar physics 
 data analysis environment.
@@
 SunPy is built on top of the core scientific Python packages namely 
-\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}, and \texttt{Pandas}. As of 
-the release 0.4, SunPy is also using the newly release \texttt{Astropy} package 
-(0.3). Leveraging all of these packages has allowed the development of SunPy to 
-provide many capabilities without much effort. The design philosophy of SunPy 
-is to provide a clean, simple to use, and well structured package that provides 
+\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core packages provide
+capabilities surpassing that provided by IDL for array manipulation and 2-d plotting
+\cite{2011ASPC..442..425G}. Providing similar capabilities as SSW/gen in Python is made
+easier by leveraging the diverse Python community. For example, SunPy makes use of 
+the \texttt{Pandas} package to provide high-performance, easy-to-use data structures and data analysis tools
+for time series data\cite{mckinney2012python}. \texttt{Pandas} was originally developed for quantitative analysis of financial
+data and has seen grown into a generalized data analysis package. SunPy also relies on 
+and is coordinating with the \texttt{Astropy} package \cite{2013A&A...558A..33A}. It is still in
+active development but already provides many relevant capabilities such as full-featured
+support for FITS files, absolute dates and time conversions, units and unit conversions,
+and model-fitting. Pandas (134k lines of code) and AstroPy (90k lines of code) allow
+SunPy to leverage a total value of \$7.6M worth of development which is close to the 
+\$10.4M for SSW/gen assuming a rough equivalency between a line of Python code and a line
+of IDL code.
+
+The design philosophy of SunPy is to provide a clean, simple to use, and well structured package that provides 
 the \textit{core} tools for solar physics. The primary focus of SunPy's 
-development early development is to providing specialised,  linked, datatypes 
-that allow the import, processing and visualisation of solar  data. Currently 
-the datatypes implemented are \texttt{Map}, \texttt{LightCurve} and 
-\texttt{Spectrum}, these cover spatial, timeseries and spectral data  
+development early development is to provide specialised, linked, datatypes 
+that allow the import, processing and visualisation of all types of solar data. These include \texttt{Map}, 
+\texttt{LightCurve} and \texttt{Spectrum}, these cover spatial, timeseries and spectral data  
 respectively.
@@
 in PyPI and can be installed in the usual manner.
+
+%citations
+% 2013A&A...558A..33A http://adsabs.harvard.edu/abs/2013A&A...558A..33A astropy
+% 2011ASPC..442..425G http://adsabs.harvard.edu/abs/2011ASPC..442..425G greenfield2011
+% 2013ApJ...763...86L  http://adsabs.harvard.edu/abs/2013ApJ...763...86L chianti
+%@book{mckinney2012python,
+%  title={Python for Data Analysis: Data Wrangling with Pandas, NumPy, and IPython},
+%  author={McKinney, W.},
+%  isbn={9781449323615},
+%  url={http://books.google.com/books?id=v3n4\_AK8vu0C},
+%  year={2012},
+%  publisher={O'Reilly Media}
+%}
+% 2008JPhCS.119d2011D http://adsabs.harvard.edu/abs/2008JPhCS.119d2011D rapid web development in python
+%@Article{PER-GRA:2007,
+%  Author    = {P\'erez, Fernando and Granger, Brian E.},
+%  Title     = {{IP}ython: a System for Interactive Scientific Computing},
+%  Journal   = {Computing in Science and Engineering},
+%  Volume    = {9},
+%  Number    = {3},
+%  Pages     = {21--29},
+%  month     = may,
+%  year      = 2007,
+%  url       = "http://ipython.org",
+%  ISSN      = "1521-9615",
+%  doi       = {10.1109/MCSE.2007.53},
+%  publisher = {IEEE Computer Society},
+%}

### 2014-01-22 2-1-Map.tex

@@
 Map is a 2D spatial data type, primarily used for images of the Sun and 
-inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
-\texttt{ndarray}) and gives easy access to standard meta data in the header of 
-the image, via the \texttt{.meta} attribute as well as some convienience 
-properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
-\texttt{.wavelength} or \texttt{.coordinate\_system}.
-The \texttt{Map} data type provides convenience methods for many functions 
+inner heliosphere. It provides a wrapper around a data array (numpy 
+ndarray) and gives easy access to standard meta data in the header of the 
+image.
+The \texttt{Map} datatype provides convenience methods for many functions 
 such as, rotation and re-sampling as well as convenience visualisation 
-functions, providing a easy to use as well as powerful interface.
-
+functions.
 The design of the map submodule is such that each instrument or 
@@
 
-As can been seen in Listing \ref{code:aia_1} the map datatype parses header 
-information for many purposes including visualisation on correct physical axes 
-and limb plotting as well as making this information easily available to the 
-user.
-
-\begin{listing}[H]
+\begin{listing}[h]
 \begin{minted}{pycon}
@@
        [ 0.5   , -0.125 ,  0.4375, ...,  0.6875,  0.6875,  0.6875]])
-
 >>> aia.peek()
@@
 \includegraphics[width=0.8\columnwidth]{aia_map_example}
-\caption{Demonstration of the \texttt{AIAMap} specilisation of 
-\texttt{GenericMap}. The Map is created from a \textit{AIA} FITS file and the 
-key meta data and array overview is printed. Then a quick view plot is created 
-by using the \texttt{.peek()} method.}
+\caption{Demonstration of the \textit{AIA} map quick view plotting method.}
 \label{code:aia_1}
 \end{listing}
+
+As can been seen in Listing \ref{code:aia_1} the map datatype parses header 
+information for many purposes including visualisation on correct physical axes 
+and limb plotting as well as making this information easily available to the 
+user.
 
@@
 
-\begin{listing}[H]
+\begin{listing}[h]
 \begin{minted}{python}

### 2014-01-22 4-Util.tex

@@
 \subsubsection{Sun}
-The purpose of this module is to provide solar-specific data
+The purpose of this module is to provide solar-specific data for example ephemeris and
+solar constants. The main namespace contains a number of functions which provide solar
+ephemeris such as sun to earth distance, solar cycle number, the mean anomaly, etc.
+All of these functions take a time as their input which can be provided in any parse_time
+compatible format. A future version of SunPy will integrate with the AstroPy coordinates package.
 

### 2014-01-22 3-3-HELIO.tex
example added to the helio section and some re-writting

@@
 HELIO has been built with a Service-Oriented Architecture, 
-\textit{i.e.} HELIO capabilities are split into a number of tasks that are 
+\textit{i.e.} its capabilities are split into a number of tasks that are 
 implemented as separate services. 
-HELIO counts with up to nine different public services, which allows to the scientist to look up in different catalogues of registered events, features on the sun and data from instruments in the heliosphere.
-Additionally, HELIO provides of a service that uses a propagation model to link the data in different points of the solar system by its original nature 
+HELIO counts with up to nine different public services, which allows to the 
+scientist to search in different catalogues of registered events, solar features,
+data from instruments in the heliosphere and other information like planets or 
+spacecraft position in time. 
+Additionally, HELIO provides of a service that uses a propagation model to link 
+the data in different points of the solar system by its original nature 
 (\textit{e.g.}, Earth auroras are a signature of magnetic field disturbances 
 produced few days before on the Sun).
-The main interface to acccess to HELIO is through its front-end\footnote{
+The main interface to access to HELIO is through its front-end\footnote{
 \url{http://hfe.helio-vo.eu}},
@@
 
-The current version of Sunpy has implemented an interface to access the \textit{HELIO Event Catalogue} service.  
-HELIO results are provided as VOTable format\footnote{\bf{info about votables IVOAA standard!}} 
-which reader have been integrated within Astropy, this has an additional advantage of getting metadata with information as data provenance and the performed query.
+The current version of SunPy has includes an interface to access the 
+\textit{HELIO Event Catalogue} (HEC) service developed as part of Google
+Summer of Code project in 2013.
+This service provides at the moment access to 84 catalogues from different
+sources (automated and manual classification, event lists from publications, \cdot).
+HEC results (as the rest of HELIO services) provides the results in VOTable 
+data format (defined by IVOA \cite{ochsenbein_ivoa_2011})
+which the \textttt{astropy.io.votable} can interact with.
+This format has the advantage of contain metadata with information like
+data provenance and the performed query.
 
-%example on how to use it
+On listing~\ref{code:helio} we show some an example on how to obtain information
+from different \textit{Coronal Mass Ejections}(CMEs) catalogues.
 
-%In the future, when the rest of services are implemented HELIO tools could interact with other services like database or data visualisation in a seemlessly way.
+\begin{listing}[h]
+\begin{minted}{pycon}
+>>> from sunpy.net.helio import hec
+>>> hc = hec.Client()
+
+Desired time range and event type
+>>> tstart = '2011-06-07T06:00:00'
+>>> tend = '2011-06-07T12:00:00'
+>>> event_type = 'cme'
+
+Obtain from all the catalogues these which name contain our event of interest
+>>> catalogues = hc.get_table_names()
+>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
+>>> print catalogues_event
+
+Query all the catalogues that comes from cactus
+>>> results = [hc.time_query(tstart, tend, event) for event in catalogues_event if 'cactus' in event]
+>>> print results
+********** This need to be added!
+\end{minted}
+\caption{Demonstration of the \texttt{helio.hec} interface.}
+\label{code:helio}
+\end{listing}
+
+It is in the SunPy roadmap to add support from the other HELIO services and improve
+the usability of them towards a seamlessly interaction of this tool with the rest of
+the environment, as for example with data visualisation or the database module.

### 2014-01-22 2-2-Lightcurve.tex
more changes

@@
 >>> print lyra.data
-<class 'pandas.core.frame.DataFrame'>
+<class pandas.core.frame.DataFrame>
 DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
@@
 >>> print lyra.data.index
-<class 'pandas.tseries.index.DatetimeIndex'>
+<class pandas.tseries.index.DatetimeIndex>
 [2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]

### 2014-01-22 6-Future.tex
Fix merge related issues
More post-merge changes
more changes

@@
 SunPy as a project has existed for roughly three years. In this time the code 
-base has grown to over $110,000$ lines. SunPy in it's current form is a useful 
+base has grown to over 110,000 lines. SunPy in it's current form is a useful 
 package for the analysis of calibrated solar data, however, the code base is 
@@
 
-The near-term future of the SunPy library is likely to continue this changeable 
-nature with re-factoring and restructuring planned, especially within the 
-core data types. The main focus upon the data types defined inside sunpy is to 
-improve the interoperability and to redesign them in a more consistent manner.
+As discussed in Section \ref{sec:Intro}, the primary focus of the 
+\texttt{sunpy} library is the analysis and visualisation of `high level' solar 
+data. This means data that has been put through instrument processing and 
+calibration routines, and contains full (WCS) coordinate information. The 
+development plan for SunPy is to continue development within this scope. The 
+primary components of this plan are to provide a set of data types that are 
+interchangeable with one another, \textit{i.e.} if you slice a \texttt{MapCube} 
+along one coordinate a \texttt{LightCurve} of intensity along the time range of 
+the \texttt{MapCube} should be returned. To achieve this goal all the data 
+types need to share a unified coordinate system architecture so that each data 
+type is aware of what the physical type of it's data is and how operations on 
+that data should be performed.
 
-In the past 12 months the collaboration with the Astropy project 
-\cite{theastropycollaboration2013} has grown. The future of SunPy 
-will continue this collaboration as the Astropy package provides many core 
-tools that are applicable to all types of astronomy. For example the 
-\texttt{astropy.units} submodule provides a simple and efficient way of 
-representing physical units in Python data types, there are plans to 
-incorporate this widely in the SunPy code-base.
+In concert with the work on the data types further integration with the 
+\texttt{astropy} package will enable SunPy to inherit the large amounts of work 
+done in that project to support a platform for astronomical data analysis. For 
+example the \texttt{astropy.units} submodule provides a simple and efficient 
+way of representing physical units in Python data types, there are plans to 
+incorporate this widely in the SunPy code-base. In the past 12 months the 
+collaboration with the Astropy project \cite{theastropycollaboration2013} and 
+it's community has grown, this direct collaboration between Astropy and 
+SunPy will be one of the key strengths of SunPy going forward.

### 2014-01-22 3-1-VSO.tex
VSO section added

\subsection{VSO}\label{ssec:vso}

The Virtual Solar Observatory (VSO) was built to facilitate
access to solar data from the different archives around the 
world \cite{hill_virtual_2009}.  
Enabling therefore a single standard query interface to all
the available products from solar observation.  
VSO allows to query data not just by instrument or mission for 
a time range but by physical physical variables as for example:
intensity, magnetic field, particle flux or spectral range to name a few.
VSO's main interface is web-based\footnote{\url{http://virtualsolar.org}}, 
however a SOAP webservice is also available.
SunPy access to the VSO through the \texttt{vso} module which it uses 
the \texttt{suds} package to connect to the webservice.
This module was developed under the ESA's Summer of Code programme of 2010.

The \texttt{vso} module includes advances features through the use
of VSO attributes objects.  
The time range, the instrument, the wavelength, the physical observable,
and many other properties are set as attributes objects which could
be combine using \texttt{and} - just by chaining together the arguments -
or \texttt{or} operators - by joining the attributes using the ``$|$'' operator.
Listing~\ref{code:vso_query} shows few examples of queries made using
such attributes.

\begin{listing}[h]
\begin{minted}{pycon}
>>> from sunpy.net import vso
>>> client=vso.VSOClient()
>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'

Querying just a single instrument
>>> lasco_query = client.query(vso.attrs.Time(tstart, tend), 
...                            vso.attrs.Instrument('lasco'))
>>> lasco_query.num_records()
40
>>> qr.show() 
Start time           End time             Source  Instrument  Type  
----------           --------             ------  ----------  ----  
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
...

Adding to the query STEREO's coronographs: COR1
>>> instrument_condition = ( vso.attrs.Instrument('lasco') | 
...                          vso.attrs.Detector('cor1') )
>>> coronographs = client.query(vso.attrs.Time(tstart, tend)), 
...                             instrument_condition)
>>> coronographs.num_records()
485
>>> coronographs.show() 
Start time           End time             Source    Instrument  Type  
----------           --------             ------    ----------  ----  
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO      LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO      LASCO       CORONA
...
2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
\end{minted}
\caption{Examples of different advanced queries through the \texttt{vso} 
  module using the attributes objects.}
\label{code:vso_query}
\end{listing}

The \texttt{vso} module also provides of an interface to download the data,
allowing to customise the directory structure to save the data.
Listing~\ref{code:vso_down} exemplifies such case.

\begin{listing}[h]
\begin{minted}{pycon}
>>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
>>> results = client.get(coronographs, 
...                      path = pathformat)

\end{minted}
\caption{From listing~\ref{code:vso_query}, this examples shows the 
  download method of the \texttt{vso} module.}
\label{code:vso_down}
\end{listing}

### 2014-01-22 3-1-VSO.tex
fix typo in python code for vso

@@
 40
->>> qr.show() 
+>>> lasco_query.show() 
 Start time           End time             Source  Instrument  Type  

### 2014-01-23 3-5-Database.tex
removed undo/redo code snippet

@@
 
-The need for a database package arose because using VSO alone lead to two major
+The need for a database package arose because using VSO alone led to two major
 problems:
@@
 removed because they have been added first and are therefore the entries that
-have been used least recently. To undo this operation, the \texttt{undo} method
-is used in code listing \ref{code:db_4} to add the 3 removed entries back to
-the database. The \texttt{redo} method removes them again.
-
-\begin{listing}
-\begin{minted}{python}
->>> database.undo()
->>> len(database)
-6
->>> database.redo()
->>> len(database)
-3
-\end{minted}
-\caption{Undoing and redoing operations.}
-\label{code:db_4}
-\end{listing}
-
-% TODO: 'clever fetching'
+have been used least recently.

### 2014-01-23 3-5-Database.tex
removed microseconds from output

@@
 -- ---------------------- -------        -------           -------------      
-1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525397
-2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525469
-3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525532
-4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429665
-5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429731
-6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429792
+1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
+2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
+3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
+4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
+5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
+6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
 \end{minted}

### 2014-01-23 3-5-Database.tex
removed code snippets for set_cache_size

@@
 first.  % FIXME is 'whose' correct here? ^
-
-\begin{listing}
-\begin{minted}{python}
->>> database.set_cache_size(3)
->>> print display_entries(
-...     database,
-...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
-id observation_time_start wavemin        wavemax           download_time             
--- ---------------------- -------        -------           -------------             
-4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429665
-5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429731
-6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429792
-\end{minted}
-\caption{Displaying database entries in a table.}
-\label{code:db_3}
-\end{listing}
-
-In code listing \ref{code:db_3} the entries with the IDs \#1 -- \#3 have been
-removed because they have been added first and are therefore the entries that
-have been used least recently.

### 2014-01-23 2-3-Spectra.tex

@@
 
-Spectroscopy consists in the study of the radiative energy related to the its wavelength.
+Spectroscopy consists in the study of the radiative energy related to the wavelength.
 An spectrum is normally obtained by observing a range of frequencies at the same time; 
-this can be done either for example in radio wavelengths by swiping over different frequencies - e.g., with radio receiver - 
-or in visible and ultraviolet by the dispersion of the incident light through a diffraction grating or prism.
-By analysing the resultant spectrum properties such temperature, density, speed and other kinematics can be obtained.
-Therefore, spectroscopy provides to the solar physicists invaluable information about the composition and the physical properties of the Sun.
+An spectrum can be measured for example in radio wavelengths by a frequency sweep with 
+a radio receiver or in visible and ultraviolet by the dispersion of the incident light 
+through a diffraction grating or prism.
+The analysis of the resultant spectrum can provide properties of the plasma observed 
+such temperature, density, speed and other kinematics can be obtained. 
+Therefore, spectroscopy provides to the solar physicists invaluable information about 
+the composition and the physical properties of the Sun.
 
-Sunpy intents to provide support to most of solar spectroscopy instrument, however the complexity of this kind of datasets makes very challenging to add support to them all in a general way.  
-Nevertheless, the design of the \textit{Spectra} object is consistent with the other data types available in Sunpy.
-As yet, Sunpy offers a \textit{Spectrogram} object that supports radio spectra from the e-Callisto 
-network\footnote{e-Callisto is an international network of solar radio spectrometers, all the data is available at: \url{http://www.e-callisto.org/} } 
+SunPy aims to provide support to most of solar spectroscopy instrument, however the 
+complexity of this kind of datasets makes very challenging to add support to them all 
+in a general way.  
+Nevertheless, the \texttt{Spectra} object has been designed to be consistent with the 
+other data types available in Sunpy.
+The \texttt{Spectra} object was implemented as a wrapper around a data array (numpy ndarray)
+because a spectra is a 1D intensity versus frequency array.
+Using the \texttt{Spectra} object, Sunpy also offers a 2D array object called \textit{Spectrogram},
+which it is built as a group of spectrum meassured over time.
+These two objects were implemented by funding provided by the Astrophysics Research 
+Group at Trinity College Dublin.
+As yet, Sunpy \textit{Spectrogram} object supports radio spectra from the e-Callisto 
+network\footnote{e-Callisto is an international network of solar radio spectrometers, 
+                 all the data is available at: \url{http://www.e-callisto.org/} } 
 and STEREO/SWAVES spectrograms.
-These radio spectrograms are consecutive 1D frequency spectra measured over time.  
-However, the study of this type of spectrograms is normally driven by the variation of the spectra through time, therefore the data files normally contains a 2D array, with one axis for frequency and another for time, providing an image as the one shown in figure \ref{spectrogram:example}.
-The Spectrogram object offers some common functionality to both type of instruments to help its analysis, this includes:
-read the data (fits format for e-Callisto, ASCII for STEREO/SWAVES); 
+Like for the \texttt{Lightcurve} object, the \texttt{Spectrogram} object has been
+built so each instrument initialises it from a sub-class containing the instrument-specific 
+functionalities while offering common functionalities to them all to help its analysis, 
+this includes:
+read the data %(fits format for e-Callisto, ASCII for STEREO/SWAVES); 
 join different time ranges and frequencies; 
@@
 and point-and-click functionality to save pixels of interest for further analysis.
-In addition, this object is equipped with a download data interface for e-Callisto that only requires the observatory name and the desired time-range.
-STEREO/SWAVES can be obtained via the virtual solar observatory (see \s\ref{sec:vso}).
+In addition, this object is equipped with a download data interface for e-Callisto that 
+only requires the observatory name and the desired time-range. 
+STEREO/SWAVES data can be obtained via the virtual solar observatory (see \S\ref{sec:vso}).
+
+Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram} object retrieves
+from the online data archive the files that are between the time range specified and
+the observatory of interest.  In this case \textit{BIR} which is the code name of the
+Rosse Observatory at Birr Castle (Ireland)\footnote{\url{http://www.rosseobservatory.ie}}.
+When the data is requested using the \texttt{.from\_range} function, the object merges
+into a single spectrogram all the files downloaded, each with 15 minutes observation data 
+and in some cases with different files for different frequency ranges.  
+In the example shown here BIR observed in two frequency ranges: 20 - 90\,MHz and 55 - 355\,MHz.
+Since the data is not evenly spaced in the frequency range, the \texttt{Spectrogram} object
+linearise the frequency axis for a better analisys, as shown in the resultant figures.
+It is also shown in the example the effect of the implemented background substraction and
+plotting.
+
+\begin{listing}[h]
+\begin{minted}{python}
+from sunpy.spectra.sources.callisto import CallistoSpectrogram
+tstart = "2011-06-07T06:00:00"
+tend = "2011-06-07T07:45:00"
+callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
+callisto_nobg = callisto.substract_bg()
+callisto.peek()
+callisto_nobg.peek(vmin = 0)
+\end{minted}
+\includegraphics[width=0.8\columnwidth]{callisto} %\hfill
+\includegraphics[width=0.8\columnwidth]{callisto_nobg}
+\caption{Demonstration of how \texttt{CallistoSpectrogram} object retrieve the data
+for the time range and observatory requested, merge it all and removes the background
+signal.}
+\label{code:spectra}
+\end{listing}
 

### 2014-01-23 2-1-Map.tex

--- 2014-01-21 2-1-Map.tex
@@
 properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
-\texttt{.wavelength} or \texttt{.coordinate\_system}.
-The \texttt{Map} data type provides convenience methods for many functions 
+\texttt{.wavelength} or \texttt{.coordinate\_system}. Demonstrated in Listing 
+\ref{code:aia_1} is this meta data parsing and `pretty printing' of the Map.
+The \texttt{Map} object provides convenience methods for many functions 
 such as, rotation and re-sampling as well as convenience visualisation 
 functions, providing a easy to use as well as powerful interface.
+Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
+\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.
 
@@
 
-As can been seen in Listing \ref{code:aia_1} the map datatype parses header 
-information for many purposes including visualisation on correct physical axes 
-and limb plotting as well as making this information easily available to the 
-user.
+\texttt{GenericMap} is a subclass of \texttt{astropy.nddata.NDData} which is a 
+generic wrapper around a \texttt{ndarray} with a \texttt{.meta} attribute, like 
+\texttt{Map}. Having this inheritance structure with \texttt{astropy} provides 
+potential for simple integration with other parts of \texttt{astropy} and other 
+packages based on \texttt{astropy}, as \texttt{GenericMap} should form a 
+drop-in replacement for \texttt{NDData}.
 

### 2014-01-23 2-Data_Types.tex

@@
 \subsection{Visualisation}
+\label{subsec:Viz}
 As has been demonstrated in this section, the core SunPy datatypes include 

### 2014-01-23 3-4-Helioviewer.tex
add pdf conversions of eps figures

@@
 SunPy provides the ability to download images from Helioviewer Project 
-servers.  The aim of the Helioviewer Project is to enable the
-exploration of solar and heliospheric data from multiple data sources
-(such as instrumentation and feature/event catalogs) via easy-to-use
-visual interfaces.  The primary data provided by the Helioviewer
-Project are images in the JPEG2000 format (for further details on the
-Helioviewer Project see \cite{muller2009}\footnote{SunPy is used in Helioviewer 
-production servers to manage the download and ingestion of JPEG2000
-files from remote servers.}.)  The JPEG2000 files are typically
-highly compressed compared to the source FITS files they are generated
-from, and so can be a used as a shortcut to visualize large amounts of
-data from multiple sources.
+servers.  The aim of the Helioviewer Project is to enable the exploration of 
+solar and heliospheric data from multiple data sources (such as instrumentation 
+and feature/event catalogs) via easy-to-use visual interfaces.  The primary 
+data provided by the Helioviewer Project are images in the JPEG2000 format (for 
+further details on the Helioviewer Project see \cite{muller2009} 
+\footnote{SunPy is used in Helioviewer production servers to manage the 
+download and ingestion of JPEG2000 files from remote servers.}.)  The JPEG2000 
+files are typically highly compressed compared to the source FITS files they 
+are generated from, and so can be a used as a shortcut to visualize large 
+amounts of data from multiple sources.
 
@@
 \end{minted}
-\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
+\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304}
 \caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
@@
 \end{minted}
-\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
+\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example}
 \caption{Acquisition of a PNG image composed from data from three
@@
 \end{minted}
-\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map.eps}
+\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
 \caption{Acquisition and display of a Helioviewer JPEG2000 file as a

### 2014-01-23 1-Introduction.tex
bibliography formating and updates

@@
 \section{Introduction}
-Modern solar physics, similar to astrophysics, requires increasingly complex 
-software tools both for the retrieval as well as the analysis of data. The Sun 
-is the most well-observed star. As such, solar physics is unique in its ability 
-to access large amounts of high resolution ground- and space-based observations 
-of the Sun at many different wavelengths and spatial scales with high time 
-cadence. Modern solar physics, similar to astrophysics, therefore requires 
-increasingly complex software tools, both for the retrieval and the analysis of 
-data. For example, NASA's Solar Dynamics Observatory (SDO) satellite records 
-over 1 TB of data per day all of which is telemetered to the ground and 
-available for analysis. As a result, scientists have to process large volumes 
-of complex data products. In order to make meaningful advances in solar 
-physics, it is important for the software tools to be standardized, easy to 
-use, and transparent, so that the community can build upon a common foundation.
+Modern solar physics, similar to astrophysics, requires increasingly 
+complex software tools both for the retrieval as well as the analysis 
+of data. The Sun is the most well-observed star. As such, solar 
+physics is unique in its ability to access large amounts of high 
+resolution ground- and space-based observations of the Sun at many 
+different wavelengths and spatial scales with high time cadence. 
+Modern solar physics, similar to astrophysics, therefore requires 
+increasingly complex software tools, both for the retrieval and the 
+analysis of data. For example, NASA's Solar Dynamics Observatory 
+(SDO) satellite records over 1 TB of data per day all of which is 
+telemetered to the ground and available for analysis. As a result, 
+scientists have to process large volumes of complex data products. In 
+order to make meaningful advances in solar physics, it is important 
+for the software tools to be standardized, easy to use, and 
+transparent, so that the community can build upon a common foundation.
 
-Currently, most solar data analysis is performed with a large library of 
-routines called SolarSoft, also referred to as SSW \cite{ssw_ref}. SolarSoft is a set of integrated software 
-libraries, databases, and system utilities which provide a common programming 
-and data analysis environment for solar physics. It is overwhelmingly an 
-environment which relies upon IDL (Interactive Data Language), a commercial and 
-closed-source interactive data analysis environment sold by Exelis, a global 
-aerospace, defense, information and services company. The SSW gen package
-provides the base analysis capabilities such as time series analysis, time 
-conversions, spectral fitting, image display, and file I/O. It is composed of 
-89\% IDL code while the remainder is mostly perl (5.4\%) and csh scripts 
-(3.8\%). According to data generated using David A. Wheeler's 'SLOCCount', 
-SSW/gen is composed of 289,724 lines of code with a total approximate value of 
-\$10.4M (based on the Basic COCOMO model). Individual missions and instruments 
-provide additional optional packages to support and process their data. 
-For example, the SDO package \cite{sdo} is 100\% IDL code and is 11k lines of code (\$360k) 
-and the SOHO package \cite{soho} is 100k lines of 
-code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
-Lockheed Martin Solar and Astrophysics Laboratory.
+Currently, most solar data analysis is performed with a large library 
+of routines called SolarSoft, also referred to as SSW 
+\cite{freeland1998}. SolarSoft is a set of integrated software 
+libraries, databases, and system utilities which provide a common 
+programming and data analysis environment for solar physics. It is 
+overwhelmingly an environment which relies upon IDL (Interactive Data 
+Language), a commercial and closed-source interactive data analysis 
+environment sold by Exelis, a global aerospace, defense, information 
+and services company. The SSW gen package provides the base analysis 
+capabilities such as time series analysis, time conversions, spectral 
+fitting, image display, and file I/O. It is composed of 89\% IDL code 
+while the remainder is mostly perl (5.4\%) and csh scripts (3.8\%). 
+According to data generated using David A. Wheeler's 'SLOCCount', 
+SSW/gen is composed of 289,724 lines of code with a total approximate 
+value of \$10.4M (based on the Basic COCOMO model). Individual 
+missions and instruments provide additional optional packages to 
+support and process their data. For example, the SDO package 
+\cite{sdo} is 100\% IDL code and is 11k lines of code (\$360k) 
+and the SOHO package \cite{soho} is 100k lines of code (\$3M) and is 
+99.9\% IDL code. SSW is hosted and distributed by the Lockheed Martin 
+Solar and Astrophysics Laboratory.
 
@@
 
-While SSW is open-source and freely available, the IDL core. The cost of IDL is prohibitive
-for many undergraduates as well as institutions with limited means.
+While SSW is open-source and freely available, the IDL core. The cost 
+of IDL is prohibitive for many undergraduates as well as institutions 
+with limited means.
 
 One of SunPy's key aims is to provide a free and modern alternative 
-to the SolarSoft (gen) library. This is made possible by the recent rise of the 
-scientific Python community. Python is a general purpose high-level programming 
-language. It is free to use, cross-platform and is both an accessible and powerful
-programming language. Python is one of the top ten most popular programming languages 
-in the world according to the 2014 TIOBE Index\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
-It therefore has a very large user community which extends far outside of the solar 
-physics or astronomy communities. It is very extensible with C, C++, Fortran or 
-even IDL. Many books and on-line documentation is 
-available. For example at the time writing a search on Amazon for books 
-on IDL programming generated $189$ results while a search for Python yielded 
-$1,788$ results. Python has a strong emphasis on 
-readability a concept which is well-aligned with the scientific endeavor.
+to the SolarSoft (gen) library. This is made possible by the recent 
+rise of the scientific Python community. Python is a general purpose 
+high-level programming language. It is free to use, cross-platform 
+and is both an accessible and powerful programming language. Python 
+is one of the top ten most popular programming languages in the world 
+according to the 2014 TIOBE Index 
+\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
+It therefore has a very large user community which extends faroutside 
+of the solar physics or astronomy communities. It is very extensible 
+with C, C++, Fortran or even IDL. Many books and on-line 
+documentation is available. For example at the time writing a search 
+on Amazon for books on IDL programming generated $189$ results while 
+a search for Python yielded $1,788$ results. Python has a strong 
+emphasis on readability a concept which is well-aligned with the 
+scientific endeavor.
 Additionally, Python is increasingly being taught in universities,
@@
 language. Finally, knowledge of Python is a skill which is useful and well 
-compensated outside of the scientific community (average salary of \$110k in 
-the Washington DC area according to indeed.com at the time of writing).
-Python continues to see increased use in the astronomy community 
-\cite{2011ASPC..442..425G} which has similar goals and requirements as the solar physics
-community. Finally, Python plays well with many technologies such as web servers \cite{2008JPhCS.119d2011D}, 
-SQL databases, interactive and shareable notebook-based computing \cite{PER-GRA:2007}.
-For all of these reasons, Python is an ideal platform for a modern solar physics 
-data analysis environment.
+compensated outside of the scientific community (average salary of 
+\$110k in the Washington DC area according to indeed.com at the time 
+of writing). Python continues to see increased use in the astronomy 
+community \cite{greenfield2011} which has similar goals and 
+requirements as the solar physics community. Finally, Python plays 
+well with many technologies such as web servers \cite{dolgert2008}, 
+SQL databases, interactive and shareable notebook-based computing 
+\cite{perez2007}. For all of these reasons, Python is an ideal 
+platform for a modern solar physics data analysis environment.
 
 SunPy is built on top of the core scientific Python packages namely 
-\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core packages provide
-capabilities surpassing that provided by IDL for array manipulation and 2-d plotting
-\cite{2011ASPC..442..425G}. Providing similar capabilities as SSW/gen in Python is made
-easier by leveraging the diverse Python community. For example, SunPy makes use of 
-the \texttt{Pandas} package to provide high-performance, easy-to-use data structures and data analysis tools
-for time series data\cite{mckinney2012python}. \texttt{Pandas} was originally developed for quantitative analysis of financial
-data and has seen grown into a generalized data analysis package. SunPy also relies on 
-and is coordinating with the \texttt{Astropy} package \cite{2013A&A...558A..33A}. It is still in
-active development but already provides many relevant capabilities such as full-featured
-support for FITS files, absolute dates and time conversions, units and unit conversions,
-and model-fitting. Pandas (134k lines of code) and AstroPy (90k lines of code) allow
-SunPy to leverage a total value of \$7.6M worth of development which is close to the 
-\$10.4M for SSW/gen assuming a rough equivalency between a line of Python code and a line
-of IDL code.
+\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core 
+packages provide capabilities surpassing that provided by IDL for 
+array manipulation and 2-d plotting \cite{greenfield2011}. Providing 
+similar capabilities as SSW/gen in Python is made easier by 
+leveraging the diverse Python community. For example, SunPy makes use 
+of the \texttt{Pandas} package to provide high-performance, 
+easy-to-use data structures and data analysis tools for time series 
+data\cite{mckinney2012}. \texttt{Pandas} was originally developed for 
+quantitative analysis of financial data and has seen grown into a 
+generalized data analysis package. SunPy also relies on and is 
+coordinating with the \texttt{Astropy} package 
+\cite{theastropycollaboration2013}. It is still in active development 
+but already provides many relevant capabilities such as full-featured
+support for FITS files, absolute dates and time conversions, units 
+and unit conversions, and model-fitting. Pandas (134k lines of code) 
+and AstroPy (90k lines of code) allow SunPy to leverage a total value 
+of \$7.6M worth of development which is close to the \$10.4M for 
+SSW/gen assuming a rough equivalency between a line of Python code 
+and a line of IDL code.
 
-The design philosophy of SunPy is to provide a clean, simple to use, and well structured package that provides 
-the \textit{core} tools for solar physics. The primary focus of SunPy's 
-development early development is to provide specialised, linked, datatypes 
-that allow the import, processing and visualisation of all types of solar data. These include \texttt{Map}, 
-\texttt{LightCurve} and \texttt{Spectrum}, these cover spatial, timeseries and spectral data  
+The design philosophy of SunPy is to provide a clean, simple to use, 
+and well structured package that provides the \textit{core} tools for 
+solar physics. The primary focus of SunPy's development early 
+development is to provide specialised, linked, datatypes that allow 
+the import, processing and visualisation of all types of solar data. 
+These include \texttt{Map}, \texttt{LightCurve} and 
+\texttt{Spectrum}, these cover spatial, timeseries and spectral data  
 respectively.
 
-The purpose of this paper is to provide an overview of SunPy's current 
-capabilities, an overview of the development model and community aspects of the 
-SunPy project as well as future plans. The latest release of SunPy is available 
-in PyPI and can be installed in the usual manner.
-
-%citations
-% 2013A&A...558A..33A http://adsabs.harvard.edu/abs/2013A&A...558A..33A astropy
-% 2011ASPC..442..425G http://adsabs.harvard.edu/abs/2011ASPC..442..425G greenfield2011
-% 2013ApJ...763...86L  http://adsabs.harvard.edu/abs/2013ApJ...763...86L chianti
-%@book{mckinney2012python,
-%  title={Python for Data Analysis: Data Wrangling with Pandas, NumPy, and IPython},
-%  author={McKinney, W.},
-%  isbn={9781449323615},
-%  url={http://books.google.com/books?id=v3n4\_AK8vu0C},
-%  year={2012},
-%  publisher={O'Reilly Media}
-%}
-% 2008JPhCS.119d2011D http://adsabs.harvard.edu/abs/2008JPhCS.119d2011D rapid web development in python
-%@Article{PER-GRA:2007,
-%  Author    = {P\'erez, Fernando and Granger, Brian E.},
-%  Title     = {{IP}ython: a System for Interactive Scientific Computing},
-%  Journal   = {Computing in Science and Engineering},
-%  Volume    = {9},
-%  Number    = {3},
-%  Pages     = {21--29},
-%  month     = may,
-%  year      = 2007,
-%  url       = "http://ipython.org",
-%  ISSN      = "1521-9615",
-%  doi       = {10.1109/MCSE.2007.53},
-%  publisher = {IEEE Computer Society},
-%}
+The purpose of this paper is to provide an overview of SunPy's 
+current capabilities, an overview of the development model and 
+community aspects of the SunPy project as well as future plans. The 
+latest release of SunPy is available in PyPI and can be installed in 
+the usual manner.

### 2014-01-23 5-Dev.tex
bibliography formating and updates

@@
 distributed 
-version control software git. \footnote{\url{http://git-scm.com/}}
+version control software \href{http://git-scm.com/}{git}.
 

### 2014-01-23 2-Data_Types.tex
bibliography formating and updates
fix astropy ref

@@
 \texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
-\texttt{LightCurve} respectively. Each data type has a \texttt{.data} attribute 
-where this data object is located and some meta data. It is possible to 
-instantiate the data types from various different sources, \textit{e.g.} files, 
-urls, arrays or time ranges. The specific sources supported is dependant upon 
-which data type and which instrument. All the SunPy data types support 
-specialisation on a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
-\texttt{AIAMap} sub-type. This design allows simple extensions to cope with the 
-diversity of data from different sources in solar physics. As well as support 
-for different instruments and data sources each data type supports different 
-visualisation wrappers that allow both quick view plotting (the peek command) 
-and more fine-grained control plotting that integrates well with 
+\texttt{LightCurve} respectively. Each data type has a \texttt{.data} 
+attribute where this data object is located and some meta data. It is 
+possible to instantiate the data types from various different 
+sources, \textit{e.g.} files, urls, arrays or time ranges. The 
+specific sources supported is dependant upon which data type and 
+which instrument. All the SunPy data types support specialisation on 
+a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
+\texttt{AIAMap} sub-type. This design allows simple extensions to 
+cope with the diversity of data from different sources in solar 
+physics. As well as support for different instruments and data 
+sources each data type supports different visualisation wrappers that 
+allow both quick view plotting (the peek command) and more 
+fine-grained control plotting that integrates well with 
 \texttt{matplotlib} (the plot command).
@@
 \label{subsec:Viz}
-As has been demonstrated in this section, the core SunPy datatypes include 
-visualisation code that is specialised to that data type. These visualisation 
-methods all currently utilise the matplotlib package, and are designed in such 
-a way that they integrate well with the pyplot functional interface of 
-matplotlib, as demonstrated in Listing \ref{code:mpl_1}.
+As has been demonstrated in this section, the core SunPy datatypes 
+include visualisation code that is specialised to that data type. 
+These visualisation methods all currently utilise the matplotlib 
+package, and are designed in such a way that they integrate well with 
+the pyplot functional interface of matplotlib, as demonstrated in 
+Listing \ref{code:mpl_1}.
 
-\begin{listing}[h]
+\begin{listing}[H]
 \begin{minipage}{0.49\columnwidth}
@@
 
-This design philosophy makes the behaviour of SunPy's visualisation routines 
-intuitive to those who already understand how matplotlib's interface is 
-designed as well as allowing the use of the standard matplotlib commands to 
-change the plot, \textit{e.g.} set the title. 
-More technically what is done in the plotting routines is firstly, to make sure 
-that the current state of the figure and axes is mantined in the same way as it 
-is inside the \texttt{pyplot} functions. For \texttt{Map} this means setting 
-\texttt{pyplot.sci()} or set current image, so that \texttt{plt.colorbar()} 
-automatically detects the plotted \texttt{AxesImage} object. Secondly, it also 
-means returning the same type of object as the \texttt{pyplot} interfaces 
-function, \textit{i.e.} for \texttt{Map} it returns the \texttt{AxesImage} 
-instance which is the same type of return as \texttt{pyplot.imshow}.
+This design philosophy makes the behaviour of SunPy's visualisation 
+routines intuitive to those who already understand how matplotlib's 
+interface is designed as well as allowing the use of the standard 
+matplotlib commands to change the plot, \textit{e.g.} set the title. 
+More technically what is done in the plotting routines is firstly, to 
+make sure that the current state of the figure and axes is mantined 
+in the same way as it is inside the \texttt{pyplot} functions. For 
+\texttt{Map} this means setting \texttt{pyplot.sci()} or set current 
+image, so that \texttt{plt.colorbar()} 
+automatically detects the plotted \texttt{AxesImage} object. 
+Secondly, it also means returning the same type of object as the 
+\texttt{pyplot} interfaces function, \textit{i.e.} for \texttt{Map} 
+it returns the \texttt{AxesImage} instance which is the same type of 
+return as \texttt{pyplot.imshow}.

### 2014-01-24 3-5-Database.tex
bibliography formating and updates
more prose than lists. explained the benefits and less the underlying code.

@@
 that has been retrieved via packages from the net package. Note that currently
-only the VSO package is supported, not the HEK package.
+only the \textsc{VSO} package is supported, not the HEK package. It is also
+possible to add entries by file or directory which is especially useful when
+\textsc{FITS} files already exist on the user's local hard drive. This
+facilitates the transition to using the database package for users who have
+been using the \textsc{VSO} package isolated before.
 
-The need for a database package arose because using VSO alone led to two major
-problems:
+The need for a database package arose because using \textsc{VSO} alone led to
+two major problems:
+
 \begin{enumerate}
@@
 
-Here is a list of the main features:
-\begin{itemize}
-  \item detects if certain query has already been used before and queries
-    the database then instead of the VSO
-  % TODO: reference to SA docs? or list all currently supported SQL dialects here?
-  \item many supported SQL dialects
-  % TODO: footnotes for LRU/LFU or some explanation in parens behind them?
-  \item database may act as a Cache (algorithm may be LRU, LFU or a custom one)
-  \item all writing operations can be undone and redone
-\end{itemize}
+Because the Python library SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}
+is used, many SQL dialects are supported. Using a file-based SQLite database
+has the advantage of being easy to set up (the file will be created
+automatically, so the user doesn't have to configure anything beforehand).
+It is also handy to be passed around because all the database entries are just
+in one single file. A server-based database, on the other hand, is the better
+option for collaborative teams who work together from different machines on the
+same data: a central database server stores all data and the clients connect to
+it to read or write data.
 
-Using the database package, one uses the Database class to connect with a
-database and perform operations on it.
+Each database is a cache with a certain size limit (the size is determined by
+the number of saved database entries). If no cache size is given, it is per
+default $\infty$, which in practice means that caching is disabled then. There
+are two builtin caching algorithm to choose from (LRU\footnote{Least Recently
+Used}, LFU\footnote{Least Frequently Used}) but it's also possible to implement
+a custom algorithm.
+
+To solve the second problem that was mentioned above, the database saves all
+queries which have been sent to the \textsc{VSO} to add new entries. If a query
+has already been used once and the \texttt{fetch} method of the \texttt{Database}
+class is called, the database is queried instead of the \textsc{VSO}. This
+reduces bandwidth and is especially advantageous if there are big files behind
+the query or if the query results in a big list of files.
+
+A very special feature of the database package is the support to \texttt{undo}
+and \texttt{redo} all writing operations. This is particularly convenient in
+interactive sessions of the Python interpreter to revert accidental operations
+easily. But looking ahead, this feature will also be desired when creating a
+frontend for this package, for example a graphical user interface
+(\textsc{GUI}).
+
+Using the database package, one uses the \texttt{Database} class to connect
+with a database and perform operations on it.
 
@@
 following code example, listing \ref{code:db_2}, that indeed the entries can
-be grouped to two results.
+be grouped to two results. The reason for six entries in the database is that
+these RHESSI files have three headers each in this case, so the total number of
+FITS headers is $2 \times 3 = 6$ headers.
 
@@
 \end{listing}
-
-As said before, the database can be used as a cache. By default, the size of
-the cache is not limited which in other words means that caching is disabled.
-To limit the number of database entries to a certain number a posteriori, use
-the method \texttt{set\_cache\_size} and pass it the number of maximum entries.
-The default algorithm to remove entries from the cache is \textsc{LRU}
-(least recently used), i.e. the item whose usage is farthest away is removed
-first.  % FIXME is 'whose' correct here? ^

### 2014-01-24 3-1-VSO.tex

@@
 VSO allows to query data not just by instrument or mission for 
-a time range but by physical physical variables as for example:
+a time range but by physical variables as for example:
 intensity, magnetic field, particle flux or spectral range to name a few.
@@
 
-The \texttt{vso} module includes advances features through the use
+The \texttt{vso} module includes advanced features through the use
 of VSO attributes objects.  
@@
 
-The \texttt{vso} module also provides of an interface to download the data,
+The \texttt{vso} module also provides an interface to download the data,
 allowing to customise the directory structure to save the data.

### 2014-01-24 3-2-HEK.tex

@@
 the HEK API
-(http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print).
+(\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
 Every event type has required and optional properties; the current
 list of events maintained by the HEK and their properties can be found
-at http://www.lmsal.com/hek/VOEvent_Spec.html.
+at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
@@
 letter strings, and are identical to the two letter abbreviations
-found at the HEK website, http://www.lmsal.com/hek/VOEvent_Spec.html.
+found at the HEK website, \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
-\begin{listing}
+\begin{listing}[H]
 \begin{minted}{python}
@@
 tend = '2011/08/09 12:40:29'
-event_type = 'FL'
-result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type))
+event\_type = 'FL'
+result = client.query(hek.attrs.Time(tstart,tend), 
+hek.attrs.EventType(event\_type))
 \end{minted}
@@
 to return only those events that have the FRM 'SSW Latest Events'.
-\begin{listing}
+\begin{listing}[H]
 \begin{minted}{python}
-result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), hek.attrs.FRM.Name == 'SSW Latest Events')
+result = client.query(hek.attrs.Time(tstart,tend), 
+hek.attrs.EventType(event\_type), hek.attrs.FRM.Name == 'SSW Latest Events')
 \end{minted}
@@
 and are described at the HEK website).
-\begin{listing}
+\begin{listing}[H]
 \begin{minted}{python}
-result = client.query(hek.attrs.Time(tstart,tend), hek.attrs.EventType(event_type), (hek.attrs.Event.Coord1 > 50) or (hek.attrs.FL.PeakFlux > 1000.0) )
+result = client.query(hek.attrs.Time(tstart,tend), 
+hek.attrs.EventType(event\_type), (hek.attrs.Event.Coord1 > 50) or 
+(hek.attrs.FL.PeakFlux > 1000.0) )
+\end{minted}
 \caption{HEK query using the 'or' operator.}
@@
 All FRMs report the required feature attributes (as described at
-http://www.lmsal.com/hek/VOEvent_Spec.html), but the optional
+\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional
 attributes are FRM dependent.  If a FRM does not have one of the

### 2014-01-24 3-3-HELIO.tex

@@
 This service provides at the moment access to 84 catalogues from different
-sources (automated and manual classification, event lists from publications, \cdot).
+sources (automated and manual classification, event lists from publications, \ldots).
 HEC results (as the rest of HELIO services) provides the results in VOTable 
 data format (defined by IVOA \cite{ochsenbein_ivoa_2011})
-which the \textttt{astropy.io.votable} can interact with.
+which the \texttt{astropy.io.votable} can interact with.
 This format has the advantage of contain metadata with information like
@@
 >>> print catalogues_event
+******** This need to be added!
 
 Query all the catalogues that comes from cactus
->>> results = [hc.time_query(tstart, tend, event) for event in catalogues_event if 'cactus' in event]
+>>> results = [hc.time_query(tstart, tend, event) 
+...            for event in catalogues_event if 'cactus' in event]
 >>> print results

### 2014-01-24 6-Future.tex

@@
 \section{Future of SunPy}
-SunPy as a project has existed for roughly three years. In this time the code 
-base has grown to over 110,000 lines. SunPy in it's current form is a useful 
-package for the analysis of calibrated solar data, however, the code base is 
+SunPy as a project has existed for roughly three years. In this time 
+the code 
+base has grown to over 110,000 lines. SunPy in it's current form is a 
+useful 
+package for the analysis of calibrated solar data, however, the code 
+base is 
 still very changeable from release to release.
@@
 As discussed in Section \ref{sec:Intro}, the primary focus of the 
-\texttt{sunpy} library is the analysis and visualisation of `high level' solar 
-data. This means data that has been put through instrument processing and 
-calibration routines, and contains full (WCS) coordinate information. The 
-development plan for SunPy is to continue development within this scope. The 
-primary components of this plan are to provide a set of data types that are 
-interchangeable with one another, \textit{i.e.} if you slice a \texttt{MapCube} 
-along one coordinate a \texttt{LightCurve} of intensity along the time range of 
-the \texttt{MapCube} should be returned. To achieve this goal all the data 
-types need to share a unified coordinate system architecture so that each data 
-type is aware of what the physical type of it's data is and how operations on 
+\texttt{sunpy} library is the analysis and visualisation of `high 
+level' solar 
+data. This means data that has been put through instrument processing 
+and 
+calibration routines, and contains full (WCS) coordinate information. 
+The 
+development plan for SunPy is to continue development within this 
+scope. The 
+primary components of this plan are to provide a set of data types 
+that are 
+interchangeable with one another, \textit{i.e.} if you slice a 
+\texttt{MapCube} 
+along one coordinate a \texttt{LightCurve} of intensity along the 
+time range of 
+the \texttt{MapCube} should be returned. To achieve this goal all the 
+data 
+types need to share a unified coordinate system architecture so that 
+each data 
+type is aware of what the physical type of it's data is and how 
+operations on 
 that data should be performed.
 
-In concert with the work on the data types further integration with the 
-\texttt{astropy} package will enable SunPy to inherit the large amounts of work 
-done in that project to support a platform for astronomical data analysis. For 
-example the \texttt{astropy.units} submodule provides a simple and efficient 
-way of representing physical units in Python data types, there are plans to 
-incorporate this widely in the SunPy code-base. In the past 12 months the 
-collaboration with the Astropy project \cite{theastropycollaboration2013} and 
-it's community has grown, this direct collaboration between Astropy and 
+In concert with the work on the data types further integration with 
+the 
+\texttt{astropy} package will enable SunPy to inherit the large 
+amounts of work 
+done in that project to support a platform for astronomical data 
+analysis. For 
+example the \texttt{astropy.units} submodule provides a simple and 
+efficient 
+way of representing physical units in Python data types, there are 
+plans to 
+incorporate this widely in the SunPy code-base. In the past 12 months 
+the 
+collaboration with the Astropy project 
+\citep{theastropycollaboration2013} and 
+it's community has grown, this direct collaboration between Astropy 
+and 
 SunPy will be one of the key strengths of SunPy going forward.

### 2014-01-24 4-Util.tex
added code example for wcs package and tidying up of text

--- 2014-01-20 4-Util.tex
@@
 are used by the other SunPy modules and are made available to the user. Two 
-modules are described in this Section, namely, solar coordinates (coords), and 
+modules are described in this Section, namely, solar coordinates (wcs), and 
 the Sun module (sun).
 
-\subsection{Coordinates}
+\subsection{WCS Coordinates}
 Coordinate transformations are frequently a necessary task within the solar 
@@
 different solar features. This type of transformation is not unique
-to solar observations (e.g. planetary) but it is not provided by the Astropy 
-coordinates package. The coordinates package implements the World Coordinate 
-System (WCS) for solarcoordinates as described by \cite{Thompson2000}. The 
-coordinate system transformations currently implemented as those most useful 
+to solar observations (e.g. planetary) but is not often considered by astronomical packages
+such as the Astropy 
+coordinates package. The wcs package implements the World Coordinate 
+System (WCS) for solar coordinates as described by \cite{Thompson2000}. The 
+coordinate system transformations currently implemented are those most useful 
 for most solar data analysis, namely converting from Helioprojective-Cartesian 
-(HPC) to Heliographic coordinates (HG). HPC which describes the positions on 
+(HPC) to Heliographic coordinates (HG). HPC describes the positions on 
 the Sun as angles measured from the center of the solar disk (usually in 
-arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
+arcseconds) using cartesian coordinates (X, Y). This is the coordinates 
 most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). 
 HG coordinates express positions on the Sun using longitude and latitude on 
-the 
-solar sphere. There are two standards for this coordinate system, 
+the solar sphere. There are two standards for this coordinate system, 
 Stonyhurst-Heliographic where the origin is at the intersection of the solar 
 equator and the central meridian as seen from Earth and 
-Carrington-Heliographic 
-is a system which is fixed to the Sun and does not depend on Earth. The 
-implementation of these transformations pass through common coordinate system 
+Carrington-Heliographic is a system which is fixed to the Sun and does not depend on Earth. The 
+implementation of these transformations pass through a common coordinate system 
 called Heliocentric-Cartesian (HCC) where positions are expressed in true 
@@
 These transformations require some knowledge of the location of the observer 
-which is usually provided by the image header information. In case where it is 
-not, the observer is assumed to be at Earth.
+which is usually provided by the image header . In case where it is 
+not, the observer is assumed to be at Earth. An example of the
+
+\begin{listing}[H]
+\begin{minted}{pycon}
+>>> from sunpy import wcs
+Find the helioprojective coordinate of a given longitude and latitude on the Sun
+>>> wcs.convert_hg_hpc(10,53)
+(100.49244115330731, 767.97438321917502)
+Convert that position back to heliographic coordinates
+>>> wcs.convert_hpc_hg(100.49, 767.97)
+(9.9996521808465175, 52.999563684874893)
+Try to convert a position which is not on the Sun to heliographic coordinates
+>>> wcs.convert_hpc_hg(-1500,0)
+sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
+  distance = q - np.sqrt(distance)
+(nan, nan)
+Convert sky coordinate to a position on the Sun in cartesian coordinates (HCC)
+>>> wcs.convert_hpc_hcc(-300,400, z = True)
+(-216716967.63331246, 288956420.9477042, 594364636.2208252)
+\end{minted}
+\caption{Using the sunpy.wcs sub-package.}
+\label{code:wcs_code}
+\end{listing}
 
 \subsubsection{Sun}
-The purpose of this module is to provide solar-specific data
+The purpose of this module is to provide solar-specific data for example ephemeris and
+solar constants. The main namespace contains a number of functions which provide solar
+ephemeris such as the sun to earth distance, solar cycle number, the mean anomaly, etc.
+All of these functions take a time as their input which can be provided in any 
+parse\_time
+compatible format. 
+A future version of SunPy will integrate with the AstroPy coordinates package and will 
+likely make use of an ephemeris package.
 
@@
 Numpy's ndarray, they work well with standard representations of numbers.
-For convenience a number shortcuts to frequently used constants are provided 
+For convenience a number of shortcuts to frequently used constants are provided 
 directly when importing the sub-package. A larger list of constants can be 
@@
 package and are available as a dictionary called \texttt{physical\_constants}. 
-To view all quickly a \texttt{print\_all()} function is available.
+To view them all quickly a \texttt{print\_all()} function is available.
 
-\begin{listing}[h]
+\begin{listing}[H]
 \begin{minted}{pycon}
@@
 \end{minted}
-\caption{Using sunpy.sun.constants sub-package.}
+\caption{Using the sunpy.sun.constants sub-package.}
 \label{code:constants_code}

### 2014-01-24 1-Introduction.tex
added some comments as footnote and converted to British English spealling

@@
 different wavelengths and spatial scales with high time cadence. 
-Modern solar physics, similar to astrophysics, therefore requires 
+Solar physics therefore requires
 increasingly complex software tools, both for the retrieval and the 
@@
 order to make meaningful advances in solar physics, it is important 
-for the software tools to be standardized, easy to use, and 
+for the software tools to be standardised, easy to use, and 
 transparent, so that the community can build upon a common foundation.
@@
 libraries, databases, and system utilities which provide a common 
-programming and data analysis environment for solar physics. It is 
+programming and data analysis environment for solar physics. 
+SSW is structured by a package system which contains
+specialised software for different instrument or tools, 
+allowing the installation of just the needed packages.
+It is 
 overwhelmingly an environment which relies upon IDL (Interactive Data 
@@
 fitting, image display, and file I/O. It is composed of 89\% IDL code 
-while the remainder is mostly perl (5.4\%) and csh scripts (3.8\%). 
-According to data generated using David A. Wheeler's 'SLOCCount', 
+while the remainder is mostly perl (5.4\%) and csh scripts (3.8\%)
+\footnote{{\bf This data was calculated using...}}. 
+According to data generated using David A. Wheeler's 'SLOCCount'\footnote{
+\url{http://www.dwheeler.com/sloccount/}}, 
 SSW/gen is composed of 289,724 lines of code with a total approximate 
-value of \$10.4M (based on the Basic COCOMO model). Individual 
+value of \$10.4M (based on the Basic COCOMO model \cite{_cocomo_2014}).
+\footnote{{\bf This data was calculated using...} If we can add them to the
+repository will improve the quality of the paper and we can always repeat the calculation in the future}. 
+Individual 
 missions and instruments provide additional optional packages to 
@@
 Solar and Astrophysics Laboratory.
-
+\footnote{Do we know whether they have some licence owning it? do we know the solarsoft licence at all?}
 %The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
-
-While SSW is open-source and freely available, the IDL core. The cost 
+While SSW is open-source and freely available, the IDL core is not. The cost 
 of IDL is prohibitive for many undergraduates as well as institutions 
@@
 according to the 2014 TIOBE Index 
-\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
+\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}}.
 It therefore has a very large user community which extends faroutside 
@@
 documentation is available. For example at the time writing a search
+\footnote{We need to be careful with this! IDL means more things that
+our beloved ``Interactive Data Language''. If we search for that
+and programming then we get just 7 books! - from which 5 are just the same.
+I don't know how we could make a more accurate search.
+If we script it it would be amazing!  Also, I would just provide the order
+of magnitude, and not a exact number, i.e. 190 and 1800 results} 
 on Amazon for books on IDL programming generated $189$ results while 
-a search for Python yielded $1,788$ results. Python has a strong 
+a search for Python yielded $1\,788$ results. Python has a strong 
 emphasis on readability a concept which is well-aligned with the 

### 2014-01-24 1-Introduction.tex
spellchecked now and changed the use of import for acquisition

@@
 Language), a commercial and closed-source interactive data analysis 
-environment sold by Exelis, a global aerospace, defense, information 
+environment sold by Exelis, a global aerospace, defence, information 
 and services company. The SSW gen package provides the base analysis 
@@
 fitting, image display, and file I/O. It is composed of 89\% IDL code 
-while the remainder is mostly perl (5.4\%) and csh scripts (3.8\%)
+while the remainder is mostly Perl (5.4\%) and csh scripts (3.8\%)
 \footnote{{\bf This data was calculated using...}}. 
@@
 Solar and Astrophysics Laboratory.
-\footnote{Do we know whether they have some licence owning it? do we know the solarsoft licence at all?}
+\footnote{Do we know whether they have some licence owning it? do we know the SolarSoft licence at all?}
 %The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
@@
 \footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}}.
-It therefore has a very large user community which extends faroutside 
+It therefore has a very large user community which extends far outside 
 of the solar physics or astronomy communities. It is very extensible 
-with C, C++, Fortran or even IDL. Many books and on-line 
+with C, C++, FORTRAN or even IDL. Many books and on-line 
 documentation is available. For example at the time writing a search
@@
 emphasis on readability a concept which is well-aligned with the 
-scientific endeavor.
+scientific endeavour.
 Additionally, Python is increasingly being taught in universities,
@@
 quantitative analysis of financial data and has seen grown into a 
-generalized data analysis package. SunPy also relies on and is 
+generalised data analysis package. SunPy also relies on and is 
 coordinating with the \texttt{Astropy} package 
@@
 and unit conversions, and model-fitting. Pandas (134k lines of code) 
-and AstroPy (90k lines of code) allow SunPy to leverage a total value 
+and Astropy (90k lines of code) allow SunPy to leverage a total value 
 of \$7.6M worth of development which is close to the \$10.4M for 
@@
 development is to provide specialised, linked, datatypes that allow 
-the import, processing and visualisation of all types of solar data. 
+the acquisition, processing and visualisation of all types of solar data. 
 These include \texttt{Map}, \texttt{LightCurve} and 

### 2014-01-24 2-Data_Types.tex
Some edits to datatypes

@@
 (\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
-(\texttt{Spectrum} and \texttt{Spectra}).
+(\texttt{Spectrum} and \texttt{Spectrogram}).
 
 The design of SunPy's core data types is as a wrapper around a data object, 
-either a \texttt{numpy} \texttt{ndarray} or a \texttt{pandas} 
-\texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
-\texttt{LightCurve} respectively. Each data type has a \texttt{.data} 
+either a \texttt{numpy} \texttt{ndarray} -- for \texttt{Map} and \texttt{Spectra} -- or a \texttt{pandas} \texttt{DataFrame} -- for \texttt{LightCurve}.
+ Each data type has a \texttt{.data} 
 attribute where this data object is located and some meta data. It is 
@@
 which instrument. All the SunPy data types support specialisation on 
-a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
+a per-instrument basis, \textit{i.e.} \texttt{Map} has an 
 \texttt{AIAMap} sub-type. This design allows simple extensions to 
@@
 physics. As well as support for different instruments and data 
-sources each data type supports different visualisation wrappers that 
+sources each data type provides different visualisation wrappers that 
 allow both quick view plotting (the peek command) and more 

### 2014-01-24 2-1-Map.tex
Added bg for listing in main and map files, plus few typos fixed.  Also reorderd some sentence into s/c launch

@@
 \texttt{ndarray}) and gives easy access to standard meta data in the header of 
-the image, via the \texttt{.meta} attribute as well as some convienience 
+the image, via the \texttt{.meta} attribute as well as some convenience 
 properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
@@
 such as, rotation and re-sampling as well as convenience visualisation 
-functions, providing a easy to use as well as powerful interface.
+functions, providing an easy to use as well as powerful interface.
 Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
@@
 subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
-following instruments: \textit{IRIS} SJI frames, \textit{SDO/AIA} and 
-\textit{HMI}, \textit{SOHO/EIT} and	\textit{LASCO}, \textit{STEREO/EUVI} and 
-\textit{COR}, \textit{YOHKOH/SXT}, \textit{RHESSI}, \textit{PROBA2/SWAP} and 
-\textit{HINODE/XRT}.
+following instruments: 
+\textit{YOHKOH/SXT},\textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
+\textit{STEREO/EUVI} and \textit{COR}, \textit{HINODE/XRT},
+\textit{PROBA2/SWAP}, \textit{SDO/AIA} and \textit{HMI}, 
+and \textit{IRIS} SJI frames.
 
@@
 \begin{listing}[H]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 
@@
 
->>> aia.peek()
+>>> aiamap.peek()
 \end{minted}
 \includegraphics[width=0.8\columnwidth]{aia_map_example}
-\caption{Demonstration of the \texttt{AIAMap} specilisation of 
-\texttt{GenericMap}. The Map is created from a \textit{AIA} FITS file and the 
+\caption{Demonstration of the \texttt{AIAMap} specialisation of 
+\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file and the 
 key meta data and array overview is printed. Then a quick view plot is created 
@@
 collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
-temporally and spatially aligned data respectively. \texttt{MapCube} 
-provides methods for animation of its series of \texttt{Map} objects. 
+temporally and spatially aligned data respectively.
 \texttt{CompositeMap} provides methods for overlaying spatially aligned 
@@
 upon each other.
+\texttt{MapCube} 
+provides methods for animation of its series of \texttt{Map} objects. 
+Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
+with these classes.
+In addition, Listing~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
+classes interacts with the \texttt{animation} module to save a video.
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 import matplotlib.pyplot as plt
@@
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 import sunpy.map
@@
 \begin{listing}[h]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 import sunpy.map

### 2014-01-24 2-3-Spectra.tex
Spectra with bg colours and some minor corrections

@@
 An spectrum is normally obtained by observing a range of frequencies at the same time; 
-An spectrum can be measured for example in radio wavelengths by a frequency sweep with 
+it can be measured for example in radio wavelengths by a frequency sweep with 
 a radio receiver or in visible and ultraviolet by the dispersion of the incident light 
@@
 The analysis of the resultant spectrum can provide properties of the plasma observed 
-such temperature, density, speed and other kinematics can be obtained. 
+such temperature, density, speed, etc.
 Therefore, spectroscopy provides to the solar physicists invaluable information about 
@@
 other data types available in Sunpy.
-The \texttt{Spectra} object was implemented as a wrapper around a data array (numpy ndarray)
-because a spectra is a 1D intensity versus frequency array.
-Using the \texttt{Spectra} object, Sunpy also offers a 2D array object called \textit{Spectrogram},
+It was implemented as a wrapper around a data array (numpy ndarray)
+because its 1D nature (intensity versus frequency).
+Using the \texttt{Spectra} object, Sunpy also offers a 2D array object called \texttt{Spectrogram},
 which it is built as a group of spectrum meassured over time.
@@
 Group at Trinity College Dublin.
-As yet, Sunpy \textit{Spectrogram} object supports radio spectra from the e-Callisto 
+As yet, Sunpy \texttt{Spectrogram} object supports radio spectra from the e-Callisto 
 network\footnote{e-Callisto is an international network of solar radio spectrometers, 
@@
 Like for the \texttt{Lightcurve} object, the \texttt{Spectrogram} object has been
-built so each instrument initialises it from a sub-class containing the instrument-specific 
+built so each instrument initialises from a sub-class containing the instrument-specific 
 functionalities while offering common functionalities to them all to help its analysis, 
 this includes:
-read the data %(fits format for e-Callisto, ASCII for STEREO/SWAVES); 
+read the data; %(fits format for e-Callisto, ASCII for STEREO/SWAVES); 
 join different time ranges and frequencies; 
@@
 from the online data archive the files that are between the time range specified and
-the observatory of interest.  In this case \textit{BIR} which is the code name of the
+the observatory of interest.  In this case the data is requested from \textit{BIR} which is the code name of the
 Rosse Observatory at Birr Castle (Ireland)\footnote{\url{http://www.rosseobservatory.ie}}.
@@
 It is also shown in the example the effect of the implemented background substraction and
-plotting.
+\texttt{.peek} method.
 
-\begin{listing}[h]
-\begin{minted}{python}
+\begin{listing}[H]
+\begin{minted}[bgcolor=bg]{python}
 from sunpy.spectra.sources.callisto import CallistoSpectrogram

### 2014-01-24 3-1-VSO.tex

@@
 \begin{listing}[h]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.net import vso
@@
 \begin{listing}[h]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> pathformat = '/data/{instrument}/{detector}/{file}.fits'

### 2014-01-24 2-2-Lightcurve.tex

@@
 
-Time series data and analyses are a fundamental aspect of solar physics for which many data sources are available.
-In recognition of this fact, SunPy provides a \textit{Lightcurve} object designed to provide a convenient and consistent interface for handling solar time series data.
-The main engine behind the \textit{Lightcurve} object is the \textit{pandas} data analysis library.
-This library contains a large amount of functionality for manipulating and analysing time series data, making it an ideal basis for \textit{Lightcurve}.
-Like all other SunPy objects, \textit{Lightcurve} is a wrapper around a data object, which in this case is the \textit{pandas} object.
+Time series data and analyses are a fundamental aspect of solar physics 
+for which many data sources are available. 
+In recognition of this fact, SunPy provides a \texttt{LightCurve} object 
+designed to provide a convenient and consistent interface for handling 
+solar time series data. 
+The main engine behind the \texttt{LightCurve} object is the \texttt{pandas} 
+data analysis library. 
+This library contains a large amount of functionality for manipulating 
+and analysing time series data, making it an ideal basis for 
+\texttt{LightCurve}.  
+Like all other SunPy objects, \texttt{LightCurve} is a wrapper around 
+a data object, which in this case is the \texttt{pandas} object.
 
-Currently, the \textit{Lightcurve} object is compatible with the following data sources; the GOES X-ray Sensor (XRS), the SDO EUV Variability Experiment (EVE), and PROBA2/LYRA.
-For each of these instruments, a sub-class of the \textit{Lightcurve} object is initialized (e.g.
-\textit{GOESLightCurve, LYRALightCurve}) which inherits from \textit{Lightcurve} but allows instrument-specific functionality to be included.
-Future developments will introduce support for additional instruments and data products.
-Since time series data is generally relatively small and there is no established standard as to how it should be stored and distributed, each SunPy \textit{Lightcurve} object provides the ability to download its own data in its constructor.
+Currently, the \texttt{LightCurve} object is compatible with the following 
+data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, 
+and the SDO EUV Variability Experiment (EVE). 
+For each of these instruments, a sub-class of the \texttt{LightCurve} object 
+is initialised (e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits 
+from \texttt{LightCurve} but allows instrument-specific functionality to be 
+included. 
+Future developments will introduce support for additional instruments and data 
+products. 
+Since time series data is generally relatively small and there is no 
+established standard as to how it should be stored and distributed, 
+each SunPy \texttt{LightCurve} object provides the ability to download 
+its own data in its constructor.
 
-\subsubsection{Creating and using Lightcurves}
+%\subsubsection{Creating and using Lightcurves}
 
-A \textit{Lightcurve} object may be created using a range of different methods. 
-Firstly, a \textit{Lightcurve} may be created for a specific instrument based 
-on an input time range (see Listing \ref{goes_lc_code} below). In this example, 
-the Lightcurve constructor searches remote sites for the GOES X-ray data 
+A \texttt{LightCurve} object may be created using a range of different methods. 
+Firstly, a \texttt{LightCurve} may be created for a specific instrument based 
+on an input time range. In Listing \ref{code:goes_lc_code}, 
+the LightCurve constructor searches remote sites for the GOES X-ray data 
 specified by the time interval, downloads the required files and subsequently 
-creates the object (see also Listing \ref{goes_lc_code}).
+creates the object.
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy import lightcurve
 >>> goes=lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-'2011-06-07 08:00')
+...                                       '2011-06-07 08:00')
 >>> goes.peek()
@@
 \includegraphics[width=14cm]{goes_lightcurve.pdf}
-\label{goes_lc_code}
 \caption{Creating a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
-2011 June 7 using a time range, and the result of the \texttt{peek()} command.}
+2011 June 7 using a time range, and the result of the \texttt{peek()} method.}
+\label{code:goes_lc}
 \end{listing}
@@
 Alternatively, if the data file already exists on the local system, the 
-\textit{Lightcurve} object may instead be initialized using that file as input 
-(see Listing \ref{lyra_lc_code}).
+\texttt{Lightcurve} object may instead be initialised using that file as input 
+(see Listing \ref{code:lyra_lc}).
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy import lightcurve
@@
 \includegraphics[width=14cm]{lyra_lightcurve.pdf}
-\label{lyra_lc_code}
 \caption{Creating a LYRA lightcurve for the full day of 2011 June 7 using an 
-existing data file, and the result of the \texttt{peek()} command}
+existing data file, and the result of the \texttt{peek()} method}
+\label{code:lyra_lc}
 \end{listing}
 
-Once the \textit{Lightcurve} has been created it may be manipulated in a variety of ways in order to perform time series analysis.
-Continuing from the above, we show a few simple examples of using a LYRA lightcurve.
+Once the \texttt{Lightcurve} has been created it may be manipulated in 
+a variety of ways in order to perform time series analysis. 
+Continuing from Listing~\ref{code:lyra_lc}, we show a few simple 
+examples of using a LYRA lightcurve.
 
-In the above case (Listing \ref{lyra_lc_code}), we created a LYRA Lightcurve spanning the full day of 2011 June 7.
-To extract the sub-interval 06:00 - 07:00 UT into a new \textit{Lightcurve} called \verb|lyra_zoom| we simply do the following:
+In Listing~\ref{code:lyra_lc} we created a LYRA Lightcurve spanning the 
+full day of 2011 June 7. 
+To extract the sub-interval 06:00 - 07:00 UT into a new \texttt{Lightcurve} 
+called \texttt{lyra\_zoom} we simply do as shown on 
+Listing~\ref{code:lyra_truncate}.
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.time import TimeRange
->>> tran=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
->>> lyra_zoom = lyra.truncate(tran)
+>>> trange=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+>>> lyra_zoom = lyra.truncate(trange)
 \end{minted}
-\label{lyra_truncate}
 \caption{Extracting a sub-interval from a Lightcurve.}
+\label{code:lyra_truncate}
 \end{listing}
 
-Also in the example shown in Listing \ref{lyra_lc_code}, direct access to the data and time information in the object is available through \verb|lyra.data| and \verb|lyra.data.index| respectively.
+Also from the example shown in Listing~\ref{code:lyra_lc}, direct access to 
+the data and time information in the object is available through 
+\texttt{lyra.data} and \texttt{lyra.data.index} respectively 
+(see Listing~\ref{code:lyra_pandas}).
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{{pycon}
 >>> print lyra.data
@@
 \end{minted}
-\label{lyra_pandas}
 \caption{Accessing the data and time axis in a Lightcurve}
+\label{code:lyra_pandas}
 \end{listing}

### 2014-01-24 Sunpy_paper_0.4.tex
Fixed reference symbol and added url to packages in main file
First draft for Dev and Future as well lc tweaks.
Changed to minted typesetting for code examples in lc section.
Fix merge related issues
added my affil to title page
more changes
Added dps affiliation and name
Added bg for listing in main and map files, plus few typos fixed.  Also reorderd some sentence into s/c launch
added my author details to tex file

@@
 
+\usepackage{natbib}
+\usepackage{minted}
+\definecolor{bg}{rgb}{0.95, 0.95, 0.95}
+\usepackage{hyperref}
 %Uncomment next line if AMS fonts required
 %\usepackage{iopams}
-
+\usepackage{graphicx}
+\graphicspath{{./images/}}
+\newcommand*{\newblock}{Bibliography}
 \begin{document}
@@
 
-\author{S J Mumford}
+\author{The SunPy Community}
+\address{\url{http://sunpy.org}}
+\ead{sunpy@googlegroups.com}
+
+\author{Stuart J Mumford}
 \address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
@@
 
-\author{J Bloggs}
-\address{Wibble wiblle wiblle}
+\author{Steven Christe}
+\address{NASA Goddard Space Flight Center, Greenbelt, U.S.A.}
 
-\ead{sunpy@googlegroups.com}
+\author{David P\'erez-Su\'arez}
+\address{South African National Space Agency - Space Science,
+Hospital Street, 7200 Hermanus, Western Cape, South Africa}
+
+\author{Andrew R Inglis}
+\address{NASA Goddard Space Flight Center, Greenbelt, USA}
+\address{The Catholic University of America, Washington, DC, USA}
 
@@
 \input{1-Introduction}
+\label{sec:Intro}
 
 \input{2-Data_Types}
+\label{sec:DataTypes}
 
 \input{3-Retrieval}
+\label{sec:retrevial}
 
 \input{4-Util}
+\label{sec:util}
 
 \input{5-Dev}
+\label{sec:dev}
 
 \input{6-Future}
+\label{sec:future}
+
+\section{Conclusion}
 
 %%% References
-\bibliography{sunpy_paper_0.4}{}
+\bibliographystyle{stunat}
+\bibliography{Sunpy_paper_0.4}{}
 

### 2014-01-24 2-2-Lightcurve.tex

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> print lyra.data

### 2014-01-26 3-5-Database.tex
rewrite of the database section

--- 2014-01-23 3-5-Database.tex
@@
-\subsection{The SunPy Database}
-% TODO: reference / footnote to Summer of Code website?
-The database package has been added as a Google Summer of Code (GSoC) project
-in 2013. Its purpose is to offer a database interface to store and manage data
-that has been retrieved via packages from the net package. Note that currently
-only the VSO package is supported, not the HEK package.
+\subsection{The File Database}
+Easy access to large quantities of solar data frequently leads to datafiles accumulating
+in local storage such as laptops and desktop computers. Keeping data organized and available
+is typically a cumbersome task for the average user. The file database is a sub-package of 
+Sunpy which is meant to solve this problem by providing a unified database to store and manage information about 
+local data files. The database package was developed as part of the 2013 
+Google Summer of Code.
 
-The need for a database package arose because using VSO alone led to two major
-problems:
-\begin{enumerate}
-  \item downloaded data cannot be queried or browsed
-  \item to fetch data that has already been saved on the local hard drive,
-    the VSO has to be queried again
-\end{enumerate}
+The database sub-package makes use of a SQLite database supported by  
+SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}. This library was chosen
+since it supports many SQL dialects. The database is stored as a single file which is 
+created automatically. This solution makes it possibly to easily backup, copy and distribute
+a database file. A server-based database, on the other hand, could be used by a collaboration 
+who work together from different machines on the
+same data: a central database server stores all data and the clients connect to
+it to read or write data.
 
-Here is a list of the main features:
-\begin{itemize}
-  \item detects if certain query has already been used before and queries
-    the database then instead of the VSO
-  % TODO: reference to SA docs? or list all currently supported SQL dialects here?
-  \item many supported SQL dialects
-  % TODO: footnotes for LRU/LFU or some explanation in parens behind them?
-  \item database may act as a Cache (algorithm may be LRU, LFU or a custom one)
-  \item all writing operations can be undone and redone
-\end{itemize}
+The database can store and manage all data that is retrieved via sunpy from the net
+package though currently only the \textsc{VSO} package is supported. 
+It also possible to add entries manually by file or directory. The package also provides
+a \texttt{fetch} method which provides a unified data search which includes both local files
+and files on the \textsc{VSO} are searched. This reduces the likelihood of downloading the same file 
+multiple times. When a file is added to the database the file is scanned and a file hash is produced. 
+The current date is associated with the entry along with metadata summaries such 
+as instrument, date of observation, field of view, etc. 
+The database also provides the ability to associate custom meta-data to 
+each database entry such as keywords, comments, and favoriting.
 
-Using the database package, one uses the Database class to connect with a
-database and perform operations on it.
+A very special feature of the database package is the support of \texttt{undo}
+and \texttt{redo} operations. This is particularly convenient in
+interactive sessions to easily revert accidental operations. 
+This feature will also be desirable when creating a GUI frontend for this package.
 
-\begin{listing}
+Using the database package, one uses the \texttt{Database} class to connect
+with a database and perform operations on it. Figure~\ref{code:database} shows how to connect
+to an in-memory database and download data from the \textsc{VSO}. These entried are
+automatically added to the database. The function \texttt{len} is used to get the number of
+records. The function \texttt{display\_entries} displays an iterable of database entries
+in a nicely-formatted \textsc{ASCII} table. The headlines correspond to the
+attributes of the respective database entries.
+
+\begin{listing}[H]
 \begin{minted}{python}
@@
 6
-\end{minted}
-\caption{Connecting to a database and adding new entries.}
-\label{code:db_1}
-\end{listing}
-
-In the code listing \ref{code:db_1}, a connection to new SQLite in-memory
-database is established. After that, the attributes from the \textsc{VSO}
-package are used to query the \textsc{VSO} and download the corresponding
-files. The function \texttt{len} can be used to get the number of all database
-records.
-
-Note that the number of new database entries does not depend on the
-number of files being downloaded but on the total number of \textsc{FITS}
-headers in the files! If the used query had been used to query the \textsc{VSO}
-directly, the number of query results would have been 2. You can see in the
-following code example, listing \ref{code:db_2}, that indeed the entries can
-be grouped to two results.
-
-The function \texttt{display\_entries} displays an iterable of database entries
-in a nicely-formatted \textsc{ASCII} table. The headlines correspond to the
-attributes of the respective database entries.
-
-\begin{listing}
-\begin{minted}{python}
 >>> from sunpy.database.tables import display_entries
@@
 1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
-2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
-3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
-4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
-5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
-6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
+
 \end{minted}
-\caption{Displaying database entries in a table.}
-\label{code:db_2}
+\caption{Example usage of the database sub-package.}
+\label{code:database}
 \end{listing}
-
-As said before, the database can be used as a cache. By default, the size of
-the cache is not limited which in other words means that caching is disabled.
-To limit the number of database entries to a certain number a posteriori, use
-the method \texttt{set\_cache\_size} and pass it the number of maximum entries.
-The default algorithm to remove entries from the cache is \textsc{LRU}
-(least recently used), i.e. the item whose usage is farthest away is removed
-first.  % FIXME is 'whose' correct here? ^

### 2014-01-26 4-Util.tex
some edits to Util section.

@@
-\section{Utilities}
+\section{Additional functionality}
 SunPy is meant to provide a consistent environment for solar data analysis. In 
-order to achieve this goal SunPy provides a number of utility functions which 
-are used by the other SunPy modules and are made available to the user. Two 
-modules are described in this Section, namely, solar coordinates (wcs), and 
-the Sun module (sun).
+order to achieve this goal SunPy provides a number of utility functions and packages which 
+are used by the other SunPy modules and are made available to the user. This section 
+briefly describes some of these functions.
 
-\subsection{WCS Coordinates}
+%Two modules are described in this Section, namely, solar coordinates (WCS), and 
+%the Sun module.
+
+\subsection{World Coordinate System (WCS) Coordinates}
 Coordinate transformations are frequently a necessary task within the solar 
@@
 different solar features. This type of transformation is not unique
-to solar observations (e.g. planetary) but is not often considered by astronomical packages
+to solar observations, but is not often considered by astronomical packages
 such as the Astropy 
-coordinates package. The wcs package implements the World Coordinate 
+coordinates package. The \verb|wcs| package in SunPy implements the World Coordinate 
 System (WCS) for solar coordinates as described by \cite{Thompson2000}. The 
-coordinate system transformations currently implemented are those most useful 
+transformations currently implemented are those most useful 
 for most solar data analysis, namely converting from Helioprojective-Cartesian 
@@
 the Sun as angles measured from the center of the solar disk (usually in 
-arcseconds) using cartesian coordinates (X, Y). This is the coordinates 
-most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). 
+arcseconds) using cartesian coordinates (X, Y). This is the coordinate system 
+most often defined in solar imaging data (see for example, images from SDO/AIA, SOHO/EIT, and TRACE). 
 HG coordinates express positions on the Sun using longitude and latitude on 
@@
 These transformations require some knowledge of the location of the observer 
-which is usually provided by the image header . In case where it is 
-not, the observer is assumed to be at Earth. An example of the
+which is usually provided by the image header. In the case where it is 
+not, the observer is assumed to be at Earth.Listing \ref{code:wcs_code} shows some examples of coordinate transforms carried out in SunPy using the \verb|wcs| utilities.
 

### 2014-01-26 4-Util.tex
more edits to util.

@@
 All of these functions take a time as their input which can be provided in any 
-parse\_time
+\texttt{parse\_time}
 compatible format. 
@@
 values both within the SunPy code base but also to the user. Every solar 
-constants is provided as a Constant objects as defined by Astropy. Each 
+constant is provided as a Constant object as defined by Astropy. Each 
 Constant object defines a Quantity, a number associated with a unit, along with 
@@
 different units as can be seen in Figure~\ref{fig:constants_code} as well
-as between SI or cgs with a single command.  As these objects inherit from 
+as between the SI or cgs unit systems with a single command.  As these objects inherit from 
 Numpy's ndarray, they work well with standard representations of numbers.
@@
 accessed through an interface modelled on that provided by the SciPy constants 
-package and are available as a dictionary called \texttt{physical\_constants}. 
+package and is available as a dictionary called \texttt{physical\_constants}. 
 To view them all quickly a \texttt{print\_all()} function is available.

### 2014-01-26 4-Util.tex
added short section on Instruments to Util

@@
 \end{listing}
+
+\subsubsection{Instruments}
+In addition to providing support for solar data via the main data classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, some instrument-specific functions may be found within the \texttt{instr} package.
+These functions are generally those that are unique to one particular solar instrument, rather than of general use, for example a function to construct a GOES flare event list or a function to query the LYRA timeline annotation file.
+Currently, functions are included in this way for the GOES, LYRA, RHESSI and IRIS instruments.

### 2014-01-27 3-5-Database.tex
typo fix
clarify that SQLite is not the default dialect (there is no default at all)

@@
 
-The database sub-package makes use of a SQLite database supported by  
+The database sub-package makes use of a database supported by
 SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}. This library was chosen
-since it supports many SQL dialects. The database is stored as a single file which is 
+since it supports many SQL dialects. If SQLite is choosen, the database is stored as a single file which is
 created automatically. This solution makes it possibly to easily backup, copy and distribute

### 2014-01-27 3-1-VSO.tex
Edited the VSO section

--- 2014-01-24 3-1-VSO.tex
@@
 
-The Virtual Solar Observatory (VSO) was built to facilitate
-access to solar data from the different archives around the 
-world \cite{hill_virtual_2009}.  
-Enabling therefore a single standard query interface to all
-the available products from solar observation.  
-VSO allows to query data not just by instrument or mission for 
-a time range but by physical variables as for example:
-intensity, magnetic field, particle flux or spectral range to name a few.
-VSO's main interface is web-based\footnote{\url{http://virtualsolar.org}}, 
-however a SOAP webservice is also available.
-SunPy access to the VSO through the \texttt{vso} module which it uses 
-the \texttt{suds} package to connect to the webservice.
-This module was developed under the ESA's Summer of Code programme of 2010.
+The Virtual Solar Observatory (VSO) provides a single, standard query
+interface to access solar data from different archives around the world
+ \cite{hill2009}.
+Data products can be requested for specific instruments or missions, but
+can also be requested based on physical parameters of the data product such
+as the wavelength range.
+In addition to the VSO's primary, web-based interface
+(\url{http://virtualsolar.org}), a SOAP (Simple Object Access Protocol)
+service is also available.
+SunPy's \texttt{vso} module accesses the VSO via the SOAP service using the
+\texttt{suds} package.
+This module was developed under the ESA's Summer of Code programme of 2011.
 
-The \texttt{vso} module includes advanced features through the use
-of VSO attributes objects.  
-The time range, the instrument, the wavelength, the physical observable,
-and many other properties are set as attributes objects which could
-be combine using \texttt{and} - just by chaining together the arguments -
-or \texttt{or} operators - by joining the attributes using the ``$|$'' operator.
-Listing~\ref{code:vso_query} shows few examples of queries made using
-such attributes.
+Listing~\ref{code:vso_query} shows a number of examples of how to make queries
+using the \texttt{vso} module.
+Each query is constructed by one or more attributes objects, where each
+attribute object is a constraint on a parameter of the data set, such as the
+time, instrument, wavelength, or  other properties.
+Two attribute objects can be combined with a logical \texttt{or} operation
+using the ``$|$'' operator.
+All attribute objects provided to the query as keyword arguments are combined
+with a logical \texttt{and} operation.
 
 \begin{listing}[h]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.net import vso
->>> client=vso.VSOClient()
->>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'
+>>> client = vso.VSOClient()
+>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 05:45'
 
-Querying just a single instrument
+Querying a single instrument over a time range
 >>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
@@
 >>> lasco_query.num_records()
-40
+2
 >>> lasco_query.show() 
@@
 2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
-...
 
-Adding to the query STEREO's coronographs: COR1
+Querying multiple instruments/missions over the same time range
 >>> instrument_condition = ( vso.attrs.Instrument('lasco') |
 ...                          vso.attrs.Detector('cor1') )
->>> coronographs = client.query(vso.attrs.Time(tstart, tend)), 
+>>> coronagraphs = client.query(vso.attrs.Time(tstart, tend),
 ...                             instrument_condition)
->>> coronographs.num_records()
-485
+>>> coronagraphs.num_records()
+30
 >>> coronographs.show() 
@@
 2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO      LASCO       CORONA
+2011-06-07 05:30:00  2011-06-07 05:30:01  STEREO_A  SECCHI      CORONA
 ...
-2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
-2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
+2011-06-07 05:43:13  2011-06-07 05:43:15  STEREO_B  SECCHI      CORONA
+2011-06-07 05:45:00  2011-06-07 05:45:01  STEREO_A  SECCHI      CORONA
+
+Querying two wavelength ranges over the same time range
+>>> wavelength_condition = ( vso.attrs.Wave(125, 135) |
+...                          vso.attrs.Wave(165, 175) ) # in angstroms
+>>> euv = client.query(vso.attrs.Time(tstart, tend),
+...                    wavelength_condition)
+>>> euv.num_records()
+199
+>>> euv.show()
+Start time           End time             Source    Instrument  Type
+----------           --------             ------    ----------  ----
+2011-06-07 00:00:00  2011-06-08 00:00:00  SDO       EVE         FULLDISK
+...
+2011-06-07 05:31:09  2011-06-07 05:31:19  PROBA2    SWAP        FULLSUN
+...
+2011-06-07 05:45:00  2011-06-07 05:45:01  SDO       AIA         FULLDISK
 \end{minted}
-\caption{Examples of different advanced queries through the \texttt{vso} 
-  module using the attributes objects.}
+\caption{Examples of different VSO queries using attribute objects.}
 \label{code:vso_query}
@@
 
-The \texttt{vso} module also provides an interface to download the data,
-allowing to customise the directory structure to save the data.
-Listing~\ref{code:vso_down} exemplifies such case.
+Listing~\ref{code:vso_down} shows how to download the data using the result
+from the query.
+One can use the metadata associated with the data sets to specify how the
+files will be named locally, such as creating subdirectories based on the
+instrument names.
 
 \begin{listing}[h]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
->>> results = client.get(coronographs, 
-...                      path = pathformat)
-
+>>> results = client.get(coronagraphs, path = pathformat)
 \end{minted}
-\caption{From listing~\ref{code:vso_query}, this examples shows the 
-  download method of the \texttt{vso} module.}
+\caption{Example of how to download data using a query result (see
+listing~\ref{code:vso_query}).}
 \label{code:vso_down}

### 2014-01-27 3-3-HELIO.tex
Edited the HELIO section

@@
 (HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web 
-services which allows the scientist to query them in order to discover data in 
+services which allows scientists to query and discover data throughout 
 the heliosphere (\textit{e.g.}, solar, planetary, inter-planetary data, 
-...)\cite{dps2012}. 
+\ldots)\cite{dps2012}. 
 HELIO has been built with a Service-Oriented Architecture, 
@@
 implemented as separate services. 
-HELIO counts with up to nine different public services, which allows to the 
-scientist to search in different catalogues of registered events, solar features,
+HELIO comprises nine different public services, which allows scientists
+to search in different catalogues of registered events, solar features,
 data from instruments in the heliosphere and other information like planets or 
 spacecraft position in time. 
-Additionally, HELIO provides of a service that uses a propagation model to link 
+Additionally, HELIO provides a service that uses a propagation model to link 
 the data in different points of the solar system by its original nature 
@@
 produced few days before on the Sun).
-The main interface to access to HELIO is through its front-end\footnote{
-\url{http://hfe.helio-vo.eu}},
-but since the system is based in webservices they can be accessed from many different tools.
+In addition to the primary, web-based interface to HELIO
+(\url{http://hfe.helio-vo.eu}), the services can be separately accessed.
 
-The current version of SunPy has includes an interface to access the 
-\textit{HELIO Event Catalogue} (HEC) service developed as part of Google
-Summer of Code project in 2013.
-This service provides at the moment access to 84 catalogues from different
+SunPy's \texttt{hec} module provides an interface to the
+\textit{HELIO Event Catalogue} (HEC) service, and this module was developed as
+part of a Google Summer of Code project in 2013.
+The HEC service currently provides access to 84 catalogues from different
 sources (automated and manual classification, event lists from publications, \ldots).
-HEC results (as the rest of HELIO services) provides the results in VOTable 
-data format (defined by IVOA \cite{ochsenbein_ivoa_2011})
-which the \texttt{astropy.io.votable} can interact with.
-This format has the advantage of contain metadata with information like
+As with all of the HELIO services, the HEC service provides results in VOTable 
+data format (defined by IVOA \cite{ochsenbein_ivoa_2011}), and the \texttt{hec}
+module parses this output using the \texttt{astropy.io.votable} package.
+This format has the advantage of containing metadata with information like
 data provenance and the performed query.
 
-On listing~\ref{code:helio} we show some an example on how to obtain information
-from different \textit{Coronal Mass Ejections}(CMEs) catalogues.
+Listing~\ref{code:helio} shows an example of how to obtain information
+from different catalogues of coronal mass ejections (CMEs).
 
 \begin{listing}[h]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.net.helio import hec
@@
 \end{minted}
-\caption{Demonstration of the \texttt{helio.hec} interface.}
+\caption{Example of querying the HEC service.}
 \label{code:helio}
 \end{listing}
-
-It is in the SunPy roadmap to add support from the other HELIO services and improve
-the usability of them towards a seamlessly interaction of this tool with the rest of
-the environment, as for example with data visualisation or the database module.

### 2014-01-27 3-3-HELIO.tex
More edits to HELIO section

@@
 Desired time range and event type
->>> tstart = '2011-06-07T06:00:00'
->>> tend = '2011-06-07T12:00:00'
+>>> tstart, tend = '2011-06-07T06:00:00', '2011-06-07T12:00:00'
 >>> event_type = 'cme'
@@
 >>> print catalogues_event
-******** This need to be added!
+['hi_cme_list', 'cactus_stereoa_cme', 'icme_earth_cycle23', 'cactus_cme_list', '
+goes_flare_no_sep_radio_cme', 'ulysses_swoops_icme', 'cme_forbush_event', 'seeds
+_cme', 'cme_inner_heliosphere', 'mars_earth_icme', 'stereo_hi_cme', 'cactus_ster
+eob_cme', 'cactus_soho_cme', 'lasco_cme_list', 'cactus_stb_cme_list', 'cactus_so
+ho_cme_list', 'halo_cme_flare_magnetic_storm', 'lasco_cme_cat', 'cactus_sta_cme_
+list', 'stereoa_impactplastic_icme', 'stereob_impactplastic_icme', 'soho_lasco_c
+me', 'stereo_impactplastic_icme', 'wind_typeii_soho_cme']
 
@@
 \end{listing}
+
+Additional HELIO services will be supported in the future by SunPy.

### 2014-01-27 2-2-Lightcurve.tex
edits to lightcurve section

@@
-\subsection{Lightcurve}
+\subsection{Lightcurve}\label{sec:lightcurve}
 
-Time series data and analyses are a fundamental aspect of solar physics 
-for which many data sources are available. 
-In recognition of this fact, SunPy provides a \texttt{LightCurve} object 
-designed to provide a convenient and consistent interface for handling 
-solar time series data. 
-The main engine behind the \texttt{LightCurve} object is the \texttt{pandas} 
-data analysis library. 
-This library contains a large amount of functionality for manipulating 
-and analysing time series data, making it an ideal basis for 
-\texttt{LightCurve}.  
-Like all other SunPy objects, \texttt{LightCurve} is a wrapper around 
-a data object, which in this case is the \texttt{pandas} object.
+Time series data and their analysis are a fundamental aspect of solar
+physics for which many data sources are available.  In recognition of
+this fact, SunPy provides a \texttt{LightCurve} object designed to
+provide a convenient and consistent interface for handling solar time
+series data.  The main engine behind the \texttt{LightCurve} object is
+the \texttt{pandas} data analysis library (available at
+\url{http://pandas.pydata.org}).  This library contains a large amount
+of functionality for manipulating and analysing time series data,
+making it an ideal basis for \texttt{LightCurve}.  Like other SunPy
+objects, \texttt{LightCurve} is a wrapper around a data object, which
+in this case is the \texttt{pandas} object.  \texttt{LightCurve}
+assumes that the input data are time-ordered list(s) of numbers.  Each
+list becomes a column in a \texttt{pandas} DataFrame object.
 
-Currently, the \texttt{LightCurve} object is compatible with the following 
-data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, 
-and the SDO EUV Variability Experiment (EVE). 
-For each of these instruments, a sub-class of the \texttt{LightCurve} object 
-is initialised (e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits 
-from \texttt{LightCurve} but allows instrument-specific functionality to be 
-included. 
-Future developments will introduce support for additional instruments and data 
-products. 
-Since time series data is generally relatively small and there is no 
-established standard as to how it should be stored and distributed, 
-each SunPy \texttt{LightCurve} object provides the ability to download 
-its own data in its constructor.
+Currently, the \texttt{LightCurve} object is compatible with the
+following data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, and
+the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
+average CSV files - see \url{http://lasp.colorado.edu/home/eve/data/}
+for more detail).  For each of these instruments, a sub-class of the
+\texttt{LightCurve} object is initialised
+(e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits from
+\texttt{LightCurve} but allows instrument-specific functionality to be
+included.  Future developments will introduce support for additional
+instruments and data products.  Since time series data is generally
+relatively small and there is no established standard as to how it
+should be stored and distributed, each SunPy \texttt{LightCurve}
+object provides the ability to download its own data in its
+constructor.
 
@@
 
-A \texttt{LightCurve} object may be created using a range of different methods. 
-Firstly, a \texttt{LightCurve} may be created for a specific instrument based 
-on an input time range. In Listing \ref{code:goes_lc_code}, 
-the LightCurve constructor searches remote sites for the GOES X-ray data 
-specified by the time interval, downloads the required files and subsequently 
-creates the object.
+A \texttt{LightCurve} object may be created using a range of different
+methods.  Firstly, a \texttt{LightCurve} may be created for a specific
+instrument based on an input time range. In Listing
+\ref{code:goes_lc_code}, the LightCurve constructor searches remote
+sites for the GOES X-ray data specified by the time interval,
+downloads the required files and subsequently creates the object.
 
@@
 
-Alternatively, if the data file already exists on the local system, the 
-\texttt{Lightcurve} object may instead be initialised using that file as input 
-(see Listing \ref{code:lyra_lc}).
+Alternatively, if the data file already exists on the local system,
+the \texttt{Lightcurve} object may instead be initialised using that
+file as input (see Listing \ref{code:lyra_lc}).
 
@@
 
-In Listing~\ref{code:lyra_lc} we created a LYRA Lightcurve spanning the 
-full day of 2011 June 7. 
-To extract the sub-interval 06:00 - 07:00 UT into a new \texttt{Lightcurve} 
-called \texttt{lyra\_zoom} we simply do as shown on 
-Listing~\ref{code:lyra_truncate}.
+In Listing~\ref{code:lyra_lc} we created a LYRA Lightcurve spanning
+the full day of 2011 June 7.  To extract the sub-interval 06:00 -
+07:00 UT into a new \texttt{Lightcurve} called \texttt{lyra\_zoom} we
+simply do as shown on Listing~\ref{code:lyra_truncate}.
 

### 2014-01-27 1-Introduction.tex
Add the intro changes!

--- 2014-01-23 1-Introduction.tex
@@
 \section{Introduction}
-Modern solar physics, similar to astrophysics, requires increasingly 
-complex software tools both for the retrieval as well as the analysis 
-of data. The Sun is the most well-observed star. As such, solar 
-physics is unique in its ability to access large amounts of high 
-resolution ground- and space-based observations of the Sun at many 
-different wavelengths and spatial scales with high time cadence. 
-Modern solar physics, similar to astrophysics, therefore requires 
-increasingly complex software tools, both for the retrieval and the 
-analysis of data. For example, NASA's Solar Dynamics Observatory 
-(SDO) satellite records over 1 TB of data per day all of which is 
-telemetered to the ground and available for analysis. As a result, 
-scientists have to process large volumes of complex data products. In 
-order to make meaningful advances in solar physics, it is important 
-for the software tools to be standardized, easy to use, and 
-transparent, so that the community can build upon a common foundation.
+Modern solar physics and astrophysics, along with most of modern science is 
+increasingly becoming data-driven. Where observational and numerical data is 
+being produced at a faster rate than new hypotheses. For example, NASA's Solar 
+Dynamics Observatory (SDO) satellite records over 1 TB of data per day all of 
+which is telemetered to the ground and available for analysis.
+Solar physics therefore requires increasingly complex software tools to enable 
+scientific discovery by analysis of this data. To make meaningful and 
+reproducible advances in our understanding of the Sun it is important that the 
+software tools to be standardised, easy to use, and transparent, so that the 
+community can build upon a common foundation.
 
-Currently, most solar data analysis is performed with a large library 
-of routines called SolarSoft, also referred to as SSW 
-\cite{freeland1998}. SolarSoft is a set of integrated software 
-libraries, databases, and system utilities which provide a common 
-programming and data analysis environment for solar physics. It is 
-overwhelmingly an environment which relies upon IDL (Interactive Data 
-Language), a commercial and closed-source interactive data analysis 
-environment sold by Exelis, a global aerospace, defense, information 
-and services company. The SSW gen package provides the base analysis 
-capabilities such as time series analysis, time conversions, spectral 
-fitting, image display, and file I/O. It is composed of 89\% IDL code 
-while the remainder is mostly perl (5.4\%) and csh scripts (3.8\%). 
-According to data generated using David A. Wheeler's 'SLOCCount', 
-SSW/gen is composed of 289,724 lines of code with a total approximate 
-value of \$10.4M (based on the Basic COCOMO model). Individual 
-missions and instruments provide additional optional packages to 
-support and process their data. For example, the SDO package 
-\cite{sdo} is 100\% IDL code and is 11k lines of code (\$360k) 
-and the SOHO package \cite{soho} is 100k lines of code (\$3M) and is 
-99.9\% IDL code. SSW is hosted and distributed by the Lockheed Martin 
-Solar and Astrophysics Laboratory.
+SunPy aims to provide a free, open source and openly developed software package 
+for the analysis and visualisation of solar data. SunPy makes use of the Python 
+programming language and the breath of high-quality scientific focused packages 
+available for it. The Python programming language is a general purpose, 
+powerful and easy to learn high-level programming language. Python is one of 
+the top ten most popular programming languages in the world according to the 
+2014 TIOBE Index 
+\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+ and is widely used outside of scientific fields in web development, education 
+and even 3D game design.
 
-%The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
+The development of a package such as SunPy in Python is made possible by the 
+rich scientific Python ecosystem of packages available. Core packages in this 
+ecosystem such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
+provide the basic functionality expected of a scientific programming language, 
+\textit{i.e.} array manipulation, core numerical algorithms and visualisation. 
+Ontop of this packages such as \texttt{Astropy}, \texttt{pandas} and 
+\texttt{scikit-image} provide a tremendous amount of more domain-specific 
+functionality.
 
-While SSW is open-source and freely available, the IDL core. The cost 
-of IDL is prohibitive for many undergraduates as well as institutions 
-with limited means.
+The design philosophy of SunPy is to provide a clean, simple to use, and well 
+structured package that provides the \textit{core} tools for solar physics. The 
+primary focus of SunPy's early development is to provide specialised, linked, 
+datatypes that allow the acquisition, processing and visualisation of all types 
+of solar data.
 
-One of SunPy's key aims is to provide a free and modern alternative 
-to the SolarSoft (gen) library. This is made possible by the recent 
-rise of the scientific Python community. Python is a general purpose 
-high-level programming language. It is free to use, cross-platform 
-and is both an accessible and powerful programming language. Python 
-is one of the top ten most popular programming languages in the world 
-according to the 2014 TIOBE Index 
-\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
-It therefore has a very large user community which extends faroutside 
-of the solar physics or astronomy communities. It is very extensible 
-with C, C++, Fortran or even IDL. Many books and on-line 
-documentation is available. For example at the time writing a search 
-on Amazon for books on IDL programming generated $189$ results while 
-a search for Python yielded $1,788$ results. Python has a strong 
-emphasis on readability a concept which is well-aligned with the 
-scientific endeavor.
-Additionally, Python is increasingly being taught in universities,
-which means that research projects can begin quickly 
-without the need for students to learn a new (and relatively niche) 
-language. Finally, knowledge of Python is a skill which is useful and well 
-compensated outside of the scientific community (average salary of 
-\$110k in the Washington DC area according to indeed.com at the time 
-of writing). Python continues to see increased use in the astronomy 
-community \cite{greenfield2011} which has similar goals and 
-requirements as the solar physics community. Finally, Python plays 
-well with many technologies such as web servers \cite{dolgert2008}, 
-SQL databases, interactive and shareable notebook-based computing 
-\cite{perez2007}. For all of these reasons, Python is an ideal 
-platform for a modern solar physics data analysis environment.
-
-SunPy is built on top of the core scientific Python packages namely 
-\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core 
-packages provide capabilities surpassing that provided by IDL for 
-array manipulation and 2-d plotting \cite{greenfield2011}. Providing 
-similar capabilities as SSW/gen in Python is made easier by 
-leveraging the diverse Python community. For example, SunPy makes use 
-of the \texttt{Pandas} package to provide high-performance, 
-easy-to-use data structures and data analysis tools for time series 
-data\cite{mckinney2012}. \texttt{Pandas} was originally developed for 
-quantitative analysis of financial data and has seen grown into a 
-generalized data analysis package. SunPy also relies on and is 
-coordinating with the \texttt{Astropy} package 
-\cite{theastropycollaboration2013}. It is still in active development 
-but already provides many relevant capabilities such as full-featured
-support for FITS files, absolute dates and time conversions, units 
-and unit conversions, and model-fitting. Pandas (134k lines of code) 
-and AstroPy (90k lines of code) allow SunPy to leverage a total value 
-of \$7.6M worth of development which is close to the \$10.4M for 
-SSW/gen assuming a rough equivalency between a line of Python code 
-and a line of IDL code.
-
-The design philosophy of SunPy is to provide a clean, simple to use, 
-and well structured package that provides the \textit{core} tools for 
-solar physics. The primary focus of SunPy's development early 
-development is to provide specialised, linked, datatypes that allow 
-the import, processing and visualisation of all types of solar data. 
-These include \texttt{Map}, \texttt{LightCurve} and 
-\texttt{Spectrum}, these cover spatial, timeseries and spectral data  
-respectively.
-
-The purpose of this paper is to provide an overview of SunPy's 
-current capabilities, an overview of the development model and 
-community aspects of the SunPy project as well as future plans. The 
-latest release of SunPy is available in PyPI and can be installed in 
-the usual manner.
+The purpose of this paper is to provide an overview of SunPy's current 
+capabilities, an overview of the development model and community aspects of the 
+SunPy project as well as future plans. The latest release of SunPy is available 
+in PyPI and can be installed in the usual manner for a Python package
+\footnote{http://docs.sunpy.org/en/latest/sunpy/guide/installation/index.html}.

### 2014-01-27 3-1-VSO.tex
Minor edit
Fixed and split the VSO example

@@
 interface to access solar data from different archives around the world
- \cite{hill2009}.
+ \citep{hill2009}.
 Data products can be requested for specific instruments or missions, but
@@
 
-Listing~\ref{code:vso_query} shows a number of examples of how to make queries
+Listing~\ref{code:vso_query_simple} shows an example of how to query the VSO
 using the \texttt{vso} module.
@@
 time, instrument, wavelength, or  other properties.
+Listing~\ref{code:vso_query_advanced} shows examples of how to make advanced
+queries by combining attribute objects.
 Two attribute objects can be combined with a logical \texttt{or} operation
@@
 >>> client = vso.VSOClient()
->>> tstart, tend = '2011/6/7 05:30', '2011/6/7 05:45'
-
-Querying a single instrument over a time range
+>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'
 >>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
@@
 >>> lasco_query.num_records()
-2
+40
 >>> lasco_query.show() 
@@
 2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
+...
+\end{minted}
+\caption{Example of querying a single instrument over a time range.}
+\label{code:vso_query_simple}
+\end{listing}
 
+\begin{listing}[h]
+\begin{minted}[bgcolor=bg]{pycon}
 Querying multiple instruments/missions over the same time range
@@
 >>> coronagraphs.num_records()
-30
->>> coronographs.show() 
+485
+>>> coronagraphs.show()
 Start time           End time             Source    Instrument  Type
@@
 2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO      LASCO       CORONA
-2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO      LASCO       CORONA
-2011-06-07 05:30:00  2011-06-07 05:30:01  STEREO_A  SECCHI      CORONA
 ...
-2011-06-07 05:43:13  2011-06-07 05:43:15  STEREO_B  SECCHI      CORONA
-2011-06-07 05:45:00  2011-06-07 05:45:01  STEREO_A  SECCHI      CORONA
+2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
+2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
 
@@
 >>> euv.num_records()
-199
+3989
 >>> euv.show()
@@
 ...
-2011-06-07 05:45:00  2011-06-07 05:45:01  SDO       AIA         FULLDISK
+2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK
 \end{minted}
-\caption{Examples of different VSO queries using attribute objects.}
-\label{code:vso_query}
+\caption{Examples of advanced VSO queries using attribute objects,
+continuing from listing~\ref{code:vso_query_simple}.}
+\label{code:vso_query_advanced}
 \end{listing}
@@
 \end{minted}
-\caption{Example of how to download data using a query result (see
-listing~\ref{code:vso_query}).}
+\caption{Example of how to download data using a query result, continuing from
+listing~\ref{code:vso_query_advanced}).}
 \label{code:vso_down}

### 2014-01-27 solarsoft.tex

\section{Comparison to SolarSoft}
This section compares the SunPy library that is described in Sections 
\ref{sec:DataTypes} - \ref{sec:util} with the current de-facto standard solar 
physics data analysis library, SolarSoft (SSW) \citep{freeland1998}.
SolarSoft is a set of integrated software libraries, databases, and system 
utilities which provide a common programming and data analysis environment for 
solar physics. SSW is modular in nature, which allows users to add required 
packages which contain specialised software for different instrument or tools.

It is overwhelmingly an environment which relies upon IDL (Interactive Data 
Language), a commercial and closed-source interactive data analysis environment 
sold by Exelis, a global aerospace, defence, information and services company. 
The SSW `gen' package provides the base analysis capabilities such as time 
series analysis, time conversions, spectral fitting, image display, and file 
I/O. It is composed of 89\% IDL code while the remainder is mostly Perl (5.4\%) 
and csh scripts (3.8\%) \footnote{{\bf This data was calculated using...}}. 
According to data generated using David A. Wheeler's 'SLOCCount' 
\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
289,724 lines of code with a total approximate value of \$10.4M (based on the 
Basic COCOMO model \citep{_cocomo_2014}). \footnote{{\bf This data was 
calculated using...} If we can add them to the repository will improve the 
quality of the paper and we can always repeat the calculation in the future}. 
Individual missions and instruments provide additional optional packages to 
support and process their data. For example, the SDO package \citep{sdo} is 
100\% IDL code and is 11k lines of code (\$360k) and the SOHO package 
\citep{soho} is 100k lines of code (\$3M) and is 99.9\% IDL code. SSW is hosted 
and distributed by the Lockheed Martin Solar and Astrophysics Laboratory.
\footnote{Do we know whether they have some licence owning it? do we know the 
SolarSoft licence at all?}
%The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
While SSW is open-source and freely available, the IDL core is not. The cost 
of IDL is prohibitive for many undergraduates as well as institutions 
with limited means. As well as this the development of SolarSoft is closed, 
with no open issue tracker or community contribution mechanism.

One of SunPy's key aims is to provide a free and modern alternative to the 
SolarSoft (gen) library. This is made possible by the recent rise of the 
scientific Python community. Python, as described in Section \ref{sec:Intro}, 
is a general purpose high-level programming language which is free to use and 
cross-platform and powerful programming language.
It therefore has a very large user community which extends far outside of the 
solar physics or astronomy communities. It is very extensible with C, C++, 
FORTRAN or even IDL. Many books and on-line documentation is available. For 
example at the time writing a search 
%
\footnote{We need to be careful with this! IDL means more things that our 
beloved ``Interactive Data Language''. If we search for that and programming 
then we get just 7 books! - from which 5 are just the same. I don't know how we 
could make a more accurate search.
If we script it it would be amazing!  Also, I would just provide the order
of magnitude, and not a exact number, i.e. 190 and 1800 results} 
%
on Amazon for books on IDL programming generated $189$ results while a search 
for Python yielded $1\,788$ results. Python has a strong emphasis on 
readability a concept which is well-aligned with the scientific endeavour.
Additionally, Python is increasingly being taught in universities, which means 
that research projects can begin quickly without the need for students to learn 
a new (and relatively niche) language. Finally, knowledge of Python is a skill 
which is useful and well compensated outside of the scientific community 
(average salary of \$110k in the Washington DC area according to indeed.com at 
the time of writing). Python continues to see increased use in the astronomy 
community \citep{greenfield2011} which has similar goals and requirements as 
the solar physics community. Finally, Python integrates well with many 
technologies such as web servers \citep{dolgert2008}, SQL databases, 
interactive and shareable notebook-based computing \citep{perez2007}. For all 
of these reasons, Python is an ideal platform for a modern solar physics data 
analysis environment.

SunPy is built on top of the core scientific Python packages namely 
\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core packages 
provide capabilities surpassing that provided by IDL for array manipulation and 
2-d plotting \citep{greenfield2011}. Providing similar capabilities as SSW/gen 
in Python is made easier by leveraging the diverse Python community. For 
example, SunPy makes use of the \texttt{Pandas} package to provide 
high-performance, easy-to-use data structures and data analysis tools for time 
series data\citep{mckinney2012}. \texttt{Pandas} was originally developed for 
quantitative analysis of financial data and has seen grown into a generalised 
data analysis package. SunPy also relies on and is coordinating with the 
\texttt{Astropy} package \citep{theastropycollaboration2013}. It is still in 
active development but already provides many relevant capabilities such as 
full-featured support for FITS files, absolute dates and time conversions, 
units and unit conversions, and model-fitting. Pandas (134k lines of code) 
and Astropy (90k lines of code) allow SunPy to leverage a total value of \$7.6M 
worth of development which is close to the \$10.4M for SSW/gen assuming a rough 
equivalency between a line of Python code and a line of IDL code.

### 2014-01-27 3-2-HEK.tex

@@
 
-The Sun is an active star and exhibits a wide range of phenomena on
-many different time-scales, length-scales and wavelengths.
-Observations and metadata concerning these phenomena are collected at
-the Heliophysics Event Knowledgebase (HEK).  Entries are generated
-both by automated algorithms and human observers.  Some of the
-information in the HEK reproduces feature/event data elsewhere (for
-example, the GOES flare catalog), and some is generated by the Solar
-Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
-populate the HEK.  The advantage of the HEK to SunPy is that it is a
-single service that provides a homogeneous and well-described
-interface to a large amount of feature/event information of interest
-to the solar physics community.
+The Sun is an active star and exhibits a wide range of phenomena on many 
+different time-scales, length-scales and wavelengths. Observations and metadata 
+concerning these phenomena are collected at the Heliophysics Event 
+Knowledgebase (HEK).  Entries are generated both by automated algorithms and 
+human observers.  Some of the information in the HEK reproduces feature/event 
+data elsewhere (for example, the GOES flare catalog), and some is generated by 
+the Solar Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
+populate the HEK.  The advantage of the HEK to SunPy is that it is a single 
+service that provides a homogeneous and well-described interface to a large 
+amount of feature/event information of interest to the solar physics community.
 
-SunPy accesses this information through the \texttt{hek} module, which
-was developed through support from the European Space Agency Summer of
-Code in Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of
-the HEK API
+SunPy accesses this information through the \texttt{hek} module, which was 
+developed through support from the European Space Agency Summer of Code in 
+Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of the HEK API
 (\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
-Every event type has required and optional properties; the current
-list of events maintained by the HEK and their properties can be found
-at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+Every event type has required and optional properties; the current list of 
+events maintained by the HEK and their properties can be found at 
+\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
-Simple HEK queries consist of start time, an end time, and an event
-type (Example \ref{code:hek:simple}). Times can be specified in any
-SunPy-acceptable format. Event types are specified as upper case, two
-letter strings, and are identical to the two letter abbreviations
-found at the HEK website, \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+Simple HEK queries consist of start time, an end time, and an event type 
+(Listing \ref{code:hek:simple}). Times can be specified in any SunPy-acceptable 
+format. Event types are specified as upper case, two letter strings, and are 
+identical to the two letter abbreviations found at the HEK website, 
+\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 from sunpy.net import hek
@@
 tend = '2011/08/09 12:40:29'
-event\_type = 'FL'
+event_type = 'FL'
 result = client.query(hek.attrs.Time(tstart,tend), 
-hek.attrs.EventType(event\_type))
+hek.attrs.EventType(event_type))
 \end{minted}
@@
 The module \texttt{hek.attrs} contains attributes of the HEK that can be used to
-construct HEK queries.  For example, a flare is an attribute of the
-HEK, and so instead of specifying \texttt{hek.attrs.EventType('FL')}
-in Example \ref{code:hek:simple}, this can also be expressed as
-\texttt{hek.attrs.FL}.
+construct HEK queries.  For example, a flare is an attribute of the HEK, and so 
+instead of specifying \texttt{hek.attrs.EventType('FL')} in Listing 
+\ref{code:hek:simple}, this can also be expressed as \texttt{hek.attrs.FL}.
 
-HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in
-that many of them are wrappers that conveniently expose
-comparisions by overloading Python operators.  This allows filtering
-of the HEK entries by the properties of the event.  As was mentioned
-above, the HEK stores feature/event metadata obtained in different
-ways, known generally as {\it feature recognition methods}, or FRMs.
-Example \ref{code:hek:frm} filters the results of the previous result
-to return only those events that have the FRM 'SSW Latest Events'.
+HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in that many 
+of them are wrappers that conveniently expose comparisons by overloading Python 
+operators.  This allows filtering of the HEK entries by the properties of the 
+event.  As was mentioned above, the HEK stores feature/event metadata obtained 
+in different ways, known generally as {\it feature recognition methods}, or 
+FRMs. Example \ref{code:hek:frm} filters the results of the previous result to 
+return only those events that have the FRM 'SSW Latest Events'.
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 result = client.query(hek.attrs.Time(tstart,tend), 
-hek.attrs.EventType(event\_type), hek.attrs.FRM.Name == 'SSW Latest Events')
+                      hek.attrs.EventType(event_type),
+                      hek.attrs.FRM.Name == 'SSW Latest Events')
 \end{minted}
@@
 
-HEK comparisons can be combined using Python’s logical operators AND
-and OR. This makes complex queries easy to create: example
-\ref{code:hek:or} returns flares west of 50 arcseconds or those that
-have a peak flux above 1000.0 (the units of the flux are FRM dependent
-and are described at the HEK website).
+HEK comparisons can be combined using Python’s logical operators e.g. AND
+and OR. This makes complex queries easy to create: Listing \ref{code:hek:or} 
+returns flares west of 50 arcseconds or those that have a peak flux above 
+1000.0 (the units of the flux are FRM dependent and are described at the HEK 
+website).
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 result = client.query(hek.attrs.Time(tstart,tend), 
-hek.attrs.EventType(event\_type), (hek.attrs.Event.Coord1 > 50) or 
-(hek.attrs.FL.PeakFlux > 1000.0) )
+                      hek.attrs.EventType(event_type),
+      (hek.attrs.Event.Coord1 > 50) or (hek.attrs.FL.PeakFlux > 1000.0))
 \end{minted}
@@
 All FRMs report the required feature attributes (as described at 
-\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional
-attributes are FRM dependent.  If a FRM does not have one of the
-optional attribute, a 'None' is returned by the \texttt{hek} module.
+\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
+are FRM dependent.  If a FRM does not have one of the optional attribute, a 
+'None' is returned by the \texttt{hek} module.
 
-The ability to use comparison and logical operators on HEK attributes
-allows the construction of queries of almost arbitrary complexity,
-bringing powerful feature/event search capabilities to SunPy.
+The ability to use comparison and logical operators on HEK attributes allows 
+the construction of queries of almost arbitrary complexity, bringing powerful 
+feature/event search capabilities to SunPy. It is also possible to use the 
+results of a HEK query to download the corresponding data from the VSO by using 
+SunPy's \texttt{H2VClient}.

### 2014-01-27 2-1-Map.tex

@@
 \subsection{Map}
-Map is a 2D spatial data type, primarily used for images of the Sun and 
-inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
-\texttt{ndarray}) and gives easy access to standard meta data in the header of 
-the image, via the \texttt{.meta} attribute as well as some convenience 
-properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
-\texttt{.wavelength} or \texttt{.coordinate\_system}. Demonstrated in Listing 
-\ref{code:aia_1} is this meta data parsing and `pretty printing' of the Map.
-The \texttt{Map} object provides convenience methods for many functions 
-such as, rotation and re-sampling as well as convenience visualisation 
-functions, providing an easy to use as well as powerful interface.
-Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
-\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.
+The purpose of the Map datatype is to represent 2D spatial data such as images of the Sun and 
+inner heliosphere. It provides a wrapper around a data array and its associated
+spatial coordinates and as well as meta data. The \texttt{Map} object provides 
+convenience methods for many functions 
+such as rotation and re-sampling as well as convenience visualisation 
+functions, providing an easy to use as well as powerful interface. The \texttt{Map} object
+also provides a convenient interface for loadings data from a variety of sources, typically
+a FITS file as shown in Figure~\ref{code:aia_1}.
 
-The design of the map submodule is such that each instrument or 
-detector can subclass the parent \texttt{GenericMap} class to implement 
-special meta data handling or other data specific functions. Each subclass 
-of \texttt{GenericMap} can register with the \texttt{Map} factory class and 
-by implementing a method that returns \texttt{True} if the meta data 
-matches meta data for that instrument or detector, the \texttt{Map} factory 
-will automatically return an instance of the specific \texttt{GenericMap} 
-subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
+The architecture of the \texttt{Map} object consists of a template map called
+\texttt{GenericMap} which is a subclass of \texttt{astropy.nddata.NDData}. \texttt{NDData} is a 
+generic wrapper around a \texttt{ndarray} with a \texttt{.meta} attribute to store meta data.
+As \texttt{NDData} is currently still in development, \texttt{GenericMap} does not make full
+use of its capabilities but this inheritance structure provides 
+for future integration of \texttt{astropy}. In order to provide instrument/
+detector specific integration \textt{GenericMap} is subclassed on creation. 
+Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (i.e. factory)
+by implementing a method that returns \texttt{True} if matching meta data 
+for that instrument or detector is found in the file header. The \texttt{Map} factory 
+will then automatically return an instance of the specific \texttt{GenericMap} 
+subclass. As of this version Sunpy has \texttt{Map} specialisations for the 
 following instruments: 
@@
 
-\texttt{GenericMap} is a subclass of \texttt{astropy.nddata.NDData} which is a 
-generic wrapper around a \texttt{ndarray} with a \texttt{.meta} attribute, like 
-\texttt{Map}. Having this inheritance structure with \texttt{astropy} provides 
-potential for simple integration with other parts of \texttt{astropy} and other 
-packages based on \texttt{astropy}, as \texttt{GenericMap} should form a 
-drop-in replacement for \texttt{NDData}.
+The \texttt{Map} object stores standard meta data retrieved in the header of 
+the image file, via the \texttt{.meta} attribute and provides convenience 
+properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
+\texttt{.wavelength} or \texttt{.coordinate\_system}. 
+Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
+\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
-
 >>> import sunpy.map
-
 >>> aiamap = sunpy.map.Map('aia_file.fits')
->>> aiamap
-SunPy AIAMap
----------
-Observatory: SDO
-Instrument:  AIA
-Detector:    AIA
-Measurement: 171
-Obs Date:    2011-03-19T10:54:00.34
-dt:          1.999601
-Dimension:   [1024, 1024]
-[dx, dy] =   [2.400000, 2.400000]
-
-array([[ 0.3125, -0.0625, -0.125 , ...,  0.625 , -0.625 ,  0.    ],
-       [ 1.    ,  0.1875, -0.8125, ...,  0.625 , -0.625 ,  0.    ],
-       [-1.1875,  0.375 , -0.5   , ..., -0.125 , -0.625 , -1.1875],
-       ..., 
-       [-0.625 ,  0.0625, -0.3125, ...,  0.125 ,  0.125 ,  0.125 ],
-       [ 0.5625,  0.0625,  0.5625, ..., -0.0625, -0.0625,  0.    ],
-       [ 0.5   , -0.125 ,  0.4375, ...,  0.6875,  0.6875,  0.6875]])
-
 >>> aiamap.peek()
@@
 
-As well as providing the base classes the map submodule provides two 
+As well as providing the base classes the map sub-package provides two 
 collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
@@
 provides methods for animation of its series of \texttt{Map} objects. 
-Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
+Figure~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
 with these classes.
-In addition, Listing~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
+In addition, Figure~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
 classes interacts with the \texttt{animation} module to save a video.

### 2014-01-27 2-2-Lightcurve.tex
subsection label corrected

--- 2014-01-24 2-2-Lightcurve.tex
@@
 for which many data sources are available. 
-In recognition of this fact, SunPy provides a \texttt{LightCurve} object 
+Sunpy therefore provides a \texttt{LightCurve} object 
 designed to provide a convenient and consistent interface for handling 
-solar time series data. 
-The main engine behind the \texttt{LightCurve} object is the \texttt{pandas} 
+time series data. 
+The main engine behind the \texttt{LightCurve} object is the \texttt{pandas}\footnote{\url{http://pandas.pydata.org}} 
 data analysis library. 
@@
 \texttt{LightCurve}.  
-Like all other SunPy objects, \texttt{LightCurve} is a wrapper around 
+Like all other Sunpy objects, \texttt{LightCurve} is a wrapper around 
 a data object, which in this case is the \texttt{pandas} object.
@@
 established standard as to how it should be stored and distributed, 
-each SunPy \texttt{LightCurve} object provides the ability to download 
+each Sunpy \texttt{LightCurve} object provides the ability to download 
 its own data in its constructor.
@@
 Firstly, a \texttt{LightCurve} may be created for a specific instrument based 
-on an input time range. In Listing \ref{code:goes_lc_code}, 
-the LightCurve constructor searches remote sites for the GOES X-ray data 
+on an input time range. In Figure~\ref{code:goes_lc_code}, 
+the LightCurve constructor searches a remote site for the GOES X-ray data 
 specified by the time interval, downloads the required files and subsequently 
@@
 
-\begin{listing}[H]
+\begin{Figure}[H]
 \begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy import lightcurve
+>>> from sunpy.time import TimeRange
 >>> goes=lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-...                                       '2011-06-07 08:00')
+...                                       '2011-06-07 10:00')
 >>> goes.peek()
+>>> trange=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+>>> goes_zoom = goes.truncate(trange)
+% the above does not work!
+>>> resampled_goes = goes.data.resample("1H")
 \end{minted}
 \includegraphics[width=14cm]{goes_lightcurve.pdf}
-\caption{Creating a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
-2011 June 7 using a time range, and the result of the \texttt{peek()} method.}
+\caption{Example usage of a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
+2011 June 7 using a time range, and the result of the \texttt{peek()} method.
+A sub-interval is then extracted from the Lightcurve and finally the data is resampled
+to 1 hour cadence.}
 \label{code:goes_lc}
-\end{listing}
+\end{Figure}
 
 Alternatively, if the data file already exists on the local system, the 
-\texttt{Lightcurve} object may instead be initialised using that file as input 
-(see Listing \ref{code:lyra_lc}).
-
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import lightcurve
->>> file='lyra_20110607-000000_lev2_std.fits'
->>> lyra=lightcurve.LYRALightCurve.create(file)
->>> lyra.peek()
-\end{minted}
-\includegraphics[width=14cm]{lyra_lightcurve.pdf}
-\caption{Creating a LYRA lightcurve for the full day of 2011 June 7 using an 
-existing data file, and the result of the \texttt{peek()} method}
-\label{code:lyra_lc}
-\end{listing}
-
+\texttt{Lightcurve} object may instead be initialised using that file as input.
 Once the \texttt{Lightcurve} has been created it may be manipulated in 
 a variety of ways in order to perform time series analysis. 
-Continuing from Listing~\ref{code:lyra_lc}, we show a few simple 
+Continuing from Figure~\ref{code:lyra_lc}, we show a few simple 
 examples of using a LYRA lightcurve.
-
-In Listing~\ref{code:lyra_lc} we created a LYRA Lightcurve spanning the 
-full day of 2011 June 7. 
-To extract the sub-interval 06:00 - 07:00 UT into a new \texttt{Lightcurve} 
-called \texttt{lyra\_zoom} we simply do as shown on 
-Listing~\ref{code:lyra_truncate}.
-
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.time import TimeRange
->>> trange=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
->>> lyra_zoom = lyra.truncate(trange)
-\end{minted}
-\caption{Extracting a sub-interval from a Lightcurve.}
-\label{code:lyra_truncate}
-\end{listing}
-
-Also from the example shown in Listing~\ref{code:lyra_lc}, direct access to 
-the data and time information in the object is available through 
-\texttt{lyra.data} and \texttt{lyra.data.index} respectively 
-(see Listing~\ref{code:lyra_pandas}).
-
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> print lyra.data
-<class pandas.core.frame.DataFrame>
-DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
-2011-01-28 23:59:59.983993
-Data columns (total 4 columns):
-CHANNEL1    1496629  non-null values
-CHANNEL2    1496629  non-null values
-CHANNEL3    1496629  non-null values
-CHANNEL4    1496629  non-null values
-dtypes: float64(4)
-
->>> print lyra.data.index
-<class pandas.tseries.index.DatetimeIndex>
-[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
-Length: 1496629, Freq: None, Timezone: None
-\end{minted}
-\caption{Accessing the data and time axis in a Lightcurve}
-\label{code:lyra_pandas}
-\end{listing}

### 2014-01-27 5-Dev.tex

@@
 \section{Development and Community}
-SunPy is a community developed library, it is designed and developed for and by 
+SunPy is a community-developed library, designed and developed for and by 
 the solar physics community. Not only is all the source code publicly available 
@@
 process is also online and open for anyone to contribute to.
-The primary media by which SunPy's development is facilitated is the online 
-service GitHub \footnote{\url{http://github.com}} which makes use of the 
-distributed 
-version control software \href{http://git-scm.com/}{git}.
+SunPy's development makes use of the online 
+service GitHub \footnote{\url{http://github.com}} and \href{http://git-scm.com/}{git} 
+as its distributed version control software.
 
+The continued success of an open source projects depends on many factors of which 
+three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
+active community \cite{bangerth2013}. Several tools (some specific to Python) are used by
+Sunpy to make achieving these goals more accessible. To maintain high quality code, a 
+transparent and collaborative development workflow made possible by Github is used (described
+further below). Sunpy includes a number of unit tests which test the functionality 
+of the code base. Additionally, Sunpy makes use of `continuous integration' provided by
+Travis\footnote{\url{http://travis-ci.org}}, a process by which the addition of any new code 
+automatically triggers a comprehensive review of all unit tests. If any single test
+fails then the community is alerted before the code is accepted. The unit test coverage is
+also monitored by the \href{http://coveralls.io}{Coveralls} service.
+
+Quality documentation is
+one of the most important factors determining the success of any software project. 
+Thankfully powerful tools already exist in Python to support this thanks to native
+Python's focus on its own documentation. Sunpy makes use of the Sphinx\footnote{\url{http://sphinx-doc.org}}
+documentation generator. Sphinx uses reStructuredText as its markup language, 
+an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
+many output formats most notably HTML as well as PDF, and ePub and provides a rich
+hierarchically structured view of in-code documentation strings. The Sunpy documentation 
+s built automatically and hosted on Readthedocs \footnote{\url{http://readthedocs.org}} 
+at \url{http://docs.sunpy.org}.
+
+In order to maintain an active community communication is key.  The Sunpy community makes
+use of a number of channels to communicate. For immediate communications, an active IRC chat
+room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs such as
+developer comments or discussion, a open mailing list is used hosted on Google groups. 
+Discussion of bugs and bug tracking are provided directly on Github as well as new code
+review discussions.
+
+Many of the larger features in SunPy have been developed 
+with the support of both the ESA's Summer Of Code In Space (SOCIS) and the Google
+Summer of Code (GSOC). Initial development of SunPy's VSO and HEK 
+implementations were funded by the SOCIS program as well as a prototyped GUI 
+and N-Dimensional datatype implementations. Sunpy was supported by GSOC in 2013 
+through the Python Software Foundation (PSF). It supported development of the HELIO and 
+database sub-packages.
+
+\subsection{Development Workflow}
 The development workflow that GitHub enables is simple and transparent. The 
@@
 a 'Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
-repository where it can be reviewed by anyone and then accepted by one of the 
-development team who have commit rights to the main SunPy repository.
+repository in order to incorporate their modification into the Sunpy code base. 
+Pull requests are reviewed by the Sunpy community before being accepted. Community consensus
+is required to add new features.
 
 Pull requests are a very powerful tool to maintain code quality, as each line 
-of code that has been modified is highlighted for review. For code to be 
-accepted into the SunPy repository three primary things have to have been 
-completed:
+of code that has been modified is highlighted for review and can be commented on. 
+In order to maintain high quality code the following conditions must typically be met 
+before code is accepted.
 
 \begin{enumerate}
-	\item  The code has to follow 	
+	\item  The code must follow 	
 	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
-	guidelines, this keeps all the code in SunPy (and 99\% of all other Python 
-	code) styled in a consistent manner and easy to read.
+	guidelines, this keeps all the code in Sunpy styled in a consistent manner and easy to read.
 
-	\item The code must be documented. SunPy's documentation is generated by 
-	the Sphinx package, which is automatically run and hosted by 
-	\url{http://readthedocs.org}.
+	\item All new features require documentation in the form of doc strings as well as user
+	guides.
 
-	\item The code must contain full unit test coverage. SunPy code is well 
-	tested and coverage is increasing all the time. All SunPy's tests are 
-	automatically run for each `Pull Request' and branch by the 
-	\href{http://travis-ci.org/sunpy/sunpy}{Travis-CI }	service, and a test 
-	coverage record is kept by 
-	\href{http://coveralls.io/r/sunpy/sunpy}{Coveralls}
+	\item The code must contain significant unit test coverage.
 \end{enumerate}
@@
 This kind of development model is widely used within the scientific Python 
-community as well as buy a wide variety of other projects both open and closed 
+community as well as by a wide variety of other projects both open and closed 
 source.
-
-As well as having a open source and open development model SunPy has a active 
-community, with lots of both on-topic and off-topic chat on the \#SunPy IRC 
-channel on freenode.net and on the mailing lists. The project always welcomes 
-new contributions of any scale.
-
-Many of the larger features added to SunPy during it's life have been added 
-with the aid of both ESA's Summer Of Code In Space (SOCIS) program and Google's 
-Summer of Code (GSOC) program. Initial development of SunPy's VSO and HEK 
-implementations were funded by the SOCIS program as well as a prototyped GUI 
-and N-Dimensional datatype implementations. 2013 was the first year that SunPy 
-obtained GSOC funding, through the Python Software Foundation (PSF). The two 
-projects that were undertaken was the development of a HELIO package and a 
-package for integration between the HEK and VSO, allowing the download of data 
-from VSO relating to a HEK query. As well as the Database module, which 
-provides a single query-able interface between local data and the VSO.

### 2014-01-27 2-2-Lightcurve.tex
updated based on Jack's comments

@@
-\subsection{Lightcurve}
+\subsection{Lightcurve}\label{ssec:lightcurve}
 
-Time series data and analyses are a fundamental aspect of solar physics 
-for which many data sources are available. 
-Sunpy therefore provides a \texttt{LightCurve} object 
-designed to provide a convenient and consistent interface for handling 
-time series data. 
-The main engine behind the \texttt{LightCurve} object is the \texttt{pandas}\footnote{\url{http://pandas.pydata.org}} 
-data analysis library. 
-This library contains a large amount of functionality for manipulating 
-and analysing time series data, making it an ideal basis for 
-\texttt{LightCurve}.  
-Like all other Sunpy objects, \texttt{LightCurve} is a wrapper around 
-a data object, which in this case is the \texttt{pandas} object.
+Time series data and their analysis are a fundamental aspect of solar
+physics for which many data sources are available.  In recognition of
+this fact, SunPy provides a \texttt{LightCurve} object designed to
+provide a convenient and consistent interface for handling solar time
+series data.  The main engine behind the \texttt{LightCurve} object is
+the \texttt{pandas} data analysis library (available at
+\url{http://pandas.pydata.org}).  This library contains a large amount
+of functionality for manipulating and analysing time series data,
+making it an ideal basis for \texttt{LightCurve}.  Like other SunPy
+objects, \texttt{LightCurve} is a wrapper around a data object, which
+in this case is the \texttt{pandas} object.  \texttt{LightCurve}
+assumes that the input data are time-ordered list(s) of numbers.  Each
+list becomes a column in a \texttt{pandas} DataFrame object.
 
-Currently, the \texttt{LightCurve} object is compatible with the following 
-data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, 
-and the SDO EUV Variability Experiment (EVE). 
-For each of these instruments, a sub-class of the \texttt{LightCurve} object 
-is initialised (e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits 
-from \texttt{LightCurve} but allows instrument-specific functionality to be 
-included. 
-Future developments will introduce support for additional instruments and data 
-products. 
-Since time series data is generally relatively small and there is no 
-established standard as to how it should be stored and distributed, 
-each Sunpy \texttt{LightCurve} object provides the ability to download 
-its own data in its constructor.
+Currently, the \texttt{LightCurve} object is compatible with the
+following data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, and
+the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
+average CSV files - see \url{http://lasp.colorado.edu/home/eve/data/}
+for more detail).  For each of these instruments, a sub-class of the
+\texttt{LightCurve} object is initialised
+(e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits from
+\texttt{LightCurve} but allows instrument-specific functionality to be
+included.  Future developments will introduce support for additional
+instruments and data products.  Since time series data is generally
+relatively small and there is no established standard as to how it
+should be stored and distributed, each SunPy \texttt{LightCurve}
+object provides the ability to download its own data in its
+constructor.
 
@@
 
-\begin{Figure}[H]
+\begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}

### 2014-01-27 4-Util.tex

--- 2014-01-26 4-Util.tex
@@
 \end{listing}
+
+\subsubsection{Instruments}
+In addition to providing support for instrument-specific solar data via the main data classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, some instrument-specific functions may be found within the \texttt{instr} package.
+These functions are generally those that are unique to one particular solar instrument, rather than of general use, for example a function to construct a GOES flare event list or a function to query the LYRA timeline annotation file.
+Currently, support is included in this way for the GOES, LYRA, RHESSI and IRIS instruments, while future developments will include support for additional missions.
+It is anticipated that, ultimately, solar missions requiring a large suite of software tools will be supported via a separately maintained package affiliated with SunPy.

### 2014-01-27 2-1-Map.tex
all of my changes

@@
 also provides a convenient interface for loadings data from a variety of sources, typically
-a FITS file as shown in Figure~\ref{code:aia_1}.
+a FITS file as shown in Listing~\ref{code:aia_1}.
 
@@
 for future integration of \texttt{astropy}. In order to provide instrument/
-detector specific integration \textt{GenericMap} is subclassed on creation. 
+detector specific integration \texttt{GenericMap} is subclassed on creation. 
 Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (i.e. factory)
@@
 will then automatically return an instance of the specific \texttt{GenericMap} 
-subclass. As of this version Sunpy has \texttt{Map} specialisations for the 
+subclass. As of this version SunPy has \texttt{Map} specialisations for the 
 following instruments: 
@@
 \end{minted}
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{aia_map_example}
+\end{center}
 \caption{Demonstration of the \texttt{AIAMap} specialisation of 
@@
 provides methods for animation of its series of \texttt{Map} objects. 
-Figure~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
+Listing~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
 with these classes.
-In addition, Figure~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
+In addition, Listing~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
 classes interacts with the \texttt{animation} module to save a video.
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
-import matplotlib.pyplot as plt
-import sunpy.map
-
-#Create a composite map from two files
-compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
-composite=True)
-
-#Set the RHESSI image (index 1) to have contour levels and a red colour map.
-compmap.set_levels(1,range(0,50,5),percent=True)
-compmap.set_colors(1,'Reds_r')
-
+\begin{minted}[bgcolor=bg]{pycon}
+>>> import matplotlib.pyplot as plt
+>>> import sunpy.map
+>>> compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
+...                         composite=True)
+>>> compmap.set_levels(1, range(0,50,5), percent=True)
+>>> compmap.set_colors(1, 'Reds_r')
 #Plot the result and crop
-ax = plt.subplot()
-compmap.plot()
-ax.axis([200,600,-600,-200])
+>>> ax = plt.subplot()
+>>> compmap.plot()
+>>> ax.axis([200, 600, -600, -200])
+>>> plt.show()
 \end{minted}
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{comp_map_example}
+\end{center}
 \caption{Example demonstrating a CompositeMap plot, using contours and how 
@@
 
+%schriste - stuart, i agree if you want to remove the following two listings.
 \begin{listing}[H]
@@
 \end{minted}
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{aia_cube_controls}
+\end{center}
 \caption{An example showing creation of a MapCube from a glob file search. The 

### 2014-01-27 2-Data_Types.tex
added bg to listings in visualisation section
all of my changes

--- 2014-01-23 2-Data_Types.tex
@@
 \section{Core Data Types}
-One of the primary focus' of the SunPy library is to provide data structures 
-that are specifically designed for the various types of data generally 
-processed for solar physics. Currently SunPy provides three data 
-types, each separate from one another to process 2D spatial data 
+The primary focus of the SunPy package is to provide data structures 
+that are specifically designed for the various types of solar physics data, namely
+images, time series, and spectra. SunPy provides three data core
+objects to support these data types, 2D spatial data 
 (\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
-(\texttt{Spectrum} and \texttt{Spectra}).
+(\texttt{Spectrum} and \texttt{Spectrogram}).
 
-The design of SunPy's core data types is as a wrapper around a data object, 
-either a \texttt{numpy} \texttt{ndarray} or a \texttt{pandas} 
-\texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
-\texttt{LightCurve} respectively. Each data type has a \texttt{.data} 
-attribute where this data object is located and some meta data. It is 
+The philosophy of these objects is that they should provide a access to the original data
+along with associated meta data and provide appropriate convenience functions to
+enable data analysis and visualization. For all core data types, the data is stored in 
+stored in the \texttt{.data}) attribute while the meta data is stored 
+in the \texttt{.meta} attribute. It is 
 possible to instantiate the data types from various different 
-sources, \textit{e.g.} files, urls, arrays or time ranges. The 
-specific sources supported is dependant upon which data type and 
-which instrument. All the SunPy data types support specialisation on 
-a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
-\texttt{AIAMap} sub-type. This design allows simple extensions to 
-cope with the diversity of data from different sources in solar 
-physics. As well as support for different instruments and data 
-sources each data type supports different visualisation wrappers that 
-allow both quick view plotting (the peek command) and more 
-fine-grained control plotting that integrates well with 
-\texttt{matplotlib} (the plot command).
+sources, \textit{e.g.} files, urls, arrays or time ranges.  In order to provide
+instrument-specific specialisation, all the core SunPy data types support specialisation, 
+\textit{i.e.} \texttt{Map} has an \texttt{AIAMap} sub-type. 
+Data visualisation is provided by two functions; \texttt{peek()}, allows quick view plotting
+, while more fine-grained control plotting that integrates with 
+\texttt{matplotlib} is provided by \texttt{plot()}.
 
@@
 the pyplot functional interface of matplotlib, as demonstrated in 
-Listing \ref{code:mpl_1}.
+Figure \ref{code:mpl_1}.
 
+%schriste - I vote for removing all of the following code as being too down in the weeds
 \begin{listing}[H]
 \begin{minipage}{0.49\columnwidth}
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{python}
 import sunpy.map
@@
 #Read in a aia file using SunPy
-aiamap = sunpy.map.Map('aia.fits')
+aiamap = SunPy.map.Map('aia.fits')
 
@@
 \begin{minipage}{0.49\columnwidth}
-\begin{minted}{python}
-import sunpy.map
+\begin{minted}[bgcolor=bg]{python}
+import SunPy.map
 import matplotlib.pyplot as plt
@@
 More technically what is done in the plotting routines is firstly, to 
-make sure that the current state of the figure and axes is mantined 
+make sure that the current state of the figure and axes is mantained 
 in the same way as it is inside the \texttt{pyplot} functions. For 

### 2014-01-27 3-4-Helioviewer.tex
all of my changes

@@
 
-SunPy provides the ability to download images from Helioviewer Project 
-servers.  The aim of the Helioviewer Project is to enable the exploration of 
+SunPy provides the ability to download images hosted by the Helioviewer Project.  
+The aim of the Helioviewer Project is to enable the exploration of 
 solar and heliospheric data from multiple data sources (such as instrumentation 
@@
 data provided by the Helioviewer Project are images in the JPEG2000 format (for 
-further details on the Helioviewer Project see \cite{muller2009} 
-\footnote{SunPy is used in Helioviewer production servers to manage the 
-download and ingestion of JPEG2000 files from remote servers.}.)  The JPEG2000 
+further details on the Helioviewer Project see \cite{muller2009}). 
+SunPy is used in Helioviewer production servers to manage the 
+download and ingestion of JPEG2000 files from remote servers.  The JPEG2000 
 files are typically highly compressed compared to the source FITS files they 
@@
 \ref{code:hv:datasources}.
-
-\begin{listing}
-\begin{minted}{python}
-from sunpy.net.helioviewer import HelioviewerClient
-
-hv = HelioviewerClient()
-datasources = hv.get_data_sources()
+%schriste - what is the point of the following listing? remove?
+\begin{listing}[H]
+\begin{minted}{pycon}
+>>> from sunpy.net.helioviewer import HelioviewerClient
+>>> hv = HelioviewerClient()
+>>> datasources = hv.get_data_sources()
 
 # print a list of datasources and their associated ids
-for observatory, instruments in datasources.items():
-    for inst, detectors in instruments.items():
-        for det, measurements in detectors.items():
-            for meas, params in measurements.items():
-                print("%s %s: %d" % (observatory, params['nickname'], 
-                %%%%params['sourceId']))
+>>> for observatory, instruments in datasources.items():
+>>>     for inst, detectors in instruments.items():
+>>>         for det, measurements in detectors.items():
+>>>             for meas, params in measurements.items():
+>>>                 print(observatory, params['nickname'], 
+>>>                 params['sourceId']))
 \end{minted}
@@
 
-\begin{listing}
+\begin{listing}[H]
 \begin{minted}{python}
@@
 \end{minted}
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example}
+\end{center}
 \caption{Acquisition of a PNG image composed from data from three
@@
 
-\begin{listing}
-\begin{minted}{python}
-filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
- instrument='HMI', detector='HMI', measurement='continuum')
-from sunpy.map import Map
-hmi = Map(filepath)
-hmi.submap([200,550],[-400,-200]).peek()
+\begin{listing}[H]
+\begin{minted}{pycon}
+>>> filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
+>>>                            instrument='HMI', detector='HMI', 
+>>>                            measurement='continuum')
+>>> from sunpy.map import Map
+>>> hmi = Map(filepath)
+>>> hmi.submap([200,550],[-400,-200]).peek()
 \end{minted}
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
+\end{center}
 \caption{Acquisition and display of a Helioviewer JPEG2000 file as a

### 2014-01-27 1-Introduction.tex

@@
 \section{Introduction}
-Modern solar physics and astrophysics, along with most of modern science is 
-increasingly becoming data-driven. Where observational and numerical data is 
-being produced at a faster rate than new hypotheses. For example, NASA's Solar 
-Dynamics Observatory (SDO) satellite records over 1 TB of data per day all of 
-which is telemetered to the ground and available for analysis.
-Solar physics therefore requires increasingly complex software tools to enable 
-scientific discovery by analysis of this data. To make meaningful and 
-reproducible advances in our understanding of the Sun it is important that the 
-software tools to be standardised, easy to use, and transparent, so that the 
-community can build upon a common foundation.
+Science, including solar physics and astrophysics, is driven by the analysis 
+and summarizing of data. Modern advances in sensor technology combined with 
+the availability of cheap storage and large bandwidth communications has led to 
+a rapid and overwhelming increase in amount of data which scientists are responsible
+for analyzing. For example, NASA's Solar 
+Dynamics Observatory (SDO) satellite records over 1 TB of data per day. To analyze this 
+mountain of data and enable scientific discovery requires increasingly complex software 
+tools. Standardised, easy to use,
+and transparent software tools are a key enabling technology in the scientific endeavor
+so that the community can build upon a common foundation.
+%schriste - the opening paragraph still needs work
 
@@
 the top ten most popular programming languages in the world according to the 
-2014 TIOBE Index 
-\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
 and is widely used outside of scientific fields in web development, education 
-and even 3D game design.
+and `big data' analytics.
 
@@
 \textit{i.e.} array manipulation, core numerical algorithms and visualisation. 
-Ontop of this packages such as \texttt{Astropy}, \texttt{pandas} and 
-\texttt{scikit-image} provide a tremendous amount of more domain-specific 
-functionality.
+Build upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
+\texttt{scikit-image} provide more domain-specific functionality.
 
@@
 capabilities, an overview of the development model and community aspects of the 
-SunPy project as well as future plans. The latest release of SunPy is available 
-in PyPI and can be installed in the usual manner for a Python package
-\footnote{http://docs.sunpy.org/en/latest/sunpy/guide/installation/index.html}.
+SunPy project as well as future plans. The latest release of SunPy (0.4) from
+the sunpy website (\url{http://sunpy.org}) or can be installed using 
+the Python package index (\mbox{\url{http://pypi.python.org/pypi}}).
+%schriste - the mbox prevents latex from breaking the url across different lines.

### 2014-01-27 2-2-Lightcurve.tex

@@
 Firstly, a \texttt{LightCurve} may be created for a specific instrument based 
-on an input time range. In Figure~\ref{code:goes_lc_code}, 
+on an input time range. In Listing~\ref{code:goes_lc}, 
 the LightCurve constructor searches a remote site for the GOES X-ray data 
@@
 >>> trange=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
->>> goes_zoom = goes.truncate(trange)
+%>>> goes_zoom = goes.truncate(trange)
 % the above does not work!
@@
 \end{minted}
-\includegraphics[width=14cm]{goes_lightcurve.pdf}
+\begin{center}
+\includegraphics[width=10cm]{goes_lightcurve.pdf}
+\end{center}
 \caption{Example usage of a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
@@
 \label{code:goes_lc}
-\end{Figure}
+\end{listing}
+%schriste - note to self, fix this example, add resampled points on top of plot?
 
@@
 a variety of ways in order to perform time series analysis.
-Continuing from Figure~\ref{code:lyra_lc}, we show a few simple 
-examples of using a LYRA lightcurve.

### 2014-01-27 2-3-Spectra.tex

@@
 \subsection{Spectra}\label{sec:spectra}
+%schriste - this section needs major work
 
@@
 Nevertheless, the \texttt{Spectra} object has been designed to be consistent with the 
-other data types available in Sunpy.
+other data types available in SunPy.
 It was implemented as a wrapper around a data array (numpy ndarray)
 because its 1D nature (intensity versus frequency).
-Using the \texttt{Spectra} object, Sunpy also offers a 2D array object called \texttt{Spectrogram},
+Using the \texttt{Spectra} object, SunPy also offers a 2D array object called \texttt{Spectrogram},
 which it is built as a group of spectrum meassured over time.
@@
 Group at Trinity College Dublin.
-As yet, Sunpy \texttt{Spectrogram} object supports radio spectra from the e-Callisto 
-network\footnote{e-Callisto is an international network of solar radio spectrometers, 
-                 all the data is available at: \url{http://www.e-callisto.org/} } 
+As yet, SunPy \texttt{Spectrogram} object supports radio spectra from the e-Callisto 
+solar radio spectrometer network(\url{http://www.e-callisto.org/}).
 and STEREO/SWAVES spectrograms.
@@
 only requires the observatory name and the desired time-range. 
-STEREO/SWAVES data can be obtained via the virtual solar observatory (see \S\ref{sec:vso}).
+STEREO/SWAVES data can be obtained via the virtual solar observatory (see \S\ref{ssec:vso}).
 
@@
 the observatory of interest.  In this case the data is requested from \textit{BIR} which is the code name of the
-Rosse Observatory at Birr Castle (Ireland)\footnote{\url{http://www.rosseobservatory.ie}}.
+Rosse Observatory at Birr Castle (Ireland)(\url{http://www.rosseobservatory.ie}).
 When the data is requested using the \texttt{.from\_range} function, the object merges
@@
 \begin{minted}[bgcolor=bg]{python}
-from sunpy.spectra.sources.callisto import CallistoSpectrogram
+from SunPy.spectra.sources.callisto import CallistoSpectrogram
 tstart = "2011-06-07T06:00:00"
@@
 callisto_nobg = callisto.substract_bg()
-callisto.peek()
 callisto_nobg.peek(vmin = 0)
 \end{minted}
-\includegraphics[width=0.8\columnwidth]{callisto} %\hfill
+\begin{center}
 \includegraphics[width=0.8\columnwidth]{callisto_nobg}
+\end{center}
 \caption{Demonstration of how \texttt{CallistoSpectrogram} object retrieve the data

### 2014-01-27 3-1-VSO.tex

@@
 time, instrument, wavelength, or  other properties.
+The also shows how to download the data using the result
+from the query. One can use the metadata associated with the data sets to specify how the
+files will be named locally, such as creating subdirectories based on the
+instrument names.
+
 Listing~\ref{code:vso_query_advanced} shows examples of how to make advanced
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net import vso
+>>> from SunPy.net import vso
 >>> client = vso.VSOClient()
@@
 ...
+>>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
+>>> results = client.get(coronagraphs, path = pathformat)
 \end{minted}
-\caption{Example of querying a single instrument over a time range.}
+\caption{Example of querying a single instrument over a time range and downloading the data}
 \label{code:vso_query_simple}
@@
 
+%schriste - what about just listing the sources as an array to instead of doing a show
+%           to make the point that the | query worked appropriately? That would make this
+%            listing much shorter.
 \begin{listing}[h]
@@
 \end{listing}
-
-Listing~\ref{code:vso_down} shows how to download the data using the result
-from the query.
-One can use the metadata associated with the data sets to specify how the
-files will be named locally, such as creating subdirectories based on the
-instrument names.
-
-\begin{listing}[h]
-\begin{minted}[bgcolor=bg]{pycon}
->>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
->>> results = client.get(coronagraphs, path = pathformat)
-\end{minted}
-\caption{Example of how to download data using a query result, continuing from
-listing~\ref{code:vso_query_advanced}).}
-\label{code:vso_down}
-\end{listing}

### 2014-01-27 3-2-HEK.tex

@@
 
-The Sun is an active star and exhibits a wide range of phenomena on many 
+The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
+radio burst) on many 
 different time-scales, length-scales and wavelengths. Observations and metadata 
@@
 the Solar Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
-populate the HEK.  The advantage of the HEK to SunPy is that it is a single 
-service that provides a homogeneous and well-described interface to a large 
+populate the HEK.  The advantage of the HEK is it provides a homogeneous and 
+well-described interface to a large 
 amount of feature/event information of interest to the solar physics community.
@@
 SunPy accesses this information through the \texttt{hek} module, which was 
-developed through support from the European Space Agency Summer of Code in 
+developed with support from the European Space Agency Summer of Code in 
 Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of the HEK API
 (\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
-Every event type has required and optional properties; the current list of 
+The current list of 
 events maintained by the HEK and their properties can be found at 
@@
 Simple HEK queries consist of start time, an end time, and an event type 
-(Listing \ref{code:hek:simple}). Times can be specified in any SunPy-acceptable 
-format. Event types are specified as upper case, two letter strings, and are 
+(Listing \ref{code:hek:simple}). Event types are specified as upper case, 
+two letter strings, and are 
 identical to the two letter abbreviations found at the HEK website, 
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
-from sunpy.net import hek
-client = hek.HEKClient()
-tstart = '2011/08/09 07:23:56'
-tend = '2011/08/09 12:40:29'
-event_type = 'FL'
-result = client.query(hek.attrs.Time(tstart,tend), 
-hek.attrs.EventType(event_type))
+\begin{minted}[bgcolor=bg]{pycon}
+>>> from sunpy.net import hek
+>>> client = hek.HEKClient()
+>>> tstart = '2011/08/09 00:00:00'
+>>> tend = '2011/08/10 00:00:00'
+# FL = flare
+>>> event_type = 'FL'
+>>> result = client.query(hek.attrs.Time(tstart,tend), 
+...                       hek.attrs.EventType(event_type))
+>>> len(result)
+52
 \end{minted}
-\caption{Simple HEK query, returning 19 entries.}
+\caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
+which occurred on the 2011/08/09.}
 \label{code:hek:simple}
@@
 event.  As was mentioned above, the HEK stores feature/event metadata obtained 
-in different ways, known generally as {\it feature recognition methods}, or 
-FRMs. Example \ref{code:hek:frm} filters the results of the previous result to 
+in different ways, known generally as {\it feature recognition methods} ( 
+FRMs). Example \ref{code:hek:frm} filters the results of the previous result to 
 return only those events that have the FRM 'SSW Latest Events'.
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
-result = client.query(hek.attrs.Time(tstart,tend), 
+\begin{minted}[bgcolor=bg]{pycon}
+>>> result = client.query(hek.attrs.Time(tstart,tend), 
                       hek.attrs.EventType(event_type),
                       hek.attrs.FRM.Name == 'SSW Latest Events')
+>>> len(result)
+9
 \end{minted}
@@
 \begin{minted}[bgcolor=bg]{python}
-result = client.query(hek.attrs.Time(tstart,tend), 
-                      hek.attrs.EventType(event_type),
-      (hek.attrs.Event.Coord1 > 50) or (hek.attrs.FL.PeakFlux > 1000.0))
+>>> result = client.query(hek.attrs.Time(tstart,tend), 
+...                       hek.attrs.EventType(event_type),
+...                       (hek.attrs.Event.Coord1 > 50) 
+...                       or (hek.attrs.FL.PeakFlux > 1000.0))
 \end{minted}
@@
 The ability to use comparison and logical operators on HEK attributes allows 
-the construction of queries of almost arbitrary complexity, bringing powerful 
-feature/event search capabilities to SunPy. It is also possible to use the 
+the construction of queries of almost arbitrary complexity. 
+It is also possible to use the 
 results of a HEK query to download the corresponding data from the VSO by using 
 SunPy's \texttt{H2VClient}.
+%schriste - this is a weird way to end this section, either show how it is done or 
+% do not mention it, i think.

### 2014-01-27 3-3-HELIO.tex
Minor edit

@@
 The HELiophysics Integrated Observatory 
-(HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web 
+(HELIO, \url{http://helio-vo.eu}) has put together a list of web 
 services which allows scientists to query and discover data throughout 
 the heliosphere (\textit{e.g.}, solar, planetary, inter-planetary data, 
-\ldots)\cite{dps2012}. 
+\ldots)\citep{dps2012}.
 HELIO has been built with a Service-Oriented Architecture, 
@@
 >>> hc = hec.Client()
-
-Desired time range and event type
 >>> tstart, tend = '2011-06-07T06:00:00', '2011-06-07T12:00:00'

### 2014-01-27 3-5-Database.tex
typos

@@
 is typically a cumbersome task for the average user. The file database is a sub-package of 
-Sunpy which is meant to solve this problem by providing a unified database to store and manage information about 
+SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
 local data files. The database package was developed as part of the 2013 
@@
 The database sub-package makes use of a database supported by
-SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}. This library was chosen
+SQLAlchemy(\url{http://www.sqlalchemy.org}). This library was chosen
 since it supports many SQL dialects. If SQLite is choosen, the database is stored as a single file which is
-created automatically. This solution makes it possibly to easily backup, copy and distribute
+created automatically. This solution makes it possible to easily backup, copy and distribute
 a database file. A server-based database, on the other hand, could be used by a collaboration 
@@
 Using the database package, one uses the \texttt{Database} class to connect
-with a database and perform operations on it. Figure~\ref{code:database} shows how to connect
-to an in-memory database and download data from the \textsc{VSO}. These entried are
+with a database and perform operations on it. Listing~\ref{code:database} shows how to connect
+to an in-memory database and download data from the \textsc{VSO}. These entries are
 automatically added to the database. The function \texttt{len} is used to get the number of

### 2014-01-27 4-Util.tex

@@
 >>> from sunpy import wcs
-Find the helioprojective coordinate of a given longitude and latitude on the Sun
 >>> wcs.convert_hg_hpc(10,53)
 (100.49244115330731, 767.97438321917502)
-Convert that position back to heliographic coordinates
+# Convert that position back to heliographic coordinates
 >>> wcs.convert_hpc_hg(100.49, 767.97)
 (9.9996521808465175, 52.999563684874893)
-Try to convert a position which is not on the Sun to heliographic coordinates
+# Try to convert a position which is not on the Sun to HG
 >>> wcs.convert_hpc_hg(-1500,0)
@@
 (nan, nan)
-Convert sky coordinate to a position on the Sun in cartesian coordinates (HCC)
+Convert sky coordinate to a position in HCC
 >>> wcs.convert_hpc_hcc(-300,400, z = True)
@@
   Reference = Allen's Astrophysical Quantities 4th Ed.
-Verify the average density of the Sun and convert to cgs
+# Verify the average density of the Sun and convert to cgs
 >>> (sun.mass/sun.volume).cgs
 <Quantity 1.40851154227 g / (cm3)>
-Check to see if the age of the Sun is available and grab the unit and value separately
+# Search for the age of the Sun
 >>> sun.find('age')
@@
 >>> sun.value('age'), sun.unit('age')
-
+(4600000000.0, Unit("yr"))
 \end{minted}
@@
 \subsubsection{Instruments}
-In addition to providing support for instrument-specific solar data via the main data classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, some instrument-specific functions may be found within the \texttt{instr} package.
-These functions are generally those that are unique to one particular solar instrument, rather than of general use, for example a function to construct a GOES flare event list or a function to query the LYRA timeline annotation file.
-Currently, support is included in this way for the GOES, LYRA, RHESSI and IRIS instruments, while future developments will include support for additional missions.
-It is anticipated that, ultimately, solar missions requiring a large suite of software tools will be supported via a separately maintained package affiliated with SunPy.
+In addition to providing support for instrument-specific solar data via the main data 
+classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, 
+some instrument-specific functions may be found within the \texttt{instr} package. 
+These functions are generally those that are unique to one particular solar instrument, 
+rather than of general use, for example a function to construct a GOES flare event list 
+or a function to query the LYRA timeline annotation file. Currently, some support is included
+ in this way for the GOES, LYRA, RHESSI and IRIS instruments, while future developments 
+ will include support for additional missions. It is anticipated that, ultimately, solar
+  missions requiring a large suite of software tools will be supported via a separately 
+  maintained package affiliated with SunPy.

### 2014-01-27 5-Dev.tex

@@
 the solar physics community. Not only is all the source code publicly available 
-online under the permissive 2-clause BSD licence 
-\footnote{\url{http://opensource.org/licenses/BSD-2-Clause}}, the whole 
+online under the permissive 2-clause BSD licence, the whole 
 development 
@@
 SunPy's development makes use of the online 
-service GitHub \footnote{\url{http://github.com}} and \href{http://git-scm.com/}{git} 
+service GitHub (\url{http://github.com}) and git\footnote{\url{http://git-scm.com/}}
 as its distributed version control software.
@@
 of the code base. Additionally, Sunpy makes use of `continuous integration' provided by
-Travis\footnote{\url{http://travis-ci.org}}, a process by which the addition of any new code 
+Travis(\url{http://travis-ci.org}), a process by which the addition of any new code 
 automatically triggers a comprehensive review of all unit tests. If any single test
@@
 Thankfully powerful tools already exist in Python to support this thanks to native
-Python's focus on its own documentation. Sunpy makes use of the Sphinx\footnote{\url{http://sphinx-doc.org}}
+Python's focus on its own documentation. Sunpy makes use of the Sphinx (\url{http://sphinx-doc.org})
 documentation generator. Sphinx uses reStructuredText as its markup language, 
@@
 hierarchically structured view of in-code documentation strings. The Sunpy documentation 
-s built automatically and hosted on Readthedocs \footnote{\url{http://readthedocs.org}} 
+s built automatically and hosted on Readthedocs (\url{http://readthedocs.org})
 at \url{http://docs.sunpy.org}.

### 2014-01-27 solarsoft.tex

@@
 I/O. It is composed of 89\% IDL code while the remainder is mostly Perl (5.4\%) 
-and csh scripts (3.8\%) \footnote{{\bf This data was calculated using...}}. 
-According to data generated using David A. Wheeler's 'SLOCCount' 
-\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
+and csh scripts (3.8\%). 
+According to data generated using David A. Wheeler's 'SLOCCount'\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
 289,724 lines of code with a total approximate value of \$10.4M (based on the 
-Basic COCOMO model \citep{_cocomo_2014}). \footnote{{\bf This data was 
-calculated using...} If we can add them to the repository will improve the 
-quality of the paper and we can always repeat the calculation in the future}. 
+Basic COCOMO model \citep{_cocomo_2014}). 
+%stuart - This data was calculated using...} If we can add them to the repository 
+%will improve the quality of the paper and we can always repeat the calculation in the future.
+%schriste - i don't know what you mean by this 
 Individual missions and instruments provide additional optional packages to 
@@
 and distributed by the Lockheed Martin Solar and Astrophysics Laboratory.
-\footnote{Do we know whether they have some licence owning it? do we know the 
-SolarSoft licence at all?}
 %The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
@@
 %
-\footnote{We need to be careful with this! IDL means more things that our 
-beloved ``Interactive Data Language''. If we search for that and programming 
-then we get just 7 books! - from which 5 are just the same. I don't know how we 
-could make a more accurate search.
-If we script it it would be amazing!  Also, I would just provide the order
-of magnitude, and not a exact number, i.e. 190 and 1800 results} 
+%stuart - \footnote{We need to be careful with this! IDL means more things that our 
+%beloved Interactive Data Language. If we search for that and programming 
+%then we get just 7 books! - from which 5 are just the same. I don't know how we 
+%could make a more accurate search.
+%If we script it it would be amazing!  Also, I would just provide the order
+%of magnitude, and not a exact number, i.e. 190 and 1800 results}
 % 
+% schriste - I think we defined IDL properly. I was being generous with the book search for IDL
 on Amazon for books on IDL programming generated $189$ results while a search 

### 2014-01-27 2-Data_Types.tex
First glob of edits

@@
 \section{Core Data Types}
-The primary focus of the SunPy package is to provide data structures 
-that are specifically designed for the various types of solar physics data, namely
-images, time series, and spectra. SunPy provides three data core
-objects to support these data types, 2D spatial data 
-(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
-(\texttt{Spectrum} and \texttt{Spectrogram}).
+The primary focus of SunPy is to provide data structures 
+that are specifically designed for the various kinds of solar physics data, namely
+images, time series, and spectra. SunPy provides three core data
+types using Python classes:
+\texttt{Map} (2D spatial data),
+\texttt{LightCurve} (1D temporal series)
+and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).
 
-The philosophy of these objects is that they should provide a access to the original data
-along with associated meta data and provide appropriate convenience functions to
-enable data analysis and visualization. For all core data types, the data is stored in 
-stored in the \texttt{.data}) attribute while the meta data is stored 
+The classes provide access to the original data
+along with associated metadata and provide appropriate convenience functions to
+enable data analysis and visualization. For each of these classes, the data is
+stored in the \texttt{.data} attribute while the metadata is stored 
 in the \texttt{.meta} attribute. It is 
 possible to instantiate the data types from various different 
-sources, \textit{e.g.} files, urls, arrays or time ranges.  In order to provide
-instrument-specific specialisation, all the core SunPy data types support specialisation, 
-\textit{i.e.} \texttt{Map} has an \texttt{AIAMap} sub-type. 
-Data visualisation is provided by two functions; \texttt{peek()}, allows quick view plotting
-, while more fine-grained control plotting that integrates with 
-\texttt{matplotlib} is provided by \texttt{plot()}.
+sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order to provide
+instrument-specific specialisation, all the core SunPy data types support specialisation;
+\textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} sub-type. 
+Data visualisation is provided by two functions: \texttt{peek()}, for quick plotting,
+and \texttt{plot()}, for more fine-grained control plotting that integrates with 
+\texttt{matplotlib}.
 
 This section will give a brief overview of the \textit{current} functionality 
-of each of these modules.
+of each of these data types.
 
@@
 As has been demonstrated in this section, the core SunPy datatypes 
-include visualisation code that is specialised to that data type. 
+include visualisation code that is tailored to that data type. 
 These visualisation methods all currently utilise the matplotlib 
 package, and are designed in such a way that they integrate well with 
-the pyplot functional interface of matplotlib, as demonstrated in 
+the \texttt{pyplot} functional interface of \texttt{matplotlib}, as demonstrated in 
 Figure \ref{code:mpl_1}.
@@
 \caption{A simple example of how SunPy's plotting functions provide similar 
-behaviour to matplotlib's pyplot interface.}
+behaviour to the \texttt{matplotlib.pyplot} interface.}
 \label{code:mpl_1}
@@
 This design philosophy makes the behaviour of SunPy's visualisation 
-routines intuitive to those who already understand how matplotlib's 
-interface is designed as well as allowing the use of the standard 
-matplotlib commands to change the plot, \textit{e.g.} set the title. 
+routines intuitive to those who already understand the \texttt{matplotlib}
+interface, as well as allowing the use of the standard 
+\texttt{matplotlib} commands to manipulate the plot parameters, such as the title.
+
+%ayshih - I recommend removing the following sentences
 More technically what is done in the plotting routines is firstly, to 
-make sure that the current state of the figure and axes is mantained 
+make sure that the current state of the figure and axes is maintained 
 in the same way as it is inside the \texttt{pyplot} functions. For 

### 2014-01-27 3-3-HELIO.tex
First glob of edits

@@
 
-Obtain from all the catalogues these which name contain our event of interest
+#Obtain from all the catalogues these which name contain our event of interest
 >>> catalogues = hc.get_table_names()
 >>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
->>> print catalogues_event
-['hi_cme_list', 'cactus_stereoa_cme', 'icme_earth_cycle23', 'cactus_cme_list', '
-goes_flare_no_sep_radio_cme', 'ulysses_swoops_icme', 'cme_forbush_event', 'seeds
-_cme', 'cme_inner_heliosphere', 'mars_earth_icme', 'stereo_hi_cme', 'cactus_ster
-eob_cme', 'cactus_soho_cme', 'lasco_cme_list', 'cactus_stb_cme_list', 'cactus_so
-ho_cme_list', 'halo_cme_flare_magnetic_storm', 'lasco_cme_cat', 'cactus_sta_cme_
-list', 'stereoa_impactplastic_icme', 'stereob_impactplastic_icme', 'soho_lasco_c
-me', 'stereo_impactplastic_icme', 'wind_typeii_soho_cme']
 
-Query all the catalogues that comes from cactus
+#Query all the catalogues that comes from cactus
 >>> results = [hc.time_query(tstart, tend, event) 

### 2014-01-28 3-2-HEK.tex
Second glob of edits

@@
 >>> client = hek.HEKClient()
->>> tstart = '2011/08/09 00:00:00'
->>> tend = '2011/08/10 00:00:00'
-# FL = flare
->>> event_type = 'FL'
+>>> tstart, tend = '2011/08/09 00:00:00', '2011/08/10 00:00:00'
+>>> event_type = 'FL' # 'FL' indicates flare
 >>> result = client.query(hek.attrs.Time(tstart,tend), 

### 2014-01-28 3-3-HELIO.tex
Second glob of edits

@@
 
-#Obtain from all the catalogues these which name contain our event of interest
+# Obtain from all the catalogues these which name contain our event of interest
 >>> catalogues = hc.get_table_names()
@@
 
-#Query all the catalogues that comes from cactus
+# Query all the catalogues that comes from cactus
 >>> results = [hc.time_query(tstart, tend, event) 

### 2014-01-28 2-2-Lightcurve.tex

@@
 Time series data and their analysis are a fundamental aspect of solar
-physics for which many data sources are available.  In recognition of
-this fact, SunPy provides a \texttt{LightCurve} object designed to
-provide a convenient and consistent interface for handling solar time
-series data.  The main engine behind the \texttt{LightCurve} object is
-the \texttt{pandas} data analysis library (available at
-\url{http://pandas.pydata.org}).  This library contains a large amount
-of functionality for manipulating and analysing time series data,
-making it an ideal basis for \texttt{LightCurve}.  Like other SunPy
-objects, \texttt{LightCurve} is a wrapper around a data object, which
-in this case is the \texttt{pandas} object.  \texttt{LightCurve}
-assumes that the input data are time-ordered list(s) of numbers.  Each
-list becomes a column in a \texttt{pandas} DataFrame object.
+physics for which many data sources are available.
+SunPy provides a \texttt{LightCurve} class
+with a convenient and consistent interface for handling solar time-series
+data.  The main engine behind the \texttt{LightCurve} class is
+the \texttt{pandas} data-analysis library (\url{http://pandas.pydata.org}),
+and \texttt{LightCurve}'s
+\texttt{.data} attribute is a \texttt{pandas.DataFrame} class.
+The \texttt{pandas} library contains a large amount
+of functionality for manipulating and analysing time-series data,
+making it an ideal basis for \texttt{LightCurve}.  \texttt{LightCurve}
+assumes that the input data are time-ordered list(s) of numbers, and each
+list becomes a column in the \texttt{pandas} DataFrame class.
 
-Currently, the \texttt{LightCurve} object is compatible with the
+Currently, the \texttt{LightCurve} class is compatible with the
 following data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, and
 the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
-average CSV files - see \url{http://lasp.colorado.edu/home/eve/data/}
-for more detail).  For each of these instruments, a sub-class of the
+average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
+for more detail).  For each of these instruments, a subclass of the
 \texttt{LightCurve} object is initialised
-(e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits from
+(\textit{e.g.}, \texttt{GOESLightCurve}) which inherits from
 \texttt{LightCurve} but allows instrument-specific functionality to be
 included.  Future developments will introduce support for additional
-instruments and data products.  Since time series data is generally
-relatively small and there is no established standard as to how it
+instruments and data products.  Since there is no established standard
+as to how time-series data
 should be stored and distributed, each SunPy \texttt{LightCurve}
-object provides the ability to download its own data in its
-constructor.
+object provides the ability to download its corresponding specific
+data format in its constructor.
 
@@
 
-A \texttt{LightCurve} object may be created using a range of different methods. 
-Firstly, a \texttt{LightCurve} may be created for a specific instrument based 
-on an input time range. In Listing~\ref{code:goes_lc}, 
-the LightCurve constructor searches a remote site for the GOES X-ray data 
+A \texttt{LightCurve} object may be created using a number of different methods. 
+Firstly, a \texttt{LightCurve} may be created for a specific instrument given
+an input time range. In Listing~\ref{code:goes_lc}, 
+the \texttt{LightCurve} constructor searches a remote site for the GOES X-ray data 
 specified by the time interval, downloads the required files and subsequently 
@@
 >>> from sunpy.time import TimeRange
->>> goes=lightcurve.GOESLightCurve.create('2011-06-07 06:00',
+>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
 ...                                         '2011-06-07 10:00')
 >>> goes.peek()
->>> trange=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+>>> trange = TimeRange('2011-06-07 06:00','2011-06-07 07:00')
 %>>> goes_zoom = goes.truncate(trange)
@@
 \end{center}
-\caption{Example usage of a GOES lightcurve for the time interval 06:00 - 08:00 UT on 
-2011 June 7 using a time range, and the result of the \texttt{peek()} method.
+\caption{Example retrieval of a GOES lightcurve for the time interval 06:00--08:00 UT on 
+2011 June 7 using a time range, and the output of the \texttt{peek()} method.
 A sub-interval is then extracted from the Lightcurve and finally the data is resampled
@@
 \texttt{Lightcurve} object may instead be initialised using that file as input.
-Once the \texttt{Lightcurve} has been created it may be manipulated in 
-a variety of ways in order to perform time series analysis.
+Once the \texttt{Lightcurve} has been created, it may be manipulated in 
+a variety of ways in order to perform time-series analysis.

### 2014-01-28 4-Util.tex

@@
 \begin{listing}[H]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy import wcs
@@
 \begin{listing}[H]
-\begin{minted}{pycon}
-
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.sun import constants as sun

### 2014-01-28 solarsoft.tex

@@
 This section compares the SunPy library that is described in Sections 
-\ref{sec:DataTypes} - \ref{sec:util} with the current de-facto standard solar 
-physics data analysis library, SolarSoft (SSW) \citep{freeland1998}.
+\ref{sec:DataTypes}--\ref{sec:util} with the current de-facto standard solar 
+physics data analysis library: SolarSoft (SSW) \citep{freeland1998}.
 SolarSoft is a set of integrated software libraries, databases, and system 
-utilities which provide a common programming and data analysis environment for 
+utilities which provide a common programming and data-analysis environment for 
 solar physics. SSW is modular in nature, which allows users to add required 
@@
 
-It is overwhelmingly an environment which relies upon IDL (Interactive Data 
+SSW relies upon IDL (Interactive Data 
 Language), a commercial and closed-source interactive data analysis environment 
 sold by Exelis, a global aerospace, defence, information and services company. 
-The SSW `gen' package provides the base analysis capabilities such as time 
-series analysis, time conversions, spectral fitting, image display, and file 
+The SSW `gen' package provides the base analysis capabilities such as time-series
+analysis, time conversions, spectral fitting, image display, and file 
 I/O. It is composed of 89\% IDL code while the remainder is mostly Perl (5.4\%) 
 and csh scripts (3.8\%). 
-According to data generated using David A. Wheeler's 'SLOCCount'\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
+According to data generated using David A. Wheeler's `SLOCCount'\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
 289,724 lines of code with a total approximate value of \$10.4M (based on the 
@@
 %The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)
-While SSW is open-source and freely available, the IDL core is not. The cost 
+While SSW itself is open-source and freely available, the IDL core is not. The cost 
 of IDL is prohibitive for many undergraduates as well as institutions 
-with limited means. As well as this the development of SolarSoft is closed, 
-with no open issue tracker or community contribution mechanism.
+with limited means.
+Even though SSW's source is open, the development of the source is primarily closed,
+with no open issue tracker or established mechanism for community contributions.
 
@@
 FORTRAN or even IDL. Many books and on-line documentation is available. For 
-example at the time writing a search 
+example, at the time writing a search 
 %
@@
 which is useful and well compensated outside of the scientific community 
-(average salary of \$110k in the Washington DC area according to indeed.com at 
+(average salary of \$110k in the Washington, DC, area according to indeed.com at 
 the time of writing). Python continues to see increased use in the astronomy 
@@
 interactive and shareable notebook-based computing \citep{perez2007}. For all 
-of these reasons, Python is an ideal platform for a modern solar physics data 
-analysis environment.
+of these reasons, Python is an ideal platform for a modern data-
+analysis environment for solar physics.
 
@@
 provide capabilities surpassing that provided by IDL for array manipulation and 
-2-d plotting \citep{greenfield2011}. Providing similar capabilities as SSW/gen 
+2D plotting \citep{greenfield2011}. Providing similar capabilities as SSW/gen 
 in Python is made easier by leveraging the diverse Python community. For 
-example, SunPy makes use of the \texttt{Pandas} package to provide 
+example, SunPy makes use of the \texttt{pandas} package to provide 
 high-performance, easy-to-use data structures and data analysis tools for time 
-series data\citep{mckinney2012}. \texttt{Pandas} was originally developed for 
-quantitative analysis of financial data and has seen grown into a generalised 
+series data\citep{mckinney2012}. \texttt{pandas} was originally developed for 
+quantitative analysis of financial data and has since grown into a generalised 
 data analysis package. SunPy also relies on and is coordinating with the 
-\texttt{Astropy} package \citep{theastropycollaboration2013}. It is still in 
+\texttt{Astropy} package \citep{theastropycollaboration2013}. \texttt{Astropy} is still in 
 active development but already provides many relevant capabilities such as 
-full-featured support for FITS files, absolute dates and time conversions, 
+full-featured support for FITS files, absolute date and time conversions, 
 units and unit conversions, and model-fitting. Pandas (134k lines of code) 

### 2014-01-28 1-Introduction.tex

@@
 the availability of cheap storage and large bandwidth communications has led to 
-a rapid and overwhelming increase in amount of data which scientists are responsible
-for analyzing. For example, NASA's Solar 
-Dynamics Observatory (SDO) satellite records over 1 TB of data per day. To analyze this 
-mountain of data and enable scientific discovery requires increasingly complex software 
-tools. Standardised, easy to use,
-and transparent software tools are a key enabling technology in the scientific endeavor
-so that the community can build upon a common foundation.
+a rapid and overwhelming increase in amount of data for scientists to analyse.
+For example, NASA's Solar 
+Dynamics Observatory (SDO) satellite records over 1 TB of data per day. Analysing this 
+mountain of data to enable scientific discovery requires increasingly complex software 
+tools. Standardised, easy-to-use,
+and transparent software tools are a key enabling technology
+so that the scientific community can build upon a common foundation.
 %schriste - the opening paragraph still needs work
 
-SunPy aims to provide a free, open source and openly developed software package 
+SunPy aims to provide a free, open-source and openly developed software package 
 for the analysis and visualisation of solar data. SunPy makes use of the Python 
-programming language and the breath of high-quality scientific focused packages 
-available for it. The Python programming language is a general purpose, 
-powerful and easy to learn high-level programming language. Python is one of 
-the top ten most popular programming languages in the world according to the 
+programming language and the breadth of high-quality science-focused packages 
+written in that language. Python is a general-purpose, 
+powerful and easy-to-learn high-level programming language.
+According to the 
 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+ Python is one of the top ten most popular programming languages in the world 
 and is widely used outside of scientific fields in web development, education 
@@
 The development of a package such as SunPy in Python is made possible by the 
-rich scientific Python ecosystem of packages available. Core packages in this 
+rich ecosystem of scientific packages available in Python. Core packages in this 
 ecosystem such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
-provide the basic functionality expected of a scientific programming language, 
-\textit{i.e.} array manipulation, core numerical algorithms and visualisation. 
-Build upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
+provide the basic functionality expected of a scientific programming language: 
+\textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 
+Built upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
 \texttt{scikit-image} provide more domain-specific functionality.
 
-The design philosophy of SunPy is to provide a clean, simple to use, and well 
-structured package that provides the \textit{core} tools for solar physics. The 
+The design philosophy of SunPy is to provide a clean, simple-to-use, and well 
+structured package that provides the \textit{core} tools for solar-physics data analysis. The 
 primary focus of SunPy's early development is to provide specialised, linked, 
-datatypes that allow the acquisition, processing and visualisation of all types 
+data types that allow the acquisition, processing and visualisation of all types 
 of solar data.
@@
 capabilities, an overview of the development model and community aspects of the 
-SunPy project as well as future plans. The latest release of SunPy (0.4) from
-the sunpy website (\url{http://sunpy.org}) or can be installed using 
+SunPy project, as well as future plans. The latest release of SunPy (0.4)
+can be downloaded from
+the official website (\url{http://sunpy.org}) or can be installed using 
 the Python package index (\mbox{\url{http://pypi.python.org/pypi}}).

### 2014-01-28 2-3-Spectra.tex

@@
 
+%ayshih - this whole paragraph can be deleted
 Spectroscopy consists in the study of the radiative energy related to the wavelength.
@@
 
-SunPy aims to provide support to most of solar spectroscopy instrument, however the 
-complexity of this kind of datasets makes very challenging to add support to them all 
+SunPy aims to provide broad support for solar spectroscopy instruments, however the 
+variety and complexity of such datasets makes it very challenging to add support to them all 
 in a general way.
-Nevertheless, the \texttt{Spectra} object has been designed to be consistent with the 
-other data types available in SunPy.
-It was implemented as a wrapper around a data array (numpy ndarray)
-because its 1D nature (intensity versus frequency).
-Using the \texttt{Spectra} object, SunPy also offers a 2D array object called \texttt{Spectrogram},
-which it is built as a group of spectrum meassured over time.
-These two objects were implemented by funding provided by the Astrophysics Research 
+The \texttt{spectra} module implements a \texttt{Spectrum} class for 1D data
+(intensity versus frequency) and a \texttt{Spectrogram} class for 2D data
+(intensity versus time and frequency.
+Each of these classes use a \texttt{numpy.ndarray} class as its \texttt{.data} attribute.
+These two classes were implemented by funding provided by the Astrophysics Research 
 Group at Trinity College Dublin.
-As yet, SunPy \texttt{Spectrogram} object supports radio spectra from the e-Callisto 
-solar radio spectrometer network(\url{http://www.e-callisto.org/}).
+
+As of SunPy 0.4, the \texttt{Spectrogram} class supports radio spectra from the e-Callisto 
+solar radio spectrometer network (\url{http://www.e-callisto.org/})
 and STEREO/SWAVES spectrograms.
-Like for the \texttt{Lightcurve} object, the \texttt{Spectrogram} object has been
-built so each instrument initialises from a sub-class containing the instrument-specific 
-functionalities while offering common functionalities to them all to help its analysis, 
-this includes:
-read the data; %(fits format for e-Callisto, ASCII for STEREO/SWAVES); 
-join different time ranges and frequencies; 
-frequency dependent background subtraction;  
-linearise of frequency axis and automated downsample for proper visualisation on a normal computer screen;  
-and point-and-click functionality to save pixels of interest for further analysis.
-In addition, this object is equipped with a download data interface for e-Callisto that 
-only requires the observatory name and the desired time-range. 
-STEREO/SWAVES data can be obtained via the virtual solar observatory (see \S\ref{ssec:vso}).
+As with other SunPy data types, the \texttt{Spectrogram} class has been
+built so each instrument initialises using a subclass containing the instrument-specific 
+functionalities.
+The common functionality provided by the base \texttt{Spectrogram} class includes
+reading data,
+joining different time ranges and frequencies,
+performing frequency-dependent background subtraction,
+and convenient visualization and sampling of the data.
 
@@
 from the online data archive the files that are between the time range specified and
-the observatory of interest.  In this case the data is requested from \textit{BIR} which is the code name of the
-Rosse Observatory at Birr Castle (Ireland)(\url{http://www.rosseobservatory.ie}).
+the observatory of interest.  In this case the data is requested from \textit{BIR},
+which is the code name of the
+Rosse Observatory at Birr Castle in Ireland (\url{http://www.rosseobservatory.ie}).
 When the data is requested using the \texttt{.from\_range} function, the object merges
@@
 and in some cases with different files for different frequency ranges.  
-In the example shown here BIR observed in two frequency ranges: 20 - 90\,MHz and 55 - 355\,MHz.
+In the example shown here BIR observed in two frequency ranges: 20--90\,MHz and 55--355\,MHz.
 Since the data is not evenly spaced in the frequency range, the \texttt{Spectrogram} object
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
-from SunPy.spectra.sources.callisto import CallistoSpectrogram
-tstart = "2011-06-07T06:00:00"
-tend = "2011-06-07T07:45:00"
-callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
-callisto_nobg = callisto.substract_bg()
-callisto_nobg.peek(vmin = 0)
+\begin{minted}[bgcolor=bg]{pycon}
+>>> from SunPy.spectra.sources.callisto import CallistoSpectrogram
+>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
+>>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
+>>> callisto_nobg = callisto.substract_bg()
+>>> callisto_nobg.peek(vmin = 0)
 \end{minted}
@@
 \end{center}
-\caption{Demonstration of how \texttt{CallistoSpectrogram} object retrieve the data
-for the time range and observatory requested, merge it all and removes the background
+\caption{Example of how \texttt{CallistoSpectrogram} retrieves the data
+for the time range and observatory requested, merges it all and removes the background
 signal.}

### 2014-01-28 3-1-VSO.tex

@@
 
-\begin{listing}[h]
+\begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}
@@
 %            listing much shorter.
-\begin{listing}[h]
+\begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}
-Querying multiple instruments/missions over the same time range
+#Querying multiple instruments/missions over the same time range
 >>> instrument_condition = ( vso.attrs.Instrument('lasco') |
@@
 
-Querying two wavelength ranges over the same time range
+#Querying two wavelength ranges over the same time range
 >>> wavelength_condition = ( vso.attrs.Wave(125, 135) |

### 2014-01-28 3-4-Helioviewer.tex

@@
 \begin{listing}[H]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.net.helioviewer import HelioviewerClient
@@
 \begin{listing}[H]
-\begin{minted}{python}
-hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0,
- width=512, height=512)
+\begin{minted}[bgcolor=bg]{pycon}
+>>> hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]",
+...                 x0=0, y0=0, width=512, height=512)
 \end{minted}
@@
 \begin{listing}[H]
-\begin{minted}{python}
-hv.download_png('2099/01/01', 6, 
-"[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50], \
-[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
+\begin{minted}[bgcolor=bg]{pycon}
+>>> hv.download_png('2099/01/01', 6,
+...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50]"+
+...                 "[SOHO,LASCO,C2,white-light,1,100]",
+...                 x0=0, y0=0, width=768, height=768)
 \end{minted}
@@
 \begin{listing}[H]
-\begin{minted}{pycon}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',

### 2014-01-28 5-Dev.tex

@@
 SunPy's development makes use of the online 
-service GitHub (\url{http://github.com}) and git\footnote{\url{http://git-scm.com/}}
+service GitHub (\url{http://github.com}) and Git\footnote{\url{http://git-scm.com/}}
 as its distributed version control software.
 
-The continued success of an open source projects depends on many factors of which 
+The continued success of an open-source project depends on many factors;
 three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
 active community \cite{bangerth2013}. Several tools (some specific to Python) are used by
-Sunpy to make achieving these goals more accessible. To maintain high quality code, a 
-transparent and collaborative development workflow made possible by Github is used (described
-further below). Sunpy includes a number of unit tests which test the functionality 
-of the code base. Additionally, Sunpy makes use of `continuous integration' provided by
-Travis(\url{http://travis-ci.org}), a process by which the addition of any new code 
-automatically triggers a comprehensive review of all unit tests. If any single test
+SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
+transparent and collaborative development workflow made possible by GitHub is used (described
+further below).
+Additionally, SunPy makes use of `continuous integration' provided by
+Travis (\url{http://travis-ci.org}), a process by which the addition of any new code 
+automatically triggers a comprehensive review of written unit tests. If any single test
 fails then the community is alerted before the code is accepted. The unit test coverage is
@@
 Thankfully powerful tools already exist in Python to support this thanks to native
-Python's focus on its own documentation. Sunpy makes use of the Sphinx (\url{http://sphinx-doc.org})
-documentation generator. Sphinx uses reStructuredText as its markup language, 
+Python's focus on its own documentation. SunPy makes use of the Sphinx (\url{http://sphinx-doc.org})
+documentation generator. Sphinx uses reStructuredText as its markup language: 
 an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
 many output formats most notably HTML as well as PDF, and ePub and provides a rich
-hierarchically structured view of in-code documentation strings. The Sunpy documentation 
-s built automatically and hosted on Readthedocs (\url{http://readthedocs.org})
+hierarchically structured view of in-code documentation strings. The SunPy documentation 
+is built automatically and hosted on Read the Docs (\url{http://readthedocs.org})
 at \url{http://docs.sunpy.org}.
 
-In order to maintain an active community communication is key.  The Sunpy community makes
+In order to maintain an active community, communication is key.  The SunPy community makes
 use of a number of channels to communicate. For immediate communications, an active IRC chat
-room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs such as
-developer comments or discussion, a open mailing list is used hosted on Google groups. 
-Discussion of bugs and bug tracking are provided directly on Github as well as new code
-review discussions.
+room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
+developer comments or discussion, a open mailing list is hosted on Google Groups. 
+Discussion of bugs and bug tracking are provided directly on GitHub as well as new
+code-review discussions.
 
 Many of the larger features in SunPy have been developed 
-with the support of both the ESA's Summer Of Code In Space (SOCIS) and the Google
+with the support of both the ESA's Summer of Code in Space (SOCIS) and the Google
 Summer of Code (GSOC). Initial development of SunPy's VSO and HEK 
 implementations were funded by the SOCIS program as well as a prototyped GUI 
-and N-Dimensional datatype implementations. Sunpy was supported by GSOC in 2013 
+and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
 through the Python Software Foundation (PSF). It supported development of the HELIO and 
@@
 repository in order to incorporate their modification into the Sunpy code base. 
-Pull requests are reviewed by the Sunpy community before being accepted. Community consensus
+Pull requests are reviewed by the SunPy community before being accepted. Community consensus
 is required to add new features.
@@
 	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
-	guidelines, this keeps all the code in Sunpy styled in a consistent manner and easy to read.
+	guidelines, this keeps all the code in SunPy styled in a consistent manner and easy to read.
 

### 2014-01-28 3-2-HEK.tex
added SDO FFT reference back in

@@
 data elsewhere (for example, the GOES flare catalog), and some is generated by 
-the Solar Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
+the Solar Dynamics Observatory Feature Finding Team \cite{martens2012} to
 populate the HEK.  The advantage of the HEK is it provides a homogeneous and 

### 2014-01-28 1-Introduction.tex
edited first paragraph in intro

@@
 \section{Introduction}
-Science, including solar physics and astrophysics, is driven by the analysis 
-and summarizing of data. Modern advances in sensor technology combined with 
-the availability of cheap storage and large bandwidth communications has led to 
-a rapid and overwhelming increase in amount of data for scientists to analyse.
-For example, NASA's Solar 
-Dynamics Observatory (SDO) satellite records over 1 TB of data per day. Analysing this 
-mountain of data to enable scientific discovery requires increasingly complex software 
-tools. Standardised, easy-to-use,
-and transparent software tools are a key enabling technology
-so that the scientific community can build upon a common foundation.
+
+Science is driven by the analysis of data. Modern advances in sensor
+technology combined with the availability of cheap storage has led to
+rapid increases in amount of data available to scientists in almost
+every discipline.  Solar physics is no exception to this trend. NASA's
+Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
+produces over 1 TB of catalogued and stored data per day. Managing and
+analysing this mountain of data to enable scientific discovery
+requires increasingly sophisticated software tools.  Key qualities
+that these tools should have include robustness, ease of use, a
+transparent development history, ease of modification, and conformance
+to standards.  Software with these qualities provides a strong
+foundation which is responsive to the needs of the community as data
+volumes grow and science questions evolve.
 %schriste - the opening paragraph still needs work
+%ji - I had a go.
 

### 2014-01-28 2-Data_Types.tex
Note in the file on 2-data-types to say that the LightCurve object does not have a meta attribute

@@
 The primary focus of SunPy is to provide data structures 
-that are specifically designed for the various kinds of solar physics data, namely
+that are specifically designed for the primary varieties of solar physics data, namely
 images, time series, and spectra. SunPy provides three core data
@@
 \texttt{matplotlib}.
+% LightCurve does NOT have a meta attribute.  It looks like this would
+% be a simple fix in the main lightcurve class.
 

### 2014-01-28 3-4-Helioviewer.tex
edits to the Helioviewer setion

@@
 
-SunPy provides the ability to download images hosted by the Helioviewer Project.  
-The aim of the Helioviewer Project is to enable the exploration of 
-solar and heliospheric data from multiple data sources (such as instrumentation 
-and feature/event catalogs) via easy-to-use visual interfaces.  The primary 
-data provided by the Helioviewer Project are images in the JPEG2000 format (for 
-further details on the Helioviewer Project see \cite{muller2009}). 
-SunPy is used in Helioviewer production servers to manage the 
-download and ingestion of JPEG2000 files from remote servers.  The JPEG2000 
-files are typically highly compressed compared to the source FITS files they 
-are generated from, and so can be a used as a shortcut to visualize large 
-amounts of data from multiple sources.
+SunPy provides the ability to download images hosted by the
+Helioviewer Project.  The aim of the Helioviewer Project is to enable
+the exploration of solar and heliospheric data from multiple data
+sources (such as instrumentation and feature/event catalogs) via
+easy-to-use visual interfaces.  The primary data provided by the
+Helioviewer Project are images in the JPEG2000 format (for further
+details on the Helioviewer Project see \cite{muller2009}). The
+JPEG2000 files are typically highly compressed compared to the source
+FITS files they are generated from, and so can be a used as a shortcut
+to visualize large amounts of data from multiple sources.  SunPy is
+also used in Helioviewer production servers to manage the download and
+ingestion of JPEG2000 files from remote servers.
 
 The Helioviewer Project categorizes image data based on the physical
-construction of the source instrument, using the following hierarchy:
+construction of the source instrument, using a simple hierarchy:
 observatory $\rightarrow$ instrument $\rightarrow$ detector
 $\rightarrow$ measurement, where '$\rightarrow$' means 'provides
-(possibly multiple)'.  The full list of image data sources available
-can be found through the code snippet, Example
-\ref{code:hv:datasources}.
-%schriste - what is the point of the following listing? remove?
+(possibly multiple)'.  Each Helioviewer Project JPEG2000 file contains
+metadata which are based (in part) on the original FITS header
+information, and carry sufficient information to permit overlay with
+other Helioviewer JPEG2000 files. Images can be accessed either as
+PNGs (Section \ref{sssec:hv:png} or as JPEG2000 files (Section
+\ref{sssec:hv:jp}).
+
+\subsubsection{Download a PNG file}\label{sssec:hv:png}
+
+Listing \ref{code:hv:downloadlatestpng} demonstrates how to download a
+PNG image of the latest AIA 304\AA\ image available on
+\url{Helioviewer.org}.
+
 \begin{listing}[H]
@@
 >>> hv = HelioviewerClient()
->>> datasources = hv.get_data_sources()
-
-# print a list of datasources and their associated ids
->>> for observatory, instruments in datasources.items():
->>>     for inst, detectors in instruments.items():
->>>         for det, measurements in detectors.items():
->>>             for meas, params in measurements.items():
->>>                 print(observatory, params['nickname'], 
->>>                 params['sourceId']))
-\end{minted}
-\caption{Initializing the Helioviewer client and listing the full
-  range of image data available.}
-\label{code:hv:datasources}
-\end{listing}
-
-Each Helioviewer Project JPEG2000 file contains metadata which are
-based (in part) on the original FITS header information, and carry
-sufficient information to permit overlay with other Helioviewer
-JPEG2000 files. Images can be accessed either as PNGs (Section
-\ref{sssec:hv:png} or as JPEG2000 files (Section \ref{sssec:hv:jp}).
-
-\subsubsection{Download a PNG file}\label{sssec:hv:png}
-
-Example \ref{code:hv:downloadlatestpng} demonstrates how to download a
-PNG image of the latest AIA 304\AA\ image available on
-Helioviewer.org.
-
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
 >>> hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]",
@@
 resolution in arcseconds per pixel (larger values mean lower
-resolution).  The third argument is a string detailing the requested
-observatory $\rightarrow$ instrument $\rightarrow$ detector
-$\rightarrow$ measurement combination.  The final two numbers in this
-string are the visibility and the opacity of the this image layer (1/0
-is visible/invisible with opacity in the range $0\rightarrow100$, with
-$100$ meaning fully opaque).  The quantities $x0$ and $y0$ are the $x$
-and $y$ center points about which to center the image (measured in
-helio-projective cartesian co-ordinates) and the \texttt{width} and
-\texttt{height} are the pixel values for the image dimensions.
+resolution).  The third argument is a comma-delimited string detailing
+the requested observatory $\rightarrow$ instrument $\rightarrow$
+detector $\rightarrow$ measurement combination.  The final two numbers
+in this string are the visibility and the opacity of the this image
+layer (1/0 is visible/invisible with opacity in the range
+$0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
+$x0$ and $y0$ are the $x$ and $y$ center points about which to center
+the image (measured in helio-projective cartesian co-ordinates) and
+the \texttt{width} and \texttt{height} are the pixel values for the
+image dimensions.
 
@@
 file.  SunPy accesses this overlay/composition capability through the
-\texttt{download\_png} method of the Helioviewer client.  Example
+\texttt{download\_png} method of the Helioviewer client.  Listing
 \ref{code:hv:overlaid} gives an example of the composition of three
@@
 
-The principle difference between this code snippet and Example
+The principle difference between this code snippet and Listing
 \ref{code:hv:downloadlatestpng} is in the layer string (the third
@@
 source library for reading and writing JPEG2000 files
-(http://www.openjpeg.org).  The other package required is
-\texttt{glymur}, (https://github.com/quintusdias/glymur), an interface
-between Python and the OpenJPEG libraries (note that these packages
-are {\it not} required to use the functionality described in Section
-\ref{sssec:hv:png}).
+(\url{http://www.openjpeg.org}).  The other package required is
+\texttt{glymur}, (\url{https://github.com/quintusdias/glymur}), an
+interface between Python and the OpenJPEG libraries (note that these
+packages are {\it not} required to use the functionality described in
+Section \ref{sssec:hv:png}).
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
->>>                            instrument='HMI', detector='HMI', 
->>>                            measurement='continuum')
+>>> filepath = hv.download_jp2('2012/07/05 00:30:00',
+...                                                  observatory='SDO',
+...                                                  instrument='HMI', detector='HMI', 
+...                                                  measurement='continuum')
 >>> from sunpy.map import Map
->>> hmi = Map(filepath)
->>> hmi.submap([200,550],[-400,-200]).peek()
+>>> Map(filepath).submap([200,550],[-400,-200]).peek()
 \end{minted}

### 2014-01-28 2-1-Map.tex
Some small typo fixed and latex stuff

@@
-\subsection{Map}
-The purpose of the Map datatype is to represent 2D spatial data such as images of the Sun and 
+\subsection{Map}\label{ssec:map}
+The Map data type represents 2D spatial data such as images of the Sun and 
 inner heliosphere. It provides a wrapper around a data array and its associated
-spatial coordinates and as well as meta data. The \texttt{Map} object provides 
-convenience methods for many functions 
-such as rotation and re-sampling as well as convenience visualisation 
-functions, providing an easy to use as well as powerful interface. The \texttt{Map} object
-also provides a convenient interface for loadings data from a variety of sources, typically
+spatial coordinates and other metadata. The \texttt{Map} class provides 
+methods for typical operations on 2D data, 
+such as rotation and re-sampling, and visualisation functionality.
+The \texttt{Map} class
+also provides a convenient interface for loading data from a variety of sources, typically
 a FITS file as shown in Listing~\ref{code:aia_1}.
 
-The architecture of the \texttt{Map} object consists of a template map called
-\texttt{GenericMap} which is a subclass of \texttt{astropy.nddata.NDData}. \texttt{NDData} is a 
-generic wrapper around a \texttt{ndarray} with a \texttt{.meta} attribute to store meta data.
-As \texttt{NDData} is currently still in development, \texttt{GenericMap} does not make full
-use of its capabilities but this inheritance structure provides 
-for future integration of \texttt{astropy}. In order to provide instrument/
-detector specific integration \texttt{GenericMap} is subclassed on creation. 
-Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (i.e. factory)
-by implementing a method that returns \texttt{True} if matching meta data 
-for that instrument or detector is found in the file header. The \texttt{Map} factory 
+The architecture of the \texttt{Map} class consists of a template map called
+\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. \texttt{NDData} is a 
+generic wrapper around an \texttt{ndarray} with a \texttt{.meta} attribute to store metadata.
+As \texttt{NDData} is currently still in development, \texttt{GenericMap} does not yet make full
+use of its capabilities, but this inheritance structure provides 
+for future integration of \texttt{Astropy}. In order to provide instrument- or
+detector-specific integration, \texttt{GenericMap} is subclassed on creation. 
+Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (\textit{i.e.}, factory)
+by implementing a method that returns \texttt{True} if the metadata
+in the file header matches
+that instrument or detector.  This \texttt{Map} factory 
 will then automatically return an instance of the specific \texttt{GenericMap} 
-subclass. As of this version SunPy has \texttt{Map} specialisations for the 
+subclass. SunPy 0.4 has \texttt{Map} specialisations for the 
 following instruments: 
-\textit{YOHKOH/SXT},\textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
+\textit{YOHKOH/SXT}, \textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
 \textit{STEREO/EUVI} and \textit{COR}, \textit{HINODE/XRT},
@@
 
-The \texttt{Map} object stores standard meta data retrieved in the header of 
-the image file, via the \texttt{.meta} attribute and provides convenience 
-properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
+The \texttt{Map} class stores standard metadata retrieved from the header of 
+the image file in the \texttt{.meta} attribute and provides convenience 
+properties for commonly accessed metadata: \textit{e.g.}, \texttt{.instrument}, 
 \texttt{.wavelength} or \texttt{.coordinate\_system}. 
-Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
-\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.
+Listing \ref{code:aia_1} demonstrates the quick-plot functionality of 
+\texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.
 
@@
 \end{center}
-\caption{Demonstration of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file and the 
-key meta data and array overview is printed. Then a quick view plot is created 
-by using the \texttt{.peek()} method.}
+\caption{Example of the \texttt{AIAMap} specialisation of 
+\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file,
+and a quick-view plot is created.}
 \label{code:aia_1}
@@
 
-As well as providing the base classes the map sub-package provides two 
+In addition to the data-type classes, the \texttt{map} sub-package provides two 
 collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
@@
 provides methods for animation of its series of \texttt{Map} objects. 
-Listing~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
+Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to interact 
 with these classes.
-In addition, Listing~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
+In addition, Listing~\ref{code:mapcube_2} shows how the \texttt{MapCube} 
 classes interacts with the \texttt{animation} module to save a video.
@@
 \end{center}
-\caption{Example demonstrating a CompositeMap plot, using contours and how 
-SunPy integrates with matplotlib's pyplot functional interface.}
+\caption{Example showing a \texttt{CompositeMap} plot and the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
-import sunpy.map
-
-compmap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
-compmap.peek()
+\begin{minted}[bgcolor=bg]{pycon}
+>>> import sunpy.map
+>>> compmap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> compmap.peek()
 \end{minted}
@@
 \end{center}
-\caption{An example showing creation of a MapCube from a glob file search. The 
-resultant plot makes use of matplotlib's interactive widgets to allow scrolling 
-through the MapCube.}
+\caption{Example showing creation of a \texttt{MapCube} from a glob file search. The 
+resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 
+through the \texttt{MapCube}.}
 \label{code:mapcube_1}
@@
 
-\begin{listing}[h]
-\begin{minted}[bgcolor=bg]{python}
-import sunpy.map
-from matplotlib import animation
-
-mapc = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
-anim = mapc.plot()
-Writer = animation.writers['ffmpeg']
-writer = Writer(fps=10, metadata=dict(artist='SunPy'), bitrate=1800)
-anim.save('aia_cube.ogv')
+\begin{listing}[H]
+\begin{minted}[bgcolor=bg]{pycon}
+>>> import sunpy.map
+>>> from matplotlib import animation
+>>> mapc = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> anim = mapc.plot()
+>>> Writer = animation.writers['ffmpeg']
+>>> writer = Writer(fps=10, metadata=dict(artist='SunPy'), bitrate=1800)
+>>> anim.save('aia_cube.ogv')
 \end{minted}
-\caption{Example showing how to save a video animation from a MapCube, using 
-matplotlib's animation framework.}
+% In the above example, is Writer, writer clear? 
+% Could we add more metadata to the movie? obs_date, instrument, etc...?
+\caption{Example showing how to save a video animation from a \texttt{MapCube}, using 
+\texttt{matplotlib}'s animation framework.}
 \label{code:mapcube_2}

### 2014-01-28 2-2-Lightcurve.tex
removed that big git identifier tag thingy.
Some small typo fixed and latex stuff

@@
 the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
+% Do we need to explain what OCS means?
 average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
@@
 >>> resampled_goes = goes.data.resample("1H")
+% Does 1h resample makes sense?? I vote for an example with some utility
 \end{minted}

### 2014-01-28 2-3-Spectra.tex
Some small typo fixed and latex stuff

@@
 %schriste - this section needs major work
+%ji - there is no example of a spectrum
+%dps - I need to think in one...
 
-%ayshih - this whole paragraph can be deleted
-Spectroscopy consists in the study of the radiative energy related to the wavelength.
-An spectrum is normally obtained by observing a range of frequencies at the same time; 
-it can be measured for example in radio wavelengths by a frequency sweep with 
-a radio receiver or in visible and ultraviolet by the dispersion of the incident light 
-through a diffraction grating or prism.
-The analysis of the resultant spectrum can provide properties of the plasma observed 
-such temperature, density, speed, etc.
-Therefore, spectroscopy provides to the solar physicists invaluable information about 
-the composition and the physical properties of the Sun.
+SunPy aims to provide broad support for solar spectroscopy
+instruments.  The variety and complexity of these instruments and
+their resultant datasets makes it very challenging to support all in a
+general way.  The \texttt{spectra} module implements a
+\texttt{Spectrum} class for 1D data (intensity versus frequency) and a
+\texttt{Spectrogram} class for 2D data (intensity versus time and
+frequency).  Each of these classes use a \texttt{numpy.ndarray} class
+as its \texttt{.data} attribute.  These two classes were implemented
+by funding provided by the Astrophysics Research Group at Trinity
+College Dublin, Ireland.
 
-SunPy aims to provide broad support for solar spectroscopy instruments, however the 
-variety and complexity of such datasets makes it very challenging to add support to them all 
-in a general way.
-The \texttt{spectra} module implements a \texttt{Spectrum} class for 1D data
-(intensity versus frequency) and a \texttt{Spectrogram} class for 2D data
-(intensity versus time and frequency.
-Each of these classes use a \texttt{numpy.ndarray} class as its \texttt{.data} attribute.
-These two classes were implemented by funding provided by the Astrophysics Research 
-Group at Trinity College Dublin.
-
-As of SunPy 0.4, the \texttt{Spectrogram} class supports radio spectra from the e-Callisto 
+The \texttt{Spectrogram} class supports radio spectrograms from the e-Callisto 
 solar radio spectrometer network (\url{http://www.e-callisto.org/})
@@
 As with other SunPy data types, the \texttt{Spectrogram} class has been
-built so each instrument initialises using a subclass containing the instrument-specific 
+built so that each instrument initialises using a subclass containing the instrument-specific 
 functionalities.
-The common functionality provided by the base \texttt{Spectrogram} class includes
-reading data,
-joining different time ranges and frequencies,
-performing frequency-dependent background subtraction,
-and convenient visualization and sampling of the data.
+%The common functionality provided by the base \texttt{Spectrogram} class includes
+%reading data,
+%joining different time ranges and frequencies,
+%performing frequency-dependent background subtraction,
+%and convenient visualization and sampling of the data.
 
-Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram} object retrieves
-from the online data archive the files that are between the time range specified and
-the observatory of interest.  In this case the data is requested from \textit{BIR},
-which is the code name of the
-Rosse Observatory at Birr Castle in Ireland (\url{http://www.rosseobservatory.ie}).
-When the data is requested using the \texttt{.from\_range} function, the object merges
-into a single spectrogram all the files downloaded, each with 15 minutes observation data 
-and in some cases with different files for different frequency ranges.  
-In the example shown here BIR observed in two frequency ranges: 20--90\,MHz and 55--355\,MHz.
-Since the data is not evenly spaced in the frequency range, the \texttt{Spectrogram} object
-linearise the frequency axis for a better analisys, as shown in the resultant figures.
-It is also shown in the example the effect of the implemented background substraction and
-\texttt{.peek} method.
+Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram}
+object retrieves spectrogram data in the time range specified taken at
+the observatory of interest.  When the data is requested using the
+\texttt{.from\_range} function, the object merges all the downloaded
+files downloaded into a single spectrogram, across time and frequency.
+In the example shown, data is observed in two frequency ranges, 
+20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
+the frequency range, the \texttt{Spectrogram} object linearises the
+frequency axis for a better analysis.  The example also demonstrates
+the implemented background subtraction method.
+%ji to DPS - what is the linearisation that is happening here?
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from SunPy.spectra.sources.callisto import CallistoSpectrogram
+>>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
 >>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
 >>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
->>> callisto_nobg = callisto.substract_bg()
+>>> callisto_nobg = callisto.subtract_bg()
 >>> callisto_nobg.peek(vmin = 0)
@@
 \end{center}
-\caption{Example of how \texttt{CallistoSpectrogram} retrieves the data
-for the time range and observatory requested, merges it all and removes the background
-signal.}
+\caption{Example of how \texttt{CallistoSpectrogram} retrieves the
+  data for the requested time range and observatory, merges it and
+  removes the background signal.  The data requested -- 'BIR' -- is
+  the code name of the Rosse Observatory at Birr Castle in Ireland
+  (\url{http://www.rosseobservatory.ie})}
 \label{code:spectra}

### 2014-01-28 2-Data_Types.tex
changed the comment again
Some small typo fixed and latex stuff

--- 2014-01-27 2-Data_Types.tex
@@
-\section{Core Data Types}
+\section{Core Data Types}\label{sec:DataTypes}
+
 The primary focus of SunPy is to provide data structures 
-that are specifically designed for the various kinds of solar physics data, namely
+that are specifically designed for the primary varieties of solar physics data, namely
 images, time series, and spectra. SunPy provides three core data
@@
 along with associated metadata and provide appropriate convenience functions to
-enable data analysis and visualization. For each of these classes, the data is
+enable data analysis and visualisation. For each of these classes, the data is
 stored in the \texttt{.data} attribute while the metadata is stored 
@@
 \texttt{matplotlib}.
+% LightCurve does NOT have a meta attribute.  Needs to be fixed in the
+% re-write of LightCurve
 
@@
 the \texttt{pyplot} functional interface of \texttt{matplotlib}, as demonstrated in 
-Figure \ref{code:mpl_1}.
+Listing \ref{code:mpl_1}.
 
-%schriste - I vote for removing all of the following code as being too down in the weeds
+%schriste - I vote for removing all of the following code as being too
+%down in the weeds
+%ji -  I agree.  Do we even need to say much more than give a brief
+%outline of the .peek and .plot methods?
 \begin{listing}[H]

### 2014-01-28 3-1-VSO.tex
Some small typo fixed and latex stuff

@@
 \texttt{suds} package.
-This module was developed under the ESA's Summer of Code programme of 2011.
+This module was developed under the European Space Agency's Summer of Code in 
+Space (ESA's SOCIS) of 2011.
 
@@
 time, instrument, wavelength, or  other properties.
-The also shows how to download the data using the result
+It also shows how to download the data using the result
 from the query. One can use the metadata associated with the data sets to specify how the

### 2014-01-28 3-2-HEK.tex
Some small typo fixed and latex stuff

@@
 The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
-radio burst) on many 
+radio bursts) on many 
 different time-scales, length-scales and wavelengths. Observations and metadata 
@@
 the Solar Dynamics Observatory Feature Finding Team \cite{martens2012} to
-populate the HEK.  The advantage of the HEK is it provides a homogeneous and 
+populate the HEK.  The advantage of the HEK is it provides an homogeneous and 
 well-described interface to a large 
@@
 SunPy accesses this information through the \texttt{hek} module, which was 
-developed with support from the European Space Agency Summer of Code in 
-Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of the HEK API
+developed with support from the 
+ESA-SOCIS 2011.  The \texttt{hek} module makes use of the HEK API
 (\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
@@
 \caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
-which occurred on the 2011/08/09.}
+which occurred on August 9th, 2011.}
 \label{code:hek:simple}
@@
 in different ways, known generally as {\it feature recognition methods} ( 
-FRMs). Example \ref{code:hek:frm} filters the results of the previous result to 
+FRMs). Example in Listing~\ref{code:hek:frm} filters the results of the previous result to 
 return only those events that have the FRM 'SSW Latest Events'.
@@
 >>> result = client.query(hek.attrs.Time(tstart,tend), 
-                      hek.attrs.EventType(event_type),
-                      hek.attrs.FRM.Name == 'SSW Latest Events')
+...                       hek.attrs.EventType(event_type),
+...                       hek.attrs.FRM.Name == 'SSW Latest Events')
 >>> len(result)
@@
 % do not mention it, i think.
+%dps - I agree.

### 2014-01-28 3-4-Helioviewer.tex
small spacing edit to Helioviewer file
Some small typo fixed and latex stuff

@@
 SunPy provides the ability to download images hosted by the
-Helioviewer Project.  The aim of the Helioviewer Project is to enable
+Helioviewer Project (\url{http://helioviewer.org}).  
+The aim of the Helioviewer Project is to enable
 the exploration of solar and heliospheric data from multiple data
-sources (such as instrumentation and feature/event catalogs) via
+sources (such as instrumentation and feature/event catalogues) via
 easy-to-use visual interfaces.  The primary data provided by the
@@
 FITS files they are generated from, and so can be a used as a shortcut
-to visualize large amounts of data from multiple sources.  SunPy is
+to visualise large amounts of data from multiple sources.  SunPy is
 also used in Helioviewer production servers to manage the download and
@@
 
-The Helioviewer Project categorizes image data based on the physical
+The Helioviewer Project categorises image data based on the physical
 construction of the source instrument, using a simple hierarchy:
@@
 other Helioviewer JPEG2000 files. Images can be accessed either as
-PNGs (Section \ref{sssec:hv:png} or as JPEG2000 files (Section
+PNGs (Section \ref{sssec:hv:png}) or as JPEG2000 files (Section
 \ref{sssec:hv:jp}).
@@
 Listing \ref{code:hv:downloadlatestpng} demonstrates how to download a
-PNG image of the latest AIA 304\AA\ image available on
+PNG image of the latest AIA 304$\,$\AA\ image available on
 \url{Helioviewer.org}.
@@
 \includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304}
+%centered image?
 \caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
@@
 $0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
-$x0$ and $y0$ are the $x$ and $y$ center points about which to center
+$x0$ and $y0$ are the $x$ and $y$ centre points about which to centre
 the image (measured in helio-projective cartesian co-ordinates) and
@@
 
-The principle difference between this code snippet and Listing
+The principle difference between Listings~\ref{code:hv:overlaid} and 
 \ref{code:hv:downloadlatestpng} is in the layer string (the third
@@
 file to permit the creation of a SunPy map object (see Section
-\ref{ssec:maps}) from a Helioviewer JPEG2000 file.  This allows image
+\ref{ssec:map}) from a Helioviewer JPEG2000 file.  This allows image
 data to be manipulated in the same way as any other map object.
@@
 reading and conversion of a Helioviewer JPEG2000 file into a SunPy Map
-object.  This functionality allows users to visualize and manipulate
+object.  This functionality allows users to visualise and manipulate
 Helioviewer-supplied image data in an identical fashion to a SunPy map
-object generated from FITS data (see Section \ref{sec:maps}).
+object generated from FITS data (see Section \ref{sec:map}).
 

### 2014-01-28 3-5-Database.tex
Some small typo fixed and latex stuff

@@
-\subsection{The File Database}
+\subsection{The File Database}\label{ssec:db}
+
 Easy access to large quantities of solar data frequently leads to datafiles accumulating
-in local storage such as laptops and desktop computers. Keeping data organized and available
+in local storage such as laptops and desktop computers. Keeping data organised and available
 is typically a cumbersome task for the average user. The file database is a sub-package of 
 SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
-local data files. The database package was developed as part of the 2013 
-Google Summer of Code.
+local data files. The database package was developed as part of GSOC 2013.
 
 The database sub-package makes use of a database supported by
-SQLAlchemy(\url{http://www.sqlalchemy.org}). This library was chosen
-since it supports many SQL dialects. If SQLite is choosen, the database is stored as a single file which is
+SQLAlchemy (\url{http://www.sqlalchemy.org}). This library was chosen
+since it supports many SQL dialects. 
+If SQLite is chosen, the database is stored as a single file which is
 created automatically. This solution makes it possible to easily backup, copy and distribute
@@
 
-The database can store and manage all data that is retrieved via sunpy from the net
+The database can store and manage all data that is retrieved via SunPy from the net
 package though currently only the \textsc{VSO} package is supported. 
@@
 The database also provides the ability to associate custom meta-data to 
-each database entry such as keywords, comments, and favoriting.
+each database entry such as keywords, comments, and favouring.
 
@@
 \begin{listing}[H]
-\begin{minted}{python}
+\begin{minted}[bgcolor=bg]{pycon}
 >>> from sunpy.net import vso

### 2014-01-28 4-Util.tex
Some small typo fixed and latex stuff

@@
-\section{Additional functionality}
+\section{Additional functionality}\label{sec:util}
 SunPy is meant to provide a consistent environment for solar data analysis. In 
@@
 
-\subsection{World Coordinate System (WCS) Coordinates}
+\subsection{World Coordinate System (WCS) Coordinates}\label{ssec:util:wcs}
 Coordinate transformations are frequently a necessary task within the solar 
@@
 
-\subsubsection{Sun}
+\subsubsection{Sun}\label{ssec:util:sun}
 The purpose of this module is to provide solar-specific data for example ephemeris and
@@
 
-\subsubsection{constants}
+\subsubsection{constants}\label{ssec:util:const}
 The purpose of the constants package is to provide a number of solar-related 
@@
 
-\subsubsection{Instruments}
+\subsubsection{Instruments}\label{ssec:util:inst}
 In addition to providing support for instrument-specific solar data via the main data 

### 2014-01-28 Sunpy_paper_0.4.tex
added in my name and affiliation
Added affiliation
Some small typo fixed and latex stuff

--- 2014-01-13 Sunpy_paper_0.4.tex
@@
 \documentclass[12pt]{iopart}
-
 %Uncomment next line if AMS fonts required
 %\usepackage{iopams}
+
+\usepackage{natbib}
+\newcommand*{\newblock}{Bibliography}
+
+\usepackage{minted}
+\definecolor{bg}{rgb}{0.95, 0.95, 0.95}
+\usepackage{hyperref}
+
+\usepackage{graphicx}
+\graphicspath{{./images/}}
+
+\usepackage{perpage} %the perpage package
+\MakePerPage{footnote} %the perpage package command
 
@@
 
-\author{S J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
-Mathematics and Statistics, The University of Sheffield, Hicks Building, 
-Hounsfield Road, Sheffield, S3 7RH U.K.}
+\input{authors}
 
-\author{J Bloggs}
-\address{Wibble wiblle wiblle}
-
-\ead{sunpy@googlegroups.com}
-
-\begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package 
-for solar physics.
-
-\end{abstract}
+\input{abstract}
 
@@
 
+\input{solarsoft}
+
 \input{5-Dev}
@@
 %%% References
-\bibliography{sunpy_paper_0.4}{}
+\bibliographystyle{stunat}
+\bibliography{Sunpy_paper_0.4}{}
 

### 2014-01-28 authors.tex
Some small typo fixed and latex stuff

\author{The SunPy Community}
\address{\url{http://sunpy.org}}
\ead{sunpy@googlegroups.com}

\author{Stuart J Mumford}
\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
Mathematics and Statistics, The University of Sheffield, Hicks Building, 
Hounsfield Road, Sheffield, S3 7RH U.K.}

\author{Steven Christe}\
\address{NASA Goddard Space Flight Center, Greenbelt, U.S.A.}

\author{David P\'erez-Su\'arez}
\address{South African National Space Agency - Space Science,
Hospital Street, 7200 Hermanus, Western Cape, South Africa}

\author{Andrew R Inglis}
\address{NASA Goddard Space Flight Center, Greenbelt, USA}
\address{The Catholic University of America, Washington, DC, USA}

\author{Jack Ireland}
\address{ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space
  Flight Center, Greenbelt, MD, U.S.A.}

\author{Albert Y. Shih}
\address{NASA Goddard Space Flight Center, Greenbelt, MD, USA}

\author{}
\address{}

### 2014-01-28 1-Introduction.tex

@@
-\section{Introduction}
+\section{Introduction}\label{sec:Intro}
 
@@
  Python is one of the top ten most popular programming languages in the world 
-and is widely used outside of scientific fields in web development, education 
+and is widely used outside of scientific fields in areas like web development, education 
 and `big data' analytics.
@@
 ecosystem such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
-provide the basic functionality expected of a scientific programming language: 
+provide the basic functionality expected of a scientific programming language -- 
 \textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 

### 2014-01-28 5-Dev.tex

@@
-\section{Development and Community}
+\section{Development and Community}\label{sec:dev}
 SunPy is a community-developed library, designed and developed for and by 
@@
 Many of the larger features in SunPy have been developed 
-with the support of both the ESA's Summer of Code in Space (SOCIS) and the Google
-Summer of Code (GSOC). Initial development of SunPy's VSO and HEK 
+with the support of both the ESA-SOCIS and GSOC. 
+Initial development of SunPy's VSO and HEK 
 implementations were funded by the SOCIS program as well as a prototyped GUI 
@@
 a 'Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
-repository in order to incorporate their modification into the Sunpy code base. 
+repository in order to incorporate their modification into the SunPy code base. 
 Pull requests are reviewed by the SunPy community before being accepted. Community consensus

### 2014-01-28 6-Future.tex

--- 2014-01-20 6-Future.tex
@@
-\section{Future of SunPy}
-SunPy as a project has existed for roughly three years. In this time the code 
-base has grown to over $110,000$ lines. SunPy in it's current form is a useful 
-package for the analysis of calibrated solar data, however, the code base is 
+\section{Future of SunPy}\label{sec:future}
+SunPy as a project has existed for roughly three years. In this time 
+the code 
+base has grown to over 110,000 lines. SunPy in its current form is a 
+useful 
+package for the analysis of calibrated solar data, however, the code 
+base is 
 still very changeable from release to release.
 
-The near-term future of the SunPy library is likely to continue this changeable 
-nature with re-factoring and restructuring planned, especially within the 
-core data types. The main focus upon the data types defined inside sunpy is to 
-improve the interoperability and to redesign them in a more consistent manner.
+As discussed in Section \ref{sec:Intro}, the primary focus of the 
+\texttt{sunpy} library is the analysis and visualisation of `high-level' solar 
+data. This means data that has been put through instrument processing 
+and 
+calibration routines, and contains full (WCS) coordinate information. 
+The 
+development plan for SunPy is to continue development within this 
+scope. The 
+primary components of this plan are to provide a set of data types 
+that are 
+interchangeable with one another: \textit{e.g.}, if you slice a 
+\texttt{MapCube} 
+along one coordinate, a \texttt{LightCurve} of intensity along the 
+time range of 
+the \texttt{MapCube} should be returned. To achieve this goal, all the 
+data 
+types need to share a unified coordinate system architecture so that 
+each data 
+type is aware of what the physical type of its data is and how 
+operations on 
+that data should be performed.
 
-In the past 12 months the collaboration with the Astropy project 
-\cite{theastropycollaboration2013} has grown. The future of SunPy 
-will continue this collaboration as the Astropy package provides many core 
-tools that are applicable to all types of astronomy. For example the 
-\texttt{astropy.units} submodule provides a simple and efficient way of 
-representing physical units in Python data types, there are plans to 
-incorporate this widely in the SunPy code-base.
+In concert with the work on the data types, further integration with 
+the 
+\texttt{astropy} package will enable SunPy to inherit the large 
+amount of work 
+done in that project to support a platform for astronomical data 
+analysis. For 
+example, the \texttt{astropy.units} submodule provides a simple and 
+efficient 
+way of representing physical units in Python data types; there are 
+plans to 
+incorporate this widely in the SunPy code base. In the past 12 months, 
+the 
+collaboration with the Astropy project 
+\citep{theastropycollaboration2013} and 
+its community has grown, abd this direct collaboration between Astropy 
+% what abd means?
+and 
+SunPy will be one of the key strengths of SunPy going forward.

### 2014-01-28 abstract.tex

\begin{abstract}
This paper presents version 0.4 of SunPy a community developed Python package 
for solar physics.

\end{abstract}

### 2014-01-28 authors.tex
Add new author list

@@
-\author{The SunPy Community}
+\author{The SunPy Community,}
 \address{\url{http://sunpy.org}}
@@
 
-\author{Stuart J Mumford}
-\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
-Mathematics and Statistics, The University of Sheffield, Hicks Building, 
-Hounsfield Road, Sheffield, S3 7RH U.K.}
+\author{
+% People who have directly contributed to the text, still in no order.
+Stuart J Mumford$^1$,
+Steven Christe$^2$,
+David P\'erez-Su\'arez$^3$,
+Andrew R Inglis$^{2,5}$,
+Jack Ireland$^{6,2}$,
+Albert Y Shih$^2$,
+% Contributors to SunPy Sorted thus:
+% No. Commits to main repo + commits in open PR's
+% Date of most recent contribution
+F Mayer, %721
+K Hughitt, %446
+R Hewett, %88
+Nabil Freij$^1$, %52
+M Earnshaw, %52
+T Meszaros, %17
+N Chorley, %17
+Samuel M Bennett$^1$, %14
+M Malocha, %10
+J Evans, %10
+A Maverick, %8
+M Bates, %6
+Andrew J Leonard$^7$, %3
+J Ballew, %3
+T Robitaille, %2
+B Mampaey, %2
+%Hypnus1803 %1
+and 
+A Kustov %1
+}
 
-\author{Steven Christe}\
-\address{NASA Goddard Space Flight Center, Greenbelt, U.S.A.}
+\address{
+$^1$ Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
+School of Mathematics and Statistics, The University of Sheffield, Hicks 
+Building, Hounsfield Road, Sheffield, S3 7RH U.K.,
 
-\author{David P\'erez-Su\'arez}
-\address{South African National Space Agency - Space Science,
-Hospital Street, 7200 Hermanus, Western Cape, South Africa}
+$^2$NASA Goddard Space Flight Center, Greenbelt, MD, USA,
 
-\author{Andrew R Inglis}
-\address{NASA Goddard Space Flight Center, Greenbelt, USA}
-\address{The Catholic University of America, Washington, DC, USA}
+$^3$South African National Space Agency - Space Science, Hospital 
+Street, 7200 Hermanus, Western Cape, South Africa,
 
-\author{Jack Ireland}
-\address{ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space
-  Flight Center, Greenbelt, MD, U.S.A.}
+$^5$ The Catholic University of America, Washington, DC, USA,
 
-\author{Albert Y. Shih}
-\address{NASA Goddard Space Flight Center, Greenbelt, MD, USA}
+$^6$ADNET Systems Inc., Mail Code 671.1,
 
-\author{}
-\address{}
+$^7$Department of Mathematics and Physics, Aberystwyth University, 
+Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ,
+}

### 2014-01-28 1-Introduction.tex
a few minor changes to Intro.

@@
 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
- Python is one of the top ten most popular programming languages in the world 
+ it is one of the top ten most popular programming languages in the world 
 and is widely used outside of scientific fields in areas like web development, education 
@@
 The development of a package such as SunPy in Python is made possible by the 
-rich ecosystem of scientific packages available in Python. Core packages in this 
-ecosystem such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
-provide the basic functionality expected of a scientific programming language -- 
+rich ecosystem of scientific packages available in Python. Core packages such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
+provide the basic functionality expected of a scientific programming language,
 \textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 
-Built upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
+Building upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
 \texttt{scikit-image} provide more domain-specific functionality.

### 2014-01-28 3-3-HELIO.tex
Some small typo fixed and latex stuff
fixed helio example

@@
 \textit{HELIO Event Catalogue} (HEC) service, and this module was developed as
-part of a Google Summer of Code project in 2013.
+part of a Google Summer of Code (GSOC) project in 2013.
 The HEC service currently provides access to 84 catalogues from different
@@
 
-# Obtain from all the catalogues these which name contain our event of interest
+# From all the catalogues these which name contain our event of interest
 >>> catalogues = hc.get_table_names()
->>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
+>>> catalogues_event = [l[0] for l in catalogues 
+...                     if event_type in l[0] and 'list' not in l[0]]
 
@@
 ...            for event in catalogues_event if 'cactus' in event]
->>> print results
-********** This need to be added!
+>>> for cat in results:
+...     print "{cat} has {nres} results".format(cat = cat.ID, \
+...                                             nres = len(cat.array))
+__helio_hec-cactus_stereoa_cme has 4 results
+__helio_hec-cactus_stereob_cme has 3 results
+__helio_hec-cactus_soho_cme has 7 results
 \end{minted}
-\caption{Example of querying the HEC service.}
+\caption{Example of querying the HEC service to multiple cme
+catalogues, in this case the ones detected by \href{http://sidc.oma.be/cactus/}{CACTus}.}
 \label{code:helio}

### 2014-01-28 3-2-HEK.tex
Stuart's pass-the-paper

@@
 
-The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
-radio bursts) on many 
-different time-scales, length-scales and wavelengths. Observations and metadata 
-concerning these phenomena are collected at the Heliophysics Event 
-Knowledgebase (HEK).  Entries are generated both by automated algorithms and 
-human observers.  Some of the information in the HEK reproduces feature/event 
-data elsewhere (for example, the GOES flare catalog), and some is generated by 
-the Solar Dynamics Observatory Feature Finding Team \cite{martens2012} to
-populate the HEK.  The advantage of the HEK is it provides an homogeneous and 
-well-described interface to a large 
-amount of feature/event information of interest to the solar physics community.
+The Sun is an active star and exhibits a wide range of transient phenomena 
+(e.g. flares and radio bursts) on many different time-scales, length-scales and 
+wavelengths. Observations and metadata concerning these phenomena are collected 
+in the Heliophysics Event Knowledgebase (HEK).  Entries are generated both by 
+automated algorithms and human observers.  Some of the information in the HEK 
+reproduces feature/event data elsewhere (for example, the GOES flare catalogue),
+and some is generated by the Solar Dynamics Observatory Feature Finding Team 
+\citep{martens2012} to populate the HEK.  The advantage of the HEK is it 
+provides an homogeneous and well-described interface to a large amount of 
+feature/event information of interest to the solar physics community.
 
-SunPy accesses this information through the \texttt{hek} module, which was 
-developed with support from the 
-ESA-SOCIS 2011.  The \texttt{hek} module makes use of the HEK API
-(\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
-The current list of 
-events maintained by the HEK and their properties can be found at 
-\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+SunPy accesses this information through the \texttt{hek} module, which was also
+developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
+use of the 
+\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{HEK
+ API}.
+The current list of events maintained by the HEK and their properties can be 
+found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
@@
 event. As was mentioned above, the HEK stores feature/event metadata obtained 
-in different ways, known generally as {\it feature recognition methods} ( 
-FRMs). Example in Listing~\ref{code:hek:frm} filters the results of the previous result to 
-return only those events that have the FRM 'SSW Latest Events'.
+in different ways, known generally as {\it feature recognition methods} (FRMs). 
+Example in Listing~\ref{code:hek:frm} filters the results of the previous 
+result to return only those events that have the FRM 'SSW Latest Events'.
 \begin{listing}[H]
@@
 the construction of queries of almost arbitrary complexity. 
-It is also possible to use the 
-results of a HEK query to download the corresponding data from the VSO by using 
-SunPy's \texttt{H2VClient}.
+It is also possible to use the results of a HEK query to download the 
+corresponding data from the VSO by using SunPy's \texttt{H2VClient}.
 %schriste - this is a weird way to end this section, either show how it is done or 
@@
 %dps - I agree.
+%Stuart: Will do on my next pass

### 2014-01-28 3-3-HELIO.tex
Stuart's pass-the-paper

--- 2014-01-28 3-3-HELIO.tex
@@
 
-The HELiophysics Integrated Observatory 
-(HELIO, \url{http://helio-vo.eu}) has put together a list of web 
-services which allows scientists to query and discover data throughout 
-the heliosphere (\textit{e.g.}, solar, planetary, inter-planetary data, 
-\ldots)\citep{dps2012}.
+The HELiophysics Integrated Observatory (\href{http://helio-vo.eu}{HELIO}) has 
+put together a list of web services which allows scientists to query and 
+discover data throughout the heliosphere (\textit{e.g.}, solar, planetary, 
+inter-planetary data, \ldots)\citep{dps2012}.
 HELIO has been built with a Service-Oriented Architecture, 
@@
 implemented as separate services. 
-HELIO comprises nine different public services, which allows scientists
-to search in different catalogues of registered events, solar features,
-data from instruments in the heliosphere and other information like planets or 
-spacecraft position in time. 
-Additionally, HELIO provides a service that uses a propagation model to link 
-the data in different points of the solar system by its original nature 
-(\textit{e.g.}, Earth auroras are a signature of magnetic field disturbances 
-produced few days before on the Sun).
-In addition to the primary, web-based interface to HELIO
-(\url{http://hfe.helio-vo.eu}), the services can be separately accessed.
+\href{http://helio-vo.eu}{HELIO} comprises nine different public services, 
+which allows scientiststo search in different catalogues of registered events, 
+solar features, data from instruments in the heliosphere and other information 
+like planets or spacecraft position in time. 
+Additionally, \href{http://helio-vo.eu}{HELIO} provides a service that uses a 
+propagation model to link the data in different points of the solar system by 
+its original nature (\textit{e.g.}, Earth auroras are a signature of magnetic 
+field disturbances produced few days before on the Sun).
+In addition to the primary, web-based interface to 
+\href{http://helio-vo.eu}{HELIO}, the services can be separately accessed.
 

### 2014-01-28 4-Util.tex
Stuart's pass-the-paper

@@
 arcseconds) using cartesian coordinates (X, Y). This is the coordinate system 
-most often defined in solar imaging data (see for example, images from SDO/AIA, SOHO/EIT, and TRACE). 
+most often defined in solar imaging data (see for example, images from 
+\textit{SDO/AIA}, \textit{SOHO/EIT}, and \textit{TRACE}). 
 HG coordinates express positions on the Sun using longitude and latitude on 
@@
 which is usually provided by the image header. In the case where it is 
-not, the observer is assumed to be at Earth.Listing \ref{code:wcs_code} shows some examples of coordinate transforms carried out in SunPy using the \verb|wcs| utilities.
+not, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
+some examples of coordinate transforms carried out in SunPy using the 
+\verb|wcs| utilities.
 
@@
 \end{minted}
-\caption{Using the sunpy.wcs sub-package.}
+\caption{Using the sunpy.wcs subpackage.}
 \label{code:wcs_code}
@@
 solar constants. The main namespace contains a number of functions which provide solar
-ephemeris such as the sun to earth distance, solar cycle number, the mean anomaly, etc.
+ephemeris such as the Sun to Earth distance, solar cycle number, the mean 
+anomaly, etc.
 All of these functions take a time as their input which can be provided in any 
@@
 Astropy's Quantities, any solar constant can easily be converted between 
-different units as can be seen in Figure~\ref{fig:constants_code} as well
+different units as can be seen in Listing~\ref{code:constants_code} as well
 as between the SI or cgs unit systems with a single command.  As these objects inherit from 

### 2014-01-28 5-Dev.tex
Stuart's pass-the-paper

@@
 online under the permissive 2-clause BSD licence, the whole 
-development 
-process is also online and open for anyone to contribute to.
-SunPy's development makes use of the online 
-service GitHub (\url{http://github.com}) and Git\footnote{\url{http://git-scm.com/}}
+development process is also online and open for anyone to contribute to.
+SunPy's development makes use of the online service 
+\href{http://github.com}{GitHub} and \href{http://git-scm.com/}{Git}
 as its distributed version control software.
@@
 hierarchically structured view of in-code documentation strings. The SunPy documentation 
-is built automatically and hosted on Read the Docs (\url{http://readthedocs.org})
-at \url{http://docs.sunpy.org}.
+is built automatically and hosted by \href{http://readthedocs.org}{Read the 
+Docs} at \url{http://docs.sunpy.org}.
 
@@
 and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
-through the Python Software Foundation (PSF). It supported development of the HELIO and 
-database sub-packages.
+through the Python Software Foundation (PSF). It supported development of the 
+\texttt{HELIO} and 
+\texttt{database} subpackages.
 
@@
 wish. Upon completion of any modifications it is possible for a user to create 
-a 'Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
+a `Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
 repository in order to incorporate their modification into the SunPy code base. 

### 2014-01-28 1-Introduction.tex

--- 2014-01-28 1-Introduction.tex
@@
 programming language and the breadth of high-quality science-focused packages 
-written in that language. Python is a general-purpose, 
-powerful and easy-to-learn high-level programming language.
-According to the 
-2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+written in that language. Python is a general-purpose, powerful and 
+easy-to-learn high-level programming language.
+According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
  Python is one of the top ten most popular programming languages in the world 
-and is widely used outside of scientific fields in areas like web development, education 
-and `big data' analytics.
+and is widely used outside of scientific fields in areas like web development, education and `big data' analytics.
 
@@
 
-The design philosophy of SunPy is to provide a clean, simple-to-use, and well 
-structured package that provides the \textit{core} tools for solar-physics data analysis. The 
-primary focus of SunPy's early development is to provide specialised, linked, 
-data types that allow the acquisition, processing and visualisation of all types 
-of solar data.
+The design philosophy of SunPy is to be a clean, simple-to-use, and well 
+structured package that provides the \textit{core} tools for solar-physics data 
+analysis. The primary focus of SunPy's early development is to provide 
+specialised, linked, data types that allow the acquisition, processing and 
+visualisation of all types of solar data.
 
@@
 SunPy project, as well as future plans. The latest release of SunPy (0.4)
-can be downloaded from
-the official website (\url{http://sunpy.org}) or can be installed using 
-the Python package index (\mbox{\url{http://pypi.python.org/pypi}}).
-%schriste - the mbox prevents latex from breaking the url across different lines.
+can be downloaded from the \href{http://sunpy.org}{official website} or can be
+installed using the \href{http://pypi.python.org/pypi}{Python package index}.

### 2014-01-28 2-Data_Types.tex

@@
 
-The primary focus of SunPy is to provide data structures 
-that are specifically designed for the primary varieties of solar physics data, namely
-images, time series, and spectra. SunPy provides three core data
-types using Python classes:
-\texttt{Map} (2D spatial data),
-\texttt{LightCurve} (1D temporal series)
+Currently SunPy provides data structures that are specifically designed for the
+three primary varieties of solar physics data, namely images, time series, and
+spectra. SunPy provides core data types for these using Python classes:
+\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
 and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).
@@
 stored in the \texttt{.data} attribute while the metadata is stored 
-in the \texttt{.meta} attribute. It is 
-possible to instantiate the data types from various different 
-sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order to provide
-instrument-specific specialisation, all the core SunPy data types support specialisation;
-\textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} sub-type. 
-Data visualisation is provided by two functions: \texttt{peek()}, for quick plotting,
-and \texttt{plot()}, for more fine-grained control plotting that integrates with 
-\texttt{matplotlib}.
-% LightCurve does NOT have a meta attribute.  Needs to be fixed in the
-% re-write of LightCurve
+in the \texttt{.meta}\footnote{Except \texttt{LightCurve} which currently does 
+not.} attribute. It is possible to instantiate the data types from various 
+different sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order 
+to provide instrument-specific specialisation, all the core SunPy data types 
+support subclassing; \textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} 
+sub-type. 
+Data visualisation is provided by two functions: \texttt{peek()}, for quick 
+plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
+integrates with \texttt{matplotlib}.
 
@@
 include visualisation code that is tailored to that data type. 
-These visualisation methods all currently utilise the matplotlib 
+These visualisation methods all currently utilise the \texttt{matplotlib} 
 package, and are designed in such a way that they integrate well with 
-the \texttt{pyplot} functional interface of \texttt{matplotlib}, as demonstrated in 
-Listing \ref{code:mpl_1}.
-
-%schriste - I vote for removing all of the following code as being too
-%down in the weeds
-%ji -  I agree.  Do we even need to say much more than give a brief
-%outline of the .peek and .plot methods?
-\begin{listing}[H]
-\begin{minipage}{0.49\columnwidth}
-\begin{minted}[bgcolor=bg]{python}
-import sunpy.map
-import matplotlib.pyplot as plt
-
-#Read in a aia file using SunPy
-aiamap = SunPy.map.Map('aia.fits')
-
-#Create the figure and axis 
-#explicitly
-fig = plt.figure()
-ax = plt.subplot()
-
-#Create a image plot with raw data
-im = ax.imshow(aiamap.data,...)
-#add a colour bar
-plt.colorbar(im,ax=ax)
-
-#Add a title
-plt.title("My AIA plot")
-plt.show()
-\end{minted}
-\end{minipage}
-\begin{minipage}{0.49\columnwidth}
-\begin{minted}[bgcolor=bg]{python}
-import SunPy.map
-import matplotlib.pyplot as plt
-
-#Read in a aia file using SunPy
-aiamap = SunPy.map.Map('aia.fits')
-
-#Create the figure and axis 
-#explicitly
-fig = plt.figure()
-ax = plt.subplot()
-
-#Plot the AIA map
-im = aiamap.plot(axes=ax)
-#add a colour bar
-plt.colorbar(im,ax=ax)
-
-#Add a title
-plt.title("My AIA plot")
-plt.show()
-\end{minted}
-\end{minipage}
-\caption{A simple example of how SunPy's plotting functions provide similar 
-behaviour to the \texttt{matplotlib.pyplot} interface.}
-\label{code:mpl_1}
-\end{listing}
+the \texttt{pyplot} functional interface of \texttt{matplotlib}.
 
@@
 interface, as well as allowing the use of the standard 
-\texttt{matplotlib} commands to manipulate the plot parameters, such as the title.
-
-%ayshih - I recommend removing the following sentences
-More technically what is done in the plotting routines is firstly, to 
-make sure that the current state of the figure and axes is maintained 
-in the same way as it is inside the \texttt{pyplot} functions. For 
-\texttt{Map} this means setting \texttt{pyplot.sci()} or set current 
-image, so that \texttt{plt.colorbar()} 
-automatically detects the plotted \texttt{AxesImage} object. 
-Secondly, it also means returning the same type of object as the 
-\texttt{pyplot} interfaces function, \textit{i.e.} for \texttt{Map} 
-it returns the \texttt{AxesImage} instance which is the same type of 
-return as \texttt{pyplot.imshow}.
+\texttt{matplotlib} commands to manipulate the plot parameters, such as the 
+title.

### 2014-01-28 3-1-VSO.tex

@@
 
-The Virtual Solar Observatory (VSO) provides a single, standard query
-interface to access solar data from different archives around the world
- \citep{hill2009}.
+The Virtual Solar Observatory (\href{http://virtualsolar.org}{VSO}) provides a 
+single, standard query interface to access solar data from different archives 
+around the world \citep{hill2009}.
 Data products can be requested for specific instruments or missions, but
@@
 as the wavelength range.
-In addition to the VSO's primary, web-based interface
-(\url{http://virtualsolar.org}), a SOAP (Simple Object Access Protocol)
-service is also available.
+In addition to the VSO's primary, web-based interface, a SOAP (Simple Object 
+Access Protocol) service is also available.
 SunPy's \texttt{vso} module accesses the VSO via the SOAP service using the
@@
 using the \texttt{vso} module.
-Each query is constructed by one or more attributes objects, where each
+Each query is constructed by one or more attribute objects, where each
 attribute object is a constraint on a parameter of the data set, such as the
@@
 It also shows how to download the data using the result
-from the query. One can use the metadata associated with the data sets to specify how the
-files will be named locally, such as creating subdirectories based on the
-instrument names.
+from the query. One can use the metadata associated with the data sets to 
+specify how the files will be named locally, such as creating subdirectories 
+based on the instrument names.
 
@@
 using the ``$|$'' operator.
-All attribute objects provided to the query as keyword arguments are combined
-with a logical \texttt{and} operation.
+All attribute objects provided to the query as arguments are combined with a 
+logical \texttt{and} operation.
 
@@
 %            listing much shorter.
+%Stuart: I suggest removing the second query from here, it dosen't add much.
 \begin{listing}[H]

### 2014-01-28 3-4-Helioviewer.tex

@@
 SunPy provides the ability to download images hosted by the
-Helioviewer Project (\url{http://helioviewer.org}).  
+\href{http://helioviewer.org}{Helioviewer Project}.  
 The aim of the Helioviewer Project is to enable
@@
 
+%Stuart: Do we need this listing?? The same points can be made with 14
 \begin{listing}[H]
@@
 \end{minted}
-\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304}
-%centered image?
+\centering\includegraphics[width=0.5\columnwidth]{helioviewer_latest_aia_304}
 \caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
@@
 It should be noted that the filename of the returned file has the date
-and time of the requested time, which is not the time of the
-observation shown in the PNG image.  This is because of the
-Helioviewer API.  The API request finds images closest to the
-requested time. But since the user may ask for images from multiple
-sources, and each of them may have a different observation time, it is
-unclear which time is the most appropriate to associate with the
-resultant image.  The Helioviewer API does not select between any of
-the image observation times, but instead returns an image filename
-based on the request time, resulting in predictable filenames.
+and time of the requested time, which is not the time of the observation shown 
+in the PNG image.  This is because the Helioviewer API request finds images 
+closest to the requested time. However, since the user may ask for images from 
+multiple sources, and each of them may have a different observation time, it is
+unclear which time is the most appropriate to associate with the resultant 
+image.  The Helioviewer API therefore does not select between any of the image 
+observation times, but instead returns an image filename based on the request 
+time, resulting in predictable filenames.
 
@@
 Reading JPEG2000 file into a SunPy session requires installing two
-other pieces of software. The first, \texttt{OpenJPEG}, is an open
-source library for reading and writing JPEG2000 files
-(\url{http://www.openjpeg.org}).  The other package required is
-\texttt{glymur}, (\url{https://github.com/quintusdias/glymur}), an
+other pieces of software. The first, 
+\href{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open
+source library for reading and writing JPEG2000 files.  The other package 
+required is 
+\href{https://github.com/quintusdias/glymur}{\texttt{glymur}}, an
 interface between Python and the OpenJPEG libraries (note that these
@@
 Helioviewer-supplied image data in an identical fashion to a SunPy map
-object generated from FITS data (see Section \ref{sec:map}).
+object generated from FITS data (see Section \ref{ssec:map}).
 

### 2014-01-28 authors.tex

@@
 Albert Y Shih$^2$,
+Simon Liedtke$^11$,
+Russell J Hewett$^8$, %88
 % Contributors to SunPy Sorted thus:
@@
 K Hughitt, %446
-R Hewett, %88
 Nabil Freij$^1$, %52
 M Earnshaw, %52
-T Meszaros, %17
+Tomas Meszaros$^{10}$, %17
 N Chorley, %17
@@
 J Ballew, %3
-T Robitaille, %2
+Thomas P Robitaille, %2
 B Mampaey, %2
@@
 Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ,
+
+$^8$Department of Mathematics, Massachusetts Institute of Technology, 77 
+Massachusetts Ave, E17-317, Cambridge, MA 02142,
+
+$^9$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
+69117, Germany,
+
+$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno,
+
+$^{11}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany,
 }

### 2014-01-28 solarsoft.tex

@@
-\section{Comparison to SolarSoft}
+\section{Comparison to SolarSoft}\label{sec:ssw}
 This section compares the SunPy library that is described in Sections 
@@
 Basic COCOMO model \citep{_cocomo_2014}). 
-%stuart - This data was calculated using...} If we can add them to the repository 
+%dps - This data was calculated using...} If we can add them to the repository 
 %will improve the quality of the paper and we can always repeat the calculation in the future.
 %schriste - i don't know what you mean by this 
+%Stuart: comment was Davids
 Individual missions and instruments provide additional optional packages to 
@@
 %
-%stuart - \footnote{We need to be careful with this! IDL means more things that our 
+%dps - \footnote{We need to be careful with this! IDL means more things that 
+%our 
 %beloved Interactive Data Language. If we search for that and programming 
@@
 % 
-% schriste - I think we defined IDL properly. I was being generous with the book search for IDL
+% schriste - I think we defined IDL properly. I was being generous with the 
+%book search for IDL
+%Stuart: again not not mine, I think we should drop the book thing, in 
+%comparison to the other metrics used it's a little weak.
 on Amazon for books on IDL programming generated $189$ results while a search 
@@
 high-performance, easy-to-use data structures and data analysis tools for time 
-series data\citep{mckinney2012}. \texttt{pandas} was originally developed for 
+series data \citep{mckinney2012}. \texttt{pandas} was originally developed for 
 quantitative analysis of financial data and has since grown into a generalised 

### 2014-01-28 2-1-Map.tex

@@
 \subsection{Map}\label{ssec:map}
-The Map data type represents 2D spatial data such as images of the Sun and 
-inner heliosphere. It provides a wrapper around a data array and its associated
-spatial coordinates and other metadata. The \texttt{Map} class provides 
-methods for typical operations on 2D data, 
-such as rotation and re-sampling, and visualisation functionality.
-The \texttt{Map} class
-also provides a convenient interface for loading data from a variety of sources, typically
-a FITS file as shown in Listing~\ref{code:aia_1}.
+The Map data type represents 2D spatial data, such as images of the Sun and 
+inner heliosphere. It provides a wrapper around a \texttt{numpy} data array and 
+its associated spatial coordinates and other metadata. The \texttt{Map} class 
+provides methods for typical operations on 2D data, such as rotation, 
+re-sampling, and visualisation functionality.
+The \texttt{Map} class also provides a convenient interface for loading data 
+from a variety of sources, typically a FITS file as shown in 
+Listing~\ref{code:aia_1}.
 
 The architecture of the \texttt{Map} class consists of a template map called
-\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. \texttt{NDData} is a 
-generic wrapper around an \texttt{ndarray} with a \texttt{.meta} attribute to store metadata.
-As \texttt{NDData} is currently still in development, \texttt{GenericMap} does not yet make full
-use of its capabilities, but this inheritance structure provides 
-for future integration of \texttt{Astropy}. In order to provide instrument- or
-detector-specific integration, \texttt{GenericMap} is subclassed on creation. 
-Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (\textit{i.e.}, factory)
-by implementing a method that returns \texttt{True} if the metadata
-in the file header matches
-that instrument or detector.  This \texttt{Map} factory 
-will then automatically return an instance of the specific \texttt{GenericMap} 
-subclass. SunPy 0.4 has \texttt{Map} specialisations for the 
-following instruments: 
+\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
+\texttt{NDData} is a generic wrapper around an \texttt{ndarray} with a 
+\texttt{.meta} attribute to store metadata.
+As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
+not yet make full use of its capabilities, but this inheritance structure 
+provides for future integration of \texttt{Astropy}. In order to provide 
+instrument- or detector-specific integration, \texttt{GenericMap} is designed 
+in such a way that it can be subclassed to implement instrument specific 
+functionality. Each of these subclasses of \texttt{GenericMap} can register 
+with the \texttt{Map} creation factory by implementing a method that returns 
+\texttt{True} if the metadata in the file header matches that instrument or 
+detector.  This \texttt{Map} factory will then automatically return an instance 
+of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
+SunPy 0.4 has \texttt{Map} specialisations for the following instruments: 
 \textit{YOHKOH/SXT}, \textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
@@
 In addition, Listing~\ref{code:mapcube_2} shows how the \texttt{MapCube} 
-classes interacts with the \texttt{animation} module to save a video.
+classes interacts with the \texttt{matplotlib.animation} submodule to save a 
+video.
 

### 2014-01-28 2-2-Lightcurve.tex

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the \texttt{pandas} data-analysis library (\url{http://pandas.pydata.org}),
-and \texttt{LightCurve}'s
-\texttt{.data} attribute is a \texttt{pandas.DataFrame} class.
+the \href{http://pandas.pydata.org}{\texttt{pandas}} data-analysis library, and 
+\texttt{LightCurve}'s \texttt{.data} attribute is a \texttt{pandas.DataFrame} 
+class.
 The \texttt{pandas} library contains a large amount
@@
 included.  Future developments will introduce support for additional
-instruments and data products.  Since there is no established standard
-as to how time-series data
-should be stored and distributed, each SunPy \texttt{LightCurve}
-object provides the ability to download its corresponding specific
-data format in its constructor.
-
-%\subsubsection{Creating and using Lightcurves}
+instruments and data products, as well as implementing a factory interface 
+similar to that of \texttt{Map}.  Since there is no established standard
+as to how time-series data should be stored and distributed, each SunPy 
+\texttt{LightCurve} object provides the ability to download its corresponding 
+specific data format in its constructor and parse that file type.
 
@@
 an input time range. In Listing~\ref{code:goes_lc}, 
-the \texttt{LightCurve} constructor searches a remote site for the GOES X-ray data 
-specified by the time interval, downloads the required files and subsequently 
-creates the object.
+the \texttt{LightCurve} constructor searches a remote source for the GOES X-ray 
+data specified by the time interval, downloads the required files and 
+subsequently creates and plots the object.
 
@@
 >>> goes.peek()
->>> trange = TimeRange('2011-06-07 06:00','2011-06-07 07:00')
-%>>> goes_zoom = goes.truncate(trange)
-% the above does not work!
 >>> resampled_goes = goes.data.resample("1H")
 % Does 1h resample makes sense?? I vote for an example with some utility
+% an example is an example right.
 \end{minted}
@@
 \end{center}
-\caption{Example retrieval of a GOES lightcurve for the time interval 06:00--08:00 UT on 
-2011 June 7 using a time range, and the output of the \texttt{peek()} method.
-A sub-interval is then extracted from the Lightcurve and finally the data is resampled
-to 1 hour cadence.}
+\caption{Example retrieval of a GOES lightcurve for the time interval 
+06:00--08:00 UT on 2011 June 7 using a time range, and the output of the 
+\texttt{peek()} method.
+Finally the data is resampled to a 1 hour cadence.}
 \label{code:goes_lc}
@@
 a variety of ways in order to perform time-series analysis.
+
+%Stuart: Where did the pandas section go?

### 2014-01-28 2-3-Spectra.tex

@@
 
-The \texttt{Spectrogram} class supports radio spectrograms from the e-Callisto 
-solar radio spectrometer network (\url{http://www.e-callisto.org/})
-and STEREO/SWAVES spectrograms.
+The \texttt{Spectrogram} class supports radio spectrograms from the 
+\href{http://www.e-callisto.org/}{e-Callisto}
+solar radio spectrometer network and STEREO/SWAVES spectrograms.
 As with other SunPy data types, the \texttt{Spectrogram} class has been
@@
   data for the requested time range and observatory, merges it and
-  removes the background signal.  The data requested -- 'BIR' -- is
-  the code name of the Rosse Observatory at Birr Castle in Ireland
-  (\url{http://www.rosseobservatory.ie})}
+  removes the background signal.  The data requested -- `BIR' -- is
+  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
+  at Birr Castle in Ireland.}
 \label{code:spectra}

### 2014-01-28 3-5-Database.tex

@@
 SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
-local data files. The database package was developed as part of GSOC 2013.
+local data files. The database package was developed as part of the Google 
+Summer Of Code (GSOC) program 2013.
 
 The database sub-package makes use of a database supported by
-SQLAlchemy (\url{http://www.sqlalchemy.org}). This library was chosen
+\href{http://www.sqlalchemy.org}{SQLAlchemy}. This library was chosen
 since it supports many SQL dialects. 
 If SQLite is chosen, the database is stored as a single file which is
-created automatically. This solution makes it possible to easily backup, copy and distribute
-a database file. A server-based database, on the other hand, could be used by a collaboration 
-who work together from different machines on the
+created automatically.A server-based database, on the other hand, could be used 
+by a collaboration who work together from different machines on the
 same data: a central database server stores all data and the clients connect to
@@
 
-The database can store and manage all data that is retrieved via SunPy from the net
-package though currently only the \textsc{VSO} package is supported. 
+The database can store and manage all data that can be read via SunPy's 
+\texttt{io} subpackage, while direct integration with the \textsc{VSO} 
+subpackage is supported.
 It also possible to add entries manually by file or directory. The package also provides
@@
 The database also provides the ability to associate custom meta-data to 
-each database entry such as keywords, comments, and favouring.
+each database entry such as keywords, comments, and favouring, as well as 
+querying the full metadata (\textit{i.e.} FITS header) of each entry.
 
@@
 
-Using the database package, one uses the \texttt{Database} class to connect
-with a database and perform operations on it. Listing~\ref{code:database} shows how to connect
+The \texttt{Database} class connects to a database and allows the user to 
+perform operations on it. Listing~\ref{code:database} shows how to connect
 to an in-memory database and download data from the \textsc{VSO}. These entries are
 automatically added to the database. The function \texttt{len} is used to get the number of
-records. The function \texttt{display\_entries} displays an iterable of database entries
-in a nicely-formatted \textsc{ASCII} table. The headlines correspond to the
-attributes of the respective database entries.
+records. The function \texttt{display\_entries} displays an iterable of 
+database entries in a nicely-formatted \textsc{ASCII} table. The headlines 
+correspond to the attributes of the respective database entries.
 
@@
 ...     database,
-...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
-id observation_time_start wavemin        wavemax           download_time      
--- ---------------------- -------        -------           -------------      
-1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
+...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
+id observation_time_start wavemin        wavemax    
+-- ---------------------- -------        -------    
+1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05
 

### 2014-01-28 2-3-Spectra.tex
minor edits to Spectra section

@@
 instruments.  The variety and complexity of these instruments and
-their resultant datasets makes it very challenging to support all in a
-general way.  The \texttt{spectra} module implements a
+their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
 \texttt{Spectrum} class for 1D data (intensity versus frequency) and a
@@
 \texttt{.from\_range} function, the object merges all the downloaded
-files downloaded into a single spectrogram, across time and frequency.
-In the example shown, data is observed in two frequency ranges, 
+files into a single spectrogram, across time and frequency.
+In the example shown, data is provided in two frequency ranges, 
 20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in

### 2014-01-28 3-Retrieval.tex
minor typo corrections. Added a brief introduction to Section 3 (data search and retrieval)

@@
-\section{Solar Data Search and Retrieval}
+\section{Solar Data Search and Retrieval}\label{sec:retrieval}
+
+Several well-developed resources currently exist within heliophysics which provide event databases, remote access and data retrieval for a large number of data sources.
+As a community-based project, SunPy provides support for these resources via the \texttt{sunpy.net} package.
+In the following subsections, we describe a number of these resources and introduce current methods for accessing them within SunPy.
 

### 2014-01-28 solarsoft.tex
more minor edits and comments to SolarSoft section.

@@
 physics data analysis library: SolarSoft (SSW) \citep{freeland1998}.
+%ARI - is is SolarSoft or SolarSoftWare?! The latter includes the W :-)
 SolarSoft is a set of integrated software libraries, databases, and system 
@@
 cross-platform and powerful programming language.
-It therefore has a very large user community which extends far outside of the 
+It therefore has a very large user base which extends far outside of the 
 solar physics or astronomy communities. It is very extensible with C, C++, 
-FORTRAN or even IDL. Many books and on-line documentation is available. For 
+FORTRAN or even IDL. Many books and on-line documentation sources are available. For 
 example, at the time writing a search 
@@
 for Python yielded $1\,788$ results. Python has a strong emphasis on 
-readability a concept which is well-aligned with the scientific endeavour.
+readability, a concept which is well-aligned with the scientific endeavour.
+%In fairness, IDL is also quite readable! Could move this statement to the intro instead.
 Additionally, Python is increasingly being taught in universities, which means 
@@
 interactive and shareable notebook-based computing \citep{perez2007}. For all 
-of these reasons, Python is an ideal platform for a modern data-
-analysis environment for solar physics.
+of these reasons, Python is an ideal platform for a modern data analysis environment 
+for solar physics.
 
@@
 provide capabilities surpassing that provided by IDL for array manipulation and 
-2D plotting \citep{greenfield2011}. Providing similar capabilities as SSW/gen 
+2D plotting \citep{greenfield2011}. Providing similar capabilities to SSW/gen 
 in Python is made easier by leveraging the diverse Python community. For 

### 2014-01-28 1-Introduction.tex

--- 2014-01-28 1-Introduction.tex
@@
 powerful and easy-to-learn high-level programming language.
-According to the 
-2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
  it is one of the top ten most popular programming languages in the world 

### 2014-01-28 2-1-Map.tex

@@
 In addition, Listing~\ref{code:mapcube_2} shows how the \texttt{MapCube} 
-classes interacts with the \texttt{matplotlib.animation} submodule to save a 
+classes interact with the \texttt{matplotlib.animation} submodule to save a 
 video.

### 2014-01-28 2-2-Lightcurve.tex
tiny edits to Map and Lightcurve

@@
 as to how time-series data should be stored and distributed, each SunPy 
-\texttt{LightCurve} object provides the ability to download its corresponding 
+\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
 specific data format in its constructor and parse that file type.
@@
 >>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-...                                         '2011-06-07 10:00')
+...                                         '2011-06-07 08:00')
 >>> goes.peek()
->>> resampled_goes = goes.data.resample("1H")
-% Does 1h resample makes sense?? I vote for an example with some utility
-% an example is an example right.
+%removed the resample part of the example - really we need to fix truncate!
 \end{minted}
@@
 06:00--08:00 UT on 2011 June 7 using a time range, and the output of the 
-\texttt{peek()} method.
-Finally the data is resampled to a 1 hour cadence.}
+\texttt{peek()} method.}
 \label{code:goes_lc}
@@
 %Stuart: Where did the pandas section go?
+%ARI - looks like it's up top

### 2014-01-28 3-3-HELIO.tex

@@
 put together a list of web services which allows scientists to query and 
-discover data throughout the heliosphere (\textit{e.g.}, solar, planetary, 
-inter-planetary data, \ldots)\citep{dps2012}.
+discover data throughout the heliosphere, from solar, and magnetospheric to planetary and 
+inter-planetary data \citep{dps2012}.
 HELIO has been built with a Service-Oriented Architecture, 
@@
 \href{http://helio-vo.eu}{HELIO} comprises nine different public services, 
-which allows scientiststo search in different catalogues of registered events, 
+which allows scientists to search different catalogues of registered events, 
 solar features, data from instruments in the heliosphere and other information 
@@
 SunPy's \texttt{hec} module provides an interface to the
-\textit{HELIO Event Catalogue} (HEC) service, and this module was developed as
+\textit{HELIO Event Catalogue} (HEC) service (not to be confused with the HEK, discussed in Section \ref{ssec:hek}), and this module was developed as
 part of a Google Summer of Code (GSOC) project in 2013.
 The HEC service currently provides access to 84 catalogues from different
-sources (automated and manual classification, event lists from publications, \ldots).
+sources.
 As with all of the HELIO services, the HEC service provides results in VOTable 

### 2014-01-28 3-5-Database.tex

@@
 subpackage is supported.
-It also possible to add entries manually by file or directory. The package also provides
+It is also possible to add entries manually by file or directory. The package also provides
 a \texttt{fetch} method which provides a unified data search which includes both local files
-and files on the \textsc{VSO} are searched. This reduces the likelihood of downloading the same file 
+and files on the \textsc{VSO}. This reduces the likelihood of downloading the same file 
 multiple times. When a file is added to the database the file is scanned and a file hash is produced. 

### 2014-01-28 4-Util.tex

@@
 SunPy is meant to provide a consistent environment for solar data analysis. In 
-order to achieve this goal SunPy provides a number of utility functions and packages which 
+order to achieve this goal SunPy provides a number of additional functions and packages which 
 are used by the other SunPy modules and are made available to the user. This section 

### 2014-01-28 6-Future.tex

@@
 As discussed in Section \ref{sec:Intro}, the primary focus of the 
-\texttt{sunpy} library is the analysis and visualisation of `high-level' solar 
+SunPy library is the analysis and visualisation of `high-level' solar 
 data. This means data that has been put through instrument processing 
@@
 calibration routines, and contains full (WCS) coordinate information. 
-The 
-development plan for SunPy is to continue development within this 
+The plan for SunPy is to continue development within this 
 scope. The 
@@
 \citep{theastropycollaboration2013} and 
-its community has grown, abd this direct collaboration between Astropy 
+its community has grown, and this direct collaboration between Astropy 
 % what abd means?

### 2014-01-28 3-5-Database.tex
small language tweaks in database subsection

@@
 local data files. The database package was developed as part of the Google 
-Summer Of Code (GSOC) program 2013.
+Summer Of Code (GSoC) program 2013.
 
@@
 since it supports many SQL dialects. 
-If SQLite is chosen, the database is stored as a single file which is
-created automatically.A server-based database, on the other hand, could be used 
+If SQLite is selected, the database is stored as a single file which is
+created automatically. A server-based database, on the other hand, could be used
 by a collaboration who work together from different machines on the

### 2014-01-28 3-5-Database.tex
changed code example in database subsection

@@
 >>> database.download(
-...     vso.attrs.Time((2011, 9, 20, 1), (2011, 9, 20, 2)),
-...     vso.attrs.Instrument('RHESSI'))
+...     vso.attrs.Time('2012-08-05', '2012-08-05 00:00:05'),
+...     vso.attrs.Instrument('AIA'))
 >>> len(database)
-6
+2
 >>> from sunpy.database.tables import display_entries
@@
 -- ---------------------- ------- -------
-1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05
-
+1  2012-08-05 00:00:01    9.4     9.4    
+2  2012-08-05 00:00:02    33.5    33.5   
 \end{minted}

### 2014-01-28 authors.tex
added uni information for Florian Mayer

@@
 % Date of most recent contribution
-F Mayer, %721
+F Mayer$^{12}$, %721
 K Hughitt, %446
@@
 $^{11}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany,
+
+$^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria,
 }

### 2014-01-28 authors.tex

@@
 Albert Y Shih$^2$,
-Simon Liedtke$^11$,
+Simon Liedtke$^{11}$,
 Russell J Hewett$^8$, %88

### 2014-01-29 1-Introduction.tex
Updated introduction to fix grammar and typos

@@
 Science is driven by the analysis of data. Modern advances in sensor
-technology combined with the availability of cheap storage has led to
+technology, combined with the availability of inexpensive storage has led to
 rapid increases in amount of data available to scientists in almost
-every discipline.  Solar physics is no exception to this trend. NASA's
+every discipline.  Solar physics is no exception to this trend. For example, NASA's
 Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
-produces over 1 TB of catalogued and stored data per day. Managing and
-analysing this mountain of data to enable scientific discovery
+produces over 1 TB of catalogued and stored data per day [REF]. Managing and
+analysing this mountain of data
 requires increasingly sophisticated software tools.  Key qualities
@@
 to standards.  Software with these qualities provides a strong
-foundation which is responsive to the needs of the community as data
+foundation can be responsive to the needs of the community as data
 volumes grow and science questions evolve.
@@
 powerful and easy-to-learn high-level programming language.
+% RJH: Can we cut the next sentence?  It seems superfluous and top 10 is rather
+% meaningless.
 According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
@@
 
-The design philosophy of SunPy is to be a clean, simple-to-use, and well 
-structured package that provides the \textit{core} tools for solar-physics data 
-analysis. The primary focus of SunPy's early development is to provide 
-specialised, linked, data types that allow the acquisition, processing and 
+SunPy is designed to be a clean, simple-to-use, and well 
+structured package that provides the \textit{core} tools for data analysis in 
+solar physics. The primary focus of SunPy's early development is to provide 
+specialised data types that allow the acquisition, processing and 
 visualisation of all types of solar data.
@@
 The purpose of this paper is to provide an overview of SunPy's current 
-capabilities, an overview of the development model and community aspects of the 
-SunPy project, as well as future plans. The latest release of SunPy (0.4)
-can be downloaded from the \href{http://sunpy.org}{official website} or can be
+capabilities, an overview of the project's development model, community aspects of the 
+SunPy project, as well as future plans. The latest release of SunPy, version 0.4,
+can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be
 installed using the \href{http://pypi.python.org/pypi}{Python package index}.

### 2014-01-29 2-1-Map.tex
Updated datatypes sections

@@
 \subsection{Map}\label{ssec:map}
-The Map data type represents 2D spatial data, such as images of the Sun and 
+The Map data type stores 2D spatial data, such as images of the Sun and 
 inner heliosphere. It provides a wrapper around a \texttt{numpy} data array and 
 its associated spatial coordinates and other metadata. The \texttt{Map} class 
-provides methods for typical operations on 2D data, such as rotation, 
-re-sampling, and visualisation functionality.
+provides methods for typical operations on 2D data, such as rotation and 
+re-sampling, as well as visualisation functionality.
 The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, typically a FITS file as shown in 
+from a variety of sources, including a FITS file as shown in 
 Listing~\ref{code:aia_1}.
@@
 \texttt{NDData} is a generic wrapper around an \texttt{ndarray} with a 
-\texttt{.meta} attribute to store metadata.
+\texttt{meta} attribute to store metadata.
 As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
@@
 instrument- or detector-specific integration, \texttt{GenericMap} is designed
-in such a way that it can be subclassed to implement instrument specific 
-functionality. Each of these subclasses of \texttt{GenericMap} can register 
-with the \texttt{Map} creation factory by implementing a method that returns 
-\texttt{True} if the metadata in the file header matches that instrument or 
-detector.  This \texttt{Map} factory will then automatically return an instance 
+to be subclassed. Each subclass of \texttt{GenericMap} can register 
+with the \texttt{Map} creation factory, which will then automatically return an instance
 of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
-SunPy 0.4 has \texttt{Map} specialisations for the following instruments: 
+SunPy v0.4 has \texttt{Map} specialisations for the following instruments: 
 \textit{YOHKOH/SXT}, \textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
@@
 and \textit{IRIS} SJI frames. 
+% RJH: Instruments should be consistent throughout (italics, caps, etc).  Also,
+% usually citations are provided for instruments.
 
 The \texttt{Map} class stores standard metadata retrieved from the header of 
-the image file in the \texttt{.meta} attribute and provides convenience 
-properties for commonly accessed metadata: \textit{e.g.}, \texttt{.instrument}, 
-\texttt{.wavelength} or \texttt{.coordinate\_system}. 
-Listing \ref{code:aia_1} demonstrates the quick-plot functionality of 
+the image file in the \texttt{meta} attribute and provides convenience 
+properties for commonly accessed metadata: \textit{e.g.}, \texttt{instrument}, 
+\texttt{wavelength} or \texttt{coordinate\_system}. 
+Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
 \texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file,
+\texttt{GenericMap}. The map is created from an \textit{AIA} FITS file,
 and a quick-view plot is created.}
@@
 \end{center}
-\caption{Example showing a \texttt{CompositeMap} plot and the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing a \texttt{CompositeMap} plot, with RHESSI data composed with SDO/AIA data, and the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \end{listing}
+% RJH: If this is kept, the 'artist' bit should be explained.

### 2014-01-29 2-2-Lightcurve.tex
Updated datatypes sections

@@
 
-Time series data and their analysis are a fundamental aspect of solar
+Time series data and their analyses are a fundamental aspect of solar
 physics for which many data sources are available.
@@
 the \href{http://pandas.pydata.org}{\texttt{pandas}} data-analysis library, and 
-\texttt{LightCurve}'s \texttt{.data} attribute is a \texttt{pandas.DataFrame} 
+\texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
 class.
@@
 % Do we need to explain what OCS means?
+% RJH: I'd argue that everything other than (EVE) can be cut, but I'm not 
+% confident enough to make that cut.
 average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
@@
 A \texttt{LightCurve} object may be created using a number of different methods. 
-Firstly, a \texttt{LightCurve} may be created for a specific instrument given
+For example, a \texttt{LightCurve} may be created for a specific instrument given
 an input time range. In Listing~\ref{code:goes_lc}, 

### 2014-01-29 2-3-Spectra.tex
Updated datatypes sections

@@
 their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
-\texttt{Spectrum} class for 1D data (intensity versus frequency) and a
-\texttt{Spectrogram} class for 2D data (intensity versus time and
+\texttt{Spectrum} class for 1D data (intensity as a function of frequency) and a
+\texttt{Spectrogram} class for 2D data (intensity as a function of time and
 frequency).  Each of these classes use a \texttt{numpy.ndarray} class
-as its \texttt{.data} attribute.  These two classes were implemented
+as its \texttt{data} attribute.  These two classes were implemented
 by funding provided by the Astrophysics Research Group at Trinity
@@
 the observatory of interest.  When the data is requested using the
-\texttt{.from\_range} function, the object merges all the downloaded
+\texttt{from\_range} function, the object merges all the downloaded
 files into a single spectrogram, across time and frequency.
@@
 the implemented background subtraction method.
+% RJH: Which subtraction method?  If the specifics are irrelevant, cut it.
 %ji to DPS - what is the linearisation that is happening here?

### 2014-01-29 2-Data_Types.tex
Updated datatypes sections

@@
 
-Currently SunPy provides data structures that are specifically designed for the
-three primary varieties of solar physics data, namely images, time series, and
+Currently, SunPy provides data structures that are specifically designed for the
+three primary varieties of solar physics data: images, time series, and
 spectra. SunPy provides core data types for these using Python classes:
 \texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
-and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).
+and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).
 
-The classes provide access to the original data
+These classes allow access to the original data
 along with associated metadata and provide appropriate convenience functions to
 enable data analysis and visualisation. For each of these classes, the data is
-stored in the \texttt{.data} attribute while the metadata is stored 
-in the \texttt{.meta}\footnote{Except \texttt{LightCurve} which currently does 
-not.} attribute. It is possible to instantiate the data types from various 
+stored in the \texttt{data} attribute while the metadata is stored 
+in the \texttt{meta} attribute. (Curently, \texttt{LightCurve} does 
+not support the \texttt{meta} attribute.) It is possible to instantiate the
+data types from various
 different sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order 
@@
 support subclassing; \textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} 
-sub-type. 
+sub-type for data from the SDO/AIA instrument. 
 Data visualisation is provided by two functions: \texttt{peek()}, for quick 
@@
 \label{subsec:Viz}
-As has been demonstrated in this section, the core SunPy datatypes 
-include visualisation code that is tailored to that data type. 
+As demonstrated in this section, the core SunPy datatypes 
+include visualisation methods that are tailored to that data type. 
 These visualisation methods all currently utilise the \texttt{matplotlib} 

### 2014-01-29 3-3-HELIO.tex
Updated HELIO

@@
 The HELiophysics Integrated Observatory (\href{http://helio-vo.eu}{HELIO}) has 
-put together a list of web services which allows scientists to query and 
-discover data throughout the heliosphere, from solar, and magnetospheric to planetary and 
+compiled a list of web services which allows scientists to query and 
+discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
 inter-planetary data \citep{dps2012}.
-HELIO has been built with a Service-Oriented Architecture, 
-\textit{i.e.} its capabilities are split into a number of tasks that are 
+HELIO is built with a Service-Oriented Architecture, 
+i.e., its capabilities are divided into a number of tasks that are 
 implemented as separate services. 
@@
 solar features, data from instruments in the heliosphere and other information 
-like planets or spacecraft position in time. 
+such as planetary or spacecraft position in time. 
 Additionally, \href{http://helio-vo.eu}{HELIO} provides a service that uses a 
@@
 SunPy's \texttt{hec} module provides an interface to the
-\textit{HELIO Event Catalogue} (HEC) service (not to be confused with the HEK, discussed in Section \ref{ssec:hek}), and this module was developed as
+\textit{HELIO Event Catalogue} (HEC) service. This module was developed as
 part of a Google Summer of Code (GSOC) project in 2013.
@@
 As with all of the HELIO services, the HEC service provides results in VOTable 
-data format (defined by IVOA \cite{ochsenbein_ivoa_2011}), and the \texttt{hec}
+data format (defined by IVOA \cite{ochsenbein_ivoa_2011}). The \texttt{hec}
 module parses this output using the \texttt{astropy.io.votable} package.
@@
 
-Listing~\ref{code:helio} shows an example of how to obtain information
+For example, Listing~\ref{code:helio} shows how to obtain information
 from different catalogues of coronal mass ejections (CMEs).
@@
 \end{listing}
+% RJH: CACTus should be defined and a reference provided in the reference section.
 
-Additional HELIO services will be supported in the future by SunPy.
+In the future, additional HELIO services will be supported in the future by SunPy.
+% RJH: This sentence is an orphan and should have a home constructed for it.

### 2014-01-29 3-5-Database.tex
Updated database

@@
 local data files. The database package was developed as part of the Google 
-Summer Of Code (GSoC) program 2013.
+Summer of Code (GSoC) program 2013.
 
@@
 created automatically. A server-based database, on the other hand, could be used
-by a collaboration who work together from different machines on the
-same data: a central database server stores all data and the clients connect to
+by a collaborators who work together on the
+same data from different computers: a central database server stores all data and the clients connect to
 it to read or write data.
@@
 The database can store and manage all data that can be read via SunPy's 
-\texttt{io} subpackage, while direct integration with the \textsc{VSO} 
+\texttt{io} subpackage, and direct integration with the \textsc{VSO} 
 subpackage is supported.
-It is also possible to add entries manually by file or directory. The package also provides
-a \texttt{fetch} method which provides a unified data search which includes both local files
+It is also possible to manually add file or directory entries. The package also provides
+a unified data search via the \texttt{fetch()} method, which includes both local files
 and files on the \textsc{VSO}. This reduces the likelihood of downloading the same file 
-multiple times. When a file is added to the database the file is scanned and a file hash is produced. 
+multiple times. When a file is added to the database, the file is scanned and a file hash is produced. 
 The current date is associated with the entry along with metadata summaries such 
@@
 each database entry such as keywords, comments, and favouring, as well as 
-querying the full metadata (\textit{i.e.} FITS header) of each entry.
+querying the full metadata (i.e., FITS header) of each entry.
 
@@
 to an in-memory database and download data from the \textsc{VSO}. These entries are
-automatically added to the database. The function \texttt{len} is used to get the number of
-records. The function \texttt{display\_entries} displays an iterable of 
+automatically added to the database. The function \texttt{len()} is used to get the number of
+records. The function \texttt{display\_entries()} displays an iterable of 
 database entries in a nicely-formatted \textsc{ASCII} table. The headlines 

### 2014-01-29 4-Util.tex
Updated utilities

@@
 for most solar data analysis, namely converting from Helioprojective-Cartesian 
-(HPC) to Heliographic coordinates (HG). HPC describes the positions on 
+(HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
 the Sun as angles measured from the center of the solar disk (usually in 
@@
 \subsubsection{Sun}\label{ssec:util:sun}
-The purpose of this module is to provide solar-specific data for example ephemeris and
+The purpose of this module is to provide solar-specific data, for example ephemerides and
 solar constants. The main namespace contains a number of functions which provide solar
-ephemeris such as the Sun to Earth distance, solar cycle number, the mean 
+ephemerides such as the Sun to Earth distance, solar cycle number, the mean 
 anomaly, etc.
@@
 as between the SI or cgs unit systems with a single command.  As these objects inherit from 
-Numpy's ndarray, they work well with standard representations of numbers.
+Numpy's \texttt{ndarray}, they work well with standard representations of numbers.
 For convenience a number of shortcuts to frequently used constants are provided 
@@
 or a function to query the LYRA timeline annotation file. Currently, some support is included
- in this way for the GOES, LYRA, RHESSI and IRIS instruments, while future developments 
- will include support for additional missions. It is anticipated that, ultimately, solar
+ for the GOES, LYRA, RHESSI and IRIS instruments, while future developments 
+ will include support for additional missions. Ultimately, it is anticipated that solar
   missions requiring a large suite of software tools will be supported via a separately 

### 2014-01-29 5-Dev.tex
Minor patch to dev

@@
 Additionally, SunPy makes use of `continuous integration' provided by
-Travis (\url{http://travis-ci.org}), a process by which the addition of any new code 
+Travis CI (\url{http://travis-ci.org}), a process by which the addition of any new code 
 automatically triggers a comprehensive review of written unit tests. If any single test
@@
 code-review discussions.
+% RJH: do we want to list both the community and dev lists?
 
+% RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
 Many of the larger features in SunPy have been developed 

### 2014-01-29 solarsoft.tex
Added comments to this section

@@
 packages which contain specialised software for different instrument or tools.
+
+% RJH: The entire next two paragraphs never mention SSW.  I find all of the
+% lines of code and $$ counts to be superfluous.  Do those include the documentation?
+% What about generated files?  I don't think they contribute much.
 
@@
 (average salary of \$110k in the Washington, DC, area according to indeed.com at 
+% RJH: Is this for a python developer?  Again, this is useless info, imho.
 the time of writing). Python continues to see increased use in the astronomy 

### 2014-01-29 2-1-Map.tex
Made astropy references consistent

@@
 not yet make full use of its capabilities, but this inheritance structure 
-provides for future integration of \texttt{Astropy}. In order to provide 
+provides for future integration of \texttt{astropy}. In order to provide 
 instrument- or detector-specific integration, \texttt{GenericMap} is designed

### 2014-01-29 solarsoft.tex
Made astropy references consistent

@@
 data analysis package. SunPy also relies on and is coordinating with the 
-\texttt{Astropy} package \citep{theastropycollaboration2013}. \texttt{Astropy} is still in 
+\texttt{astropy} package \citep{theastropycollaboration2013}. Astropy is still in 
 active development but already provides many relevant capabilities such as 

### 2014-01-29 2-1-Map.tex
repaired i.e. and e.g.

@@
 the image file in the \texttt{meta} attribute and provides convenience 
-properties for commonly accessed metadata: \textit{e.g.}, \texttt{instrument}, 
+properties for commonly accessed metadata: e.g., \texttt{instrument}, 
 \texttt{wavelength} or \texttt{coordinate\_system}. 

### 2014-01-29 2-Data_Types.tex
repaired i.e. and e.g.

@@
 data types from various
-different sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order 
+different sources: e.g., files, URLs, arrays or time ranges.  In order 
 to provide instrument-specific specialisation, all the core SunPy data types 
-support subclassing; \textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} 
+support subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
 sub-type for data from the SDO/AIA instrument. 

### 2014-01-29 4-Util.tex
Made astropy references consistent
repaired i.e. and e.g.

@@
 data analysis workflow. Likely the most often used transformation is from 
-observer coordinates (e.g. sky coordinates) to a coordinate system which is 
-mapped onto the solar surface (e.g. latitude and longitude). This 
+observer coordinates (e.g., sky coordinates) to a coordinate system which is 
+mapped onto the solar surface (e.g., latitude and longitude). This 
 transformation is necessary to compare the true physical distance between 
@@
 compatible format. 
-A future version of SunPy will integrate with the AstroPy coordinates package and will 
+A future version of SunPy will integrate with the Astropy coordinates package and will 
 likely make use of an ephemeris package.
@@
 Constant object defines a Quantity, a number associated with a unit, along with 
-the constant's provenance (i.e. reference) as well as its uncertainty. Using 
+the constant's provenance (i.e., reference) as well as its uncertainty. Using 
 Astropy's Quantities, any solar constant can easily be converted between 

### 2014-01-29 1-Introduction.tex
Made astropy references consistent

@@
 provide the basic functionality expected of a scientific programming language,
-\textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 
-Building upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
+e.g., array manipulation, core numerical algorithms and visualisation. 
+Building upon these foundations, packages such as \texttt{astropy}, \texttt{pandas} and 
 \texttt{scikit-image} provide more domain-specific functionality.

### 2014-01-29 3-1-VSO.tex

@@
 The Virtual Solar Observatory (\href{http://virtualsolar.org}{VSO}) provides a 
-single, standard query interface to access solar data from different archives 
+single, standard query interface to solar data from different archives 
 around the world \citep{hill2009}.
-Data products can be requested for specific instruments or missions, but
+Data products can be requested for specific instruments or missions and
 can also be requested based on physical parameters of the data product such
 as the wavelength range.
-In addition to the VSO's primary, web-based interface, a SOAP (Simple Object 
+In addition to the VSO's primary web-based interface, a SOAP (Simple Object 
 Access Protocol) service is also available.
@@
 using the \texttt{vso} module.
-Each query is constructed by one or more attribute objects, where each
+Queries are constructed using one or more attribute objects. Each
 attribute object is a constraint on a parameter of the data set, such as the
-time, instrument, wavelength, or  other properties.
-It also shows how to download the data using the result
-from the query. One can use the metadata associated with the data sets to 
+time, instrument, or wavelength.
+Listing~\ref{code:vso_query_simple} also shows how to download the data using
+the constructed query. One can use the metadata associated with the data sets to 
 specify how the files will be named locally, such as creating subdirectories 
@@
 Two attribute objects can be combined with a logical \texttt{or} operation
-using the ``$|$'' operator.
+using the \texttt{|} (pipe) operator.
 All attribute objects provided to the query as arguments are combined with a 
@@
 \caption{Examples of advanced VSO queries using attribute objects,
-continuing from listing~\ref{code:vso_query_simple}.}
+continuing from Listing~\ref{code:vso_query_simple}.}
 \label{code:vso_query_advanced}

### 2014-01-29 3-2-HEK.tex

@@
 The Sun is an active star and exhibits a wide range of transient phenomena 
-(e.g. flares and radio bursts) on many different time-scales, length-scales and 
+(e.g., flares and radio bursts) on many different time-scales, length-scales and 
 wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK).  Entries are generated both by 
+in the Heliophysics Event Knowledgebase (HEK) [REF].  Entries are generated both by 
 automated algorithms and human observers.  Some of the information in the HEK 
-reproduces feature/event data elsewhere (for example, the GOES flare catalogue),
+reproduces feature and event data from elsewhere (for example, the GOES flare catalogue),
 and some is generated by the Solar Dynamics Observatory Feature Finding Team 
-\citep{martens2012} to populate the HEK.  The advantage of the HEK is it 
+\citep{martens2012}.  The advantage of the HEK is it 
 provides an homogeneous and well-described interface to a large amount of 
-feature/event information of interest to the solar physics community.
+feature and event information of interest to the solar physics community.
 
@@
 >>> tstart, tend = '2011/08/09 00:00:00', '2011/08/10 00:00:00'
->>> event_type = 'FL' # 'FL' indicates flare
 >>> result = client.query(hek.attrs.Time(tstart,tend), 
-...                       hek.attrs.EventType(event_type))
+...                       hek.attrs.EventType('FL')) # 'FL' indicates flare
 >>> len(result)
@@
 construct HEK queries.  For example, a flare is an attribute of the HEK, and so 
-instead of specifying \texttt{hek.attrs.EventType('FL')} in Listing 
+instead of specifying \texttt{hek.attrs.EventType('FL')} as in Listing 
 \ref{code:hek:simple}, this can also be expressed as \texttt{hek.attrs.FL}.
@@
 Example in Listing~\ref{code:hek:frm} filters the results of the previous 
-result to return only those events that have the FRM 'SSW Latest Events'.
+result to return only those events that have the FRM 'SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
+conditions on the attributes in the call to the HEK query method.
 \begin{listing}[H]
@@
 >>> result = client.query(hek.attrs.Time(tstart,tend), 
-...                       hek.attrs.EventType(event_type),
+...                       hek.attrs.EventType('FL'),
 ...                       hek.attrs.FRM.Name == 'SSW Latest Events')
@@
 \end{listing}
-Multiple comparisons can be made by including more comma-separated
-conditions on the attributes in the call to the HEK query method.
 
-HEK comparisons can be combined using Python’s logical operators e.g. AND
-and OR. This makes complex queries easy to create: Listing \ref{code:hek:or} 
+HEK comparisons can be combined using Python’s logical operators e.g. \texttt{and}
+and \texttt{or}. This makes complex queries easy to create: Listing \ref{code:hek:or} 
 returns flares west of 50 arcseconds or those that have a peak flux above 
@@
 >>> result = client.query(hek.attrs.Time(tstart,tend), 
-...                       hek.attrs.EventType(event_type),
+...                       hek.attrs.EventType('FL'),
 ...                       (hek.attrs.Event.Coord1 > 50) 
@@
 \url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
-are FRM dependent.  If a FRM does not have one of the optional attribute, a 
-'None' is returned by the \texttt{hek} module.
+are FRM dependent.  If a FRM does not have one of the optional attribute, 
+\texttt{None} is returned by the \texttt{hek} module.
 
@@
 the construction of queries of almost arbitrary complexity. 
-It is also possible to use the results of a HEK query to download the 
-corresponding data from the VSO by using SunPy's \texttt{H2VClient}.
+The results of a HEK query can be used to download the 
+corresponding data from the VSO using SunPy's \texttt{H2VClient}.
 %schriste - this is a weird way to end this section, either show how it is done or 

### 2014-01-29 3-3-HELIO.tex

@@
 propagation model to link the data in different points of the solar system by 
-its original nature (\textit{e.g.}, Earth auroras are a signature of magnetic 
+its original nature (e.g., Earth auroras are a signature of magnetic 
 field disturbances produced few days before on the Sun).

### 2014-01-29 3-4-Helioviewer.tex

@@
 $0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
-$x0$ and $y0$ are the $x$ and $y$ centre points about which to centre
+\texttt{x0} and \texttt{y0} are the $x$ and $y$ centre points about which to centre
 the image (measured in helio-projective cartesian co-ordinates) and
@@
 Listing \ref{code:downloadjp2} demonstrates the querying, downloading,
-reading and conversion of a Helioviewer JPEG2000 file into a SunPy Map
+reading and conversion of a Helioviewer JPEG2000 file into a SunPy map
 object.  This functionality allows users to visualise and manipulate

### 2014-01-29 6-Future.tex
Added comments to future, minor fixes

@@
 still very changeable from release to release.
+% RJH:  Again, lines of code is a weird measure.  Also, no way there is 110,000 lines that we
+% actually wrote.  does this include docs, comments, and sphinx crap?
 
@@
 that are 
-interchangeable with one another: \textit{e.g.}, if you slice a 
+interchangeable with one another: e.g., if you slice a 
 \texttt{MapCube} 
-along one coordinate, a \texttt{LightCurve} of intensity along the 
+along one spatial coordinate, a \texttt{LightCurve} of intensity along the 
 time range of 

### 2014-01-29 authors.tex

--- 2014-01-28 authors.tex
@@
 % People who have directly contributed to the text, still in no order.
-Stuart J Mumford$^1$,
+Stuart J. Mumford$^1$,
 Steven Christe$^2$,
 David P\'erez-Su\'arez$^3$,
-Andrew R Inglis$^{2,5}$,
-Jack Ireland$^{6,2}$,
-Albert Y Shih$^2$,
-Simon Liedtke$^11$,
-Russell J Hewett$^8$, %88
+Andrew R. Inglis$^{2,5}$,
+Jack Ireland$^{6}$,
+Albert Y. Shih$^2$,
+Simon Liedtke$^{11}$,
+Russell J. Hewett$^8$, %88
 % Contributors to SunPy Sorted thus:
@@
 % Date of most recent contribution
-F Mayer, %721
-K Hughitt, %446
+Florian Mayer$^{12}$, %721
+Keith Hughitt, %446
 Nabil Freij$^1$, %52
-M Earnshaw, %52
+Matthew Earnshaw, %52
 Tomas Meszaros$^{10}$, %17
-N Chorley, %17
-Samuel M Bennett$^1$, %14
-M Malocha, %10
-J Evans, %10
-A Maverick, %8
-M Bates, %6
-Andrew J Leonard$^7$, %3
-J Ballew, %3
-Thomas P Robitaille, %2
-B Mampaey, %2
+N. Chorley, %17
+Samuel M. Bennett$^1$, %14
+M. Malocha, %10
+J. Evans, %10
+A. Maverick, %8
+M. Bates, %6
+Andrew J. Leonard$^7$, %3
+J. Ballew, %3
+Thomas P. Robitaille, %2
+B. Mampaey, %2
 %Hypnus1803 %1
 and 
-A Kustov %1
+A. Kustov %1
 }
@@
 School of Mathematics and Statistics, The University of Sheffield, Hicks 
-Building, Hounsfield Road, Sheffield, S3 7RH U.K.,
+Building, Hounsfield Road, Sheffield, S3 7RH U.K.
 
-$^2$NASA Goddard Space Flight Center, Greenbelt, MD, USA,
+$^2$NASA Goddard Space Flight Center, Greenbelt, MD, USA
 
 $^3$South African National Space Agency - Space Science, Hospital 
-Street, 7200 Hermanus, Western Cape, South Africa,
+Street, 7200 Hermanus, Western Cape, South Africa
 
-$^5$ The Catholic University of America, Washington, DC, USA,
+$^5$ The Catholic University of America, Washington, DC, USA
 
 $^6$ADNET Systems Inc., Mail Code 671.1, 
+NASA Goddard Space Flight Center, Greenbelt, MD, USA
 
 $^7$Department of Mathematics and Physics, Aberystwyth University, 
-Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ,
+Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ
 
 $^8$Department of Mathematics, Massachusetts Institute of Technology, 77 
-Massachusetts Ave, E17-317, Cambridge, MA 02142,
+Massachusetts Ave, E17-317, Cambridge, MA 02142
 
 $^9$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
-69117, Germany,
+69117, Germany
 
-$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno,
+$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno
 
-$^{11}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany,
+$^{11}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany
+
+$^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
 }

### 2014-01-29 1-Introduction.tex
closes issue #75

@@
 every discipline.  Solar physics is no exception to this trend. For example, NASA's
-Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
-produces over 1 TB of catalogued and stored data per day [REF]. Managing and
+AIA instrument on the Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
+produces over 1 TB of catalogued and stored data per day \citep{aia}. Managing and
 analysing this mountain of data

### 2014-01-29 3-4-Helioviewer.tex
closes issue #75

@@
 Helioviewer Project are images in the JPEG2000 format (for further
-details on the Helioviewer Project see \cite{muller2009}). The
+details on the Helioviewer Project see \citep{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source

### 2014-01-29 5-Dev.tex
closes issue #75

@@
 three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
-active community \cite{bangerth2013}. Several tools (some specific to Python) are used by
+active community \citep{bangerth2013}. Several tools (some specific to Python) are used by
 SunPy to make achieving these goals more accessible. To maintain high-quality code, a 

### 2014-01-29 solarsoft.tex
repaired i.e. and e.g.
closes issue #75

@@
 \ref{sec:DataTypes}--\ref{sec:util} with the current de-facto standard solar 
-physics data analysis library: SolarSoft (SSW) \citep{freeland1998}.
+physics data analysis library: SolarSoft (SSW) \citep{ssw}.
 %ARI - is is SolarSoft or SolarSoftWare?! The latter includes the W :-)
@@
 289,724 lines of code with a total approximate value of \$10.4M (based on the 
-Basic COCOMO model \citep{_cocomo_2014}). 
+Basic COCOMO model \citep{cocomo}). 
 %dps - This data was calculated using...} If we can add them to the repository 
@@
 Individual missions and instruments provide additional optional packages to 
-support and process their data. For example, the SDO package \citep{sdo} is 
-100\% IDL code and is 11k lines of code (\$360k) and the SOHO package 
+support and process their data. For example, the \texttt{sdo} package \citep{sdo} is 
+100\% IDL code and is 11k lines of code (\$360k) and the \texttt{soho} package 
 \citep{soho} is 100k lines of code (\$3M) and is 99.9\% IDL code. SSW is hosted 
@@
 %If we script it it would be amazing!  Also, I would just provide the order
-%of magnitude, and not a exact number, i.e. 190 and 1800 results}
+%of magnitude, and not a exact number, i.e., 190 and 1800 results}
 % 

### 2014-01-29 2-2-Lightcurve.tex
my changes

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the \href{http://pandas.pydata.org}{\texttt{pandas}} data-analysis library, and 
+the {\texttt{pandas}} data-analysis library (\url{http://pandas.pydata.org}), and 
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
@@
 \texttt{LightCurve} object is initialised
-(\textit{e.g.}, \texttt{GOESLightCurve}) which inherits from
+(e.g., \texttt{GOESLightCurve}) which inherits from
 \texttt{LightCurve} but allows instrument-specific functionality to be
@@
 %removed the resample part of the example - really we need to fix truncate!
+% schriste - i think it would be better to show off some of the powerful pandas methods in this section
+% as we are not likely to fix truncate and i think it should be refactored anyway
 \end{minted}

### 2014-01-29 2-3-Spectra.tex
my changes

@@
 %dps - I need to think in one...
+%schriste - can't we just take a slice off of the spectram to make a spectrum?
 
@@
 
-The \texttt{Spectrogram} class supports radio spectrograms from the 
+As with other SunPy data types, the \texttt{Spectrogram} class has been
+built so that each instrument initialises using a subclass containing the instrument-specific 
+functionalities. The common functionality provided by the base \texttt{Spectrogram} class includes
+joining different time ranges and frequencies, performing frequency-dependent background subtraction,
+and convenient visualization and sampling of the data.
+Currently, the \texttt{Spectrogram} class supports radio spectrograms from the 
 \href{http://www.e-callisto.org/}{e-Callisto}
 solar radio spectrometer network and STEREO/SWAVES spectrograms.
-As with other SunPy data types, the \texttt{Spectrogram} class has been
-built so that each instrument initialises using a subclass containing the instrument-specific 
-functionalities.
-%The common functionality provided by the base \texttt{Spectrogram} class includes
-%reading data,
-%joining different time ranges and frequencies,
-%performing frequency-dependent background subtraction,
-%and convenient visualization and sampling of the data.
 
@@
 the observatory of interest.  When the data is requested using the
-\texttt{from\_range} function, the object merges all the downloaded
+\texttt{from\_range()} function, the object merges all the downloaded
 files into a single spectrogram, across time and frequency.

### 2014-01-29 2-Data_Types.tex
my changes

@@
 
-Currently, SunPy provides data structures that are specifically designed for the
+SunPy provides data strucutures that are specifically designed for the
 three primary varieties of solar physics data: images, time series, and
-spectra. SunPy provides core data types for these using Python classes:
+spectra. These core data types are Python classes:
 \texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
@@
 
-These classes allow access to the original data
+These classes allow access to the data
 along with associated metadata and provide appropriate convenience functions to
-enable data analysis and visualisation. For each of these classes, the data is
+enable analysis and visualisation. For each of these classes, the data is
 stored in the \texttt{data} attribute while the metadata is stored 
 in the \texttt{meta} attribute. (Curently, \texttt{LightCurve} does 
-not support the \texttt{meta} attribute.) It is possible to instantiate the
+not support the \texttt{meta} attribute.) 
+% schriste - can't we just quickly fix this? should be easy enough.
+It is possible to instantiate the
 data types from various
-different sources: e.g., files, URLs, arrays or time ranges.  In order 
-to provide instrument-specific specialisation, all the core SunPy data types 
+different sources: e.g., files, URLs, arrays.  
+%schriste - i removed time ranges as that just looks up a url.
+In order to provide instrument-specific specialisation, all the core SunPy classes 
 support subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
@@
 interface, as well as allowing the use of the standard 
-\texttt{matplotlib} commands to manipulate the plot parameters, such as the 
-title.
+\texttt{matplotlib} commands to manipulate the plot parameters (e.g. title, axes).

### 2014-01-29 3-2-HEK.tex
closes issue #75
my changes

@@
 wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK) [REF].  Entries are generated both by 
+in the Heliophysics Event Knowledgebase (HEK) \citep{hek2012}.  Entries are generated both by 
 automated algorithms and human observers.  Some of the information in the HEK 
@@
 
-SunPy accesses this information through the \texttt{hek} module, which was also
+SunPy accesses this information through the \texttt{hek} module, which was
 developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 

### 2014-01-29 1-Introduction.tex

@@
 transparent development history, ease of modification, and conformance
-to standards.  Software with these qualities provides a strong
-foundation can be responsive to the needs of the community as data
+to standards.  Software with these qualities provide a strong
+foundation and can support the needs of the community as data
 volumes grow and science questions evolve.
@@
 %ji - I had a go.
+%schriste - looks good, made a small fix
 
@@
 for the analysis and visualisation of solar data. SunPy makes use of the Python 
-programming language and the breadth of high-quality science-focused packages 
-written in that language. Python is a general-purpose, 
+programming language and the scientific Python packages. Python is a general-purpose, 
 powerful and easy-to-learn high-level programming language.
@@
 % meaningless.
+% schriste - i think it's important. it contrasts nicely with IDL and its tiny community.
 According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
@@
 
-The development of a package such as SunPy in Python is made possible by the 
-rich ecosystem of scientific packages available in Python. Core packages such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
+The development of a package such as SunPy is made possible by the 
+rich ecosystem of scientific packages available in Python. Core packages such 
+as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
 provide the basic functionality expected of a scientific programming language,
@@
 
-SunPy is designed to be a clean, simple-to-use, and well 
-structured package that provides the \textit{core} tools for data analysis in 
-solar physics. The primary focus of SunPy's early development is to provide 
+SunPy is designed to be a clean, simple-to-use, and well-structured 
+package that provides the \textit{core} tools for solar data analysis. 
+The primary focus of SunPy's early development are 
 specialised data types that allow the acquisition, processing and 

### 2014-01-29 3-3-HELIO.tex
closes issue #75

@@
 implemented as separate services. 
-\href{http://helio-vo.eu}{HELIO} comprises nine different public services, 
+\href{http://helio-vo.eu}{HELIO} is made up of nine different public services, 
 which allows scientists to search different catalogues of registered events, 
@@
 In addition to the primary, web-based interface to 
-\href{http://helio-vo.eu}{HELIO}, the services can be separately accessed.
+\href{http://helio-vo.eu}{HELIO}, the services are available by API.
 
@@
 As with all of the HELIO services, the HEC service provides results in VOTable 
-data format (defined by IVOA \cite{ochsenbein_ivoa_2011}). The \texttt{hec}
+data format (defined by IVOA \citep{ochsenbein_ivoa_2011}). 
+%schriste - a short descriptions of what the hec (get it?) a vot table is needed here
+The \texttt{hec}
 module parses this output using the \texttt{astropy.io.votable} package.
@@
 % RJH: This sentence is an orphan and should have a home constructed for it.
+% schriste - it also contains too much future sauce

### 2014-01-29 3-5-Database.tex

@@
 
-Easy access to large quantities of solar data frequently leads to datafiles accumulating
+Easy access to large quantities of solar data frequently leads to data files accumulating
 in local storage such as laptops and desktop computers. Keeping data organised and available
 is typically a cumbersome task for the average user. The file database is a sub-package of 
-SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
-local data files. The database package was developed as part of the Google 
-Summer of Code (GSoC) program 2013.
+SunPy which is meant to solve this problem by providing a unified database to store and 
+manage information about local data files. The database package was developed with support from 
+the Google Summer of Code (GSoC) program 2013.
 
@@
 
-A very special feature of the database package is the support of \texttt{undo}
-and \texttt{redo} operations. This is particularly convenient in
-interactive sessions to easily revert accidental operations. 
-This feature will also be desirable when creating a GUI frontend for this package.
-
 The \texttt{Database} class connects to a database and allows the user to 
@@
 correspond to the attributes of the respective database entries.
+
+A very special feature of the database package is the support of \texttt{undo}
+and \texttt{redo} operations. This is particularly convenient in
+interactive sessions to easily revert accidental operations. 
+This feature will also be desirable when creating a GUI frontend for this package.
 

### 2014-01-29 5-Dev.tex

@@
 hierarchically structured view of in-code documentation strings. The SunPy documentation 
-is built automatically and hosted by \href{http://readthedocs.org}{Read the 
+is built automatically and is hosted by \href{http://readthedocs.org}{Read the 
 Docs} at \url{http://docs.sunpy.org}.
@@
 room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
-developer comments or discussion, a open mailing list is hosted on Google Groups. 
+developer comments or discussions, a open mailing list is hosted on Google Groups. 
 Discussion of bugs and bug tracking are provided directly on GitHub as well as new
@@
 % RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
+% schriste - we had agreed to only refer to the support in one place. we need to agree as to where
 Many of the larger features in SunPy have been developed 

### 2014-01-29 1-Introduction.tex
comments and some little fixings

@@
 % schriste - i think it's important. it contrasts nicely with IDL and its tiny community.
-According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+According to the \href{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}{2014 TIOBE Index},
  it is one of the top ten most popular programming languages in the world 

### 2014-01-29 5-Dev.tex
comments and some little fixings

@@
 Additionally, SunPy makes use of `continuous integration' provided by
-Travis CI (\url{http://travis-ci.org}), a process by which the addition of any new code 
+\href{http://travis-ci.org}{Travis CI}, a process by which the addition of any new code 
 automatically triggers a comprehensive review of written unit tests. If any single test
@@
 Thankfully powerful tools already exist in Python to support this thanks to native
-Python's focus on its own documentation. SunPy makes use of the Sphinx (\url{http://sphinx-doc.org})
+Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
 documentation generator. Sphinx uses reStructuredText as its markup language: 
@@
 and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
-through the Python Software Foundation (PSF). It supported development of the 
+through the \href{http://www.python.org/psf/}{Python Software Foundation} (PSF). It supported development of the 
 \texttt{HELIO} and 

### 2014-01-29 3-5-Database.tex
an extra comment on a word

@@
 each database entry such as keywords, comments, and favouring, as well as 
+%dps: favouring is not what we want to say here...
 querying the full metadata (i.e., FITS header) of each entry.

### 2014-01-29 6-Future.tex

@@
 its community has grown, and this direct collaboration between Astropy 
-% what abd means?
 and 

### 2014-01-29 authors.tex

@@
 % People who have directly contributed to the text, still in no order.
-Stuart J. Mumford$^1$,
+Stuart J Mumford$^1$,
 Steven Christe$^2$,
 David P\'erez-Su\'arez$^3$,
-Andrew R. Inglis$^{2,5}$,
+Andrew R Inglis$^{2,5}$,
 Jack Ireland$^{6}$,
-Albert Y. Shih$^2$,
+Albert Y Shih$^2$,
 Simon Liedtke$^{11}$,
-Russell J. Hewett$^8$, %88
+Russell J Hewett$^8$, %88
 % Contributors to SunPy Sorted thus:
@@
 Tomas Meszaros$^{10}$, %17
-N. Chorley, %17
-Samuel M. Bennett$^1$, %14
-M. Malocha, %10
-J. Evans, %10
-A. Maverick, %8
-M. Bates, %6
-Andrew J. Leonard$^7$, %3
-J. Ballew, %3
-Thomas P. Robitaille, %2
-B. Mampaey, %2
-%Hypnus1803 %1
+N Chorley, %17
+Samuel M Bennett$^1$, %14
+M Malocha, %10
+John Evans, %10 %No affil
+Ankit Agrawal$^{15}$, %8
+M Bates, %6
+Andrew J Leonard$^7$, %3
+J Ballew, %3
+Thomas P Robitaille$^9$, %2
+Benjamin Mampaey$^{13}$, %2
+Jose Iv\'an Campos-Rozo$^{14}$ %1
 and 
-A. Kustov %1
+A Kustov %1
 }
@@
 
-$^6$ADNET Systems Inc., Mail Code 671.1, 
-NASA Goddard Space Flight Center, Greenbelt, MD, USA
+$^6$ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space Flight Center, 
+Greenbelt, MD, USA
 
@@
 $^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
+
+$^{13}$ Royal Observatory of Belgium
+
+$^{14}$ Observatorio Astronómico Nacional Universidad Nacional de Colombia 
+Bogotá, D.C., Colombia
+
+$^{15}$ Indian Institute of Technology, Bombay
 }

### 2014-01-29 2-1-Map.tex

--- 2014-01-29 2-1-Map.tex
@@
-\subsection{Map}\label{ssec:map}
-The Map data type stores 2D spatial data, such as images of the Sun and 
-inner heliosphere. It provides a wrapper around a \texttt{numpy} data array and 
-its associated spatial coordinates and other metadata. The \texttt{Map} class 
-provides methods for typical operations on 2D data, such as rotation and 
-re-sampling, as well as visualisation functionality.
-The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, including a FITS file as shown in 
-Listing~\ref{code:aia_1}.
+\subsection{Map}
+The Map data type represents 2D spatial data such as images of the Sun and 
+inner heliosphere. It provides a wrapper around a data array and its associated
+spatial coordinates and other metadata. The \texttt{Map} class provides 
+methods for typical operations on 2D data, 
+such as rotation and re-sampling, and visualisation functionality.
+The \texttt{Map} class
+also provides a convenient interface for loading data from a variety of sources, typically
+a FITS file as shown in Listing~\ref{code:aia_1}.
 
 The architecture of the \texttt{Map} class consists of a template map called
-\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
-\texttt{NDData} is a generic wrapper around an \texttt{ndarray} with a 
-\texttt{meta} attribute to store metadata.
-As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
-not yet make full use of its capabilities, but this inheritance structure 
-provides for future integration of \texttt{Astropy}. In order to provide 
-instrument- or detector-specific integration, \texttt{GenericMap} is designed
-to be subclassed. Each subclass of \texttt{GenericMap} can register 
-with the \texttt{Map} creation factory, which will then automatically return an instance
-of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
-SunPy v0.4 has \texttt{Map} specialisations for the following instruments: 
+\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. \texttt{NDData} is a 
+generic wrapper around an \texttt{ndarray} with a \texttt{.meta} attribute to store metadata.
+As \texttt{NDData} is currently still in development, \texttt{GenericMap} does not yet make full
+use of its capabilities, but this inheritance structure provides 
+for future integration of \texttt{Astropy}. In order to provide instrument- or
+detector-specific integration, \texttt{GenericMap} is subclassed on creation. 
+Each subclass of \texttt{GenericMap} can register with the \texttt{Map} creation function (\textit{i.e.}, factory)
+by implementing a method that returns \texttt{True} if the metadata
+in the file header matches
+that instrument or detector.  This \texttt{Map} factory 
+will then automatically return an instance of the specific \texttt{GenericMap} 
+subclass. SunPy 0.4 has \texttt{Map} specialisations for the 
+following instruments: 
 \textit{YOHKOH/SXT}, \textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
@@
 and \textit{IRIS} SJI frames.
-% RJH: Instruments should be consistent throughout (italics, caps, etc).  Also,
-% usually citations are provided for instruments.
 
 The \texttt{Map} class stores standard metadata retrieved from the header of 
-the image file in the \texttt{meta} attribute and provides convenience 
-properties for commonly accessed metadata: \textit{e.g.}, \texttt{instrument}, 
-\texttt{wavelength} or \texttt{coordinate\_system}. 
-Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
+the image file in the \texttt{.meta} attribute and provides convenience 
+properties for commonly accessed metadata: \textit{e.g.}, \texttt{.instrument}, 
+\texttt{.wavelength} or \texttt{.coordinate\_system}. 
+Listing \ref{code:aia_1} demonstrates the quick-plot functionality of 
 \texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{AIA} FITS file,
+\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file,
 and a quick-view plot is created.}
@@
 In addition, Listing~\ref{code:mapcube_2} shows how the \texttt{MapCube} 
-classes interact with the \texttt{matplotlib.animation} submodule to save a 
-video.
+classes interacts with the \texttt{animation} module to save a video.
 
@@
 \end{center}
-\caption{Example showing a \texttt{CompositeMap} plot, with RHESSI data composed with SDO/AIA data, and the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing a \texttt{CompositeMap} plot and the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \end{minted}
-% In the above example, is Writer, writer clear? 
-% Could we add more metadata to the movie? obs_date, instrument, etc...?
 \caption{Example showing how to save a video animation from a \texttt{MapCube}, using 
@@
 \end{listing}
-% RJH: If this is kept, the 'artist' bit should be explained.

### 2014-01-29 2-2-Lightcurve.tex
comments and some little fixings

--- 2014-01-28 2-2-Lightcurve.tex
@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the \href{http://pandas.pydata.org}{\texttt{pandas}} data-analysis library, and 
-\texttt{LightCurve}'s \texttt{.data} attribute is a \texttt{pandas.DataFrame} 
-class.
+the \texttt{pandas} data-analysis library (\url{http://pandas.pydata.org}),
+and \texttt{LightCurve}'s
+\texttt{.data} attribute is a \texttt{pandas.DataFrame} class.
 The \texttt{pandas} library contains a large amount
@@
 the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
-% Do we need to explain what OCS means?
 average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
@@
 included.  Future developments will introduce support for additional
-instruments and data products, as well as implementing a factory interface 
-similar to that of \texttt{Map}.  Since there is no established standard
-as to how time-series data should be stored and distributed, each SunPy 
-\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
-specific data format in its constructor and parse that file type.
+instruments and data products.  Since there is no established standard
+as to how time-series data
+should be stored and distributed, each SunPy \texttt{LightCurve}
+object provides the ability to download its corresponding specific
+data format in its constructor.
+
+%\subsubsection{Creating and using Lightcurves}
 
@@
 an input time range. In Listing~\ref{code:goes_lc}, 
-the \texttt{LightCurve} constructor searches a remote source for the GOES X-ray 
-data specified by the time interval, downloads the required files and 
-subsequently creates and plots the object.
+the \texttt{LightCurve} constructor searches a remote site for the GOES X-ray data 
+specified by the time interval, downloads the required files and subsequently 
+creates the object.
 
@@
 >>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-...                                         '2011-06-07 08:00')
+...                                         '2011-06-07 10:00')
 >>> goes.peek()
-%removed the resample part of the example - really we need to fix truncate!
+>>> trange = TimeRange('2011-06-07 06:00','2011-06-07 07:00')
+%>>> goes_zoom = goes.truncate(trange)
+% the above does not work!
+>>> resampled_goes = goes.data.resample("1H")
 \end{minted}
@@
 \end{center}
-\caption{Example retrieval of a GOES lightcurve for the time interval 
-06:00--08:00 UT on 2011 June 7 using a time range, and the output of the 
-\texttt{peek()} method.}
+\caption{Example retrieval of a GOES lightcurve for the time interval 06:00--08:00 UT on 
+2011 June 7 using a time range, and the output of the \texttt{peek()} method.
+A sub-interval is then extracted from the Lightcurve and finally the data is resampled
+to 1 hour cadence.}
 \label{code:goes_lc}
@@
 a variety of ways in order to perform time-series analysis.
-
-%Stuart: Where did the pandas section go?
-%ARI - looks like it's up top

### 2014-01-29 2-3-Spectra.tex

--- 2014-01-28 2-3-Spectra.tex
@@
 %ji - there is no example of a spectrum
-%dps - I need to think in one...
+
+%ayshih - this whole paragraph can be deleted
+%ji - I agree, this is redundant in such a journal.
+Spectroscopy is the study of radiative energy as a function of wavelength.
+An spectrum is normally obtained by observing a range of frequencies at the same time; 
+it can be measured for example in radio wavelengths by a frequency sweep with 
+a radio receiver or in visible and ultraviolet by the dispersion of the incident light 
+through a diffraction grating or prism.
+The analysis of the resultant spectrum can provide properties of the plasma observed 
+such temperature, density, speed, etc.
+Therefore, spectroscopy provides to the solar physicists invaluable information about 
+the composition and the physical properties of the Sun.
 
@@
 instruments.  The variety and complexity of these instruments and
-their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
+their resultant datasets makes it very challenging to support all in a
+general way.  The \texttt{spectra} module implements a
 \texttt{Spectrum} class for 1D data (intensity versus frequency) and a
@@
 
-The \texttt{Spectrogram} class supports radio spectrograms from the 
-\href{http://www.e-callisto.org/}{e-Callisto}
-solar radio spectrometer network and STEREO/SWAVES spectrograms.
+The \texttt{Spectrogram} class supports radio spectrograms from the e-Callisto 
+solar radio spectrometer network (\url{http://www.e-callisto.org/})
+and STEREO/SWAVES spectrograms.
 As with other SunPy data types, the \texttt{Spectrogram} class has been
@@
 \texttt{.from\_range} function, the object merges all the downloaded
-files into a single spectrogram, across time and frequency.
-In the example shown, data is provided in two frequency ranges, 
+files downloaded into a single spectrogram, across time and frequency.
+In the example shown, data is observed in two frequency ranges, 
 20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
@@
   data for the requested time range and observatory, merges it and
-  removes the background signal.  The data requested -- `BIR' -- is
-  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
-  at Birr Castle in Ireland.}
+  removes the background signal.  The data requested -- 'BIR' -- is
+  the code name of the Rosse Observatory at Birr Castle in Ireland
+  (\url{http://www.rosseobservatory.ie})}
 \label{code:spectra}

### 2014-01-29 3-2-HEK.tex

--- 2014-01-28 3-2-HEK.tex
@@
 
-The Sun is an active star and exhibits a wide range of transient phenomena 
-(e.g. flares and radio bursts) on many different time-scales, length-scales and 
-wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK).  Entries are generated both by 
-automated algorithms and human observers.  Some of the information in the HEK 
-reproduces feature/event data elsewhere (for example, the GOES flare catalogue),
-and some is generated by the Solar Dynamics Observatory Feature Finding Team 
-\citep{martens2012} to populate the HEK.  The advantage of the HEK is it 
-provides an homogeneous and well-described interface to a large amount of 
-feature/event information of interest to the solar physics community.
+The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
+radio bursts) on many 
+different time-scales, length-scales and wavelengths. Observations and metadata 
+concerning these phenomena are collected at the Heliophysics Event 
+Knowledgebase (HEK).  Entries are generated both by automated algorithms and 
+human observers.  Some of the information in the HEK reproduces feature/event 
+data elsewhere (for example, the GOES flare catalog), and some is generated by 
+the Solar Dynamics Observatory Feature Finding Team \cite{martens2012} to
+populate the HEK.  The advantage of the HEK is it provides a homogeneous and 
+well-described interface to a large 
+amount of feature/event information of interest to the solar physics community.
 
-SunPy accesses this information through the \texttt{hek} module, which was also
-developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
-use of the 
-\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{HEK
- API}.
-The current list of events maintained by the HEK and their properties can be 
-found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+SunPy accesses this information through the \texttt{hek} module, which was 
+developed with support from the European Space Agency Summer of Code in 
+Space (ESA-SOCIS) 2011.  The \texttt{hek} module makes use of the HEK API
+(\url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}).
+The current list of 
+events maintained by the HEK and their properties can be found at 
+\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
 
@@
 \caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
-which occurred on August 9th, 2011.}
+which occurred on the 2011/08/09.}
 \label{code:hek:simple}
@@
 event.  As was mentioned above, the HEK stores feature/event metadata obtained 
-in different ways, known generally as {\it feature recognition methods} (FRMs). 
-Example in Listing~\ref{code:hek:frm} filters the results of the previous 
-result to return only those events that have the FRM 'SSW Latest Events'.
+in different ways, known generally as {\it feature recognition methods} ( 
+FRMs). Example \ref{code:hek:frm} filters the results of the previous result to 
+return only those events that have the FRM 'SSW Latest Events'.
 \begin{listing}[H]
@@
 >>> result = client.query(hek.attrs.Time(tstart,tend), 
-...                       hek.attrs.EventType(event_type),
-...                       hek.attrs.FRM.Name == 'SSW Latest Events')
+                      hek.attrs.EventType(event_type),
+                      hek.attrs.FRM.Name == 'SSW Latest Events')
 >>> len(result)
@@
 the construction of queries of almost arbitrary complexity. 
-It is also possible to use the results of a HEK query to download the 
-corresponding data from the VSO by using SunPy's \texttt{H2VClient}.
+It is also possible to use the 
+results of a HEK query to download the corresponding data from the VSO by using 
+SunPy's \texttt{H2VClient}.
 %schriste - this is a weird way to end this section, either show how it is done or 
 % do not mention it, i think.
-%dps - I agree.
-%Stuart: Will do on my next pass

### 2014-01-29 3-5-Database.tex

--- 2014-01-29 3-5-Database.tex
@@
-\subsection{The File Database}\label{ssec:db}
-
+\subsection{The File Database}
 Easy access to large quantities of solar data frequently leads to datafiles accumulating
-in local storage such as laptops and desktop computers. Keeping data organised and available
+in local storage such as laptops and desktop computers. Keeping data organized and available
 is typically a cumbersome task for the average user. The file database is a sub-package of 
 SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
-local data files. The database package was developed as part of the Google 
-Summer of Code (GSoC) program 2013.
+local data files. The database package was developed as part of the 2013 
+Google Summer of Code.
 
 The database sub-package makes use of a database supported by
-\href{http://www.sqlalchemy.org}{SQLAlchemy}. This library was chosen
-since it supports many SQL dialects. 
-If SQLite is selected, the database is stored as a single file which is
-created automatically. A server-based database, on the other hand, could be used
-by a collaborators who work together on the
-same data from different computers: a central database server stores all data and the clients connect to
+SQLAlchemy(\url{http://www.sqlalchemy.org}). This library was chosen
+since it supports many SQL dialects. If SQLite is choosen, the database is stored as a single file which is
+created automatically. This solution makes it possible to easily backup, copy and distribute
+a database file. A server-based database, on the other hand, could be used by a collaboration 
+who work together from different machines on the
+same data: a central database server stores all data and the clients connect to
 it to read or write data.
 
-The database can store and manage all data that can be read via SunPy's 
-\texttt{io} subpackage, and direct integration with the \textsc{VSO} 
-subpackage is supported.
-It is also possible to manually add file or directory entries. The package also provides
-a unified data search via the \texttt{fetch()} method, which includes both local files
-and files on the \textsc{VSO}. This reduces the likelihood of downloading the same file 
-multiple times. When a file is added to the database, the file is scanned and a file hash is produced. 
+The database can store and manage all data that is retrieved via sunpy from the net
+package though currently only the \textsc{VSO} package is supported. 
+It also possible to add entries manually by file or directory. The package also provides
+a \texttt{fetch} method which provides a unified data search which includes both local files
+and files on the \textsc{VSO} are searched. This reduces the likelihood of downloading the same file 
+multiple times. When a file is added to the database the file is scanned and a file hash is produced. 
 The current date is associated with the entry along with metadata summaries such 
@@
 The database also provides the ability to associate custom meta-data to 
-each database entry such as keywords, comments, and favouring, as well as 
-querying the full metadata (i.e., FITS header) of each entry.
+each database entry such as keywords, comments, and favoriting.
 
@@
 
-The \texttt{Database} class connects to a database and allows the user to 
-perform operations on it. Listing~\ref{code:database} shows how to connect
+Using the database package, one uses the \texttt{Database} class to connect
+with a database and perform operations on it. Listing~\ref{code:database} shows how to connect
 to an in-memory database and download data from the \textsc{VSO}. These entries are
-automatically added to the database. The function \texttt{len()} is used to get the number of
-records. The function \texttt{display\_entries()} displays an iterable of 
-database entries in a nicely-formatted \textsc{ASCII} table. The headlines 
-correspond to the attributes of the respective database entries.
+automatically added to the database. The function \texttt{len} is used to get the number of
+records. The function \texttt{display\_entries} displays an iterable of database entries
+in a nicely-formatted \textsc{ASCII} table. The headlines correspond to the
+attributes of the respective database entries.
 
@@
 >>> database.download(
-...     vso.attrs.Time('2012-08-05', '2012-08-05 00:00:05'),
-...     vso.attrs.Instrument('AIA'))
+...     vso.attrs.Time((2011, 9, 20, 1), (2011, 9, 20, 2)),
+...     vso.attrs.Instrument('RHESSI'))
 >>> len(database)
-2
+6
 >>> from sunpy.database.tables import display_entries
@@
 ...     database,
-...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
-id observation_time_start wavemin wavemax
--- ---------------------- ------- -------
-1  2012-08-05 00:00:01    9.4     9.4    
-2  2012-08-05 00:00:02    33.5    33.5   
+...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
+id observation_time_start wavemin        wavemax           download_time      
+-- ---------------------- -------        -------           -------------      
+1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
+
 \end{minted}

### 2014-01-29 6-Future.tex

--- 2014-01-28 6-Future.tex
@@
-\section{Future of SunPy}\label{sec:future}
+\section{Future of SunPy}
 SunPy as a project has existed for roughly three years. In this time 
@@
 As discussed in Section \ref{sec:Intro}, the primary focus of the 
-SunPy library is the analysis and visualisation of `high-level' solar 
+\texttt{sunpy} library is the analysis and visualisation of `high-level' solar 
 data. This means data that has been put through instrument processing 
@@
 calibration routines, and contains full (WCS) coordinate information. 
-The plan for SunPy is to continue development within this 
+The 
+development plan for SunPy is to continue development within this 
 scope. The 
@@
 \citep{theastropycollaboration2013} and 
-its community has grown, and this direct collaboration between Astropy 
-% what abd means?
+its community has grown, abd this direct collaboration between Astropy 
 and 

### 2014-01-29 3-3-HELIO.tex

@@
 such as planetary or spacecraft position in time. 
-Additionally, \href{http://helio-vo.eu}{HELIO} provides a service that uses a 
+Additionally, HELIO provides a service that uses a 
 propagation model to link the data in different points of the solar system by 
@@
 field disturbances produced few days before on the Sun).
-In addition to the primary, web-based interface to 
-\href{http://helio-vo.eu}{HELIO}, the services are available by API.
+In addition to the primary, \href{http://hfe.helio-vo.eu}{web-based interface to 
+HELIO}, the services are available by API.
 
@@
 %schriste - a short descriptions of what the hec (get it?) a vot table is needed here
+%dps - a votable format description? or what HEC gets from it?
 The \texttt{hec}
@@
 \caption{Example of querying the HEC service to multiple cme
-catalogues, in this case the ones detected by \href{http://sidc.oma.be/cactus/}{CACTus}.}
+catalogues, in this case the ones detected automatically 
+by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht_automated_2009}.}
 \label{code:helio}
 \end{listing}
-% RJH: CACTus should be defined and a reference provided in the reference section.
 
-In the future, additional HELIO services will be supported in the future by SunPy.
+In the future, additional HELIO services will be supported by SunPy, aiming to a 
+seamlessly interaction between the other services and tools available (e.g., 
+\texttt{hek}, \texttt{Map}).  
+For example, solar features available in the HELIO Feature Catalogue could be
+overplot on maps.
 % RJH: This sentence is an orphan and should have a home constructed for it.
 % schriste - it also contains too much future sauce
+% better? or this should be in the future section?

### 2014-01-29 3-4-Helioviewer.tex

--- 2014-01-29 3-4-Helioviewer.tex
@@
 sources (such as instrumentation and feature/event catalogues) via
-easy-to-use visual interfaces.  The primary data provided by the
-Helioviewer Project are images in the JPEG2000 format (for further
-details on the Helioviewer Project see \cite{muller2009}). The
+easy-to-use visual interfaces.  The primary interface to Helioviewer is a
+google-map-like website which allows users to browse images of the Sun
+taken by a variety of instruments. In order to manage all of this data, the Helioviewer
+project maintains archives of all of its data as JPEG2000 format (for further
+details on the Helioviewer Project see \citep{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source
@@
 %Stuart: Do we need this listing?? The same points can be made with 14
+% schriste - i agree with stuart here, or maybe just don't show the png file
 \begin{listing}[H]
@@
 time, resulting in predictable filenames.
+%this seems like a lot of text for a simple issue, i would recommend removing it
 

### 2014-01-29 authors.tex
added in Keith with affiliation #4 since it was missing from the previous list

@@
 Florian Mayer$^{12}$, %721
-Keith Hughitt, %446
+Keith Hughitt$^4$, %446
 Nabil Freij$^1$, %52
@@
 
+$^4$Department of Cell Biology and Molecular Genetics, University of Maryland, College Park
+
 $^5$ The Catholic University of America, Washington, DC, USA

### 2014-01-29 6-Future.tex
small changes, and comments to Future section

--- 2014-01-29 6-Future.tex
@@
 base is 
-still very changeable from release to release.
+still evolving from release to release.
 % RJH:  Again, lines of code is a weird measure.  Also, no way there is 110,000 lines that we
 % actually wrote.  does this include docs, comments, and sphinx crap?
-
+%SJM: I think this number is just wrong and never got changed.
+%JI: needs new number.  Should be the number of lines in the 0.4 sunpy release???
 As discussed in Section \ref{sec:Intro}, the primary focus of the 

### 2014-01-29 5-Dev.tex
Cadair passes the ball
dropped the 'Development workflow section, retaining the salient points about the SunPy community and dropping the git/github description.

@@
 SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
-transparent and collaborative development workflow made possible by GitHub is used (described
-further below).
+transparent and collaborative development workflow made possible by GitHub is used.
+% JI - I don't think we need a description of what is essentially how a project works
+% when you use git and github.  There is nothing SunPy specific about this.
+The following conditions typically must be met before code is accepted.
+\begin{enumerate}
+	\item  The code must follow 	
+	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
+	guidelines, keeping SunPy code in a consistent.
+
+	\item All new features require documentation in the form of doc strings as well as user
+	guides.
+
+	\item The code must contain significant unit test coverage.
+
+        \item Community consensus is reached that the new code is valuable.
+\end{enumerate}
+This kind of development model is widely used within the scientific Python 
+community as well as by a wide variety of other projects both open and closed 
+source.
+
 Additionally, SunPy makes use of `continuous integration' provided by
@@
 also monitored by the \href{http://coveralls.io}{Coveralls} service.
+% JI - what is the coveralls service?
 
@@
 one of the most important factors determining the success of any software project. 
-Thankfully powerful tools already exist in Python to support this thanks to native
+Powerful tools already exist in Python to support this, thanks to native
 Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
@@
 
-In order to maintain an active community, communication is key.  The SunPy community makes
-use of a number of channels to communicate. For immediate communications, an active IRC chat
+Communication is the key to maintaining an active community, and so the SunPy community 
+uses a number of different tools to facilitate communication. For immediate communications, an active IRC chat
 room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
@@
 Discussion of bugs and bug tracking are provided directly on GitHub as well as new
-code-review discussions.
+code-review discussions.  The SunPy community also reaches out to the wider solar physics
+community through presentations, functionality demonstrations and informal meetups at scientific
+meetings. 
 % RJH: do we want to list both the community and dev lists?
@@
 % RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
-% schriste - we had agreed to only refer to the support in one place. we need to agree as to where
+% schriste - we had agreed to only refer to the support in one place. we need 
+%to agree as to where
+% SJM: Drop the bits in the code
 Many of the larger features in SunPy have been developed 
@@
 
-\subsection{Development Workflow}
-The development workflow that GitHub enables is simple and transparent. The 
-primary source code repository \url{http://github.com/sunpy/sunpy} can be 
-`forked' by anyone with a GitHub account who can then modify their fork as they 
-wish. Upon completion of any modifications it is possible for a user to create 
-a `Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
-repository in order to incorporate their modification into the SunPy code base. 
-Pull requests are reviewed by the SunPy community before being accepted. Community consensus
-is required to add new features.
-
-Pull requests are a very powerful tool to maintain code quality, as each line 
-of code that has been modified is highlighted for review and can be commented on. 
-In order to maintain high quality code the following conditions must typically be met 
-before code is accepted.
-
-\begin{enumerate}
-	\item  The code must follow 	
-	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
-	guidelines, this keeps all the code in SunPy styled in a consistent manner and easy to read.
-
-	\item All new features require documentation in the form of doc strings as well as user
-	guides.
-
-	\item The code must contain significant unit test coverage.
-\end{enumerate}
-
-This kind of development model is widely used within the scientific Python 
-community as well as by a wide variety of other projects both open and closed 
-source.
+%JI The section ``Development workflow'' is unnecessary IMHO.  This is
+% largely a description of how git and github works.  It is not about sunpy. So I have
+% deleted it.

### 2014-01-29 3-4-Helioviewer.tex
removed the first image and listing, and compressed the description of the download_png portion

@@
 
-Listing \ref{code:hv:downloadlatestpng} demonstrates how to download a
-PNG image of the latest AIA 304$\,$\AA\ image available on
-\url{Helioviewer.org}.
-
-%Stuart: Do we need this listing?? The same points can be made with 14
-% schriste - i agree with stuart here, or maybe just don't show the png file
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net.helioviewer import HelioviewerClient
->>> hv = HelioviewerClient()
->>> hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]",
-...                 x0=0, y0=0, width=512, height=512)
-\end{minted}
-\centering\includegraphics[width=0.5\columnwidth]{helioviewer_latest_aia_304}
-\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
-available at \url{www.helioviewer.org}.}
-\label{code:hv:downloadlatestpng}
-\end{listing}
-
-The first argument is the requested time of the image.  Helioviewer
-selects images closest to the requested time.  In this case, the
-requested time is in the future and so Helioviewer will find the most
-recent available image.  The second argument refers to the image
-resolution in arcseconds per pixel (larger values mean lower
-resolution).  The third argument is a comma-delimited string detailing
-the requested observatory $\rightarrow$ instrument $\rightarrow$
-detector $\rightarrow$ measurement combination.  The final two numbers
-in this string are the visibility and the opacity of the this image
-layer (1/0 is visible/invisible with opacity in the range
-$0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
-\texttt{x0} and \texttt{y0} are the $x$ and $y$ centre points about which to centre
-the image (measured in helio-projective cartesian co-ordinates) and
-the \texttt{width} and \texttt{height} are the pixel values for the
-image dimensions.
-
-It should be noted that the filename of the returned file has the date
-and time of the requested time, which is not the time of the observation shown 
-in the PNG image.  This is because the Helioviewer API request finds images 
-closest to the requested time. However, since the user may ask for images from 
-multiple sources, and each of them may have a different observation time, it is
-unclear which time is the most appropriate to associate with the resultant 
-image.  The Helioviewer API therefore does not select between any of the image 
-observation times, but instead returns an image filename based on the request 
-time, resulting in predictable filenames.
-%this seems like a lot of text for a simple issue, i would recommend removing it
-
 The Helioviewer API allows composition and overlay of images from
@@
 \ref{code:hv:overlaid} gives an example of the composition of three
-separate images in to a single image.
+separate image layers in to a single image.
 
@@
 
-The principle difference between Listings~\ref{code:hv:overlaid} and 
-\ref{code:hv:downloadlatestpng} is in the layer string (the third
-argument).  The layer string has three separate comma separated
-entries detailing the data source, its visibility and its opacity.
+The first argument is the requested time of the image.  Helioviewer
+selects images closest to the requested time.  In this case, the
+requested time is in the future and so Helioviewer will find the most
+recent available images from each source.  The second argument refers
+to the image resolution in arcseconds per pixel (larger values mean
+lower resolution).  The third argument is a comma-delimited string of
+the three requested image layers, the details of which are enclosed
+in parentheses. The image layers are described using the observatory
+$\rightarrow$ instrument $\rightarrow$ detector $\rightarrow$
+measurement combination described above, along with the final two
+numbers that denote the visibility and the opacity of the image layer
+respectively (1/0 is visible/invisible with opacity in the range
+$0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
+\texttt{x0} and \texttt{y0} are the $x$ and $y$ centre points about
+which to centre the image (measured in helio-projective cartesian
+co-ordinates) and the \texttt{width} and \texttt{height} are the pixel
+values for the image dimensions.
+
 This functionality makes it simple for SunPy users to generate complex

### 2014-01-30 2-2-Lightcurve.tex
Edits to section 2, data types

--- 2014-01-29 2-2-Lightcurve.tex
@@
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
-class.
+object.
 The \texttt{pandas} library contains a large amount
@@
 assumes that the input data are time-ordered list(s) of numbers, and each
-list becomes a column in the \texttt{pandas} DataFrame class.
+list becomes a column in the \texttt{pandas} DataFrame object.
 
 Currently, the \texttt{LightCurve} class is compatible with the
-following data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, and
-the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
+following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and
+the \textit{SDO} EUV Variability Experiment (EVE; only the level ``OCS'' and
 % Do we need to explain what OCS means?
@@
 % confident enough to make that cut.
+% dps: I agree, JI, what do you think?
 average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
@@
 
+%removed the resample part of the example - really we need to fix truncate!
+% schriste - i think it would be better to show off some of the powerful pandas methods in this section
+% as we are not likely to fix truncate and i think it should be refactored anyway
+%ays: moved these comments outside of the listing in case we forget to delete these
 \begin{listing}[H]
@@
 >>> goes.peek()
-%removed the resample part of the example - really we need to fix truncate!
-% schriste - i think it would be better to show off some of the powerful pandas methods in this section
-% as we are not likely to fix truncate and i think it should be refactored anyway
 \end{minted}
@@
 \end{center}
-\caption{Example retrieval of a GOES lightcurve for the time interval 
-06:00--08:00 UT on 2011 June 7 using a time range, and the output of the 
+\caption{Example retrieval of a GOES lightcurve
+using a time range, and the output of the 
 \texttt{peek()} method.}
@@
 a variety of ways in order to perform time-series analysis.
-
 %Stuart: Where did the pandas section go?

### 2014-01-30 3-1-VSO.tex
my changes
comments and some little fixings
Cadair passes the ball
Edits to section 3, retrieval

@@
 Access Protocol) service is also available.
-SunPy's \texttt{vso} module accesses the VSO via the SOAP service using the
+SunPy's \texttt{vso} module provides access to the VSO via the SOAP service using the
 \texttt{suds} package.
@@
 
+%ays: commented this out because it's not developed at all
+%The \texttt{vso} module has two query interfaces implemented.
 Listing~\ref{code:vso_query_simple} shows an example of how to query the VSO
@@
 
-Listing~\ref{code:vso_query_advanced} shows examples of how to make advanced
-queries by combining attribute objects.
+Listing~\ref{code:vso_query_advanced} shows an example of how to make an advanced
+query by combining attribute objects.
 Two attribute objects can be combined with a logical \texttt{or} operation
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from SunPy.net import vso
+>>> from sunpy.net import vso
 >>> client = vso.VSOClient()
@@
 %Stuart: I suggest removing the second query from here, it dosen't add much.
+%dps: Stuart, do you mean the second listing, or the wavelength bit of this one?
+%SJM: The wavelength bit of this one.
+%ays: I removed the first one instead!  Ha ha!
 \begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}
-#Querying multiple instruments/missions over the same time range
->>> instrument_condition = ( vso.attrs.Instrument('lasco') |
-...                          vso.attrs.Detector('cor1') )
->>> coronagraphs = client.query(vso.attrs.Time(tstart, tend),
-...                             instrument_condition)
->>> coronagraphs.num_records()
-485
->>> coronagraphs.show()
-Start time           End time             Source    Instrument  Type
-----------           --------             ------    ----------  ----
-2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO      LASCO       CORONA
-...
-2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
-2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
-
 #Querying two wavelength ranges over the same time range
->>> wavelength_condition = ( vso.attrs.Wave(125, 135) |
+>>> condition = (vso.attrs.Detector('cor1') |
+...              vso.attrs.Wave(125, 135) |
 ...              vso.attrs.Wave(165, 175) ) # in angstroms
->>> euv = client.query(vso.attrs.Time(tstart, tend),
-...                    wavelength_condition)
->>> euv.num_records()
-3989
->>> euv.show()
+>>> advanced = client.query(vso.attrs.Time(tstart, tend), condition)
+>>> advanced.num_records()
+4434
+>>> advanced.show()
 Start time           End time             Source    Instrument  Type
@@
 ...
+2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
+2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
+...
 2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK
 \end{minted}
-\caption{Examples of advanced VSO queries using attribute objects,
+\caption{Example of an advanced VSO query using attribute objects,
+combining both data from a detector and any data that falls within two wavelength ranges,
 continuing from Listing~\ref{code:vso_query_simple}.}

### 2014-01-30 3-2-HEK.tex
added a comment right at the end
Edits to section 3, retrieval

--- 2014-01-29 3-2-HEK.tex
@@
 automated algorithms and human observers.  Some of the information in the HEK 
-reproduces feature and event data from elsewhere (for example, the GOES flare catalogue),
+reproduces feature and event data from elsewhere (for example, the \textit{GOES} flare catalogue),
 and some is generated by the Solar Dynamics Observatory Feature Finding Team 
@@
 >>> tstart, tend = '2011/08/09 00:00:00', '2011/08/10 00:00:00'
->>> result = client.query(hek.attrs.Time(tstart,tend), 
-...                       hek.attrs.EventType('FL')) # 'FL' indicates flare
+>>> result = client.query(hek.attrs.Time(tstart, tend), 
+...                       hek.attrs.EventType('FL')) # flares
 >>> len(result)
@@
 \caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
-which occurred on August 9th, 2011.}
+on 2011 August 9.}
 \label{code:hek:simple}
@@
 event. As was mentioned above, the HEK stores feature/event metadata obtained 
-in different ways, known generally as {\it feature recognition methods} (FRMs). 
+in different ways, known generally as feature recognition methods (FRMs). 
 Example in Listing~\ref{code:hek:frm} filters the results of the previous 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> result = client.query(hek.attrs.Time(tstart,tend), 
+>>> result = client.query(hek.attrs.Time(tstart, tend), 
 ...                       hek.attrs.EventType('FL'),
@@
 
-HEK comparisons can be combined using Python’s logical operators e.g. \texttt{and}
-and \texttt{or}. This makes complex queries easy to create: Listing \ref{code:hek:or} 
+HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
+and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
 returns flares west of 50 arcseconds or those that have a peak flux above 
-1000.0 (the units of the flux are FRM dependent and are described at the HEK 
+1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
 website).
@@
 \begin{minted}[bgcolor=bg]{python}
->>> result = client.query(hek.attrs.Time(tstart,tend), 
+>>> result = client.query(hek.attrs.Time(tstart, tend), 
 ...                       hek.attrs.EventType('FL'),
@@
 \end{minted}
-\caption{HEK query using the 'or' operator.}
+\caption{HEK query using the logical \texttt{or} operator.}
 \label{code:hek:or}
@@
 \url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
-are FRM dependent.  If a FRM does not have one of the optional attribute, 
+are FRM dependent.  If a FRM does not have one of the optional attributes, 
 \texttt{None} is returned by the \texttt{hek} module.
@@
 %dps - I agree.
+%JI - I agree
 %Stuart: Will do on my next pass
+%ays: hmm, still nothing?

### 2014-01-30 3-3-HELIO.tex
Edits to section 3, retrieval

@@
 \end{minted}
-\caption{Example of querying the HEC service to multiple cme
+\caption{Example of querying the HEC service to multiple CME
 catalogues, in this case the ones detected automatically 
@@
 
-In the future, additional HELIO services will be supported by SunPy, aiming to a 
-seamlessly interaction between the other services and tools available (e.g., 
-\texttt{hek}, \texttt{Map}).  
-For example, solar features available in the HELIO Feature Catalogue could be
-overplot on maps.
+In the future, additional HELIO services will be supported by SunPy, aiming for
+seamless interaction between the other services and tools available (e.g., 
+\texttt{hek}, \texttt{map}).  
 % RJH: This sentence is an orphan and should have a home constructed for it.
@@
 % better? or this should be in the future section?
+% JI - moved bit about HELIO overplotting to Future.tex.  Might want to have
+% a bit in the future section about other net services.

### 2014-01-30 4-Util.tex
comments and some little fixings
Edits to the rest

@@
 such as the Astropy 
-coordinates package. The \verb|wcs| package in SunPy implements the World Coordinate 
-System (WCS) for solar coordinates as described by \cite{Thompson2000}. The 
+coordinates package. The \texttt{wcs} package in SunPy implements the World Coordinate 
+System (WCS) for solar coordinates as described by \citep{thompson2006}. The 
 transformations currently implemented are those most useful 
@@
 the Sun as angles measured from the center of the solar disk (usually in 
-arcseconds) using cartesian coordinates (X, Y). This is the coordinate system 
+arcseconds) using Cartesian coordinates (X, Y). This is the coordinate system 
 most often defined in solar imaging data (see for example, images from 
-\textit{SDO/AIA}, \textit{SOHO/EIT}, and \textit{TRACE}). 
+\textit{SDO}/AIA, \textit{SOHO}/EIT, and \textit{TRACE}). 
 HG coordinates express positions on the Sun using longitude and latitude on 
-the solar sphere. There are two standards for this coordinate system, 
-Stonyhurst-Heliographic where the origin is at the intersection of the solar 
-equator and the central meridian as seen from Earth and 
-Carrington-Heliographic is a system which is fixed to the Sun and does not depend on Earth. The 
+the solar sphere. There are two standards for this coordinate system:
+Stonyhurst-Heliographic, where the origin is at the intersection of the solar 
+equator and the central meridian as seen from Earth, and 
+Carrington-Heliographic, which is fixed to the Sun and does not depend on Earth. The 
 implementation of these transformations pass through a common coordinate system 
-called Heliocentric-Cartesian (HCC) where positions are expressed in true 
-(deprojected) physical distances instead of angles on the celestial sphere.
+called Heliocentric-Cartesian (HCC), where positions are expressed in true 
+(de-projected) physical distances instead of angles on the celestial sphere.
 These transformations require some knowledge of the location of the observer 
@@
 some examples of coordinate transforms carried out in SunPy using the 
-\verb|wcs| utilities.
+\texttt{wcs} utilities.
 
@@
 \end{minted}
-\caption{Using the sunpy.wcs subpackage.}
+\caption{Using the \texttt{wcs} subpackage.}
 \label{code:wcs_code}
@@
 \subsubsection{Sun}\label{ssec:util:sun}
-The purpose of this module is to provide solar-specific data, for example ephemerides and
+The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
 solar constants. The main namespace contains a number of functions which provide solar
-ephemerides such as the Sun to Earth distance, solar cycle number, the mean 
+ephemerides such as the Sun to Earth distance, solar-cycle number, the mean 
 anomaly, etc.
-All of these functions take a time as their input which can be provided in any 
-\texttt{parse\_time}
-compatible format. 
+All of these functions take a time as their input which can be provided in a format
+compatible with \texttt{sunpy.time.parse\_time()}. 
 A future version of SunPy will integrate with the Astropy coordinates package and will 
@@
 
-\subsubsection{constants}\label{ssec:util:const}
-The purpose of the constants package is to provide a number of solar-related 
+%ays: I removed this as a separate subsection because constants is part of sun...
+%\subsubsection{constants}\label{ssec:util:const}
+The \texttt{sun.constants} module provides a number of solar-related 
 constants in order to provide consistency in the calculations of derived solar 
 values both within the SunPy code base but also to the user. Every solar 
-constant is provided as a Constant object as defined by Astropy. Each 
-Constant object defines a Quantity, a number associated with a unit, along with 
+constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
+\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
 the constant's provenance (i.e., reference) as well as its uncertainty. Using 
-Astropy's Quantities, any solar constant can easily be converted between 
+Astropy's {Quantity} objects, any solar constant can easily be converted between 
 different units as can be seen in Listing~\ref{code:constants_code} as well
 as between the SI or cgs unit systems with a single command.  As these objects inherit from 
-Numpy's \texttt{ndarray}, they work well with standard representations of numbers.
+NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
 For convenience a number of shortcuts to frequently used constants are provided 
-directly when importing the sub-package. A larger list of constants can be 
+directly when importing the module. A larger list of constants can be 
 accessed through an interface modelled on that provided by the SciPy constants 
 package and is available as a dictionary called \texttt{physical\_constants}. 
-To view them all quickly a \texttt{print\_all()} function is available.
+To view them all quickly, a \texttt{print\_all()} function is available.
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.sun import constants as sun
+>>> from sunpy.sun import constants
 >>> print(sun.mass)
@@
 # Verify the average density of the Sun and convert to cgs
->>> (sun.mass/sun.volume).cgs
+>>> (constants.mass/constants.volume).cgs
 <Quantity 1.40851154227 g / (cm3)>
 # Search for the age of the Sun
->>> sun.find('age')
+>>> constants.find('age')
 ['age', 'average angular size', 'average density', 'average intensity']
->>> sun.value('age'), sun.unit('age')
+>>> constants.value('age'), constants.unit('age')
 (4600000000.0, Unit("yr"))
 \end{minted}
-\caption{Using the sunpy.sun.constants sub-package.}
+\caption{Using the \texttt{sun.constants} module.}
 \label{code:constants_code}
@@
 classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, 
-some instrument-specific functions may be found within the \texttt{instr} package. 
+some instrument-specific functions may be found within the \texttt{instr} subpackage. 
 These functions are generally those that are unique to one particular solar instrument, 
-rather than of general use, for example a function to construct a GOES flare event list 
-or a function to query the LYRA timeline annotation file. Currently, some support is included
- for the GOES, LYRA, RHESSI and IRIS instruments, while future developments 
+rather than of general use, such as a function to construct a \textit{GOES} flare event list 
+or a function to query the \textit{LYRA} timeline annotation file. Currently, some support is included
+ for the \textit{GOES}, \tetxit{LYRA}, \textit{RHESSI} and \textit{IRIS} instruments, while future developments 
  will include support for additional missions. Ultimately, it is anticipated that solar
   missions requiring a large suite of software tools will be supported via a separately 
-  maintained package affiliated with SunPy.
+  maintained package that is affiliated with SunPy.

### 2014-01-30 solarsoft.tex
Edits to the rest

@@
 % What about generated files?  I don't think they contribute much.
+% dps: I agree... I don't like the lines of code connection with work or efficiency
+%   but at the same time is something used by some people... so... I don't know.
 
@@
 sold by Exelis, a global aerospace, defence, information and services company. 
-The SSW `gen' package provides the base analysis capabilities such as time-series
+The SSW \texttt{gen} package provides the base analysis capabilities such as time-series
 analysis, time conversions, spectral fitting, image display, and file 
@@
 and csh scripts (3.8\%). 
-According to data generated using David A. Wheeler's `SLOCCount'\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/gen is composed of 
+According to data generated using David A. Wheeler's `SLOCCount'\footnote{\url{http://www.dwheeler.com/sloccount/}}, SSW/\texttt{gen} is composed of 
 289,724 lines of code with a total approximate value of \$10.4M (based on the 
@@
 %schriste - i don't know what you mean by this 
-%Stuart: comment was Davids
+%dps: schriste, could you tell -at least us- how that was measured? can we make an
+% script that we could use next year and see how much it changed?
 Individual missions and instruments provide additional optional packages to 
@@
 One of SunPy's key aims is to provide a free and modern alternative to the 
-SolarSoft (gen) library. This is made possible by the recent rise of the 
+SSW/\texttt{gen} library. This is made possible by the recent rise of the 
 scientific Python community. Python, as described in Section \ref{sec:Intro}, 
@@
 solar physics or astronomy communities. It is very extensible with C, C++, 
-FORTRAN or even IDL. Many books and on-line documentation sources are available. For 
-example, at the time writing a search 
+FORTRAN or even IDL. Many books and online documentation sources are available. For 
+example, a simple search on Amazon.com yields hundreds of books on Python programming.
 %
@@
 %comparison to the other metrics used it's a little weak.
-on Amazon for books on IDL programming generated $189$ results while a search 
-for Python yielded $1\,788$ results. Python has a strong emphasis on 
-readability, a concept which is well-aligned with the scientific endeavour.
+% schriste - ok, how about this?
+%dps: sounds better... but I'm skeptic of using Amazon.com...
+Python has a strong emphasis on readability, a concept which is well-aligned with scientific endeavours.
 %In fairness, IDL is also quite readable! Could move this statement to the intro instead.
@@
 % RJH: Is this for a python developer?  Again, this is useless info, imho.
+% schriste - it is the only way to make a comparison and is fairly accepted by
+% the software engineering community as far as i can tell.
 the time of writing). Python continues to see increased use in the astronomy 
@@
 the solar physics community. Finally, Python integrates well with many 
-technologies such as web servers \citep{dolgert2008}, SQL databases, 
+technologies such as web servers \citep{dolgert2008}, SQL databases, and 
 interactive and shareable notebook-based computing \citep{perez2007}. For all 
@@
 provide capabilities surpassing that provided by IDL for array manipulation and 
-2D plotting \citep{greenfield2011}. Providing similar capabilities to SSW/gen 
+2D plotting \citep{greenfield2011}. Providing similar capabilities to SSW/\texttt{gen} 
 in Python is made easier by leveraging the diverse Python community. For 
@@
 data analysis package. SunPy also relies on and is coordinating with the 
-\texttt{astropy} package \citep{theastropycollaboration2013}. Astropy is still in 
+\texttt{astropy} package \citep{theastropycollaboration2013}. \texttt{astropy} is still in 
 active development but already provides many relevant capabilities such as 
 full-featured support for FITS files, absolute date and time conversions, 
-units and unit conversions, and model-fitting. Pandas (134k lines of code) 
-and Astropy (90k lines of code) allow SunPy to leverage a total value of \$7.6M 
-worth of development which is close to the \$10.4M for SSW/gen assuming a rough 
+units and unit conversions, and model-fitting. \texttt{pandas} (134k lines of code) 
+and \texttt{astropy} (90k lines of code) allow SunPy to leverage a total value of \$7.6M 
+worth of development, which is close to the \$10.4M for SSW/\texttt{gen} assuming a rough 
 equivalency between a line of Python code and a line of IDL code.

### 2014-01-30 1-Introduction.tex

--- 2014-01-29 1-Introduction.tex
@@
 
-Science is driven by the analysis of data. Modern advances in sensor
-technology, combined with the availability of inexpensive storage has led to
-rapid increases in amount of data available to scientists in almost
-every discipline.  Solar physics is no exception to this trend. For example, NASA's
-AIA instrument on the Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
+Science is driven by the analysis of data of growing variety and complexity.
+Modern advances in sensor
+technology, combined with the availability of inexpensive storage, has led to
+rapid increases in the sheer amount of data available to scientists in almost
+every discipline.  Solar physics is no exception to this trend. For example,
+NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched in February 2010,
 produces over 1 TB of catalogued and stored data per day \citep{aia}. Managing and
 analysing this mountain of data
-requires increasingly sophisticated software tools.  Key qualities
-that these tools should have include robustness, ease of use, a
-transparent development history, ease of modification, and conformance
+requires increasingly sophisticated software tools.
+These tools should be robust, be easy of use and modify, have a
+transparent development history, and conform
 to standards.  Software with these qualities provide a strong
@@
 
-SunPy aims to provide a free, open-source and openly developed software package 
+The SunPy project aims to provide a free, open-source and openly developed software package 
 for the analysis and visualisation of solar data. SunPy makes use of the Python 
-programming language and the scientific Python packages. Python is a general-purpose, 
+programming language and scientific Python packages. Python is a general-purpose,
 powerful and easy-to-learn high-level programming language.
@@
 % meaningless.
-% schriste - i think it's important. it contrasts nicely with IDL and its tiny community.
+% schriste - i think it's important. it contrasts nicely with IDL and its tiny 
+%community.
+%SJM: I think it should stay, it makes a point.
 According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
@@
 as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
-provide the basic functionality expected of a scientific programming language,
+provide the basic functionality expected of a scientific programming language:
 e.g., array manipulation, core numerical algorithms and visualisation. 
@@
 The primary focus of SunPy's early development are 
-specialised data types that allow the acquisition, processing and 
+specialised data types that enable the acquisition, processing and 
 visualisation of all types of solar data.
@@
 capabilities, an overview of the project's development model, community aspects of the 
-SunPy project, as well as future plans. The latest release of SunPy, version 0.4,
+SunPy project, and future plans for the project. The latest release of SunPy, version 0.4,
 can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be

### 2014-01-30 2-1-Map.tex

--- 2014-01-29 2-1-Map.tex
@@
 The Map data type stores 2D spatial data, such as images of the Sun and 
-inner heliosphere. It provides a wrapper around a \texttt{numpy} data array and 
-its associated spatial coordinates and other metadata. The \texttt{Map} class 
-provides methods for typical operations on 2D data, such as rotation and 
+inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array; 
+the images associated spatial coordinates; and other metadata. The \texttt{Map} 
+class provides methods for typical operations on 2D data, such as rotation and 
 re-sampling, as well as visualisation functionality.
@@
 \texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
-\texttt{NDData} is a generic wrapper around an \texttt{ndarray} with a 
+\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
 \texttt{meta} attribute to store metadata.
@@
 not yet make full use of its capabilities, but this inheritance structure 
-provides for future integration of \texttt{astropy}. In order to provide 
+provides for future integration with \texttt{astropy}. In order to provide 
 instrument- or detector-specific integration, \texttt{GenericMap} is designed
@@
 SunPy v0.4 has \texttt{Map} specialisations for the following instruments: 
-\textit{YOHKOH/SXT}, \textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
-\textit{STEREO/EUVI} and \textit{COR}, \textit{HINODE/XRT},
-\textit{PROBA2/SWAP}, \textit{SDO/AIA} and \textit{HMI}, 
+\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
+\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
+\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
 and \textit{IRIS} SJI frames. 
@@
 % usually citations are provided for instruments.
+% dps: I would agree to add the citations if we were using the instrument in 
+% the paper, but I don't think this is the case here.
 
@@
 Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
-\texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.
+\texttt{Map}; see Section \ref{subsec:Viz} for additional discussion of plotting.
+%dps: See section viz does not apply any more, right? The examples have been 
+%removed now.
+%SJM: the example is gone, but the section remains
+&ays: it does remain, but it's so short it's not worth referring to
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> aiamap = sunpy.map.Map('aia_file.fits')
+>>> from sunpy import map
+>>> aiamap = map.Map('aia_file.fits')
 >>> aiamap.peek()
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{AIA} FITS file,
+\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file,
 and a quick-view plot is created.}
@@
 \begin{minted}[bgcolor=bg]{pycon}
+>>> from sunpy import map
 >>> import matplotlib.pyplot as plt
->>> import sunpy.map
->>> compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
+>>> compmap = map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
 ...                   composite=True)
@@
 \end{center}
-\caption{Example showing a \texttt{CompositeMap} plot, with RHESSI data composed with SDO/AIA data, and the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing a \texttt{CompositeMap} plot, with RHESSI data composited
+with \textit{SDO}/AIA data, and the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> compmap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> from sunpy import map
+>>> compmap = map.Map('aia_lev1_171a_2014_01*fits', cube=True)
 >>> compmap.peek()
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
+>>> from sunpy import map
 >>> from matplotlib import animation
->>> mapc = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> mapc = map.Map('aia_lev1_171a_2014_01*fits', cube=True)
 >>> anim = mapc.plot()
@@
 % Could we add more metadata to the movie? obs_date, instrument, etc...?
-\caption{Example showing how to save a video animation from a \texttt{MapCube}, using 
+\caption{Example showing how to save a video animation from a \texttt{MapCube} using 
 \texttt{matplotlib}'s animation framework.}

### 2014-01-30 2-3-Spectra.tex

--- 2014-01-29 2-3-Spectra.tex
@@
 %schriste - can't we just take a slice off of the spectram to make a spectrum?
-
+%dps - Spectrum does not really do much, just peek and plot. I don't think
+% it brings anything to the content.
 SunPy aims to provide broad support for solar spectroscopy
@@
 \texttt{Spectrogram} class for 2D data (intensity as a function of time and
-frequency).  Each of these classes use a \texttt{numpy.ndarray} class
+frequency).  Each of these classes use a \texttt{numpy.ndarray} object
 as its \texttt{data} attribute.  These two classes were implemented
@@
 \href{http://www.e-callisto.org/}{e-Callisto}
-solar radio spectrometer network and STEREO/SWAVES spectrograms.
+solar radio spectrometer network and \textit{STEREO}/SWAVES spectrograms.
 
@@
 files into a single spectrogram, across time and frequency.
-In the example shown, data is provided in two frequency ranges, 
+In the example shown, data is provided in two frequency ranges:
 20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
 the frequency range, the \texttt{Spectrogram} object linearises the
-frequency axis for a better analysis.  The example also demonstrates
-the implemented background subtraction method.
+frequency axis to assist analysis.  The example also demonstrates
+the implemented background subtraction method, which calculates
+a constant background over time for each frequency channel.
 % RJH: Which subtraction method?  If the specifics are irrelevant, cut it.
+% RJH: is this better?
 %ji to DPS - what is the linearisation that is happening here?
+%ji- the linearisation consist in the frequency axis being linear and the 
+% data being streched with it.  The frequency normally are not evenly spaced
+%ays: I deleted the phrase "based on the values closer to the average" because I don't understand what that means
 
@@
 \end{listing}
-
-% Download Callisto
-% Merge multiple time-ranges / frequencies (just work from downlad!)
-% Merge callisto with swaves

### 2014-01-30 2-Data_Types.tex
comments and some little fixings

@@
 These classes allow access to the data
-along with associated metadata and provide appropriate convenience functions to
+and associated metadata and provide appropriate convenience functions to
 enable analysis and visualisation. For each of these classes, the data is
@@
 % schriste - can't we just quickly fix this? should be easy enough.
+% dps - Spectrogram does not contain meta either! I would suggest
+%(Curently, this is just supported by Map, but the other data types will 
+%include such attribute soon.)
+%SJM: oh what, drop it all together.
 It is possible to instantiate the
@@
 %schriste - i removed time ranges as that just looks up a url.
-In order to provide instrument-specific specialisation, all the core SunPy classes 
-support subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
-sub-type for data from the SDO/AIA instrument. 
+In order to provide instrument-specific specialisation, the core SunPy classes 
+make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
+sub-type for data from the \textit{SDO}/AIA instrument. 
 Data visualisation is provided by two functions: \texttt{peek()}, for quick 
@@
 \label{subsec:Viz}
-As demonstrated in this section, the core SunPy datatypes 
-include visualisation methods that are tailored to that data type. 
+As demonstrated in this section, the core SunPy data types 
+include visualisation methods that are tailored to each data type. 
 These visualisation methods all currently utilise the \texttt{matplotlib} 

### 2014-01-30 3-4-Helioviewer.tex

@@
 easy-to-use visual interfaces.  The primary interface to Helioviewer is a
-google-map-like website which allows users to browse images of the Sun
+Google-Maps-like website which allows users to browse images of the Sun
 taken by a variety of instruments. In order to manage all of this data, the Helioviewer
-project maintains archives of all of its data as JPEG2000 format (for further
-details on the Helioviewer Project see \citep{muller2009}). The
+project maintains archives of all of its data in JPEG2000 format (for further
+details on the Helioviewer Project see \cite{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source
-FITS files they are generated from, and so can be a used as a shortcut
-to visualise large amounts of data from multiple sources.  SunPy is
+FITS files they are generated from, and thus can be used to quickly
+visualise large amounts of data from multiple sources.  SunPy is
 also used in Helioviewer production servers to manage the download and
@@
 \begin{minted}[bgcolor=bg]{pycon}
+>>> from sunpy.net.helioviewer import HelioviewerClient
+>>> hv = HelioviewerClient()
 >>> hv.download_png('2099/01/01', 6,
-...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50]"+
+...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
 ...                 "[SOHO,LASCO,C2,white-light,1,100]",
@@
 which to centre the image (measured in helio-projective cartesian
-co-ordinates) and the \texttt{width} and \texttt{height} are the pixel
+coordinates), and the \texttt{width} and \texttt{height} are the pixel
 values for the image dimensions.
@@
 positioning of the image data.  There is sufficient metadata in each
-file to permit the creation of a SunPy map object (see Section
+file to permit the creation of a SunPy \texttt{Map} object (see Section
 \ref{ssec:map}) from a Helioviewer JPEG2000 file.  This allows image
@@
 object.  This functionality allows users to visualise and manipulate
-Helioviewer-supplied image data in an identical fashion to a SunPy map
+Helioviewer-supplied image data in an identical fashion to a SunPy \texttt{Map}
 object generated from FITS data (see Section \ref{ssec:map}).
@@
 ...                            measurement='continuum')
->>> from sunpy.map import Map
->>> Map(filepath).submap([200,550],[-400,-200]).peek()
+>>> from sunpy import map
+>>> map.Map(filepath).submap([200,550],[-400,-200]).peek()
 \end{minted}
@@
 \caption{Acquisition and display of a Helioviewer JPEG2000 file as a
-  SunPy map object.}
+  SunPy \texttt{Map} object.}
 \label{code:downloadjp2}

### 2014-01-30 3-5-Database.tex

--- 2014-01-29 3-5-Database.tex
@@
 
-The database sub-package makes use of a database supported by
-\href{http://www.sqlalchemy.org}{SQLAlchemy}. This library was chosen
+The \texttt{database} subpackage makes use of a database supported by
+\href{http://www.sqlalchemy.org}{\texttt{SQLAlchemy}}. This library was chosen
 since it supports many SQL dialects. 
@@
 The database can store and manage all data that can be read via SunPy's 
-\texttt{io} subpackage, and direct integration with the \textsc{VSO} 
-subpackage is supported.
+\texttt{io} subpackage, and direct integration with the \texttt{vso} 
+module is supported.
 It is also possible to manually add file or directory entries. The package also provides
@@
 and files on the \textsc{VSO}. This reduces the likelihood of downloading the same file 
-multiple times. When a file is added to the database, the file is scanned and a file hash is produced. 
+multiple times. When a file is added to the database, the file is scanned for metadata,
+and a file hash is produced. 
 The current date is associated with the entry along with metadata summaries such 
 as instrument, date of observation, field of view, etc. 
-The database also provides the ability to associate custom meta-data to 
+The database also provides the ability to associate custom metadata to 
 each database entry such as keywords, comments, and favouring, as well as 
 %dps: favouring is not what we want to say here...
-querying the full metadata (i.e., FITS header) of each entry.
+%JI: ``assigning favourites'' - is this what is meant?
+%ays: i'll let someone else fix this
+querying the full metadata (e.g., FITS header) of each entry.
 
@@
 
-A very special feature of the database package is the support of \texttt{undo}
+A useful feature of the database package is the support of \texttt{undo}
 and \texttt{redo} operations. This is particularly convenient in
@@
 This feature will also be desirable when creating a GUI frontend for this package.
+%JI - revert accidental operations of any kind?
 
@@
 \end{minted}
-\caption{Example usage of the database sub-package.}
+\caption{Example usage of the \texttt{database} subpackage.}
 \label{code:database}

### 2014-01-30 3-Retrieval.tex

@@
 
-Several well-developed resources currently exist within heliophysics which provide event databases, remote access and data retrieval for a large number of data sources.
-As a community-based project, SunPy provides support for these resources via the \texttt{sunpy.net} package.
-In the following subsections, we describe a number of these resources and introduce current methods for accessing them within SunPy.
+Several well-developed resources currently exist within heliophysics which provide event databases, 
+remote access and data retrieval for a large number of data sources. As a community-based project, 
+SunPy provides support for these resources via the \texttt{net} subpackage. 
+In the following subsections, we describe a number of these resources and 
+how to access them using SunPy.
 

### 2014-01-30 5-Dev.tex

@@
 \begin{enumerate}
-	\item  The code must follow 	
-	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
-	guidelines, keeping SunPy code in a consistent.
+	\item  The code must follow the
+	\href{http://www.python.org/dev/peps/pep-0008/}{PEP 8} Python style 
+	guidelines to maintain consistency in the SunPy code.
 
@@
 
-	\item The code must contain significant unit test coverage.
+	\item The code must contain significant unit-test coverage.
 
-        \item Community consensus is reached that the new code is valuable.
+        \item Community consensus is reached that the new code is valuable and appropriately implemented.
 \end{enumerate}
 This kind of development model is widely used within the scientific Python 
-community as well as by a wide variety of other projects both open and closed 
+community as well as by a wide variety of other projects, both open and closed 
 source.
@@
 automatically triggers a comprehensive review of written unit tests. If any single test
-fails then the community is alerted before the code is accepted. The unit test coverage is
+fails, the community is alerted before the code is accepted. The unit test coverage is
 also monitored by the \href{http://coveralls.io}{Coveralls} service.
@@
 
-Quality documentation is
+High-quality documentation is
 one of the most important factors determining the success of any software project. 
-Powerful tools already exist in Python to support this, thanks to native
+Powerful tools already exist in Python to support documentation, thanks to native
 Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
-documentation generator. Sphinx uses reStructuredText as its markup language: 
+documentation generator. Sphinx uses reStructuredText as its markup language, which is
 an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
-many output formats most notably HTML as well as PDF, and ePub and provides a rich
+many output formats most notably HTML, as well as PDF and ePub, and provides a rich,
 hierarchically structured view of in-code documentation strings. The SunPy documentation 
@@
 
-Communication is the key to maintaining an active community, and so the SunPy community 
+Communication is the key to maintaining an active community, and the SunPy community 
 uses a number of different tools to facilitate communication. For immediate communications, an active IRC chat
@@
 developer comments or discussions, a open mailing list is hosted on Google Groups. 
-Discussion of bugs and bug tracking are provided directly on GitHub as well as new
-code-review discussions.  The SunPy community also reaches out to the wider solar physics
+Bug tracking, code reviews, and feature-request discussions take place directly on GitHub.
+The SunPy community also reaches out to the wider solar physics
 community through presentations, functionality demonstrations and informal meetups at scientific
@@
 through the \href{http://www.python.org/psf/}{Python Software Foundation} (PSF). It supported development of the 
-\texttt{HELIO} and 
+\texttt{helio} and 
 \texttt{database} subpackages.

### 2014-01-30 6-Future.tex

@@
 the code 
-base has grown to over 110,000 lines. SunPy in its current form is a 
+base has grown to over 17,000 lines. SunPy is already a 
 useful 
@@
 %JI: needs new number.  Should be the number of lines in the 0.4 sunpy release???
-As discussed in Section \ref{sec:Intro}, the primary focus of the 
+%ays: I changed the number to ohloh's count unless there's a reason to think it's >110k
+The primary focus of the 
+%ays: Not actually discussed in Section \ref{sec:Intro}, so I removed the reference
 SunPy library is the analysis and visualisation of `high-level' solar 
@@
 operations on 
-that data should be performed.
+that data should be performed. This will enable useful operations
+such as the coordinate and solar-rotation-aware 
+overplotting of HELIO (Section \ref{ssec:helio}) and HEK
+results (Section \ref{ssec:hek}) onto maps (Section \ref{ssec:map}).
 
@@
 analysis. For 
-example, the \texttt{astropy.units} submodule provides a simple and 
+example, the \texttt{astropy.units} subpackage provides a simple and 
 efficient 

### 2014-01-30 1-Introduction.tex
small tweaks to intro

@@
 technology, combined with the availability of inexpensive storage, has led to
-rapid increases in the sheer amount of data available to scientists in almost
+rapid increases in the amount of data available to scientists in almost
 every discipline.  Solar physics is no exception to this trend. For example,
 NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched in February 2010,
-produces over 1 TB of catalogued and stored data per day \citep{aia}. Managing and
+produces over 1 TB of data per day \citep{aia}. Managing and
 analysing this mountain of data
 requires increasingly sophisticated software tools.
-These tools should be robust, be easy of use and modify, have a
+These tools should be robust, easy of use and modify, have a
 transparent development history, and conform
-to standards.  Software with these qualities provide a strong
+to modern software engineering standards.  Software with these qualities provide a strong
 foundation and can support the needs of the community as data
 volumes grow and science questions evolve.
-%schriste - the opening paragraph still needs work
-%ji - I had a go.
-%schriste - looks good, made a small fix
 
@@
 capabilities, an overview of the project's development model, community aspects of the 
-SunPy project, and future plans for the project. The latest release of SunPy, version 0.4,
+project, and future plans. The latest release of SunPy, version 0.4,
 can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be

### 2014-01-30 3-2-HEK.tex
more lightish editing

@@
 The Sun is an active star and exhibits a wide range of transient phenomena 
-(e.g., flares and radio bursts) on many different time-scales, length-scales and 
+(e.g., flares, radio bursts) on many different time-scales, length-scales and 
 wavelengths. Observations and metadata concerning these phenomena are collected 
@@
 use of the 
-\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{HEK
- API}.
+HEK API\footnote{For more information see 
+\href{\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}}.
 The current list of events maintained by the HEK and their properties can be 
@@
 identical to the two letter abbreviations found at the HEK website, 
-\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
 
@@
 
-HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
+Similar to the \texttt{vso} module, HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
 and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 

### 2014-01-30 3-3-HELIO.tex
edits to helio section

@@
 
-The HELiophysics Integrated Observatory (\href{http://helio-vo.eu}{HELIO}) has 
+The HELiophysics Integrated Observatory (HELIO\footenote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
 compiled a list of web services which allows scientists to query and 
@@
 implemented as separate services. 
-\href{http://helio-vo.eu}{HELIO} is made up of nine different public services, 
+HELIO is made up of nine different public services, 
 which allows scientists to search different catalogues of registered events, 
@@
 field disturbances produced few days before on the Sun).
-In addition to the primary, \href{http://hfe.helio-vo.eu}{web-based interface to 
-HELIO}, the services are available by API.
+In addition to the primary, web-based interface to 
+HELIO, the services are available by API.
 
 SunPy's \texttt{hec} module provides an interface to the
-\textit{HELIO Event Catalogue} (HEC) service. This module was developed as
+\textit{HELIO Event Catalogue} (HEC) service. 
+%schriste - why is this italics?
+This module was developed as
 part of a Google Summer of Code (GSOC) project in 2013.
@@
 data format (defined by IVOA \citep{ochsenbein_ivoa_2011}).
-%schriste - a short descriptions of what the hec (get it?) a vot table is needed here
-%dps - a votable format description? or what HEC gets from it?
-The \texttt{hec}
-module parses this output using the \texttt{astropy.io.votable} package.
+The \texttt{hec} module parses this output using the \texttt{astropy.io.votable} package.
 This format has the advantage of containing metadata with information like

### 2014-01-30 5-Dev.tex
added concluding summary

@@
 SunPy's development makes use of the online service 
-\href{http://github.com}{GitHub} and \href{http://git-scm.com/}{Git}
+GitHub (\href{http://github.com}{http://github.com}) and Git\footenote{For more information see \href{http://git-scm.com/}{http://git-scm.com/}}
 as its distributed version control software.

### 2014-01-30 3-2-HEK.tex
bug fixes

@@
 HEK API\footnote{For more information see 
-\href{\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}}.
-The current list of events maintained by the HEK and their properties can be 
-found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.
+\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
 
 Simple HEK queries consist of start time, an end time, and an event type 
-(Listing \ref{code:hek:simple}). Event types are specified as upper case, 
+(Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
 two letter strings, and are 
 identical to the two letter abbreviations found at the HEK website,
-\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
+%\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
+% schriste - above line causes an error, can't figure out why
 
@@
 conditions on the attributes in the call to the HEK query method.
+
 \begin{listing}[H]
@@
 \end{listing}
-All FRMs report the required feature attributes (as described at 
-\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
+All FRMs report the required feature attributes, but the optional attributes 
 are FRM dependent.  If a FRM does not have one of the optional attributes, 

### 2014-01-30 3-3-HELIO.tex
bug fixes

@@
 
-The HELiophysics Integrated Observatory (HELIO\footenote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
+The HELiophysics Integrated Observatory (HELIO\footnote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
 compiled a list of web services which allows scientists to query and 

### 2014-01-30 2-2-Lightcurve.tex

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the {\texttt{pandas}} data-analysis library (\url{http://pandas.pydata.org}), and 
+the {\texttt{pandas}} data-analysis library (\href{http://pandas.pydata.org}{http://pandas.pydata.org}), and 
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
@@
 \end{listing}
-%schriste - note to self, fix this example, add resampled points on top of plot?
 
@@
 a variety of ways in order to perform time-series analysis.
-%Stuart: Where did the pandas section go?
-%ARI - looks like it's up top

### 2014-01-30 2-3-Spectra.tex

@@
 \subsection{Spectra}\label{sec:spectra}
-%schriste - this section needs major work
-%ji - there is no example of a spectrum
-%dps - I need to think in one...
-%schriste - can't we just take a slice off of the spectram to make a spectrum?
-%dps - Spectrum does not really do much, just peek and plot. I don't think
-% it brings anything to the content.
 SunPy aims to provide broad support for solar spectroscopy
@@
 as its \texttt{data} attribute.  These two classes were implemented
-by funding provided by the Astrophysics Research Group at Trinity
+with support from by the Astrophysics Research Group at Trinity
 College Dublin, Ireland.
+% schriste - is this necessary? surely we don't need to thank all of our employers
 

### 2014-01-30 2-Data_Types.tex

@@
 three primary varieties of solar physics data: images, time series, and
-spectra. These core data types are Python classes:
+spectra. These core data types are supported by SunPy's classes:
 \texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
@@
 enable analysis and visualisation. For each of these classes, the data is
-stored in the \texttt{data} attribute while the metadata is stored 
-in the \texttt{meta} attribute. (Curently, \texttt{LightCurve} does 
-not support the \texttt{meta} attribute.) 
+stored in the \texttt{data} attribute while the metadata should be stored 
+in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature fully implemented) 
 % schriste - can't we just quickly fix this? should be easy enough.
@@
 different sources: e.g., files, URLs, arrays.  
-%schriste - i removed time ranges as that just looks up a url.
 In order to provide instrument-specific specialisation, the core SunPy classes 
@@
 sub-type for data from the \textit{SDO}/AIA instrument.
-Data visualisation is provided by two functions: \texttt{peek()}, for quick 
-plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
-integrates with \texttt{matplotlib}.
 
@@
 
-\input{2-1-Map}
-\input{2-2-Lightcurve}
-\input{2-3-Spectra}
-
 \subsection{Visualisation}
 \label{subsec:Viz}
-As demonstrated in this section, the core SunPy data types 
+All of the core SunPy data types 
 include visualisation methods that are tailored to each data type. 
@@
 \texttt{matplotlib} commands to manipulate the plot parameters (e.g. title, axes).
+Data visualisation is provided by two functions: \texttt{peek()}, for quick 
+plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
+integrates with \texttt{matplotlib}.
+
+\input{2-1-Map}
+\input{2-2-Lightcurve}
+\input{2-3-Spectra}

### 2014-01-30 3-4-Helioviewer.tex

@@
 SunPy provides the ability to download images hosted by the
-\href{http://helioviewer.org}{Helioviewer Project}.  
+Helioviewer Project (\href{http://helioviewer.org}{http://helioviewer.org}).  
 The aim of the Helioviewer Project is to enable
@@
 JPEG2000 files are typically highly compressed compared to the source
-FITS files they are generated from, and thus can be used to quickly
+FITS files they are generated from but high-fidelity, and thus can be used to quickly
 visualise large amounts of data from multiple sources.  SunPy is
@@
 $\rightarrow$ measurement, where '$\rightarrow$' means 'provides
-(possibly multiple)'.  Each Helioviewer Project JPEG2000 file contains
+(possibly multiple)'.  
+%schriste - say what?!
+Each Helioviewer Project JPEG2000 file contains
 metadata which are based (in part) on the original FITS header

### 2014-01-30 3-Retrieval.tex

--- 2014-01-13 3-Retrieval.tex
@@
-\section{Solar Data Search and Retrieval}
+\section{Solar Data Search and Retrieval}\label{sec:retrieval}
+
+Several well-developed resources currently exist within heliophysics which provide  
+remote access and data retrieval for a large number of data sources as well as access to 
+event databases. As a community-based project, 
+SunPy provides support for these resources via the \texttt{net} subpackage. 
+In the following subsections, we describe a number of these resources and 
+how to use them in SunPy.
 

### 2014-01-30 4-Util.tex

@@
 or a function to query the \textit{LYRA} timeline annotation file. Currently, some support is included
- for the \textit{GOES}, \tetxit{LYRA}, \textit{RHESSI} and \textit{IRIS} instruments, while future developments 
+ for the \textit{GOES}, \textit{LYRA}, \textit{RHESSI} and \textit{IRIS} instruments, while future developments 
  will include support for additional missions. Ultimately, it is anticipated that solar

### 2014-01-30 5-Dev.tex

--- 2014-01-30 5-Dev.tex
@@
 SunPy's development makes use of the online service 
-\href{http://github.com}{GitHub} and \href{http://git-scm.com/}{Git}
+GitHub (\href{http://github.com}{http://github.com}) and Git\footnote{For more information see \href{http://git-scm.com/}{http://git-scm.com/}}
 as its distributed version control software.

### 2014-01-30 6-Future.tex

@@
 \section{Future of SunPy}\label{sec:future}
+
 SunPy as a project has existed for roughly three years. In this time 
-the code 
-base has grown to over 17,000 lines. SunPy is already a 
-useful 
-package for the analysis of calibrated solar data, however, the code 
-base is 
-still evolving from release to release.
+the code base has grown to over 17,000 lines. SunPy is already a 
+useful package for the analysis of calibrated solar data, however, the code 
+base is still evolving from release to release.
 % RJH:  Again, lines of code is a weird measure.  Also, no way there is 110,000 lines that we
@@
 %ays: I changed the number to ohloh's count unless there's a reason to think it's >110k
+%schriste - using the ohloh number is consistent with sloccount so at least we are
+%internally consistent +1
 The primary focus of the 
@@
 the 
-\texttt{astropy} package will enable SunPy to inherit the large 
-amount of work 
-done in that project to support a platform for astronomical data 
-analysis. For 
-example, the \texttt{astropy.units} subpackage provides a simple and 
-efficient 
-way of representing physical units in Python data types; there are 
-plans to 
-incorporate this widely in the SunPy code base. In the past 12 months, 
-the 
-collaboration with the Astropy project 
-\citep{theastropycollaboration2013} and 
-its community has grown, and this direct collaboration between Astropy 
-and 
-SunPy will be one of the key strengths of SunPy going forward.
+\texttt{astropy} package will enable SunPy to incorporate many new features
+with little effort. Collaboration and joint development with the 
+Astropy project \citep{theastropycollaboration2013} is ongoing.
+%schriste - shortened this bit as it was a bit vague and gave the impression that we may be subsumed by astropy

### 2014-01-30 abstract.tex
Very minor abstract patch
my changes

@@
 \begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package 
-for solar physics.
+This paper presents version 0.4 of SunPy, a community-developed Python package 
+for solar physics and data analysis.
 
+Python, a free, cross platform, general purpose, high-level programming language, 
+has seen widespread adoption among the scientific community resulting in the availability 
+of a large range of software, from numerical computation (NumPy, SciPy) and machine 
+learning to spectral analysis and visualization (Matplotlib). SunPy is a data analysis 
+toolkit specializing in providing the software necessary to analyze solar and heliospheric 
+datasets in Python. It aims to provide a free and open-source alternative to the 
+IDL-based SolarSoft (SSW) solar data analysis environment. We present the latest 
+release of SunPy (0.4). SunPy provides downloading capability through integration with the Virtual Solar 
+Observatory (VSO) and the the Heliophysics Event Knowledgebase (HEK). It can open 
+image fits files from major solar missions (SDO/AIA, SOHO/EIT, SOHO/LASCO, STEREO) 
+into WCS-aware maps. SunPy provides advanced time-series tools for data from mission 
+such as GOES, SDO/EVE, and Proba2/LYRA as well as support for radio spectra (e.g. e-Callisto). 
+We present examples of solar data analysis in SunPy, and show how Python-based solar 
+data-analysis can leverage the many existing data analysis tools already available in 
+Python. We discuss the future goals of the project and encourage interested users to 
+become involved in the planning and development of SunPy.
+
+% schriste - we need an abstract!
+% just pasted in old abstract as place holder but still needs work
 \end{abstract}

### 2014-01-30 authors.tex

@@
 Benjamin Mampaey$^{13}$, %2
-Jose Iv\'an Campos-Rozo$^{14}$ %1
+Jose Iv\'an Campos-Rozo$^{14}$, %1
+Michael S. Kirk$^{2}$
 and 

### 2014-01-30 3-4-Helioviewer.tex
update for jack

@@
 sources (such as instrumentation and feature/event catalogues) via
-easy-to-use visual interfaces.  The primary interface to Helioviewer is a
-Google-Maps-like website which allows users to browse images of the Sun
-taken by a variety of instruments. In order to manage all of this data, the Helioviewer
+easy-to-use visual interfaces. The Helioviewer Project have developed two client 
+applications that allow users to browse images and create movies of the Sun taken 
+by a variety of instruments: \href{http://www.helioviewer.org}{Helioviewer.org}, a 
+Google Maps-like web application, and \href{http://www.jhelioviewer.org}{JHelioviewer}, 
+a movie streaming desktop application. In order to manage all of this data, the Helioviewer
 project maintains archives of all of its data in JPEG2000 format (for further

### 2014-01-30 3-5-Database.tex
edits to database section
Added Michael affiliation and British spelling to the abs. Notice Summary.tex is missing

@@
 The \texttt{database} subpackage makes use of a database supported by
-\href{http://www.sqlalchemy.org}{\texttt{SQLAlchemy}}. This library was chosen
+{\texttt{SQLAlchemy} (\href{http://www.sqlalchemy.org}{http://www.sqlalchemy.org}). This library was chosen
 since it supports many SQL dialects. 
@@
 The database also provides the ability to associate custom metadata to 
-each database entry such as keywords, comments, and favouring, as well as 
+each database entry such as keywords, comments, and favourite tags, as well as 
 %dps: favouring is not what we want to say here...
 %JI: ``assigning favourites'' - is this what is meant?
-%ays: i'll let someone else fix this
+%dps: Yes, how does it sounds now?
 querying the full metadata (e.g., FITS header) of each entry.
@@
 2  2012-08-05 00:00:02    33.5    33.5
+%schriste - need to add back in the other entries that i deleted
 \end{minted}

### 2014-01-30 authors.tex
Added Michael affiliation and British spelling to the abs. Notice Summary.tex is missing

@@
 Samuel M Bennett$^1$, %14
-M Malocha, %10
+M Malocha$^{16}$, %10
 John Evans, %10 %No affil
@@
 $^{15}$ Indian Institute of Technology, Bombay
+
+$^{16}$ Humboldt State University, 1 Harpst St, Arcata, CA 95521, United States
 }

### 2014-01-30 abstract.tex

@@
 of a large range of software, from numerical computation (NumPy, SciPy) and machine 
-learning to spectral analysis and visualization (Matplotlib). SunPy is a data analysis 
-toolkit specializing in providing the software necessary to analyze solar and heliospheric 
+learning to spectral analysis and visualisation (Matplotlib). SunPy is a data analysis 
+toolkit specialising in providing the software necessary to analyse solar and heliospheric 
 datasets in Python. It aims to provide a free and open-source alternative to the 

### 2014-01-30 authors.tex
Comment out summary and tweaks to author list

@@
 Samuel M Bennett$^1$, %14
-M Malocha$^{16}$, %10
+Michael Malocha$^{16}$, %10
 John Evans, %10 %No affil
@@
 Jose Iv\'an Campos-Rozo$^{14}$, %1
-Michael S. Kirk$^{2}$
+Michael S Kirk$^{2}$
 and 
@@
 
-$^{14}$ Observatorio Astronómico Nacional Universidad Nacional de Colombia 
+$^{14}$ Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
 Bogotá, D.C., Colombia

### 2014-01-30 2-1-Map.tex
fixed albert's comment bug
edits to map section
Small tweaks to Map

@@
 \subsection{Map}\label{ssec:map}
-The Map data type stores 2D spatial data, such as images of the Sun and 
+The map data type stores 2D spatial data, such as images of the Sun and 
 inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array; 
@@
 
-The architecture of the \texttt{Map} class consists of a template map called
+The architecture of the map subpackage consists of a template map called
 \texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
@@
 of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
-SunPy v0.4 has \texttt{Map} specialisations for the following instruments: 
+SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
+instruments: 
 \textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
@@
 Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
-\texttt{Map}; see Section \ref{subsec:Viz} for additional discussion of plotting.
-%dps: See section viz does not apply any more, right? The examples have been 
-%removed now.
-%SJM: the example is gone, but the section remains
-&ays: it does remain, but it's so short it's not worth referring to
+\texttt{Map}.
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import map
->>> aiamap = map.Map('aia_file.fits')
+>>> import sunpy.map
+>>> aiamap = sunpy.map.Map('aia_file.fits')
 >>> aiamap.peek()
@@
 upon each other.
-\texttt{MapCube} 
-provides methods for animation of its series of \texttt{Map} objects. 
-Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to interact 
-with these classes.
-In addition, Listing~\ref{code:mapcube_2} shows how the \texttt{MapCube} 
-classes interact with the \texttt{matplotlib.animation} submodule to save a 
-video.
+\texttt{MapCube} provides methods for animation of its series of \texttt{Map} 
+objects. Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to 
+interact with these classes.
 
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import map
+>>> import sunpy.map
 >>> import matplotlib.pyplot as plt
->>> compmap = map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
+>>> compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
 ...                         composite=True)
@@
 
-%schriste - stuart, i agree if you want to remove the following two listings.
 \begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import map
->>> compmap = map.Map('aia_lev1_171a_2014_01*fits', cube=True)
->>> compmap.peek()
+>>> import sunpy.map
+>>> cubemap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> cubemap.peek()
 \end{minted}
@@
 \end{listing}
-
-\begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import map
->>> from matplotlib import animation
->>> mapc = map.Map('aia_lev1_171a_2014_01*fits', cube=True)
->>> anim = mapc.plot()
->>> Writer = animation.writers['ffmpeg']
->>> writer = Writer(fps=10, metadata=dict(artist='SunPy'), bitrate=1800)
->>> anim.save('aia_cube.ogv')
-\end{minted}
-% In the above example, is Writer, writer clear? 
-% Could we add more metadata to the movie? obs_date, instrument, etc...?
-\caption{Example showing how to save a video animation from a \texttt{MapCube} using 
-\texttt{matplotlib}'s animation framework.}
-\label{code:mapcube_2}
-\end{listing}
-% RJH: If this is kept, the 'artist' bit should be explained.

### 2014-01-30 2-Data_Types.tex
Changes mainly to the visualisation section

@@
 
-SunPy provides data strucutures that are specifically designed for the
+SunPy currently provides data strucutures that are specifically designed for the
 three primary varieties of solar physics data: images, time series, and
@@
 stored in the \texttt{data} attribute while the metadata should be stored 
-in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature fully implemented) 
+in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature 
+fully implemented.) 
 % schriste - can't we just quickly fix this? should be easy enough.
@@
 %SJM: oh what, drop it all together.
+%SJM see PR #785 to the main repo.
 It is possible to instantiate the
@@
 Data visualisation is provided by two functions: \texttt{peek()}, for quick 
-plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
-integrates with \texttt{matplotlib}.
+plotting, and \texttt{plot()}, for plotting with more fine-grained control.
 

### 2014-01-30 1-Introduction.tex

@@
 every discipline.  Solar physics is no exception to this trend. For example,
-NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched in February 2010,
-produces over 1 TB of data per day \citep{aia}. Managing and
-analysing this mountain of data
-requires increasingly sophisticated software tools.
-These tools should be robust, easy of use and modify, have a
-transparent development history, and conform
-to modern software engineering standards.  Software with these qualities provide a strong
-foundation and can support the needs of the community as data
-volumes grow and science questions evolve.
+NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched 
+in February 2010, produces over 1 TB of data per day \citep{aia}. Managing and
+analysing this mountain of data requires increasingly sophisticated software 
+tools.
+These tools should be robust, easy of use and modify, have a transparent 
+development history, as well as conforming to modern software engineering 
+standards.
+Software with these qualities provide a strong foundation which can support the 
+needs of the community as data volumes grow and science questions evolve.
 
-The SunPy project aims to provide a free, open-source and openly developed software package 
-for the analysis and visualisation of solar data. SunPy makes use of the Python 
-programming language and scientific Python packages. Python is a general-purpose,
-powerful and easy-to-learn high-level programming language.
+The SunPy project aims to provide a free, open-source and openly developed 
+software package for the analysis and visualisation of solar data. SunPy makes 
+use of the Python programming language and scientific Python packages. Python 
+is a general-purpose, powerful and easy-to-learn high-level programming 
+language.
 % RJH: Can we cut the next sentence?  It seems superfluous and top 10 is rather
@@
 %SJM: I think it should stay, it makes a point.
-According to the 2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+According to the 2014 TIOBE 
+Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
 it is one of the top ten most popular programming languages in the world 
-and is widely used outside of scientific fields in areas like web development, education 
-and `big data' analytics.
+and is widely used outside of scientific fields in areas like web development, 
+education and `big data' analytics.
 

### 2014-01-30 3-3-HELIO.tex

@@
 
-The HELiophysics Integrated Observatory (HELIO\footnote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
+The HELiophysics Integrated Observatory (HELIO\footnote{For more information 
+see \url{http://helio-vo.eu}{http://helio-vo.eu}}) has 
 compiled a list of web services which allows scientists to query and 

### 2014-01-30 3-Retrieval.tex

@@
 
-Several well-developed resources currently exist within heliophysics which provide  
-remote access and data retrieval for a large number of data sources as well as access to 
-event databases. As a community-based project, 
-SunPy provides support for these resources via the \texttt{net} subpackage. 
-In the following subsections, we describe a number of these resources and 
-how to use them in SunPy.
+Several well-developed resources currently exist which provide remote access to 
+and data retrieval form a large number of solar and heliospheric data sources 
+and event databases. SunPy provides support for these resources via the 
+\texttt{net} subpackage. In the following subsections, we describe a number of 
+these resources and how to use them in SunPy.
 

### 2014-01-30 abstract.tex

--- 2014-01-28 abstract.tex
@@
 \begin{abstract}
-This paper presents version 0.4 of SunPy a community developed Python package 
-for solar physics.
-
+This paper presents version 0.4 of SunPy, a community-developed Python package 
+for solar physics and data analysis.
+Python, a free, cross platform, general purpose, high-level programming 
+language, has seen widespread adoption among the scientific community resulting 
+in the availability of a large range of available software, from numerical 
+computation (NumPy, SciPy) and machine learning (scikit-learn) to spectral 
+analysis and visualisation (Matplotlib).
+SunPy is a data analysis toolkit specialising in providing the software 
+necessary to analyse solar and heliospheric datasets in Python. 
+SunPy is open source software (BSD licence) and has a open and transparent 
+development workflow that anyone can contribute to.
+SunPy provides access to solar data through integration with the Virtual 
+Solar Observatory (VSO), the the Heliophysics Event Knowledgebase (HEK) and the 
+HELIO webservices. It can open data files from major solar missions (e.g. 
+SDO, SOHO, STEREO and IRIS) into WCS-aware `Maps'. Time-series data from 
+mission such as GOES, SDO/EVE, and Proba2/LYRA into `LightCurves' and radio 
+spectra from e-Callisto or STEREO/SWAVES into `Spectrograms'. We present 
+examples of solar data analysis in SunPy, and show how Python-based solar 
+data-analysis can leverage the many existing data analysis tools already 
+available in Python. We discuss the future goals of the project and encourage 
+interested users to become involved in the planning and development of SunPy.
 \end{abstract}

### 2014-01-30 Summary.tex

\section{Summary}
We have presented the release of SunPy (v0.4), a Python package for solar physics. In
this paper we have described the main functionality which includes the SunPy data types, 
\texttt{Map} (see Section~\ref{ssec:map}), \texttt{Lightcurve} (see Section~\ref{ssec:lightcurve}), and \texttt{Spectrogram} (see Section~\ref{sec:spectra}).
We have described the data and event catalogue retrieval capabilities of SunPy for
the Virtual Solar Observatory (see Section~\ref{ssec:vso}), the Heliophysics Event Knowledgebase (see Section~\ref{ssec:hek}), as well as
the Heliophysics Integrated Observatory (see Section~\ref{ssec:helio}). We described
a new organization tool for data files integrated into SunPy (see Section~\ref{ssec:db}) 
and we discussed the community aspects, development model (see Section~\ref{sec:dev}), and future plans (see Section~\ref{{sec:future}}) for the project.
We invite members of community to contribute to the effort by using SunPy for their 
research, reporting bugs, sharing new functionality with the project.

### 2014-01-30 2-1-Map.tex
made map example more useful

@@
 >>> aiamap = sunpy.map.Map('aia_file.fits')
->>> aiamap.peek()
+>>> smap = aiamap.submap( [-1200, -200], [-1000, -0] )
+>>> aiamap.peek(draw_limb = True)
 \end{minted}
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file,
-and a quick-view plot is created.}
+\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a sub range
+of the map is created and then a quick-view plot is created with heliographic coordinates over-plotted.}
 \label{code:aia_1}

### 2014-01-30 2-1-Map.tex
fixed bug

@@
 >>> smap = aiamap.submap( [-1200, -200], [-1000, -0] )
->>> aiamap.peek(draw_limb = True)
+>>> smap.peek(draw_limb = True)
 \end{minted}

### 2014-01-30 2-1-Map.tex
small reword

@@
 \texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a sub range
-of the map is created and then a quick-view plot is created with heliographic coordinates over-plotted.}
+of the map is created and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}

### 2014-01-30 2-1-Map.tex
small fix

@@
 >>> smap = aiamap.submap( [-1200, -200], [-1000, -0] )
->>> smap.peek(draw_limb = True)
+>>> smap.peek(draw_grid = True)
 \end{minted}

### 2014-01-30 2-1-Map.tex
pep8 fix

@@
 >>> aiamap = sunpy.map.Map('aia_file.fits')
->>> smap = aiamap.submap( [-1200, -200], [-1000, -0] )
->>> smap.peek(draw_grid = True)
+>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
+>>> smap.peek(draw_grid=True)
 \end{minted}

### 2014-01-30 2-1-Map.tex
albert sucks

@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a sub range
+\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a sub-range
 of the map is created and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}

### 2014-01-30 2-1-Map.tex
everyone sucks

@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a sub-range
+\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
 of the map is created and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}

### 2014-01-30 1-Introduction.tex
edit to introduction

@@
 %SJM: I think it should stay, it makes a point.
-According to the 2014 TIOBE 
-Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
-it is one of the top ten most popular programming languages in the world 
-and is widely used outside of scientific fields in areas like web development, 
+%According to the 2014 TIOBE 
+%Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
+%it is one of the top ten most popular programming languages in the world 
+%removed until better reference is found for this statistic.
+Python is widely used outside of scientific fields in areas like web development, 
 education and `big data' analytics.

### 2014-01-30 1-Introduction.tex
removed ack

@@
 project, and future plans. The latest release of SunPy, version 0.4,
-can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be
-installed using the \href{http://pypi.python.org/pypi}{Python package index}.
+can be downloaded from \url{http://sunpy.org} or can be
+installed using the Python package index (\url{http://pypi.python.org/pypi}).

### 2014-01-30 2-2-Lightcurve.tex
added lines to GOES lightcurve code example
more updates to GOES lightcurve code block.
removed ack

@@
 Currently, the \texttt{LightCurve} class is compatible with the
-following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and
-the \textit{SDO} EUV Variability Experiment (EVE; only the level ``OCS'' and
-% Do we need to explain what OCS means?
-% RJH: I'd argue that everything other than (EVE) can be cut, but I'm not 
-% confident enough to make that cut.
-% dps: I agree, JI, what do you think?
-average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
-for more detail).  For each of these instruments, a subclass of the
+following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
+average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
 \texttt{LightCurve} object is initialised
@@
 
-%removed the resample part of the example - really we need to fix truncate!
-% schriste - i think it would be better to show off some of the powerful pandas methods in this section
-% as we are not likely to fix truncate and i think it should be refactored anyway
-%ays: moved these comments outside of the listing in case we forget to delete these
 \begin{listing}[H]

### 2014-01-30 2-Data_Types.tex
removed ack

@@
 stored in the \texttt{data} attribute while the metadata should be stored 
-in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature 
-fully implemented.) 
-% schriste - can't we just quickly fix this? should be easy enough.
-% dps - Spectrogram does not contain meta either! I would suggest
-%(Curently, this is just supported by Map, but the other data types will 
-%include such attribute soon.)
-%SJM: oh what, drop it all together.
-%SJM see PR #785 to the main repo.
+in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
+fully implemented). 
+% schriste - change this until all fixed
 It is possible to instantiate the
 data types from various
-different sources: e.g., files, URLs, arrays.  
+different sources: e.g., files, URLs and arrays.  
 In order to provide instrument-specific specialisation, the core SunPy classes 

### 2014-01-30 3-1-VSO.tex
arg closed in VSO

@@
 \texttt{suds} package.
-This module was developed under the European Space Agency's Summer of Code in 
-Space (ESA's SOCIS) of 2011.
 
-%ays: commented this out because it's not developed at all
-%The \texttt{vso} module has two query interfaces implemented.
 Listing~\ref{code:vso_query_simple} shows an example of how to query the VSO
@@
 
-%schriste - what about just listing the sources as an array to instead of doing a show
-%           to make the point that the | query worked appropriately? That would make this
-%            listing much shorter.
-%Stuart: I suggest removing the second query from here, it dosen't add much.
-%dps: Stuart, do you mean the second listing, or the wavelength bit of this one?
-%SJM: The wavelength bit of this one.
-%ays: I removed the first one instead!  Ha ha!
 \begin{listing}[H]
 \begin{minted}[bgcolor=bg]{pycon}
-#Querying two wavelength ranges over the same time range
 >>> condition = (vso.attrs.Detector('cor1') |

### 2014-01-30 3-2-HEK.tex
HEK section

@@
 two letter strings, and are 
-identical to the two letter abbreviations found at the HEK website,
-%\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
-% schriste - above line causes an error, can't figure out why
+identical to the two letter abbreviations found at the HEK website
+(\url{http://www.lmsal.com/hek/VOEvent_Spec.html}).
 
@@
 the construction of queries of almost arbitrary complexity.
-The results of a HEK query can be used to download the 
-corresponding data from the VSO using SunPy's \texttt{H2VClient}.
+%The results of a HEK query can be used to download the 
+%corresponding data from the VSO using SunPy's \texttt{H2VClient}.
 %schriste - this is a weird way to end this section, either show how it is done or 
@@
 %ays: hmm, still nothing?
+% removed sentence until it is fixed.

### 2014-01-30 acknowledgements.tex
Add an acknowledgements section

\section{Acknowledgements}
Many of the larger features in SunPy have been developed with external support. 
Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
Summer of Code In Space (SOCIS) program, as well as a prototyped GUI and 
N-Dimensional datatype implementations. In 2013 with support from Google's 
Summer Of Code (GSOC) program, through the 
\href{http://www.python.org/psf/}{Python Software Foundation} (PSF), the 
\texttt{helio}, \texttt{hek2vso} and \texttt{database} subpackages were 
developed.The Spectra and Spectrogram classes were implemented with support 
from by the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
2012.

### 2014-01-30 2-2-Lightcurve.tex
udpate to Intro

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the {\texttt{pandas}} data-analysis library (\href{http://pandas.pydata.org}{http://pandas.pydata.org}), and 
+the {\texttt{pandas}} data-analysis library, and 
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
-object.
-The \texttt{pandas} library contains a large amount
+object. The \texttt{pandas} library contains a large amount
 of functionality for manipulating and analysing time-series data,
-making it an ideal basis for \texttt{LightCurve}.  \texttt{LightCurve}
+making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
 assumes that the input data are time-ordered list(s) of numbers, and each

### 2014-01-30 3-4-Helioviewer.tex
Resize png image in Helioviewer

@@
 \begin{center}
-\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example}
+\includegraphics[width=0.6\columnwidth]{helioviewer_overlay_example}
 \end{center}
@@
 \begin{minted}[bgcolor=bg]{pycon}
+>>> import sunpy.map
 >>> filepath = hv.download_jp2('2012/07/05 00:30:00',
@@
 ...                            measurement='continuum')
->>> from sunpy import map
->>> map.Map(filepath).submap([200,550],[-400,-200]).peek()
+>>> sunpy.map.Map(filepath).submap([200,550],[-400,-200]).peek()
 \end{minted}

### 2014-01-30 3-2-HEK.tex
removed orphan sentence
all hail the SSW overlords

--- 2014-01-30 3-2-HEK.tex
@@
 The results of a HEK query can be used to download the 
-corresponding data from the VSO using SunPy's \texttt{H2VClient}.
-%schriste - this is a weird way to end this section, either show how it is done or 
-% do not mention it, i think.
-%dps - I agree.
-%JI - I agree
-%Stuart: Will do on my next pass
-%ays: hmm, still nothing?
+corresponding data from the VSO using SunPy's \texttt{H2VClient}, as 
+demonstrated in Listing~\ref{code:hek2vso}
+\begin{listing}[H]
+\begin{minted}[bgcolor=bg]{python}
+>>> from sunpy.net import hek2vso
+>>> h2v = hek2vso.H2VClient()
+>>> vso_results = h2v.translate_and_query(result[0])
+>>> h2v.vso_client.get(vso_results[0]).wait()
+\end{minted}
+\caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 
+query and download of data from the first HEK result from the VSO.}
+\label{code:hek2vso}
+\end{listing}

### 2014-01-30 acknowledgements.tex
all hail the SSW overlords

@@
 N-Dimensional datatype implementations. In 2013 with support from Google's 
-Summer Of Code (GSOC) program, through the 
-\href{http://www.python.org/psf/}{Python Software Foundation} (PSF), the 
+Summer Of Code (GSOC) program, through the Python Software Foundation, the 
 \texttt{helio}, \texttt{hek2vso} and \texttt{database} subpackages were 
 developed.The Spectra and Spectrogram classes were implemented with support 
-from by the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
+from the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
 2012.

### 2014-01-30 1-Introduction.tex

@@
 Science is driven by the analysis of data of growing variety and complexity.
-Modern advances in sensor
-technology, combined with the availability of inexpensive storage, has led to
-rapid increases in the amount of data available to scientists in almost
+Modern advances in sensor technology, combined with the availability of inexpensive 
+storage, has led to rapid increases in the amount of data available to scientists in almost
 every discipline.  Solar physics is no exception to this trend. For example,
@@
 analysing this mountain of data requires increasingly sophisticated software
-tools.
-These tools should be robust, easy of use and modify, have a transparent 
+tools. These tools should be robust, easy to use and modify, have a transparent
 development history, as well as conforming to modern software engineering
-standards.
-Software with these qualities provide a strong foundation which can support the 
+standards. Software with these qualities provide a strong foundation which can support the
 needs of the community as data volumes grow and science questions evolve.
@@
 software package for the analysis and visualisation of solar data. SunPy makes
-use of the Python programming language and scientific Python packages. Python 
-is a general-purpose, powerful and easy-to-learn high-level programming 
-language.
-% RJH: Can we cut the next sentence?  It seems superfluous and top 10 is rather
-% meaningless.
-% schriste - i think it's important. it contrasts nicely with IDL and its tiny 
-%community.
-%SJM: I think it should stay, it makes a point.
-%According to the 2014 TIOBE 
-%Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
-%it is one of the top ten most popular programming languages in the world 
-%removed until better reference is found for this statistic.
-Python is widely used outside of scientific fields in areas like web development, 
-education and `big data' analytics.
+use of Python and scientific Python packages. Python is a free, general-purpose, 
+powerful and easy-to-learn high-level programming language. Additionally, Python is 
+widely used outside of scientific fields in areas like `big data' analytics, web 
+development and in educational environments. For example, \texttt{pandas} was 
+originally developed for quantitative analysis of financial data and has since 
+grown into a generalised time-series data-analysis package. Python continues to 
+see increased use in the astronomy community \citep{greenfield2011}, which has 
+similar goals and requirements as the solar physics community. Finally, Python 
+integrates well with many technologies such as web servers \citep{dolgert2008} and databases.
 
-The development of a package such as SunPy is made possible by the 
-rich ecosystem of scientific packages available in Python. Core packages such 
-as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
-provide the basic functionality expected of a scientific programming language:
-e.g., array manipulation, core numerical algorithms and visualisation. 
+The development of a package such as SunPy is made possible by the rich ecosystem of 
+scientific packages available in Python. Core packages such as \texttt{NumPy}, 
+\texttt{SciPy} and \texttt{matplotlib} provide the basic functionality expected of a 
+scientific programming language,
+such as array manipulation, core numerical algorithms, and visualisation.
 Building upon these foundations, packages such as \texttt{astropy}, \texttt{pandas} and
@@
 
-SunPy is designed to be a clean, simple-to-use, and well-structured 
-package that provides the \textit{core} tools for solar data analysis. 
-The primary focus of SunPy's early development are 
-specialised data types that enable the acquisition, processing and 
-visualisation of all types of solar data.
+SunPy is designed to be a clean, simple-to-use, and well-structured package that provides 
+the \textit{core} tools for solar data analysis, motivated by the need for a free and 
+modern alternative to the existing SolarSoft (SSW) library. While SSW is open source 
+and freely available, it relies on IDL (Interactive Data Language), a proprietary 
+data-analysis environment.
 

### 2014-01-30 3-3-HELIO.tex

@@
 SunPy's \texttt{hec} module provides an interface to the
-\textit{HELIO Event Catalogue} (HEC) service. 
-%schriste - why is this italics?
+HELIO Event Catalogue (HEC) service. 
 This module was developed as
@@
 \end{listing}
-
-In the future, additional HELIO services will be supported by SunPy, aiming for
-seamless interaction between the other services and tools available (e.g., 
-\texttt{hek}, \texttt{map}).  
-% RJH: This sentence is an orphan and should have a home constructed for it.
-% schriste - it also contains too much future sauce
-% better? or this should be in the future section?
-% JI - moved bit about HELIO overplotting to Future.tex.  Might want to have
-% a bit in the future section about other net services.

### 2014-01-30 4-Util.tex

@@
 briefly describes some of these functions.
-
-%Two modules are described in this Section, namely, solar coordinates (WCS), and 
-%the Sun module.
 
@@
 
-%ays: I removed this as a separate subsection because constants is part of sun...
-%\subsubsection{constants}\label{ssec:util:const}
 The \texttt{sun.constants} module provides a number of solar-related 
@@
 >>> from sunpy.sun import constants
->>> print(sun.mass)
+>>> print(constants.mass)
   Name   = Solar mass

### 2014-01-30 5-Dev.tex

--- 2014-01-30 5-Dev.tex
@@
 SunPy's development makes use of the online service 
-\href{http://github.com}{GitHub} and \href{http://git-scm.com/}{Git}
+GitHub (\url{http://github.com}) and Git\footnote{For more information see \url{http://git-scm.com/}}
 as its distributed version control software.
@@
 transparent and collaborative development workflow made possible by GitHub is used.
-% JI - I don't think we need a description of what is essentially how a project works
-% when you use git and github.  There is nothing SunPy specific about this.
 The following conditions typically must be met before code is accepted.
@@
 
-	\item The code must contain significant unit-test coverage.
+	\item The code must contain unit tests to verify that the code is behaving 
+	as expected.
 
@@
 
-Additionally, SunPy makes use of `continuous integration' provided by
-\href{http://travis-ci.org}{Travis CI}, a process by which the addition of any new code 
-automatically triggers a comprehensive review of written unit tests. If any single test
-fails, the community is alerted before the code is accepted. The unit test coverage is
-also monitored by the \href{http://coveralls.io}{Coveralls} service.
-% JI - what is the coveralls service?
+Additionally, SunPy makes use of `continuous integration' provided by Travis CI (\url{http://travis-ci.org}), a process by which the addition of any new code 
+automatically triggers a comprehensive review of the code functionality which are maintained as unit tests.
+ If any single test
+fails, the community is alerted before the code is accepted. The unit-test coverage is monitored by
+a service called Coveralls (\url{http://coveralls.io}).
 
@@
 Powerful tools already exist in Python to support documentation, thanks to native
-Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
+Python's focus on its own documentation. SunPy makes use of the Sphinx (\url{http://sphinx-doc.org})
 documentation generator. Sphinx uses reStructuredText as its markup language, which is
@@
 hierarchically structured view of in-code documentation strings. The SunPy documentation 
-is built automatically and is hosted by \href{http://readthedocs.org}{Read the 
-Docs} at \url{http://docs.sunpy.org}.
+is built automatically and is hosted by Read-the 
+-Docs (\url{http://readthedocs.org}) at \url{http://docs.sunpy.org}.
 
@@
 room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
-developer comments or discussions, a open mailing list is hosted on Google Groups. 
+developer comments or discussions, an open mailing list is hosted by Google Groups. 
 Bug tracking, code reviews, and feature-request discussions take place directly on GitHub.
@@
 meetings.
-% RJH: do we want to list both the community and dev lists?
-
-% RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
-% schriste - we had agreed to only refer to the support in one place. we need 
-%to agree as to where
-% SJM: Drop the bits in the code
-Many of the larger features in SunPy have been developed 
-with the support of both the ESA-SOCIS and GSOC. 
-Initial development of SunPy's VSO and HEK 
-implementations were funded by the SOCIS program as well as a prototyped GUI 
-and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
-through the \href{http://www.python.org/psf/}{Python Software Foundation} (PSF). It supported development of the 
-\texttt{helio} and 
-\texttt{database} subpackages.
-
-%JI The section ``Development workflow'' is unnecessary IMHO.  This is
-% largely a description of how git and github works.  It is not about sunpy. So I have
-% deleted it.

### 2014-01-30 authors.tex

--- 2014-01-30 authors.tex
@@
 David P\'erez-Su\'arez$^3$,
+Jack Ireland$^{2,4}$,
+Albert Y Shih$^2$,
 Andrew R Inglis$^{2,5}$,
-Jack Ireland$^{6}$,
-Albert Y Shih$^2$,
-Simon Liedtke$^{11}$,
-Russell J Hewett$^8$, %88
+Simon Liedtke$^{6}$,
+Russell J Hewett$^7$, %88
 % Contributors to SunPy Sorted thus:
@@
 % Date of most recent contribution
-Florian Mayer$^{12}$, %721
-Keith Hughitt$^4$, %446
+Florian Mayer$^{8}$, %721
+Keith Hughitt$^9$, %446
 Nabil Freij$^1$, %52
-Matthew Earnshaw, %52
 Tomas Meszaros$^{10}$, %17
-N Chorley, %17
 Samuel M Bennett$^1$, %14
-M Malocha, %10
-John Evans, %10 %No affil
-Ankit Agrawal$^{15}$, %8
-M Bates, %6
-Andrew J Leonard$^7$, %3
-J Ballew, %3
-Thomas P Robitaille$^9$, %2
-Benjamin Mampaey$^{13}$, %2
-Jose Iv\'an Campos-Rozo$^{14}$, %1
-Michael S. Kirk$^{2}$
-and 
-A Kustov %1
+Michael Malocha$^{11}$, %10
+John Evans$^{12}$,%10 %No affil
+Ankit Agrawal$^{13}$, %8
+Andrew J Leonard$^{14}$, %3
+Thomas P Robitaille$^{15}$, %2
+Benjamin Mampaey$^{16}$, %2
+Jose Iv\'an Campos-Rozo$^{17}$, %1
+and Michael S Kirk$^{2}$
 }
@@
 School of Mathematics and Statistics, The University of Sheffield, Hicks 
-Building, Hounsfield Road, Sheffield, S3 7RH U.K.
+Building, Hounsfield Road, Sheffield, S3 7RH, UK
 
@@
 
-$^4$Department of Cell Biology and Molecular Genetics, University of Maryland, College Park
+$^4$ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space Flight Center, 
+Greenbelt, MD, USA
 
@@
 
-$^6$ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space Flight Center, 
-Greenbelt, MD, USA
+$^{6}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany
 
-$^7$Department of Mathematics and Physics, Aberystwyth University, 
-Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ
+$^7$Department of Mathematics, Massachusetts Institute of Technology, 77 
+Massachusetts Ave, E17-317, Cambridge, MA, USA
 
-$^8$Department of Mathematics, Massachusetts Institute of Technology, 77 
-Massachusetts Ave, E17-317, Cambridge, MA 02142
+$^{8}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
 
-$^9$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
+$^9$Department of Cell Biology and Molecular Genetics, University of Maryland, College Park, MD, USA
+
+$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno, Czech Republic
+
+$^{11}$ Humboldt State University, 1 Harpst St, Arcata, CA, USA
+
+$^{12}$ Boston Python User Group, Boston, MA, USA
+
+$^{13}$ Indian Institute of Technology, Bombay, India
+
+$^{14}$Department of Mathematics and Physics, Aberystwyth University, 
+Physical Sciences Building, Aberystwyth, SY23 3BZ, UK
+
+$^{15}$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
 69117, Germany
 
-$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno
+$^{16}$ Royal Observatory of Belgium, Brussels, Belgium
 
-$^{11}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany
-
-$^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
-
-$^{13}$ Royal Observatory of Belgium
-
-$^{14}$ Observatorio Astronómico Nacional Universidad Nacional de Colombia 
+$^{17}$ Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
 Bogotá, D.C., Colombia
 
-$^{15}$ Indian Institute of Technology, Bombay
 }

### 2014-01-31 authors.tex

@@
 \address{
-$^1$ Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
+$^1$Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
 School of Mathematics and Statistics, The University of Sheffield, Hicks 
@@
 
-$^5$ The Catholic University of America, Washington, DC, USA
+$^5$The Catholic University of America, Washington, DC, USA
 
-$^{6}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany
+$^{6}$University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany
 
@@
 
-$^{8}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
+$^{8}$Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
 
@@
 
-$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno, Czech Republic
+$^{10}$Masaryk University, Faculty of Informatics, Botanicka 68a Brno, Czech Republic
 
-$^{11}$ Humboldt State University, 1 Harpst St, Arcata, CA, USA
+$^{11}$Humboldt State University, 1 Harpst St, Arcata, CA, USA
 
-$^{12}$ Boston Python User Group, Boston, MA, USA
+$^{12}$Boston Python User Group, Boston, MA, USA
 
-$^{13}$ Indian Institute of Technology, Bombay, India
+$^{13}$Indian Institute of Technology, Bombay, India
 
@@
 
-$^{15}$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
+$^{15}$Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
 69117, Germany
 
-$^{16}$ Royal Observatory of Belgium, Brussels, Belgium
+$^{16}$Royal Observatory of Belgium, Brussels, Belgium
 
-$^{17}$ Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
+$^{17}$Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
 Bogotá, D.C., Colombia

### 2014-01-31 2-1-Map.tex
resolved argument
removed ack
Lots of minor edits

@@
 The map data type stores 2D spatial data, such as images of the Sun and 
-inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array; 
-the images associated spatial coordinates; and other metadata. The \texttt{Map} 
+inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array, 
+the images associated spatial coordinates, and other metadata. The \texttt{Map} 
 class provides methods for typical operations on 2D data, such as rotation and 
@@
 with the \texttt{Map} creation factory, which will then automatically return an instance
-of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
+of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
 SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
@@
 and \textit{IRIS} SJI frames.
-% RJH: Instruments should be consistent throughout (italics, caps, etc).  Also,
-% usually citations are provided for instruments.
-% dps: I would agree to add the citations if we were using the instrument in 
-% the paper, but I don't think this is the case here.
 
@@
 \texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
-of the map is created and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
+of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}
@@
 
-In addition to the data-type classes, the \texttt{map} sub-package provides two 
+In addition to the data-type classes, the \texttt{map} subpackage provides two 
 collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 

### 2014-01-31 2-2-Lightcurve.tex
Lots of minor edits

@@
 
-Time series data and their analyses are a fundamental aspect of solar
+Time series data and their analyses are a fundamental part of solar
 physics for which many data sources are available.
@@
 (e.g., \texttt{GOESLightCurve}) which inherits from
-\texttt{LightCurve} but allows instrument-specific functionality to be
+\texttt{LightCurve}, but allows instrument-specific functionality to be
 included.  Future developments will introduce support for additional
@@
 as to how time-series data should be stored and distributed, each SunPy 
-\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
+\texttt{LightCurve} object subclass provides the ability to download its corresponding 
 specific data format in its constructor and parse that file type.
@@
 the \texttt{LightCurve} constructor searches a remote source for the GOES X-ray 
-data specified by the time interval, downloads the required files and 
+data specified by the time interval, downloads the required files, and 
 subsequently creates and plots the object.
@@
 \caption{Example retrieval of a GOES lightcurve
-using a time range, and the output of the 
+using a time range and the output of the 
 \texttt{peek()} method.}
@@
 Alternatively, if the data file already exists on the local system, the 
-\texttt{Lightcurve} object may instead be initialised using that file as input.
-Once the \texttt{Lightcurve} has been created, it may be manipulated in 
+\texttt{LightCurve} object may instead be initialised using that file as input.
+Once the \texttt{LightCurve} object has been created, it may be manipulated in 
 a variety of ways in order to perform time-series analysis.

### 2014-01-31 2-3-Spectra.tex
Lots of minor edits

@@
 \texttt{Spectrogram} class for 2D data (intensity as a function of time and
-frequency).  Each of these classes use a \texttt{numpy.ndarray} object
-as its \texttt{data} attribute.  These two classes were implemented
-with support from by the Astrophysics Research Group at Trinity
-College Dublin, Ireland.
-% schriste - is this necessary? surely we don't need to thank all of our employers
+frequency).  Each of these classes uses a \texttt{numpy.ndarray} object
+as its \texttt{data} attribute.
 
@@
 \caption{Example of how \texttt{CallistoSpectrogram} retrieves the
-  data for the requested time range and observatory, merges it and
+  data for the requested time range and observatory, merges it, and
   removes the background signal.  The data requested -- `BIR' -- is

### 2014-01-31 3-3-HELIO.tex
Lots of minor edits

@@
 
-The HELiophysics Integrated Observatory (HELIO\footnote{For more information 
-see \url{http://helio-vo.eu}{http://helio-vo.eu}}) has 
+The HELiophysics Integrated Observatory (HELIO)\footnote{For more information 
+see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
 compiled a list of web services which allows scientists to query and 
@@
 which allows scientists to search different catalogues of registered events, 
-solar features, data from instruments in the heliosphere and other information 
+solar features, data from instruments in the heliosphere, and other information 
 such as planetary or spacecraft position in time. 

### 2014-01-31 4-Util.tex
Lots of minor edits

@@
 data analysis workflow. Likely the most often used transformation is from 
-observer coordinates (e.g., sky coordinates) to a coordinate system which is 
+observer coordinates (e.g., sky coordinates) to a coordinate system that is 
 mapped onto the solar surface (e.g., latitude and longitude). This 
@@
 coordinates package. The \texttt{wcs} package in SunPy implements the World Coordinate 
-System (WCS) for solar coordinates as described by \citep{thompson2006}. The 
+System (WCS) for solar coordinates as described by \cite{thompson2006}. The 
 transformations currently implemented are those most useful 
@@
 (de-projected) physical distances instead of angles on the celestial sphere.
-These transformations require some knowledge of the location of the observer 
-which is usually provided by the image header. In the case where it is 
-not, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
+These transformations require some knowledge of the location of the observer, 
+which is usually provided by the image header. In the cases where it is 
+not provided, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
 some examples of coordinate transforms carried out in SunPy using the 
@@
 >>> from sunpy import wcs
->>> wcs.convert_hg_hpc(10,53)
+>>> wcs.convert_hg_hpc(10, 53)
 (100.49244115330731, 767.97438321917502)
@@
 # Try to convert a position which is not on the Sun to HG
->>> wcs.convert_hpc_hg(-1500,0)
+>>> wcs.convert_hpc_hg(-1500, 0)
 sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
@@
 Convert sky coordinate to a position in HCC
->>> wcs.convert_hpc_hcc(-300,400, z = True)
+>>> wcs.convert_hpc_hcc(-300, 400, z=True)
 (-216716967.63331246, 288956420.9477042, 594364636.2208252)
@@
 The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
-solar constants. The main namespace contains a number of functions which provide solar
-ephemerides such as the Sun to Earth distance, solar-cycle number, the mean 
+solar constants. The main namespace contains a number of functions that provide solar
+ephemerides such as the Sun-to-Earth distance, solar-cycle number, the mean 
 anomaly, etc.
-All of these functions take a time as their input which can be provided in a format
+All of these functions take a time as their input, which can be provided in a format
 compatible with \texttt{sunpy.time.parse\_time()}. 
@@
 constants in order to provide consistency in the calculations of derived solar 
-values both within the SunPy code base but also to the user. Every solar 
+values  within the SunPy code base, but also to the user. Every solar 
 constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
 \texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
-the constant's provenance (i.e., reference) as well as its uncertainty. Using 
-Astropy's {Quantity} objects, any solar constant can easily be converted between 
-different units as can be seen in Listing~\ref{code:constants_code} as well
-as between the SI or cgs unit systems with a single command.  As these objects inherit from 
+the constant's provenance (i.e., reference) and its uncertainty. Using 
+Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
+different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
+As these objects inherit from 
 NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
-For convenience a number of shortcuts to frequently used constants are provided 
+For convenience, a number of shortcuts to frequently used constants are provided 
 directly when importing the module. A larger list of constants can be 
@@
 In addition to providing support for instrument-specific solar data via the main data 
-classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, 
+classes \texttt{Map}, \texttt{LightCurve}, and \texttt{Spectrum}, 
 some instrument-specific functions may be found within the \texttt{instr} subpackage. 
@@
  will include support for additional missions. Ultimately, it is anticipated that solar
-  missions requiring a large suite of software tools will be supported via a separately 
+  missions requiring a large suite of software tools will each be supported via a separately 
   maintained package that is affiliated with SunPy.

### 2014-01-31 5-Dev.tex
Lots of minor edits

@@
 three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
-active community \citep{bangerth2013}. Several tools (some specific to Python) are used by
+active community \citep{bangerth2013}. Several tools, some specific to Python, are used by
 SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
@@
 hierarchically structured view of in-code documentation strings. The SunPy documentation 
-is built automatically and is hosted by Read-the 
--Docs (\url{http://readthedocs.org}) at \url{http://docs.sunpy.org}.
+is built automatically and is hosted by Read-the-Docs (\url{http://readthedocs.org})
+at \url{http://docs.sunpy.org}.
 
@@
 The SunPy community also reaches out to the wider solar physics
-community through presentations, functionality demonstrations and informal meetups at scientific
+community through presentations, functionality demonstrations, and informal meetups at scientific
 meetings.

### 2014-01-31 1-Introduction.tex

@@
 tools. These tools should be robust, easy to use and modify, have a transparent
-development history, as well as conforming to modern software engineering
-standards. Software with these qualities provide a strong foundation which can support the
+development history, and conform to modern software-engineering
+standards. Software with these qualities provide a strong foundation that can support the
 needs of the community as data volumes grow and science questions evolve.
 
-The SunPy project aims to provide a free, open-source and openly developed
+The SunPy project aims to provide a free, open-source, and openly developed
 software package for the analysis and visualisation of solar data. SunPy makes
 use of Python and scientific Python packages. Python is a free, general-purpose, 
-powerful and easy-to-learn high-level programming language. Additionally, Python is 
+powerful, and easy-to-learn high-level programming language. Additionally, Python is 
 widely used outside of scientific fields in areas like `big data' analytics, web 
-development and in educational environments. For example, \texttt{pandas} was 
+development, and educational environments. For example, \texttt{pandas} was 
 originally developed for quantitative analysis of financial data and has since 
@@
 scientific packages available in Python. Core packages such as \texttt{NumPy}, 
-\texttt{SciPy} and \texttt{matplotlib} provide the basic functionality expected of a 
+\texttt{SciPy}, and \texttt{matplotlib} provide the basic functionality expected of a 
 scientific programming language,
 such as array manipulation, core numerical algorithms, and visualisation.
-Building upon these foundations, packages such as \texttt{astropy}, \texttt{pandas} and
+Building upon these foundations, packages such as \texttt{astropy}, \texttt{pandas}, and
 \texttt{scikit-image} provide more domain-specific functionality.

### 2014-01-31 2-Data_Types.tex

@@
 spectra. These core data types are supported by SunPy's classes:
-\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
+\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
 and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).
@@
 enable analysis and visualisation. For each of these classes, the data is
-stored in the \texttt{data} attribute while the metadata should be stored 
+stored in the \texttt{data} attribute, while the metadata should be stored 
 in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
@@
 data types from various
-different sources: e.g., files, URLs and arrays.  
+different sources: e.g., files, URLs, and arrays.  
 In order to provide instrument-specific specialisation, the core SunPy classes 
@@
 These visualisation methods all currently utilise the \texttt{matplotlib} 
-package, and are designed in such a way that they integrate well with 
+package and are designed in such a way that they integrate well with 
 the \texttt{pyplot} functional interface of \texttt{matplotlib}.
@@
 interface, as well as allowing the use of the standard 
-\texttt{matplotlib} commands to manipulate the plot parameters (e.g. title, axes).
+\texttt{matplotlib} commands to manipulate the plot parameters (e.g., title, axes).
 Data visualisation is provided by two functions: \texttt{peek()}, for quick 

### 2014-01-31 3-2-HEK.tex

@@
 The Sun is an active star and exhibits a wide range of transient phenomena 
-(e.g., flares, radio bursts) on many different time-scales, length-scales and 
+(e.g., flares, radio bursts) on many different time-scales, length-scales, and 
 wavelengths. Observations and metadata concerning these phenomena are collected 
@@
 (Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
-two letter strings, and are 
+two letter strings, and these strings are 
 identical to the two letter abbreviations found at the HEK website
@@
 The module \texttt{hek.attrs} contains attributes of the HEK that can be used to
-construct HEK queries.  For example, a flare is an attribute of the HEK, and so 
-instead of specifying \texttt{hek.attrs.EventType('FL')} as in Listing 
-\ref{code:hek:simple}, this can also be expressed as \texttt{hek.attrs.FL}.
+construct HEK queries.  For example, a flare is an attribute of the HEK,
+ and so 
+\texttt{hek.attrs.EventType('FL')} in Listing~\ref{code:hek:simple}
+can be alternatively replaced with \texttt{hek.attrs.FL}.
 
@@
 Example in Listing~\ref{code:hek:frm} filters the results of the previous 
-result to return only those events that have the FRM 'SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
+result to return only those events that have the FRM `SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
 conditions on the attributes in the call to the HEK query method.
@@
 \caption{An HEK query that returns only those flares that were
-  detected by the 'SSW Latest Events' feature recognition method.}
+  detected by the `SSW Latest Events' feature recognition method.}
 \label{code:hek:frm}
@@
 corresponding data from the VSO using SunPy's \texttt{H2VClient}, as 
-demonstrated in Listing~\ref{code:hek2vso}
+demonstrated in Listing~\ref{code:hek2vso}.
 \begin{listing}[H]

### 2014-01-31 3-4-Helioviewer.tex

@@
 JPEG2000 files are typically highly compressed compared to the source
-FITS files they are generated from but high-fidelity, and thus can be used to quickly
+FITS files from which they are generated, but are still high-fidelity, and thus can be used to quickly
 visualise large amounts of data from multiple sources.  SunPy is
@@
 file.  SunPy accesses this overlay/composition capability through the
-\texttt{download\_png} method of the Helioviewer client.  Listing
-\ref{code:hv:overlaid} gives an example of the composition of three
-separate image layers in to a single image.
+\texttt{download\_png()} method of the Helioviewer client.  Listing~\ref{code:hv:overlaid}
+gives an example of the composition of three
+separate image layers into a single image.
 
@@
 
-The first argument is the requested time of the image.  Helioviewer
+The first argument is the requested time of the image, and Helioviewer
 selects images closest to the requested time.  In this case, the
@@
 $\rightarrow$ instrument $\rightarrow$ detector $\rightarrow$
-measurement combination described above, along with the final two
-numbers that denote the visibility and the opacity of the image layer
-respectively (1/0 is visible/invisible with opacity in the range
+measurement combination described above, along with two following
+numbers that denote the visibility and the opacity of the image layer,
+respectively (1/0 is visible/invisible, and opacity is in the range
 $0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
@@
 other pieces of software. The first, 
-\href{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open
-source library for reading and writing JPEG2000 files.  The other package 
+\href{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open-source
+library for reading and writing JPEG2000 files.  The other package 
 required is 
@@
 
-Listing \ref{code:downloadjp2} demonstrates the querying, downloading,
+Listing~\ref{code:downloadjp2} demonstrates the querying, downloading,
 reading and conversion of a Helioviewer JPEG2000 file into a SunPy map
@@
 Helioviewer-supplied image data in an identical fashion to a SunPy \texttt{Map}
-object generated from FITS data (see Section \ref{ssec:map}).
+object generated from FITS data (see Section~\ref{ssec:map}).
 
@@
 ...                            measurement='continuum')
->>> sunpy.map.Map(filepath).submap([200,550],[-400,-200]).peek()
+>>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()
 \end{minted}

### 2014-01-31 3-5-Database.tex

@@
 in local storage such as laptops and desktop computers. Keeping data organised and available
-is typically a cumbersome task for the average user. The file database is a sub-package of 
-SunPy which is meant to solve this problem by providing a unified database to store and 
-manage information about local data files. The database package was developed with support from 
-the Google Summer of Code (GSoC) program 2013.
+is typically a cumbersome task for the average user. The file database is a subpackage of 
+SunPy that addresses this problem by providing a unified database to store and 
+manage information about local data files.
 
@@
 since it supports many SQL dialects. 
-If SQLite is selected, the database is stored as a single file which is
+If SQLite is selected, the database is stored as a single file, which is
 created automatically. A server-based database, on the other hand, could be used
@@
 interactive sessions to easily revert accidental operations. 
-This feature will also be desirable when creating a GUI frontend for this package.
-%JI - revert accidental operations of any kind?
+This feature will also be desirable for a planned GUI frontend for this package.
 
@@
 2  2012-08-05 00:00:02    33.5    33.5
-%schriste - need to add back in the other entries that i deleted
 \end{minted}

### 2014-01-31 6-Future.tex
udpate to Intro

@@
 
-SunPy as a project has existed for roughly three years. In this time 
+SunPy as a project has existed for roughly three years. In this time, 
 the code base has grown to over 17,000 lines. SunPy is already a 
-useful package for the analysis of calibrated solar data, however, the code 
-base is still evolving from release to release.
-% RJH:  Again, lines of code is a weird measure.  Also, no way there is 110,000 lines that we
-% actually wrote.  does this include docs, comments, and sphinx crap?
-%SJM: I think this number is just wrong and never got changed.
-%JI: needs new number.  Should be the number of lines in the 0.4 sunpy release???
-%ays: I changed the number to ohloh's count unless there's a reason to think it's >110k
-%schriste - using the ohloh number is consistent with sloccount so at least we are
-%internally consistent +1
+useful package for the analysis of calibrated solar data, and it
+continues to gain significant new capabilities with each successive release.
 The primary focus of the 
-%ays: Not actually discussed in Section \ref{sec:Intro}, so I removed the reference
 SunPy library is the analysis and visualisation of `high-level' solar 
@@
 %schriste - shortened this bit as it was a bit vague and gave the impression that we may be subsumed by astropy
+
+In the future, additional HELIO services will be supported by SunPy, aiming for
+seamless interaction between the other services and tools available (e.g., 
+\texttt{hek}, \texttt{map}).

### 2014-01-31 Summary.tex

@@
 a new organization tool for data files integrated into SunPy (see Section~\ref{ssec:db}) 
-and we discussed the community aspects, development model (see Section~\ref{sec:dev}), and future plans (see Section~\ref{{sec:future}}) for the project.
+and we discussed the community aspects, development model (see Section~\ref{sec:dev}), and future plans (see Section~\ref{sec:future}) for the project.
 We invite members of community to contribute to the effort by using SunPy for their 
-research, reporting bugs, sharing new functionality with the project.
+research, reporting bugs, and sharing new functionality with the project.

### 2014-01-31 abstract.tex

@@
 for solar physics and data analysis.
-Python, a free, cross platform, general purpose, high-level programming 
-language, has seen widespread adoption among the scientific community resulting 
+Python, a free, cross-platform, general-purpose, high-level programming 
+language, has seen widespread adoption among the scientific community, resulting 
 in the availability of a large range of available software, from numerical 
@@
 analysis and visualisation (Matplotlib).
-SunPy is a data analysis toolkit specialising in providing the software 
+SunPy is a data-analysis toolkit specialising in providing the software 
 necessary to analyse solar and heliospheric datasets in Python. 
-SunPy is open source software (BSD licence) and has a open and transparent 
+SunPy is open-source software (BSD licence) and has an open and transparent 
 development workflow that anyone can contribute to.
 SunPy provides access to solar data through integration with the Virtual 
-Solar Observatory (VSO), the the Heliophysics Event Knowledgebase (HEK) and the 
-HELIO webservices. It can open data files from major solar missions (e.g. 
+Solar Observatory (VSO), the the Heliophysics Event Knowledgebase (HEK), and the 
+HELIO webservices. It can open data files from major solar missions (e.g., 
 SDO, SOHO, STEREO and IRIS) into WCS-aware `Maps'. Time-series data from 
-mission such as GOES, SDO/EVE, and Proba2/LYRA into `LightCurves' and radio 
-spectra from e-Callisto or STEREO/SWAVES into `Spectrograms'. We present 
-examples of solar data analysis in SunPy, and show how Python-based solar 
-data-analysis can leverage the many existing data analysis tools already 
+mission such as GOES, SDO/EVE, and Proba2/LYRA become `LightCurves', and radio 
+spectra from e-Callisto or STEREO/SWAVES become `Spectrograms'. We present 
+examples of solar data analysis in SunPy and show how Python-based solar 
+data-analysis can leverage the many existing data-analysis tools already 
 available in Python. We discuss the future goals of the project and encourage 

### 2014-01-31 acknowledgements.tex

@@
 Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
-Summer of Code In Space (SOCIS) program, as well as a prototyped GUI and 
-N-Dimensional datatype implementations. In 2013 with support from Google's 
+Summer of Code In Space (SOCIS) program, as well as prototyped GUI and 
+N-Dimensional datatype implementations. In 2013, with support from Google's 
 Summer Of Code (GSOC) program, through the Python Software Foundation, the 
-\texttt{helio}, \texttt{hek2vso} and \texttt{database} subpackages were 
-developed.The Spectra and Spectrogram classes were implemented with support 
+\texttt{helio}, \texttt{hek2vso}, and \texttt{database} subpackages were 
+developed. The Spectra and Spectrogram classes were implemented with support 
 from the Astrophysics Research Group at Trinity College Dublin, Ireland, in 

### 2014-01-31 abstract.tex
fixes to abstract

@@
 This paper presents version 0.4 of SunPy, a community-developed Python package 
-for solar physics and data analysis.
+for solar physics.
 Python, a free, cross-platform, general-purpose, high-level programming 
 language, has seen widespread adoption among the scientific community, resulting 
-in the availability of a large range of available software, from numerical 
-computation (NumPy, SciPy) and machine learning (scikit-learn) to spectral 
-analysis and visualisation (Matplotlib).
-SunPy is a data-analysis toolkit specialising in providing the software 
+in the availability of a large number of software packages, from numerical 
+computation (NumPy, SciPy) and machine learning (scikit-learn) to visualisation 
+and plotting (Matplotlib).
+SunPy is a data-analysis environment specialising in providing the software 
 necessary to analyse solar and heliospheric datasets in Python. 
@@
 Solar Observatory (VSO), the the Heliophysics Event Knowledgebase (HEK), and the 
-HELIO webservices. It can open data files from major solar missions (e.g., 
-SDO, SOHO, STEREO and IRIS) into WCS-aware `Maps'. Time-series data from 
-mission such as GOES, SDO/EVE, and Proba2/LYRA become `LightCurves', and radio 
-spectra from e-Callisto or STEREO/SWAVES become `Spectrograms'. We present 
-examples of solar data analysis in SunPy and show how Python-based solar 
-data-analysis can leverage the many existing data-analysis tools already 
+HELIO webservices. It currently supports image data from major solar missions (e.g., 
+SDO, SOHO, STEREO and IRIS), time-series data from 
+mission such as GOES, SDO/EVE, and Proba2/LYRA, and radio 
+spectra from e-Callisto and STEREO/SWAVES. We describe SunPy's functionality,
+provide examples of solar data analysis in SunPy and show how Python-based solar 
+data-analysis can leverage the many existing tools already 
 available in Python. We discuss the future goals of the project and encourage 

### 2014-01-31 2-1-Map.tex
updates to Map section

@@
 \end{center}
-\caption{Example showing a \texttt{CompositeMap} plot, with RHESSI data composited
-with \textit{SDO}/AIA data, and the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
+with \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted showing the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \end{center}
-\caption{Example showing creation of a \texttt{MapCube} from a glob file search. The 
+\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
 resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 

### 2014-01-31 2-2-Lightcurve.tex
edits to remaining sections

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the {\texttt{pandas}} data-analysis library, and 
+the {\texttt{pandas}} data-analysis library.  
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
@@
 >>> goes.peek()
+>>> print goes.data['B_FLUX'].max()
+2.55542e-05
+>>> print goes.data['B_FLUX'].idxmax()
+2011-06-07 06:41:26
 \end{minted}
@@
 using a time range and the output of the 
-\texttt{peek()} method.}
+\texttt{peek()} method. The maximum flux value in the GOES 1.0 - 8.0$\AA$\ channel 
+is then retrieved along with the location in time of the maximum.}
 \label{code:goes_lc}
@@
 Alternatively, if the data file already exists on the local system, the 
-\texttt{LightCurve} object may instead be initialised using that file as input.
-Once the \texttt{LightCurve} object has been created, it may be manipulated in 
-a variety of ways in order to perform time-series analysis.
+\texttt{LightCurve} object may be initialised using that file as input.
+%Once the \texttt{LightCurve} object has been created, it may be manipulated in 
+%a variety of ways in order to perform time-series analysis.

### 2014-01-31 acknowledgements.tex
edits to remaining sections

@@
 \section{Acknowledgements}
-Many of the larger features in SunPy have been developed with external support. 
+Many of the larger features in SunPy have been developed with the generous support of 
+external organizations. 
 Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
-Summer of Code In Space (SOCIS) program, as well as prototyped GUI and 
+Summer of Code In Space (SOCIS) program, as well as a prototype GUI and 
 N-Dimensional datatype implementations. In 2013, with support from Google's 

### 2014-01-31 2-Data_Types.tex

@@
 
-SunPy currently provides data strucutures that are specifically designed for the
+The core of SunPy are a set of data strucutures that are specifically designed for the
 three primary varieties of solar physics data: images, time series, and
@@
 
-This section will give a brief overview of the \textit{current} functionality 
-of each of these data types.
-
-\subsection{Visualisation}
-\label{subsec:Viz}
 All of the core SunPy data types 
@@
 
+This section will give a brief overview of the \textit{current} functionality 
+of each of the core SunPy data types.
+
 \input{2-1-Map}

### 2014-01-31 3-4-Helioviewer.tex

@@
 project maintains archives of all of its data in JPEG2000 format (for further
-details on the Helioviewer Project see \cite{muller2009}). The
+details on the Helioviewer Project see \citealt{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source

### 2014-01-31 6-Future.tex

@@
 
-SunPy as a project has existed for roughly three years. In this time, 
-the code base has grown to over 17,000 lines. SunPy is already a 
+Over the three years of SunPy's development, the code base has grown to over 17,000 lines. 
+SunPy is already a 
 useful package for the analysis of calibrated solar data, and it
@@
 results (Section \ref{ssec:hek}) onto maps (Section \ref{ssec:map}).
+Finally, support for new data providers and services will be integrated into SunPy.
+For example, new HELIO services will be supported by SunPy, aiming for
+seamless interaction between the other services and tools available (e.g., 
+\texttt{hek}, \texttt{map}).
 
@@
 %schriste - shortened this bit as it was a bit vague and gave the impression that we may be subsumed by astropy
-
-In the future, additional HELIO services will be supported by SunPy, aiming for
-seamless interaction between the other services and tools available (e.g., 
-\texttt{hek}, \texttt{map}).

### 2014-01-31 Summary.tex

@@
 and we discussed the community aspects, development model (see Section~\ref{sec:dev}), and future plans (see Section~\ref{sec:future}) for the project.
-We invite members of community to contribute to the effort by using SunPy for their 
+We invite members of the community to contribute to the effort by using SunPy for their 
 research, reporting bugs, and sharing new functionality with the project.

### 2014-01-31 2-Data_Types.tex
Assorted minor fixes

@@
 
-The core of SunPy are a set of data strucutures that are specifically designed for the
+The core of SunPy is a set of data structures that are specifically designed for the
 three primary varieties of solar physics data: images, time series, and

### 2014-01-31 abstract.tex
Assorted minor fixes

@@
 SunPy provides access to solar data through integration with the Virtual 
-Solar Observatory (VSO), the the Heliophysics Event Knowledgebase (HEK), and the 
+Solar Observatory (VSO), the Heliophysics Event Knowledgebase (HEK), and the 
 HELIO webservices. It currently supports image data from major solar missions (e.g., 
 SDO, SOHO, STEREO and IRIS), time-series data from 
-mission such as GOES, SDO/EVE, and Proba2/LYRA, and radio 
+missions such as GOES, SDO/EVE, and Proba2/LYRA, and radio 
 spectra from e-Callisto and STEREO/SWAVES. We describe SunPy's functionality,
-provide examples of solar data analysis in SunPy and show how Python-based solar 
+provide examples of solar data analysis in SunPy, and show how Python-based solar 
 data-analysis can leverage the many existing tools already 

### 2014-01-31 abstract.tex
Abstract tweaks

@@
 in the availability of a large number of software packages, from numerical 
-computation (NumPy, SciPy) and machine learning (scikit-learn) to visualisation 
-and plotting (Matplotlib).
+computation (\texttt{NumPy}, \texttt{SciPy}) and machine learning (\texttt{scikit-learn}) to visualisation 
+and plotting (\texttt{matplotlib}).
 SunPy is a data-analysis environment specialising in providing the software 
@@
 HELIO webservices. It currently supports image data from major solar missions (e.g., 
-SDO, SOHO, STEREO and IRIS), time-series data from 
-missions such as GOES, SDO/EVE, and Proba2/LYRA, and radio 
-spectra from e-Callisto and STEREO/SWAVES. We describe SunPy's functionality,
+\textit{SDO}, \textit{SOHO}, \textit{STEREO}, and \textit{IRIS}), time-series data from 
+missions such as \textit{GOES}, \textit{SDO}/EVE, and \textit{PROBA2}/LYRA, and radio 
+spectra from e-Callisto and \textit{STEREO}/SWAVES. We describe SunPy's functionality,
 provide examples of solar data analysis in SunPy, and show how Python-based solar 

### 2014-01-31 2-1-Map.tex

@@
 ...                         composite=True)
->>> compmap.set_levels(1, range(0,50,5), percent=True)
+>>> compmap.set_levels(1, range(0, 50, 5), percent=True)
 >>> compmap.set_colors(1, 'Reds_r')
@@
 \caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
-with \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted showing the integration with the \texttt{matplotlib.pyplot} interface.}
+on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}

### 2014-01-31 acknowledgements.tex

@@
 Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
-Summer of Code In Space (SOCIS) program, as well as a prototype GUI and 
-N-Dimensional datatype implementations. In 2013, with support from Google's 
+Summer of Code In Space (SOCIS) program, as well as a prototype GUI and an
+N-dimensional data-type implementation. In 2013, with support from Google's 
 Summer Of Code (GSOC) program, through the Python Software Foundation, the 

### 2014-01-31 2-2-Lightcurve.tex
Assorted minor fixes
@Cadair's small changes

@@
 data specified by the time interval, downloads the required files, and 
-subsequently creates and plots the object.
+subsequently creates and plots the object. Alternatively, if the data file 
+already exists on the local system, the \texttt{LightCurve} object may be 
+initialised using that file as input.
 
@@
 using a time range and the output of the 
-\texttt{peek()} method. The maximum flux value in the GOES 1.0 - 8.0$\AA$\ channel 
+\texttt{peek()} method. The maximum flux value in the \textit{GOES} 1.0--8.0$\AA$\ channel 
 is then retrieved along with the location in time of the maximum.}
@@
 \end{listing}
-
-Alternatively, if the data file already exists on the local system, the 
-\texttt{LightCurve} object may be initialised using that file as input.
-%Once the \texttt{LightCurve} object has been created, it may be manipulated in 
-%a variety of ways in order to perform time-series analysis.

### 2014-01-31 4-Util.tex
@Cadair's small changes

@@
 such as the Astropy 
-coordinates package. The \texttt{wcs} package in SunPy implements the World Coordinate 
+\texttt{coordinates} package. The \texttt{wcs} package in SunPy implements the World Coordinate 
 System (WCS) for solar coordinates as described by \cite{thompson2006}. The 
@@
 compatible with \texttt{sunpy.time.parse\_time()}.
-A future version of SunPy will integrate with the Astropy coordinates package and will 
-likely make use of an ephemeris package.
 

### 2014-01-31 3-3-HELIO.tex

@@
 The HELiophysics Integrated Observatory (HELIO)\footnote{For more information 
-see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
+see \url{http://helio-vo.eu}} has 
 compiled a list of web services which allows scientists to query and 

### 2014-01-31 1-Introduction.tex
@Cadair's small changes
jack's edits

@@
 
-The SunPy project aims to provide a free, open-source, and openly developed
-software package for the analysis and visualisation of solar data. SunPy makes
+%The SunPy project aims to provide a free, open-source, and openly developed
+%software package for the analysis and visualisation of solar data.
+The SunPy project aims to provide a software package with these qualities for 
+the analysis and visualisation of solar data. SunPy makes
 use of Python and scientific Python packages. Python is a free, general-purpose, 
@@
 scientific programming language,
-such as array manipulation, core numerical algorithms, and visualisation.
-Building upon these foundations, packages such as \texttt{astropy}, \texttt{pandas}, and
-\texttt{scikit-image} provide more domain-specific functionality.
+such as array manipulation, core numerical algorithms, and visualisation, respectively.
+Building upon these foundations, packages such as \texttt{astropy} (astronomy), \texttt{pandas} (time-series), and
+\texttt{scikit-image} (image processing) provide more domain-specific functionality.
 
-SunPy is designed to be a clean, simple-to-use, and well-structured package that provides 
+SunPy is designed to be a clean, simple-to-use, and well-structured open-source package that provides 
 the \textit{core} tools for solar data analysis, motivated by the need for a free and 

### 2014-01-31 3-2-HEK.tex
edits to remaining sections
jack's edits

@@
 provides an homogeneous and well-described interface to a large amount of 
-feature and event information of interest to the solar physics community.
-
-SunPy accesses this information through the \texttt{hek} module, which was
-developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
-use of the 
-HEK API\footnote{For more information see 
-\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
+feature and event information of interest to the solar physics community. SunPy 
+accesses this information through the \texttt{hek} module.  The \texttt{hek} module makes use of the 
+HEK API\footnote{For more information see \href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
 
@@
 ...                       hek.attrs.EventType('FL'),
-...                       hek.attrs.FRM.Name == 'SSW Latest Events')
+...                       hek.attrs.FRM.Name=='SSW Latest Events')
 >>> len(result)
@@
 
-Similar to the \texttt{vso} module, HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
+HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
 and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
@@
 ...                       hek.attrs.EventType('FL'),
-...                       (hek.attrs.Event.Coord1 > 50) 
-...                       or (hek.attrs.FL.PeakFlux > 1000.0))
+...                       (hek.attrs.Event.Coord1>50) 
+...                       or (hek.attrs.FL.PeakFlux>1000.0))
 \end{minted}

### 2014-01-31 4-Util.tex
jack's edits

@@
 Coordinate transformations are frequently a necessary task within the solar 
-data analysis workflow. Likely the most often used transformation is from 
+data analysis workflow. An often used transformation is from 
 observer coordinates (e.g., sky coordinates) to a coordinate system that is 
@@
 System (WCS) for solar coordinates as described by \cite{thompson2006}. The 
-transformations currently implemented are those most useful 
-for most solar data analysis, namely converting from Helioprojective-Cartesian 
+transformations currently implemented are some of the most commonly used in solar data analysis, namely converting from Helioprojective-Cartesian 
 (HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
@@
 
-\subsubsection{Sun}\label{ssec:util:sun}
+\subsection{Sun}\label{ssec:util:sun}
 The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
@@
 
-\subsubsection{Instruments}\label{ssec:util:inst}
+\subsection{Instruments}\label{ssec:util:inst}
 In addition to providing support for instrument-specific solar data via the main data 

### 2014-01-31 2-1-Map.tex

@@
 
-The \texttt{Map} class stores standard metadata retrieved from the header of 
+The \texttt{Map} class stores all the metadata retrieved from the header of 
 the image file in the \texttt{meta} attribute and provides convenience 

### 2014-01-31 2-3-Spectra.tex

@@
 In the example shown, data is provided in two frequency ranges:
-20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
+20--90\,MHz and 55--355\,MHz.  Since the data are not evenly spaced in
 the frequency range, the \texttt{Spectrogram} object linearises the
@@
 >>> callisto_nobg = callisto.subtract_bg()
->>> callisto_nobg.peek(vmin = 0)
+>>> callisto_nobg.peek(vmin=0)
 \end{minted}

### 2014-01-31 3-4-Helioviewer.tex

@@
 Each Helioviewer Project JPEG2000 file contains
-metadata which are based (in part) on the original FITS header
+metadata which are based on the original FITS header
 information, and carry sufficient information to permit overlay with
@@
 \caption{Acquisition and display of a Helioviewer JPEG2000 file as a
-  SunPy \texttt{Map} object.}
+  SunPy \texttt{Map} object. Images values are byte-scaled in the range 0-255.}
 \label{code:downloadjp2}

### 2014-01-31 3-5-Database.tex

@@
 created automatically. A server-based database, on the other hand, could be used
-by a collaborators who work together on the
+by collaborators who work together on the
 same data from different computers: a central database server stores all data and the clients connect to
@@
 records. The function \texttt{display\_entries()} displays an iterable of 
-database entries in a nicely-formatted \textsc{ASCII} table. The headlines 
+database entries in a formatted \textsc{ASCII} table. The headlines 
 correspond to the attributes of the respective database entries.

### 2014-01-31 4-Util.tex

@@
 (nan, nan)
-Convert sky coordinate to a position in HCC
+# Convert sky coordinate to a position in HCC
 >>> wcs.convert_hpc_hcc(-300, 400, z=True)

### 2014-01-31 acknowledgements.tex

--- 2014-01-31 acknowledgements.tex
@@
 Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
-Summer of Code In Space (SOCIS) program, as well as a prototype GUI and 
-N-Dimensional datatype implementations. In 2013, with support from Google's 
+Summer of Code In Space (SOCIS 2011, 2012, 2013) program, as well as a prototype GUI and an
+N-dimensional data-type implementation. In 2013, with support from Google's 
 Summer Of Code (GSOC) program, through the Python Software Foundation, the 

### 2014-01-31 abstract.tex
Update abstract.tex

@@
 Solar Observatory (VSO), the Heliophysics Event Knowledgebase (HEK), and the 
-HELIO webservices. It currently supports image data from major solar missions (e.g., 
+HELiophysics Integrated Observatory (HELIO) webservices. It currently supports image data from major solar missions (e.g., 
 \textit{SDO}, \textit{SOHO}, \textit{STEREO}, and \textit{IRIS}), time-series data from 

### 2014-01-31 3-2-HEK.tex
Super minor edits

@@
 accesses this information through the \texttt{hek} module.  The \texttt{hek} module makes use of the 
-HEK API\footnote{For more information see \href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
+HEK API\footnote{For more information see \url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
 

### 2014-01-31 2-1-Map.tex

@@
 
-The \texttt{Map} class stores all the metadata retrieved from the header of 
+The \texttt{Map} class stores all of the metadata retrieved from the header of
 the image file in the \texttt{meta} attribute and provides convenience 

### 2014-01-31 3-3-HELIO.tex

@@
 its original nature (e.g., Earth auroras are a signature of magnetic 
-field disturbances produced few days before on the Sun).
+field disturbances produced a few days before on the Sun).
 In addition to the primary, web-based interface to 
-HELIO, the services are available by API.
+HELIO, its services are available via an API.
 
@@
 As with all of the HELIO services, the HEC service provides results in VOTable 
-data format (defined by IVOA \citep{ochsenbein_ivoa_2011}).
+data format (defined by IVOA \cite{ochsenbein_ivoa_2011}).
 The \texttt{hec} module parses this output using the \texttt{astropy.io.votable} package.

### 2014-07-20 2-1-Map.tex
all single quotes to double quotes in code

@@
 >>> import sunpy.map
->>> aiamap = sunpy.map.Map('aia_file.fits')
+>>> aiamap = sunpy.map.Map("aia_file.fits")
 >>> smap = aiamap.submap([-1200, -200], [-1000, -0])
@@
 >>> import matplotlib.pyplot as plt
->>> compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
+>>> compmap = sunpy.map.Map("aia_1600_image.fits", "RHESSI_image.fits", 
 ...                         composite=True)
 >>> compmap.set_levels(1, range(0, 50, 5), percent=True)
->>> compmap.set_colors(1, 'Reds_r')
+>>> compmap.set_colors(1, "Reds_r")
 #Plot the result and crop
@@
 >>> import sunpy.map
->>> cubemap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
+>>> cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
 >>> cubemap.peek()

### 2014-07-20 2-2-Lightcurve.tex
all single quotes to double quotes in code

@@
 >>> from sunpy.time import TimeRange
->>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-...                                         '2011-06-07 08:00')
+>>> goes = lightcurve.GOESLightCurve.create(TimeRange("2011-06-07 06:00",
+...                                         "2011-06-07 08:00"))
 >>> goes.peek()
->>> print goes.data['B_FLUX'].max()
+>>> print goes.data["B_FLUX"].max()
 2.55542e-05
->>> print goes.data['B_FLUX'].idxmax()
+>>> print goes.data["B_FLUX"].idxmax()
 2011-06-07 06:41:26

### 2014-07-20 3-1-VSO.tex
all single quotes to double quotes in code

@@
 Access Protocol) service is also available.
-SunPy's \texttt{vso} module provides access to the VSO via the SOAP service using the
+SunPy's \texttt{vso} module provides access to the VSO via this SOAP service using the
 \texttt{suds} package.
@@
 >>> client = vso.VSOClient()
->>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'
+>>> tstart, tend = "2011/6/7 05:30", "2011/6/7 10:30"
 >>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
@@
 ...
->>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
+>>> pathformat = "/data/{instrument}/{detector}/{file}.fits"
 >>> results = client.get(coronagraphs, path = pathformat)
@@
 \begin{minted}[bgcolor=bg]{pycon}
->>> condition = (vso.attrs.Detector('cor1') |
+>>> condition = (vso.attrs.Detector("cor1") |
 ...              vso.attrs.Wave(125, 135) |

### 2014-07-20 3-3-HELIO.tex
all single quotes to double quotes in code

@@
 >>> hc = hec.Client()
->>> tstart, tend = '2011-06-07T06:00:00', '2011-06-07T12:00:00'
->>> event_type = 'cme'
+>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T12:00:00"
+>>> event_type = "cme"
 

### 2014-07-20 3-4-Helioviewer.tex
Super minor edits
all single quotes to double quotes in code

@@
 >>> hv = HelioviewerClient()
->>> hv.download_png('2099/01/01', 6,
+>>> hv.download_png("2099/01/01", 6,
 ...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
@@
 >>> import sunpy.map
->>> filepath = hv.download_jp2('2012/07/05 00:30:00',
+>>> filepath = hv.download_jp2("2012/07/05 00:30:00",
 ...                            observatory='SDO',
-...                            instrument='HMI', detector='HMI', 
-...                            measurement='continuum')
+...                            instrument="HMI", detector="HMI", 
+...                            measurement="continuum")
 >>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()
@@
 \caption{Acquisition and display of a Helioviewer JPEG2000 file as a
-  SunPy \texttt{Map} object. Images values are byte-scaled in the range 0-255.}
+  SunPy \texttt{Map} object. Images values are byte-scaled in the range 0--255.}
 \label{code:downloadjp2}

### 2014-07-20 3-5-Database.tex
all single quotes to double quotes in code

@@
 >>> from sunpy.database import Database
->>> database = Database('sqlite:///')
+>>> database = Database("sqlite:///")
 >>> database.download(
-...     vso.attrs.Time('2012-08-05', '2012-08-05 00:00:05'),
+...     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
 ...     vso.attrs.Instrument('AIA'))
@@
 ...     database,
-...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
+...     ["id", "observation_time_start", "wavemin", "wavemax"])
 id observation_time_start wavemin wavemax

### 2014-07-21 3-2-HEK.tex

@@
 >>> client = hek.HEKClient()
->>> tstart, tend = '2011/08/09 00:00:00', '2011/08/10 00:00:00'
+>>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
 >>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType('FL')) # flares
+...                       hek.attrs.EventType("FL")) # flares
 >>> len(result)
@@
  and so 
-\texttt{hek.attrs.EventType('FL')} in Listing~\ref{code:hek:simple}
+\texttt{hek.attrs.EventType("FL")} in Listing~\ref{code:hek:simple}
 can be alternatively replaced with \texttt{hek.attrs.FL}.
@@
 >>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType('FL'),
-...                       hek.attrs.FRM.Name=='SSW Latest Events')
+...                       hek.attrs.EventType("FL"),
+...                       hek.attrs.FRM.Name=="SSW Latest Events")
 >>> len(result)
@@
 >>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType('FL'),
+...                       hek.attrs.EventType("FL"),
 ...                       (hek.attrs.Event.Coord1>50) 

### 2014-07-21 4-Util.tex

@@
 # Search for the age of the Sun
->>> constants.find('age')
+>>> constants.find("age")
 ['age', 'average angular size', 'average density', 'average intensity']

### 2014-07-23 2-1-Map.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> aiamap = sunpy.map.Map("aia_file.fits")
->>> smap = aiamap.submap([-1200, -200], [-1000, -0])
->>> smap.peek(draw_grid=True)
-\end{minted}
+\pythoncode{map1.py}
 \begin{center}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> import matplotlib.pyplot as plt
->>> compmap = sunpy.map.Map("aia_1600_image.fits", "RHESSI_image.fits", 
-...                         composite=True)
->>> compmap.set_levels(1, range(0, 50, 5), percent=True)
->>> compmap.set_colors(1, "Reds_r")
-#Plot the result and crop
->>> ax = plt.subplot()
->>> compmap.plot()
->>> ax.axis([200, 600, -600, -200])
->>> plt.show()
-\end{minted}
+\pythoncode{map2.py}
 \begin{center}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
->>> cubemap.peek()
-\end{minted}
+\pythoncode{map3.py}
 \begin{center}

### 2014-07-23 2-2-Lightcurve.tex
standardized mint display, moved code out to files
also created build_article script

--- 2014-01-31 2-2-Lightcurve.tex
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import lightcurve
->>> from sunpy.time import TimeRange
->>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
-...                                         '2011-06-07 08:00')
->>> goes.peek()
->>> print goes.data['B_FLUX'].max()
-2.55542e-05
->>> print goes.data['B_FLUX'].idxmax()
-2011-06-07 06:41:26
-\end{minted}
+\pythoncode{lightcurve.py}
 \begin{center}

### 2014-07-23 2-3-Spectra.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
->>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
->>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
->>> callisto_nobg = callisto.subtract_bg()
->>> callisto_nobg.peek(vmin=0)
-\end{minted}
+\pythoncode{spectra.py}
 \begin{center}

### 2014-07-23 3-1-VSO.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net import vso
->>> client = vso.VSOClient()
->>> tstart, tend = "2011/6/7 05:30", "2011/6/7 10:30"
->>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
-...                            vso.attrs.Instrument('lasco'))
->>> lasco_query.num_records()
-40
->>> lasco_query.show() 
-Start time           End time             Source  Instrument  Type
-----------           --------             ------  ----------  ----
-2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
-2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
-...
->>> pathformat = "/data/{instrument}/{detector}/{file}.fits"
->>> results = client.get(coronagraphs, path = pathformat)
-\end{minted}
+\pythoncode{vso1.py}
 \caption{Example of querying a single instrument over a time range and downloading the data}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> condition = (vso.attrs.Detector("cor1") |
-...              vso.attrs.Wave(125, 135) |
-...              vso.attrs.Wave(165, 175) ) # in angstroms
->>> advanced = client.query(vso.attrs.Time(tstart, tend), condition)
->>> advanced.num_records()
-4434
->>> advanced.show()
-Start time           End time             Source    Instrument  Type
-----------           --------             ------    ----------  ----
-2011-06-07 00:00:00  2011-06-08 00:00:00  SDO       EVE         FULLDISK
-...
-2011-06-07 05:31:09  2011-06-07 05:31:19  PROBA2    SWAP        FULLSUN
-...
-2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
-2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
-...
-2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK
-\end{minted}
+\pythoncode{vso2.py}
 \caption{Example of an advanced VSO query using attribute objects,

### 2014-07-23 3-2-HEK.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net import hek
->>> client = hek.HEKClient()
->>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL")) # flares
->>> len(result)
-52
-\end{minted}
+\pythoncode{hek.py}
 \caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       hek.attrs.FRM.Name=="SSW Latest Events")
->>> len(result)
-9
-\end{minted}
+\pythoncode{hek2.py}
 \caption{An HEK query that returns only those flares that were
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       (hek.attrs.Event.Coord1>50) 
-...                       or (hek.attrs.FL.PeakFlux>1000.0))
-\end{minted}
+\pythoncode{hek3.py}
 \caption{HEK query using the logical \texttt{or} operator.}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
->>> from sunpy.net import hek2vso
->>> h2v = hek2vso.H2VClient()
->>> vso_results = h2v.translate_and_query(result[0])
->>> h2v.vso_client.get(vso_results[0]).wait()
-\end{minted}
+\pythoncode{hek4.py}
 \caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 

### 2014-07-23 3-3-HELIO.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[h]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net.helio import hec
->>> hc = hec.Client()
->>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T12:00:00"
->>> event_type = "cme"
-
-# From all the catalogues these which name contain our event of interest
->>> catalogues = hc.get_table_names()
->>> catalogues_event = [l[0] for l in catalogues 
-...                     if event_type in l[0] and 'list' not in l[0]]
-
-# Query all the catalogues that comes from cactus
->>> results = [hc.time_query(tstart, tend, event) 
-...            for event in catalogues_event if 'cactus' in event]
->>> for cat in results:
-...     print "{cat} has {nres} results".format(cat = cat.ID, \
-...                                             nres = len(cat.array))
-__helio_hec-cactus_stereoa_cme has 4 results
-__helio_hec-cactus_stereob_cme has 3 results
-__helio_hec-cactus_soho_cme has 7 results
-\end{minted}
+\pythoncode{helio.py}
 \caption{Example of querying the HEC service to multiple CME

### 2014-07-23 3-4-Helioviewer.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net.helioviewer import HelioviewerClient
->>> hv = HelioviewerClient()
->>> hv.download_png("2099/01/01", 6,
-...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
-...                 "[SOHO,LASCO,C2,white-light,1,100]",
-...                 x0=0, y0=0, width=768, height=768)
-\end{minted}
+\pythoncode{helioviewer.py}
 \begin{center}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> import sunpy.map
->>> filepath = hv.download_jp2("2012/07/05 00:30:00",
-...                            observatory='SDO',
-...                            instrument="HMI", detector="HMI", 
-...                            measurement="continuum")
->>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()
-\end{minted}
+\pythoncode{helioviewer2.py}
 \begin{center}

### 2014-07-23 3-5-Database.tex
standardized mint display, moved code out to files
also created build_article script

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net import vso
->>> from sunpy.database import Database
->>> database = Database("sqlite:///")
->>> database.download(
-...     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
-...     vso.attrs.Instrument('AIA'))
->>> len(database)
-2
->>> from sunpy.database.tables import display_entries
->>> print display_entries(
-...     database,
-...     ["id", "observation_time_start", "wavemin", "wavemax"])
-id observation_time_start wavemin wavemax
--- ---------------------- ------- -------
-1  2012-08-05 00:00:01    9.4     9.4    
-2  2012-08-05 00:00:02    33.5    33.5
-\end{minted}
+\pythoncode{database.py}
 \caption{Example usage of the \texttt{database} subpackage.}

### 2014-07-23 4-Util.tex
standardized mint display, moved code out to files
also created build_article script

--- 2014-01-31 4-Util.tex
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy import wcs
->>> wcs.convert_hg_hpc(10, 53)
-(100.49244115330731, 767.97438321917502)
-# Convert that position back to heliographic coordinates
->>> wcs.convert_hpc_hg(100.49, 767.97)
-(9.9996521808465175, 52.999563684874893)
-# Try to convert a position which is not on the Sun to HG
->>> wcs.convert_hpc_hg(-1500, 0)
-sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
-  distance = q - np.sqrt(distance)
-(nan, nan)
-Convert sky coordinate to a position in HCC
->>> wcs.convert_hpc_hcc(-300, 400, z=True)
-(-216716967.63331246, 288956420.9477042, 594364636.2208252)
-\end{minted}
+\pythoncode{util1.py}
 \caption{Using the \texttt{wcs} subpackage.}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.sun import constants
->>> print(constants.mass)
-  Name   = Solar mass
-  Value  = 1.9891e+30
-  Error  = 5e+25
-  Units  = kg
-  Reference = Allen's Astrophysical Quantities 4th Ed.
-# Verify the average density of the Sun and convert to cgs
->>> (constants.mass/constants.volume).cgs
-<Quantity 1.40851154227 g / (cm3)>
-# Search for the age of the Sun
->>> constants.find('age')
-['age', 'average angular size', 'average density', 'average intensity']
->>> constants.value('age'), constants.unit('age')
-(4600000000.0, Unit("yr"))
-\end{minted}
+\pythoncode{util2.py}
 \caption{Using the \texttt{sun.constants} module.}

### 2014-07-23 database.py

@@ -1,0 +1,16 @@
+>>> from sunpy.net import vso
+>>> from sunpy.database import Database
+>>> database = Database("sqlite:///")
+>>> database.download(
+...     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
+...     vso.attrs.Instrument('AIA'))
+>>> len(database)
+2
+>>> from sunpy.database.tables import display_entries
+>>> print display_entries(
+...     database,
+...     ["id", "observation_time_start", "wavemin", "wavemax"])
+id observation_time_start wavemin wavemax
+-- ---------------------- ------- -------
+1  2012-08-05 00:00:01    9.4     9.4    
+2  2012-08-05 00:00:02    33.5    33.5

### 2014-07-23 hek.py

@@ -1,0 +1,7 @@
+>>> from sunpy.net import hek
+>>> client = hek.HEKClient()
+>>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
+>>> result = client.query(hek.attrs.Time(tstart, tend), 
+...                       hek.attrs.EventType("FL")) # flares
+>>> len(result)
+52

### 2014-07-23 hek4.py

@@ -1,0 +1,4 @@
+>>> from sunpy.net import hek2vso
+>>> h2v = hek2vso.H2VClient()
+>>> vso_results = h2v.translate_and_query(result[0])
+>>> h2v.vso_client.get(vso_results[0]).wait()

### 2014-07-23 helioviewer2.py

@@ -1,0 +1,6 @@
+>>> import sunpy.map
+>>> filepath = hv.download_jp2("2012/07/05 00:30:00",
+...                            observatory='SDO',
+...                            instrument="HMI", detector="HMI", 
+...                            measurement="continuum")
+>>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()

### 2014-07-23 lightcurve.py

@@ -1,0 +1,9 @@
+>>> from sunpy import lightcurve
+>>> from sunpy.time import TimeRange
+>>> goes = lightcurve.GOESLightCurve.create(TimeRange("2011-06-07 06:00",
+...                                         "2011-06-07 08:00"))
+>>> goes.peek()
+>>> print goes.data["B_FLUX"].max()
+2.55542e-05
+>>> print goes.data["B_FLUX"].idxmax()
+2011-06-07 06:41:26

### 2014-07-23 map1.py

@@ -1,0 +1,4 @@
+>>> import sunpy.map
+>>> aiamap = sunpy.map.Map("aia_file.fits")
+>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
+>>> smap.peek(draw_grid=True)

### 2014-07-23 map3.py

@@ -1,0 +1,3 @@
+>>> import sunpy.map
+>>> cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
+>>> cubemap.peek()

### 2014-07-23 spectra.py

@@ -1,0 +1,5 @@
+>>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
+>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
+>>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
+>>> callisto_nobg = callisto.subtract_bg()
+>>> callisto_nobg.peek(vmin=0)

### 2014-07-23 util1.py

@@ -1,0 +1,14 @@
+>>> from sunpy import wcs
+>>> wcs.convert_hg_hpc(10, 53)
+(100.49244115330731, 767.97438321917502)
+# Convert that position back to heliographic coordinates
+>>> wcs.convert_hpc_hg(100.49, 767.97)
+(9.9996521808465175, 52.999563684874893)
+# Try to convert a position which is not on the Sun to HG
+>>> wcs.convert_hpc_hg(-1500, 0)
+sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
+  distance = q - np.sqrt(distance)
+(nan, nan)
+# Convert sky coordinate to a position in HCC
+>>> wcs.convert_hpc_hcc(-300, 400, z=True)
+(-216716967.63331246, 288956420.9477042, 594364636.2208252)

### 2014-07-23 util2.py

@@ -1,0 +1,15 @@
+>>> from sunpy.sun import constants
+>>> print(constants.mass)
+  Name   = Solar mass
+  Value  = 1.9891e+30
+  Error  = 5e+25
+  Units  = kg
+  Reference = Allen's Astrophysical Quantities 4th Ed.
+# Verify the average density of the Sun and convert to cgs
+>>> (constants.mass/constants.volume).cgs
+<Quantity 1.40851154227 g / (cm3)>
+# Search for the age of the Sun
+>>> constants.find("age")
+['age', 'average angular size', 'average density', 'average intensity']
+>>> constants.value('age'), constants.unit('age')
+(4600000000.0, Unit("yr"))

### 2014-07-24 1-Introduction.tex
Submit paper to CSD

@@
 
-Science is driven by the analysis of data of growing variety and complexity.
-Modern advances in sensor technology, combined with the availability of inexpensive 
+Science is driven by the analysis of data of an ever-growing variety and 
+complexity.
+Modern advances in sensor technology, combined with the availability of 
+inexpensive 
 storage, has led to rapid increases in the amount of data available to scientists in almost
@@
 NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched
-in February 2010, produces over 1 TB of data per day \citep{aia}. Managing and
+in February 2010, produces over 1 TB of data per day \cite{pesnell2012}. Managing and
 analysing this mountain of data requires increasingly sophisticated software
@@
 scientific packages available in Python. Core packages such as \texttt{NumPy}, 
-\texttt{SciPy}, and \texttt{matplotlib} provide the basic functionality expected of a 
-scientific programming language,
+\texttt{SciPy} \citep{jones2001}, and \texttt{matplotlib} \citep{hunter2007} provide 
+the basic functionality expected of a scientific programming language,
 such as array manipulation, core numerical algorithms, and visualisation, respectively.
-Building upon these foundations, packages such as \texttt{astropy} (astronomy), \texttt{pandas} (time-series), and
-\texttt{scikit-image} (image processing) provide more domain-specific functionality.
+Building upon these foundations, packages such as \texttt{astropy} (astronomy)
+\cite{theastropycollaboration2013}, \texttt{pandas} (time-series) 
+\cite{mckinney2010, mckinney2012}, and \texttt{scikit-image} (image processing)
+ \citep{vanderwalt2014} provide more domain-specific functionality.
 

### 2014-07-24 3-1-VSO.tex
fix for issue #111

--- 2014-07-20 3-1-VSO.tex
@@
 
-Listing~\ref{code:vso_query_simple} shows an example of how to query the VSO
-using the \texttt{vso} module.
+Listing~\ref{code:vso_query_simple} shows an example of how to query and download data using
+from the VSO using the \texttt{vso} module.
 Queries are constructed using one or more attribute objects. Each
@@
 Listing~\ref{code:vso_query_simple} also shows how to download the data using
-the constructed query. One can use the metadata associated with the data sets to 
-specify how the files will be named locally, such as creating subdirectories 
-based on the instrument names.
+the constructed query. The path to which the data files will be downloaded us defined using custom tokens
+which reference the file metadata (e.g. instrument, detector, filename). This provides
+users the ability to organize their data into subdirectories on download.
 

### 2014-08-21 build_article.py
moved code

@@ -1,0 +1,51 @@
+#!/usr/bin/env python
+import os
+import glob
+from os.path import basename
+
+paper_name = "Sunpy_paper_0.4"
+
+# delete old output files
+py_out_files = glob.glob("py_*.txt")
+for file in py_out_files:
+    try:
+        os.remove(file)
+    except:
+        pass
+
+py_files = glob.glob("python_code/*.py")
+print(py_files)
+for file in py_files:
+    # the following just runs the file to create any pdfs the script may generate
+    os.system('python ' + file)
+
+    pretty_text_file = open('py_' + basename(file).split('.')[0] + ".txt", 'w')
+    f = open(file)
+    print("Running..." + file)
+    import_statement = ['']
+    for line in f.readlines():
+        #    pretty_text_file.write(">>> " + content)
+        #else pretty_text_file.write(content)
+        print(line)
+        if line[0] != '#':
+            pretty_text_file.write(">>> " + line)
+        else:
+            pretty_text_file.write(line)
+    f.close()
+    pretty_text_file.close()
+            
+try:
+    os.remove(paper_name + '.aux')
+except:
+    pass
+
+try:
+    os.remove(paper_name + '.bbl')
+except:
+    pass
+    
+#os.system('pdflatex -shell-escape ' + paper_name)
+#os.system('pdflatex -shell-escape ' + paper_name)
+#os.system('bibtex ' + paper_name)
+#os.system('pdflatex -shell-escape ' + paper_name)
+#os.system('pdflatex -shell-escape ' + paper_name)

### 2014-08-21 database.py

@@ -1,16 +1,0 @@
->>> from sunpy.net import vso
->>> from sunpy.database import Database
->>> database = Database("sqlite:///")
->>> database.download(
-...     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
-...     vso.attrs.Instrument('AIA'))
->>> len(database)
-2
->>> from sunpy.database.tables import display_entries
->>> print display_entries(
-...     database,
-...     ["id", "observation_time_start", "wavemin", "wavemax"])
-id observation_time_start wavemin wavemax
--- ---------------------- ------- -------
-1  2012-08-05 00:00:01    9.4     9.4    
-2  2012-08-05 00:00:02    33.5    33.5

### 2014-08-21 hek.py

@@ -1,7 +1,0 @@
->>> from sunpy.net import hek
->>> client = hek.HEKClient()
->>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL")) # flares
->>> len(result)
-52

### 2014-08-21 hek2.py

@@ -1,5 +1,0 @@
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       hek.attrs.FRM.Name=="SSW Latest Events")
->>> len(result)
-9

### 2014-08-21 hek3.py

@@ -1,4 +1,0 @@
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       (hek.attrs.Event.Coord1>50) 
-...                       or (hek.attrs.FL.PeakFlux>1000.0))

### 2014-08-21 hek4.py

@@ -1,4 +1,0 @@
->>> from sunpy.net import hek2vso
->>> h2v = hek2vso.H2VClient()
->>> vso_results = h2v.translate_and_query(result[0])
->>> h2v.vso_client.get(vso_results[0]).wait()

### 2014-08-21 helio.py

@@ -1,19 +1,0 @@
->>> from sunpy.net.helio import hec
->>> hc = hec.Client()
->>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T12:00:00"
->>> event_type = "cme"
-
-# From all the catalogues these which name contain our event of interest
->>> catalogues = hc.get_table_names()
->>> catalogues_event = [l[0] for l in catalogues 
-...                     if event_type in l[0] and 'list' not in l[0]]
-
-# Query all the catalogues that comes from cactus
->>> results = [hc.time_query(tstart, tend, event) 
-...            for event in catalogues_event if 'cactus' in event]
->>> for cat in results:
-...     print "{cat} has {nres} results".format(cat = cat.ID, \
-...                                             nres = len(cat.array))
-__helio_hec-cactus_stereoa_cme has 4 results
-__helio_hec-cactus_stereob_cme has 3 results
-__helio_hec-cactus_soho_cme has 7 results

### 2014-08-21 helioviewer.py

@@ -1,6 +1,0 @@
->>> from sunpy.net.helioviewer import HelioviewerClient
->>> hv = HelioviewerClient()
->>> hv.download_png("2099/01/01", 6,
-...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
-...                 "[SOHO,LASCO,C2,white-light,1,100]",
-...                 x0=0, y0=0, width=768, height=768)

### 2014-08-21 helioviewer2.py

@@ -1,6 +1,0 @@
->>> import sunpy.map
->>> filepath = hv.download_jp2("2012/07/05 00:30:00",
-...                            observatory='SDO',
-...                            instrument="HMI", detector="HMI", 
-...                            measurement="continuum")
->>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()

### 2014-08-21 lightcurve.py

@@ -1,9 +1,0 @@
->>> from sunpy import lightcurve
->>> from sunpy.time import TimeRange
->>> goes = lightcurve.GOESLightCurve.create(TimeRange("2011-06-07 06:00",
-...                                         "2011-06-07 08:00"))
->>> goes.peek()
->>> print goes.data["B_FLUX"].max()
-2.55542e-05
->>> print goes.data["B_FLUX"].idxmax()
-2011-06-07 06:41:26

### 2014-08-21 map1.py

@@ -1,4 +1,0 @@
->>> import sunpy.map
->>> aiamap = sunpy.map.Map("aia_file.fits")
->>> smap = aiamap.submap([-1200, -200], [-1000, -0])
->>> smap.peek(draw_grid=True)

### 2014-08-21 map2.py

@@ -1,11 +1,0 @@
->>> import sunpy.map
->>> import matplotlib.pyplot as plt
->>> compmap = sunpy.map.Map("aia_1600_image.fits", "RHESSI_image.fits", 
-...                         composite=True)
->>> compmap.set_levels(1, range(0, 50, 5), percent=True)
->>> compmap.set_colors(1, "Reds_r")
-#Plot the result and crop
->>> ax = plt.subplot()
->>> compmap.plot()
->>> ax.axis([200, 600, -600, -200])
->>> plt.show()

### 2014-08-21 map3.py

@@ -1,3 +1,0 @@
->>> import sunpy.map
->>> cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
->>> cubemap.peek()

### 2014-08-21 python_code/database.py

@@ -1,0 +1,11 @@
+from sunpy.net import vso
+from sunpy.database import Database
+database = Database("sqlite:///")
+database.download(
+     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
+     vso.attrs.Instrument('AIA'))
+len(database)
+from sunpy.database.tables import display_entries
+print display_entries(
+     database,
+     ["id", "observation_time_start", "wavemin", "wavemax"])

### 2014-08-21 python_code/hek3.py

@@ -1,0 +1,4 @@
+result = client.query(hek.attrs.Time(tstart, tend), 
+                      hek.attrs.EventType("FL"),
+                      (hek.attrs.Event.Coord1>50) 
+                      or (hek.attrs.FL.PeakFlux>1000.0))

### 2014-08-21 python_code/helioviewer2.py

@@ -1,0 +1,6 @@
+import sunpy.map
+filepath = hv.download_jp2("2012/07/05 00:30:00",
+                            observatory='SDO',
+                            instrument="HMI", detector="HMI", 
+                            measurement="continuum")
+sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()

### 2014-08-21 python_code/map1.py

@@ -1,0 +1,5 @@
+import sunpy
+import sunpy.map
+aiamap = sunpy.map.Map(sunpy.AIA_171_IMAGE)
+smap = aiamap.submap([-1200, -200], [-1000, -0])
+smap.peek(draw_grid=True)

### 2014-08-21 python_code/map2.py

@@ -1,0 +1,11 @@
+import sunpy.map
+import matplotlib.pyplot as plt
+compmap = sunpy.map.Map(sunpy.AIA_171_IMAGE, sunpy.RHESSI_IMAGE, 
+                         composite=True)
+compmap.set_levels(1, range(0, 50, 5), percent=True)
+compmap.set_colors(1, "Reds_r")
+#Plot the result and crop
+ax = plt.subplot()
+compmap.plot()
+ax.axis([200, 600, -600, -200])
+plt.show()

### 2014-08-21 python_code/map3.py

@@ -1,0 +1,3 @@
+import sunpy.map
+cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
+cubemap.peek()

### 2014-08-21 python_code/util1.py

@@ -1,0 +1,8 @@
+from sunpy import wcs
+print(wcs.convert_hg_hpc(10, 53))
+# Convert that position back to heliographic coordinates
+print(wcs.convert_hpc_hg(100.49, 767.97))
+# Try to convert a position which is not on the Sun to HG
+print(wcs.convert_hpc_hg(-1500, 0))
+# Convert sky coordinate to a position in HCC
+print(wcs.convert_hpc_hcc(-300, 400, z=True))

### 2014-08-21 python_code/vso1.py

@@ -1,0 +1,9 @@
+from sunpy.net import vso
+client = vso.VSOClient()
+tstart, tend = "2011/6/7 05:30", "2011/6/7 10:30"
+lasco_query = client.query(vso.attrs.Time(tstart, tend),
+                           vso.attrs.Instrument('lasco'))
+lasco_query.num_records()
+lasco_query.show() 
+pathformat = "/data/{instrument}/{detector}/{file}.fits"
+results = client.get(coronagraphs, path = pathformat)

### 2014-08-21 spectra.py

@@ -1,5 +1,0 @@
->>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
->>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
->>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
->>> callisto_nobg = callisto.subtract_bg()
->>> callisto_nobg.peek(vmin=0)

### 2014-08-21 util1.py

@@ -1,14 +1,0 @@
->>> from sunpy import wcs
->>> wcs.convert_hg_hpc(10, 53)
-(100.49244115330731, 767.97438321917502)
-# Convert that position back to heliographic coordinates
->>> wcs.convert_hpc_hg(100.49, 767.97)
-(9.9996521808465175, 52.999563684874893)
-# Try to convert a position which is not on the Sun to HG
->>> wcs.convert_hpc_hg(-1500, 0)
-sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
-  distance = q - np.sqrt(distance)
-(nan, nan)
-# Convert sky coordinate to a position in HCC
->>> wcs.convert_hpc_hcc(-300, 400, z=True)
-(-216716967.63331246, 288956420.9477042, 594364636.2208252)

### 2014-08-21 util2.py

@@ -1,15 +1,0 @@
->>> from sunpy.sun import constants
->>> print(constants.mass)
-  Name   = Solar mass
-  Value  = 1.9891e+30
-  Error  = 5e+25
-  Units  = kg
-  Reference = Allen's Astrophysical Quantities 4th Ed.
-# Verify the average density of the Sun and convert to cgs
->>> (constants.mass/constants.volume).cgs
-<Quantity 1.40851154227 g / (cm3)>
-# Search for the age of the Sun
->>> constants.find("age")
-['age', 'average angular size', 'average density', 'average intensity']
->>> constants.value('age'), constants.unit('age')
-(4600000000.0, Unit("yr"))

### 2014-08-21 vso1.py

@@ -1,15 +1,0 @@
->>> from sunpy.net import vso
->>> client = vso.VSOClient()
->>> tstart, tend = "2011/6/7 05:30", "2011/6/7 10:30"
->>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
-...                            vso.attrs.Instrument('lasco'))
->>> lasco_query.num_records()
-40
->>> lasco_query.show() 
-Start time           End time             Source  Instrument  Type
-----------           --------             ------  ----------  ----
-2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
-2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
-...
->>> pathformat = "/data/{instrument}/{detector}/{file}.fits"
->>> results = client.get(coronagraphs, path = pathformat)

### 2014-08-21 vso2.py

@@ -1,17 +1,0 @@
->>> condition = (vso.attrs.Detector("cor1") |
-...              vso.attrs.Wave(125, 135) |
-...              vso.attrs.Wave(165, 175) ) # in angstroms
->>> advanced = client.query(vso.attrs.Time(tstart, tend), condition)
->>> advanced.num_records()
-4434
->>> advanced.show()
-Start time           End time             Source    Instrument  Type
-----------           --------             ------    ----------  ----
-2011-06-07 00:00:00  2011-06-08 00:00:00  SDO       EVE         FULLDISK
-...
-2011-06-07 05:31:09  2011-06-07 05:31:19  PROBA2    SWAP        FULLSUN
-...
-2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
-2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
-...
-2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK

### 2014-08-21 build_article.py
created code text files

@@ -1,38 +1,7 @@
 #!/usr/bin/env python
 import os
-import glob
-from os.path import basename
 
 paper_name = "Sunpy_paper_0.4"
-
-# delete old output files
-py_out_files = glob.glob("py_*.txt")
-for file in py_out_files:
-    try:
-        os.remove(file)
-    except:
-        pass
-
-py_files = glob.glob("python_code/*.py")
-print(py_files)
-for file in py_files:
-    # the following just runs the file to create any pdfs the script may generate
-    os.system('python ' + file)
-
-    pretty_text_file = open('py_' + basename(file).split('.')[0] + ".txt", 'w')
-    f = open(file)
-    print("Running..." + file)
-    import_statement = ['']
-    for line in f.readlines():
-        #    pretty_text_file.write(">>> " + content)
-        #else pretty_text_file.write(content)
-        print(line)
-        if line[0] != '#':
-            pretty_text_file.write(">>> " + line)
-        else:
-            pretty_text_file.write(line)
-    f.close()
-    pretty_text_file.close()
             
 try:
     os.remove(paper_name + '.aux')
@@ -44,8 +13,8 @@ try:
 except:
     pass
     
-#os.system('pdflatex -shell-escape ' + paper_name)
-#os.system('pdflatex -shell-escape ' + paper_name)
-#os.system('bibtex ' + paper_name)
-#os.system('pdflatex -shell-escape ' + paper_name)
-#os.system('pdflatex -shell-escape ' + paper_name)
+os.system('pdflatex -shell-escape ' + paper_name)
+os.system('pdflatex -shell-escape ' + paper_name)
+os.system('bibtex ' + paper_name)
+os.system('pdflatex -shell-escape ' + paper_name)
+os.system('pdflatex -shell-escape ' + paper_name)

### 2014-08-25 3-2-HEK.tex
created code text files

--- 2014-07-21 3-2-HEK.tex
@@
 The Sun is an active star and exhibits a wide range of transient phenomena 
-(e.g., flares, radio bursts) on many different time-scales, length-scales, and 
+(e.g., flares, radio bursts, coronal mass ejections) at many different time-scales, 
+length-scales, and 
 wavelengths. Observations and metadata concerning these phenomena are collected 
@@
 and some is generated by the Solar Dynamics Observatory Feature Finding Team 
-\citep{martens2012}.  The advantage of the HEK is it 
+\citep{martens2012}.  A key feature of the HEK is that it
 provides an homogeneous and well-described interface to a large amount of 
@@
 accesses this information through the \texttt{hek} module.  The \texttt{hek} module makes use of the 
-HEK API\footnote{For more information see \url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
+HEK public API\footnote{For more information see \url{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.
 
 Simple HEK queries consist of start time, an end time, and an event type 
-(Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
+(see Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
 two letter strings, and these strings are 
-identical to the two letter abbreviations found at the HEK website
-(\url{http://www.lmsal.com/hek/VOEvent_Spec.html}).
+identical to the two letter abbreviations defined by HEK 
+(see \url{http://www.lmsal.com/hek/VOEvent_Spec.html}). Users can see a
+complete list and description of these abbreviations by looking at the documentation
+for \texttt{hek.attrs.EventType}.
 
@@
 
-The module \texttt{hek.attrs} contains attributes of the HEK that can be used to
-construct HEK queries.  For example, a flare is an attribute of the HEK,
- and so 
-\texttt{hek.attrs.EventType("FL")} in Listing~\ref{code:hek:simple}
-can be alternatively replaced with \texttt{hek.attrs.FL}.
+Short-cuts are also provided for some often-used event types. For example, 
+the flare attribute can be declared as either 
+\texttt{hek.attrs.EventType("FL")} or as \texttt{hek.attrs.FL}.
 
@@
 operators. This allows filtering of the HEK entries by the properties of the 
-event. As was mentioned above, the HEK stores feature/event metadata obtained 
+event. As was mentioned above, the HEK stores feature and event metadata obtained 
 in different ways, known generally as feature recognition methods (FRMs). 
 Example in Listing~\ref{code:hek:frm} filters the results of the previous 
-result to return only those events that have the FRM `SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
+result to return only those events that have the FRM `SSW Latest Events'.  
+Multiple comparisons can be made by including more comma-separated
 conditions on the attributes in the call to the HEK query method.
@@
 HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
-and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
-returns flares west of 50 arcseconds or those that have a peak flux above 
-1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
-website).
+and \texttt{or}). The ability to use comparison and logical operators on HEK attributes allows 
+the construction of queries of almost arbitrary complexity.
+For the query in Listing \ref{code:hek:or} returns
+returns flares with helioprojective x coordinates west of 50 arcseconds or 
+those that have a peak flux above 1000.0 in units defined by the FRM.
+
 \begin{listing}[H]
@@
 
-The ability to use comparison and logical operators on HEK attributes allows 
-the construction of queries of almost arbitrary complexity. 
-The results of a HEK query can be used to download the 
-corresponding data from the VSO using SunPy's \texttt{H2VClient}, as 
-demonstrated in Listing~\ref{code:hek2vso}.
+Frequently after users have found events of interest the next step is to 
+download observational data. The \texttt{H2VClient} module makes this
+much easier by providing a translation layer between HEK query results
+and VSO queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.
 \begin{listing}[H]

### 2014-08-25 4-Util.tex
removed spaces
created code text files

--- 2014-07-21 4-Util.tex
@@
 constants in order to provide consistency in the calculations of derived solar 
-values  within the SunPy code base, but also to the user. Every solar 
-constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
+values within SunPy, but also to the user. Every solar 
+constant is provided as a \texttt{Constant} object as defined by the Astropy \texttt{units} package. Each 
 \texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
@@
 directly when importing the module. A larger list of constants can be 
-accessed through an interface modelled on that provided by the SciPy constants 
+accessed through an interface modeled on that provided by the SciPy constants 
 package and is available as a dictionary called \texttt{physical\_constants}. 

### 2014-08-25 2-1-Map.tex
created code text files
small fix for issue #117.

--- 2014-07-20 2-1-Map.tex
@@
 collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
-temporally and spatially aligned data respectively.
+spatially and temporally aligned data respectively.
 \texttt{CompositeMap} provides methods for overlaying spatially aligned 

### 2014-08-25 3-5-Database.tex
created code text files
correction to database wording to address #114

--- 2014-07-20 3-5-Database.tex
@@
 
-The \texttt{database} subpackage makes use of a database supported by
+The \texttt{database} subpackage can make use of any database software supported by
 {\texttt{SQLAlchemy} (\href{http://www.sqlalchemy.org}{http://www.sqlalchemy.org}). This library was chosen

### 2014-08-25 2-1-Map.tex

--- 2014-07-23 2-1-Map.tex
@@
 \begin{listing}[H]
-\pythoncode{map1.py}
+\pythoncode{pycode_map1.txt}
 \begin{center}
@@
 \begin{listing}[H]
-\pythoncode{map2.py}
+\pythoncode{pycode_map2.txt}
 \begin{center}
@@
 \begin{listing}[H]
-\pythoncode{map3.py}
+\pythoncode{pycode_map3.txt}
 \begin{center}

### 2014-08-25 3-1-VSO.tex
created code text files

--- 2014-07-23 3-1-VSO.tex
@@
 \begin{listing}[H]
-\pythoncode{vso1.py}
+\pythoncode{pycode_vso1.txt}
 \caption{Example of querying a single instrument over a time range and downloading the data}
@@
 \begin{listing}[H]
-\pythoncode{vso2.py}
+\pythoncode{pycode_vso2.txt}
 \caption{Example of an advanced VSO query using attribute objects,

### 2014-08-25 3-2-HEK.tex

@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> from sunpy.net import hek
->>> client = hek.HEKClient()
->>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL")) # flares
->>> len(result)
-52
-\end{minted}
+\pythoncode{pycode_hek.txt}
 \caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{pycon}
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       hek.attrs.FRM.Name=="SSW Latest Events")
->>> len(result)
-9
-\end{minted}
+\pythoncode{pycode_hek2.txt}
 \caption{An HEK query that returns only those flares that were
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
->>> result = client.query(hek.attrs.Time(tstart, tend), 
-...                       hek.attrs.EventType("FL"),
-...                       (hek.attrs.Event.Coord1>50) 
-...                       or (hek.attrs.FL.PeakFlux>1000.0))
-\end{minted}
+\pythoncode{pycode_hek3.txt}
 \caption{HEK query using the logical \texttt{or} operator.}
@@
 \begin{listing}[H]
-\begin{minted}[bgcolor=bg]{python}
->>> from sunpy.net import hek2vso
->>> h2v = hek2vso.H2VClient()
->>> vso_results = h2v.translate_and_query(result[0])
->>> h2v.vso_client.get(vso_results[0]).wait()
-\end{minted}
+\pythoncode{pycode_hek4.txt}
 \caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 

### 2014-08-25 4-Util.tex

--- 2014-07-23 4-Util.tex
@@
 \begin{listing}[H]
-\pythoncode{util1.py}
+\pythoncode{pycode_util1.txt}
 \caption{Using the \texttt{wcs} subpackage.}
@@
 \begin{listing}[H]
-\pythoncode{util2.py}
+\pythoncode{pycode_util2.txt}
 \caption{Using the \texttt{sun.constants} module.}

### 2014-08-25 Sunpy_paper_0.4.tex
Comment out summary and tweaks to author list
Add an acknowledgements section
added a fix to display all quotes in codeblocks as straight quotes
small stuff and removed andy's fix for quotes

@@
 
-\usepackage{minted}
+\usepackage[section]{minted}
+%\usepackage{upquote}
+%\AtBeginDocument{%
+%\def\PYZsq{\textquotesingle}%
+%}
 \definecolor{bg}{rgb}{0.95, 0.95, 0.95}
+
+\newmintedfile[pythoncode]{pycon}{
+bgcolor=bg,
+fontfamily=tt,
+linenos=true,
+numberblanklines=true,
+numbersep=12pt,
+numbersep=5pt,
+gobble=0,
+frame=leftline,
+framerule=0.4pt,
+framesep=2mm,
+funcnamehighlighting=true,
+tabsize=4,
+obeytabs=false,
+mathescape=false
+samepage=false, %with this setting you can force the list to appear on the same page
+showspaces=false,
+showtabs =false,
+texcl=false,
+}
+
 \usepackage{hyperref}
@@
 \MakePerPage{footnote} %the perpage package command
+
+\usepackage{aas_macros}
 
@@
 
-\input{solarsoft}
-
 \input{5-Dev}
@@
 
+\input{Summary}
+
+\input{acknowledgements}
+
 %%% References
 \bibliographystyle{stunat}
-\bibliography{Sunpy_paper_0.4}{}
+\bibliography{Sunpy_paper_0.4,refs}{}
 

### 2014-08-25 3-5-Database.tex

--- 2014-07-23 3-5-Database.tex
@@
 \begin{listing}[H]
-\pythoncode{database.py}
+\pythoncode{pycode_database.txt}
 \caption{Example usage of the \texttt{database} subpackage.}

### 2014-08-26 2-2-Lightcurve.tex
Solve #118 by removing reference to Factory.

@@
 included.  Future developments will introduce support for additional
-instruments and data products, as well as implementing a factory interface 
+instruments and data products, as well as implementing an interface 
 similar to that of \texttt{Map}.  Since there is no established standard
@@
 \begin{listing}[H]
-\pythoncode{lightcurve.py}
+\pythoncode{pycode_lightcurve.txt}
 \begin{center}

### 2014-08-26 4-Util.tex
fix for issue #122

@@
 
-\subsection{Sun}\label{ssec:util:sun}
-The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
+\subsection{Solar Constants and units}\label{ssec:util:sun}
+Physical quantities (i.e. a number associated with a unit) are an important part
+of scientific data analysis. SunPy makes use of the \texttt{Quantity} object provided by 
+Astropy \texttt{units} package. This object maintains the relationship between 
+a number and its unit and makes it easy to convert between units. 
+As these objects inherit from 
+NumPy's \texttt{ndarray}, they work well with standard representations of numbers. Using proper
+quantities inside of the code base also makes it easier to catch errors in calculations.
+SunPy is currently working on integrating quantities throughout the code base.
+In order to encourage the use of units and to enable consistency SunPy provides
+the \texttt{sun} subpackage which includes solar-specific data such as ephemerides and
 solar constants. The main namespace contains a number of functions that provide solar
-ephemerides such as the Sun-to-Earth distance, solar-cycle number, the mean 
+ephemerides such as the Sun-to-Earth distance, solar-cycle number, mean 
 anomaly, etc.
@@
 
-The \texttt{sun.constants} module provides a number of solar-related 
-constants in order to provide consistency in the calculations of derived solar 
-values within SunPy, but also to the user. Every solar 
-constant is provided as a \texttt{Constant} object as defined by the Astropy \texttt{units} package. Each 
-\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
-the constant's provenance (i.e., reference) and its uncertainty. Using 
-Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
-different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
-As these objects inherit from 
-NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
+The \texttt{sunpy.sun.constants} module provides a number of solar-related 
+constants in order to enable the calculation of derived solar 
+values within SunPy, but also to the user. All solar 
+constant are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
+\texttt{Constant} object defines a \texttt{Quantity}, along with 
+the constant's provenance (i.e., reference) and its uncertainty. The use of this package
+is shown in Listing~\ref{code:constants_code}.
 For convenience, a number of shortcuts to frequently used constants are provided 
 directly when importing the module. A larger list of constants can be 
-accessed through an interface modeled on that provided by the SciPy constants 
+accessed through an interface modeled on that provided by the SciPy \texttt{constants}
 package and is available as a dictionary called \texttt{physical\_constants}. 

### 2014-08-26 2-1-Map.tex

@@
 \texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
-of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
+of the full map is created by specifying the desired $x$ and $y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}

### 2014-08-26 4-Util.tex
Fixed issue #70
typo fix

@@
-\section{Additional functionality}\label{sec:util}
+\section{Additional Functionality}\label{sec:util}
 SunPy is meant to provide a consistent environment for solar data analysis. In 
@@
 values within SunPy, but also to the user. All solar 
-constant are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
+constants are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
 \texttt{Constant} object defines a \texttt{Quantity}, along with 

### 2014-08-26 2-1-Map.tex
refer to solar x and solar y instead of just x and y.

--- 2014-08-25 2-1-Map.tex
@@
 \texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
-of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
+of the full map is created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}

### 2014-08-26 2-2-Lightcurve.tex
added more instruments that are supported by lightcurve in 0.5

@@
 Currently, the \texttt{LightCurve} class is compatible with the
-following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
-average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
+following data sources: the \textit{GOES} X-ray Sensor (XRS), the \textit{Nobeyama Radioheliograph (NoRH)}, \textit{PROBA2}/LYRA, \textit{RHESSI}, \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
+average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}, and also supports a number of solar summary indices - such as average sunspot number - that are provided by the National Oceanic and Atmospheric Administration (NOAA).
+For each of these instruments, a subclass of the
 \texttt{LightCurve} object is initialised

### 2014-08-26 2-2-Lightcurve.tex
grammar fix.

--- 2014-08-26 2-2-Lightcurve.tex
@@
 Currently, the \texttt{LightCurve} class is compatible with the
-following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
-average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
+following data sources: the \textit{GOES} X-ray Sensor (XRS), the \textit{Nobeyama Radioheliograph (NoRH)}, \textit{PROBA2}/LYRA, \textit{RHESSI}, \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
+average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.
+\texttt{LightCurve} also supports a number of solar summary indices - such as average sunspot number - that are provided by the National Oceanic and Atmospheric Administration (NOAA).
+For each of these instruments, a subclass of the
 \texttt{LightCurve} object is initialised

### 2014-08-26 2-1-Map.tex
Some words on metadata.
Add an example of metadata persistance.

--- 2014-08-25 2-1-Map.tex
@@
 
-The \texttt{Map} class stores all of the metadata retrieved from the header of
+The \texttt{GenericMap} class stores all of the metadata retrieved from the header of
 the image file in the \texttt{meta} attribute and provides convenience 
@@
 \texttt{wavelength} or \texttt{coordinate\_system}.
+These properties are dynamic mappings to the underlying metadata and all methods 
+of the \textit{GenericMap} class modify the meta data where needed.
+For example, if \verb|aiamap.meta[`instrume']| is modified then \verb|aiamap.instrument| 
+will reflect this change.
+Currently this is implemented by not preserving the keywords of the input data,
+instead modifying meta data to a set of ``standard" keys supported by SunPy.
 Listing \ref{code:aia_1} demonstrates the quick-look functionality of 

### 2014-08-26 1-Introduction.tex
added in some typical workflows in to the introduction

@@
 Science is driven by the analysis of data of an ever-growing variety and 
-complexity.
-Modern advances in sensor technology, combined with the availability of 
+complexity. Advances in sensor technology, combined with the availability of 
 inexpensive 
-storage, has led to rapid increases in the amount of data available to scientists in almost
+storage, have led to rapid increases in the amount of data available to scientists in almost
 every discipline.  Solar physics is no exception to this trend. For example,
@@
 in February 2010, produces over 1 TB of data per day \cite{pesnell2012}. Managing and
-analysing this mountain of data requires increasingly sophisticated software
+analysing these data requires increasingly sophisticated software
 tools. These tools should be robust, easy to use and modify, have a transparent
@@
 
-SunPy is designed to be a clean, simple-to-use, and well-structured open-source package that provides 
-the \textit{core} tools for solar data analysis, motivated by the need for a free and 
-modern alternative to the existing SolarSoft (SSW) library. While SSW is open source 
-and freely available, it relies on IDL (Interactive Data Language), a proprietary 
-data-analysis environment.
+A typical workflow begins with a solar physicist manually identifying
+a small number of events of interest on the Sun.  This is typically
+done in order to investigate in detail the physics of these events
+(for example, the large solar flare of 23 July 2002 has a volume of
+the Astrophysical Journal dedicated to it).  In this workflow, data
+from many different instruments are obtained.  These data are
+typically in many different storage formats (for example, FITS, CSV,
+or binary files), and contain many different types of data (such as
+images, lightcurves and spectra).  The repositories these data reside
+in can have different access methods.  This workflow is characterized
+by the large number of heterogeneous datasets used in the
+investigation of a small number of solar events.
+
+Another typical workflow begins with the solar physicist identifying a
+large sample of data or events.  The goal here is obtain information
+about the population in general.  An example might be to calculate the
+fractal dimension of a large number of active region magnetic fields
+\cite{2005ApJ...631..628M}, or to calculate the observed temperatures
+in a population of solar flares \cite{2012ApJS..202...11R}.  This
+workflow is typically characterized by lower data heterogeneity, but
+with a larger number of files.
+
+The volume and variety of solar data used in these workflows drives
+the need for an environment in which obtaining and performing common
+solar-physics operations on these data is as simple and intuitive as
+possible.  SunPy is designed to be a clean, simple-to-use, and
+well-structured open-source package that provides the \textit{core}
+tools for solar data analysis, motivated by the need for a free and
+modern alternative to the existing SolarSoft (SSW) library. While SSW
+is open source and freely available, it relies on IDL (Interactive
+Data Language), a proprietary data-analysis environment.
 

### 2014-08-26 1-Introduction.tex

@@
 done in order to investigate in detail the physics of these events
-(for example, the large solar flare of 23 July 2002 has a volume of
-the Astrophysical Journal dedicated to it).  In this workflow, data
-from many different instruments are obtained.  These data are
-typically in many different storage formats (for example, FITS, CSV,
-or binary files), and contain many different types of data (such as
-images, lightcurves and spectra).  The repositories these data reside
-in can have different access methods.  This workflow is characterized
-by the large number of heterogeneous datasets used in the
-investigation of a small number of solar events.
+(for example, the large solar flare of 23 July 2002 has Astrophysical
+Journal Letters volume 595, dedicated to the analysis of this flare).
+In this workflow, data from many different instruments are obtained.
+These data are typically in many different storage formats (for
+example, FITS, CSV, or binary files), and contain many different types
+of data (such as images, lightcurves and spectra).  The repositories
+these data reside in can have different access methods.  This workflow
+is characterized by the large number of heterogeneous datasets used in
+the investigation of a small number of solar events.
 

### 2014-08-26 3-3-HELIO.tex
Fixes for citations

@@
 discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
-inter-planetary data \citep{dps2012}.
+inter-planetary data \citep{perez-suarez2012}.
 HELIO is built with a Service-Oriented Architecture, 
@@
 As with all of the HELIO services, the HEC service provides results in VOTable 
-data format (defined by IVOA \cite{ochsenbein_ivoa_2011}).
+data format (defined by IVOA, see \citealt{ochsenbein2011}).
 The \texttt{hec} module parses this output using the \texttt{astropy.io.votable} package.
@@
 \begin{listing}[h]
-\pythoncode{helio.py}
+\pythoncode{pycode_helio.txt}
 \caption{Example of querying the HEC service to multiple CME
 catalogues, in this case the ones detected automatically 
-by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht_automated_2009}.}
+by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht2009}.}
 \label{code:helio}

### 2014-08-27 python_code/helio.py
Fix for issue #149

@@ -1,5 +1,5 @@
 from sunpy.net.helio import hec
-hc = hec.Client()
+hc = hec.HECClient()
 tstart, tend = "2011-06-07T06:00:00", "2011-06-07T12:00:00"
 event_type = "cme"
 

### 2014-08-27 reply_referee.txt
added a draft of the reply to the referees.

We thank both referees for their reports on this paper. In the revised manuscript we have taken into account the suggestions of both referees and believe the paper to be improved as a result. The specific points raised by the referees are addressed below.

RESPONSE TO REFEREE 1

1) We agree that the paper should illustrate how SunPy enables science. To that end, we have added descriptions in the Introduction section of typical workflows for solar physicists and discuss how the features of SunPy are suited to enabling those workflows.

2)

3)

4)

5)

6) We have corrected the list of references as requested.

RESPONSE TO REFEREE 2

1) The metadata and the convenience properties are indeed dynamically linked, thus a change in aia_map.meta['instrument'] (for example) will result in an identical change in the aia_map.instrument convenience property. This is clarified in the text of Section 2.1.

2) In the example shown the sub-image selection is achieved through the use of data coordinates, a common method in solar physics as an alternative to Python indexing. We agree that this was unclear in the manuscript and clarify the Listing 1 description accordingly

3) The referee is correct - the CompositeMap and MapCube descriptions were accidentally reversed. CompositeMap should refer to spatially aligned data and MapCube to temporally aligned data. We have corrected the text of the manuscript in Section 2.1.

4) We decided to remove the term 'factory' from the description of Map, as in the end we do not discuss this any further throughout the manuscript, and may cause confusion. We instead refer more generally to the Map creation.

5) We add to our discussion of units in SunPy, as the referee suggested. The goal of SunPy in the future is for all units to be handled using the Astropy sub-package. As of 0.5 however this feature has not been implemented, except in the sunpy.sun module. This is now discussed in Section 4 of the manuscript.

6)

7)

8)

9)

10) We agree with the distinction made by the referee - we clarify the text to refer to 'database software supported by SQLAlchemy' in Section 3.5.

7)

### 2014-08-27 2-1-Map.tex
explained the 'SJI' acronym
miscellaneous tweaks from aringlis.

--- 2014-08-26 2-1-Map.tex
@@
 The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, including a FITS file as shown in 
+from a variety of sources, including from FITS (Flexible Image Transport System) files, the standard format for storing image data in solar physics and astrophysics.
+An example of creating a \texttt{Map} object from a FITS file is shown in
 Listing~\ref{code:aia_1}.
@@
 \end{center}
-\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
-on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI X-ray image data composited
+on top of an \textit{SDO}/AIA 1600 $\AA$ image. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \end{center}
-\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
+\caption{Example showing the creation of a \texttt{MapCube} from a list of AIA image files. The 
 resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 

### 2014-08-27 2-Data_Types.tex
miscellaneous tweaks from aringlis.

@@
 three primary varieties of solar physics data: images, time series, and
-spectra. These core data types are supported by SunPy's classes:
+spectra. These core data types are supported by the SunPy classes:
 \texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
@@
 stored in the \texttt{data} attribute, while the metadata should be stored 
-in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
+in the \texttt{meta} attribute (currently, only \texttt{Map} and \texttt{LightCurve} have this feature 
 fully implemented). 

### 2014-08-27 3-2-HEK.tex
Fixes for citations
miscellaneous tweaks from aringlis.

@@
 in different ways, known generally as feature recognition methods (FRMs). 
-Example in Listing~\ref{code:hek:frm} filters the results of the previous 
-result to return only those events that have the FRM `SSW Latest Events'.  
+The example in Listing~\ref{code:hek:frm} repeats the previous 
+HEK query (see Listing \ref{code:hek:simple}}, with an additional filter enabled to return only those events that have the FRM `SSW Latest Events'.  
 Multiple comparisons can be made by including more comma-separated

### 2014-08-27 3-3-HELIO.tex
miscellaneous tweaks from aringlis.

--- 2014-07-23 3-3-HELIO.tex
@@
 \begin{listing}[h]
-\pythoncode{helio.py}
+\pythoncode{pycode_helio.txt}
 \caption{Example of querying the HEC service to multiple CME
 catalogues, in this case the ones detected automatically 
-by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht_automated_2009}.}
+by the Computer Aided CME Tracking feature recognition algorithm (\href{http://sidc.oma.be/cactus/}{CACTus}) \citep{robbrecht_automated_2009}.}
 \label{code:helio}

### 2014-08-27 2-Data_Types.tex

--- 2014-01-31 2-Data_Types.tex
@@
 
-The core of SunPy is a set of data structures that are specifically designed for the
-three primary varieties of solar physics data: images, time series, and
-spectra. These core data types are supported by SunPy's classes:
-\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
-and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).
+The core of SunPy is a set of data structures that are specifically
+designed for the three primary varieties of solar physics data:
+images, time series, and spectra. These core data types are supported
+by the SunPy classes: \texttt{Map} (2D spatial data),
+\texttt{LightCurve} (1D temporal series), and \texttt{Spectrum} and
+\texttt{Spectrogram} (1D and 2D spectra).  The purpose of these
+classes is to provide the same core data type to the SunPy user
+regardless of the differences in source data.  For example, if two
+different instruments use different time formats to describe the
+observation time of their images, the corresponding SunPy \texttt{Map}
+object for each of them expresses the observation time in the same
+way.  This simplifies the workflow for the user when handling data
+from multiple sources.
 

### 2014-08-27 2-1-Map.tex
included mission and instrument references for all the supported map sources

--- 2014-08-26 2-1-Map.tex
@@
 instruments:
-\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
-\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
-\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
-and \textit{IRIS} SJI frames.
+
+\textit{Yohkoh}/SXT\footnote{SXT: Solar X-ray Telescope \cite{1991SoPh..136....1O} and \cite{1991SoPh..136...37T}},
+\textit{SOHO}/EIT and LASCO\footnote{SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}},
+\textit{RHESSI}\footnote{RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}},
+\textit{STEREO}/EUVI and COR1/2\footnote{STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}},
+\textit{Hinode}/XRT\footnote{XRT: X-Ray Telescope, \cite{2007SoPh..243....3K} and \cite{2007SoPh..243...63G}},
+\textit{PROBA2}/SWAP\footnote{PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}},
+\textit{SDO}/AIA and HMI\footnote{HMI: Helioseismic Magnetic Imager, 2012SoPh..275..207S}, and
+\textit{IRIS}\footnote{IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L}} SJI (slit-jaw imager) frames.
 

### 2014-08-27 2-Data_Types.tex
included mission and instrument references for all the supported map sources

--- 2014-01-31 2-Data_Types.tex
@@
 make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
-sub-type for data from the \textit{SDO}/AIA instrument.
+sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \cite{lemen2012}) instrument.
 

### 2014-08-27 1-Introduction.tex
added in FITS reference

@@
 NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched
-in February 2010, produces over 1 TB of data per day \cite{pesnell2012}. Managing and
+in February 2010, produces over 1 TB of data per day \citep{pesnell2012}. Managing and
 analysing these data requires increasingly sophisticated software
@@
 Building upon these foundations, packages such as \texttt{astropy} (astronomy)
-\cite{theastropycollaboration2013}, \texttt{pandas} (time-series) 
-\cite{mckinney2010, mckinney2012}, and \texttt{scikit-image} (image processing)
+\citep{theastropycollaboration2013}, \texttt{pandas} (time-series)
+\citep{mckinney2010, mckinney2012}, and \texttt{scikit-image} (image processing)
 \citep{vanderwalt2014} provide more domain-specific functionality.
@@
 These data are typically in many different storage formats (for
-example, FITS, CSV, or binary files), and contain many different types
-of data (such as images, lightcurves and spectra).  The repositories
-these data reside in can have different access methods.  This workflow
-is characterized by the large number of heterogeneous datasets used in
-the investigation of a small number of solar events.
+example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
+binary files), and contain many different types of data (such as
+images, lightcurves and spectra).  The repositories these data reside
+in can have different access methods.  This workflow is characterized
+by the large number of heterogeneous datasets used in the
+investigation of a small number of solar events.
 
@@
 fractal dimension of a large number of active region magnetic fields
-\cite{2005ApJ...631..628M}, or to calculate the observed temperatures
-in a population of solar flares \cite{2012ApJS..202...11R}.  This
+\citep{2005ApJ...631..628M}, or to calculate the observed temperatures
+in a population of solar flares \citep{2012ApJS..202...11R}.  This
 workflow is typically characterized by lower data heterogeneity, but

### 2014-08-27 1-Introduction.tex
added in SSW reference

@@
 tools for solar data analysis, motivated by the need for a free and
-modern alternative to the existing SolarSoft (SSW) library. While SSW
-is open source and freely available, it relies on IDL (Interactive
-Data Language), a proprietary data-analysis environment.
+modern alternative to the existing SolarSoft (SSW) library
+\citep{freeland1998}. While SSW is open source and freely available,
+it relies on IDL (Interactive Data Language), a proprietary
+data-analysis environment.
 

### 2014-08-27 2-2-Lightcurve.tex
lightcurve data source references

@@
 Currently, the \texttt{LightCurve} class is compatible with the
-following data sources: the \textit{GOES} X-ray Sensor (XRS), the \textit{Nobeyama Radioheliograph (NoRH)}, \textit{PROBA2}/LYRA, \textit{RHESSI}, \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
-average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.
-\texttt{LightCurve} also supports a number of solar summary indices - such as average sunspot number - that are provided by the National Oceanic and Atmospheric Administration (NOAA).
-For each of these instruments, a subclass of the
-\texttt{LightCurve} object is initialised
-(e.g., \texttt{GOESLightCurve}) which inherits from
-\texttt{LightCurve}, but allows instrument-specific functionality to be
-included.  Future developments will introduce support for additional
-instruments and data products, as well as implementing an interface 
-similar to that of \texttt{Map}.  Since there is no established standard
-as to how time-series data should be stored and distributed, each SunPy 
-\texttt{LightCurve} object subclass provides the ability to download its corresponding 
-specific data format in its constructor and parse that file type.
+following data sources: the Geostationary Operational Environmental
+Satellite (\textit{GOES}) X-ray Sensor (XRS), the \textit{Nobeyama
+  Radioheliograph (NoRH)}, \textit{PROBA2} Large Yield Radiometer
+(LYRA, \cite{2013SoPh..286...21D}), \textit{RHESSI},
+\textit{SDO} EUV Variability Experiment (EVE\footnote{Note that only the level ``OCS'' and average
+  CSV files is currently implemented -- see
+  \url{http://lasp.colorado.edu/home/eve/data/}}, \citep{2012SoPh..275..115W}). \texttt{LightCurve}
+also supports a number of solar summary indices - such as average
+sunspot number - that are provided by the National Oceanic and
+Atmospheric Administration (NOAA).  For each of these sources, a
+subclass of the \texttt{LightCurve} object is initialised (e.g.,
+\texttt{GOESLightCurve}) which inherits from \texttt{LightCurve}, but
+allows instrument-specific functionality to be included.  Future
+developments will introduce support for additional instruments and
+data products, as well as implementing an interface similar to that of
+\texttt{Map}.  Since there is no established standard as to how
+time-series data should be stored and distributed, each SunPy
+\texttt{LightCurve} object subclass provides the ability to download
+its corresponding specific data format in its constructor and parse
+that file type.
 

### 2014-08-27 1-Introduction.tex

--- 2014-08-27 1-Introduction.tex
@@
 These data are typically in many different storage formats (for
-example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
-binary files), and contain many different types of data (such as
-images, lightcurves and spectra).  The repositories these data reside
-in can have different access methods.  This workflow is characterized
-by the large number of heterogeneous datasets used in the
-investigation of a small number of solar events.
+example, FITS, CSV, or binary files), and contain many different types
+of data (such as images, lightcurves and spectra).  The repositories
+these data reside in can have different access methods.  This workflow
+is characterized by the large number of heterogeneous datasets used in
+the investigation of a small number of solar events.
 

### 2014-08-27 2-1-Map.tex

--- 2014-08-27 2-1-Map.tex
@@
 \textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
-and \textit{IRIS} SJI frames.
+and \textit{IRIS} SJI (slit-jaw imager) frames.
 
-The \texttt{Map} class stores all of the metadata retrieved from the header of
+The \texttt{GenericMap} class stores all of the metadata retrieved from the header of
 the image file in the \texttt{meta} attribute and provides convenience 

### 2014-08-27 3-4-Helioviewer.tex

@@
 project maintains archives of all of its data in JPEG2000 format (for further
-details on the Helioviewer Project see \citealt{muller2009}). The
+details on the Helioviewer Project, see \citealt{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source
@@
 \begin{listing}[H]
-\pythoncode{helioviewer.py}
+\pythoncode{pycode_helioviewer.txt}
 \begin{center}
@@
 \begin{listing}[H]
-\pythoncode{helioviewer2.py}
+\pythoncode{pycode_helioviewer2.txt}
 \begin{center}

### 2014-08-27 2-1-Map.tex
small correction
changed caption for listing 1.

@@
 The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, including from FITS (Flexible Image Transport System) files, the standard format for storing image data in solar physics and astrophysics.
-An example of creating a \texttt{Map} object from a FITS file is shown in
+from a variety of sources, including a FITS file as shown in 
 Listing~\ref{code:aia_1}.
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
-of the full map is created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
+\texttt{GenericMap}. First, a map is created from an \textit{SDO}/AIA FITS file. In this case, a demonstration file contained within the SunPy repository is used. A cutout
+of the full map is then created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}
@@
 \end{center}
-\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI X-ray image data composited
-on top of an \textit{SDO}/AIA 1600 $\AA$ image. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
+\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
+on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
 \label{code:compmap_1}
@@
 \end{center}
-\caption{Example showing the creation of a \texttt{MapCube} from a list of AIA image files. The 
+\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
 resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 

### 2014-08-27 2-1-Map.tex
cleaning up citation styles

@@
 instruments:
-\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
-\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
-\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
-and \textit{IRIS} SJI (slit-jaw imager) frames.
+
+\textit{Yohkoh}/SXT\footnote{SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T}.},
+\textit{SOHO}/EIT and LASCO\footnote{SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}.},
+\textit{RHESSI}\footnote{RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}.},
+\textit{STEREO}/EUVI and COR1/2\footnote{STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}.},
+\textit{Hinode}/XRT\footnote{XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.},
+\textit{PROBA2}/SWAP\footnote{PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}.},
+\textit{SDO}/AIA and HMI\footnote{HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}.}, and
+\textit{IRIS}\footnote{IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L}.} SJI (slit-jaw imager) frames.
 
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. First, a map is created from an \textit{SDO}/AIA FITS file. In this case, a demonstration file contained within the SunPy repository is used. A cutout
-of the full map is then created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
+\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
+of the full map is created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
 \label{code:aia_1}

### 2014-08-27 2-2-Lightcurve.tex
cleaning up citation styles

@@
   Radioheliograph (NoRH)}, \textit{PROBA2} Large Yield Radiometer
-(LYRA, \cite{2013SoPh..286...21D}), \textit{RHESSI},
-\textit{SDO} EUV Variability Experiment (EVE\footnote{Note that only the level ``OCS'' and average
+(LYRA, \citealt{2013SoPh..286...21D}), \textit{RHESSI},
+\textit{SDO} EUV Variability Experiment\footnote{Note that only the level ``OCS'' and average
   CSV files is currently implemented -- see
-  \url{http://lasp.colorado.edu/home/eve/data/}}, \citep{2012SoPh..275..115W}). \texttt{LightCurve}
+  \url{http://lasp.colorado.edu/home/eve/data/}} (EVE, \citealt{2012SoPh..275..115W}). \texttt{LightCurve}
 also supports a number of solar summary indices - such as average

### 2014-08-27 2-Data_Types.tex
cleaning up citation styles

--- 2014-08-27 2-Data_Types.tex
@@
 make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
-sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \cite{lemen2012}) instrument.
+sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \citealt{lemen2012}) instrument.
 

### 2014-08-27 2-Data_Types.tex

@@
 
-The core of SunPy is a set of data structures that are specifically designed for the
-three primary varieties of solar physics data: images, time series, and
-spectra. These core data types are supported by the SunPy classes:
-\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
-and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).
+The core of SunPy is a set of data structures that are specifically
+designed for the three primary varieties of solar physics data:
+images, time series, and spectra. These core data types are supported
+by the SunPy classes: \texttt{Map} (2D spatial data),
+\texttt{LightCurve} (1D temporal series), and \texttt{Spectrum} and
+\texttt{Spectrogram} (1D and 2D spectra).  The purpose of these
+classes is to provide the same core data type to the SunPy user
+regardless of the differences in source data.  For example, if two
+different instruments use different time formats to describe the
+observation time of their images, the corresponding SunPy \texttt{Map}
+object for each of them expresses the observation time in the same
+way.  This simplifies the workflow for the user when handling data
+from multiple sources.
 

### 2014-08-27 3-3-HELIO.tex

--- 2014-08-26 3-3-HELIO.tex
@@
 catalogues, in this case the ones detected automatically 
-by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht2009}.}
+by the Computer Aided CME Tracking feature recognition algorithm (\href{http://sidc.oma.be/cactus/}{CACTus}) \citep{robbrecht_automated_2009}.}
 \label{code:helio}

### 2014-08-28 2-1-Map.tex
edits from full read thru

@@
 class provides methods for typical operations on 2D data, such as rotation and 
-re-sampling, as well as visualisation functionality.
+re-sampling, as well as visualisation.
 The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, including from FITS (Flexible Image Transport System) files, the standard format for storing image data in solar physics and astrophysics.
+from a variety of sources, including from FITS (Flexible Image Transport System) 
+files, the standard format for storing image data in solar physics and astrophysics community. 
 An example of creating a \texttt{Map} object from a FITS file is shown in 
@@
 to be subclassed. Each subclass of \texttt{GenericMap} can register 
-with the \texttt{Map} creation factory, which will then automatically return an instance
+with the \texttt{Map} creation function, which will then automatically return an instance
 of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
-SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
+SunPy v0.5 has \texttt{GenericMap} specialisations for the following 
 instruments:
 
-\textit{Yohkoh}/SXT\footnote{SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T}.},
-\textit{SOHO}/EIT and LASCO\footnote{SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}.},
-\textit{RHESSI}\footnote{RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}.},
-\textit{STEREO}/EUVI and COR1/2\footnote{STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}.},
-\textit{Hinode}/XRT\footnote{XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.},
-\textit{PROBA2}/SWAP\footnote{PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}.},
-\textit{SDO}/AIA and HMI\footnote{HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}.}, and
-\textit{IRIS}\footnote{IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L}.} SJI (slit-jaw imager) frames.
+\begin{itemize}
+\item \textit{Yohkoh}/SXT - SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T},
+\item \textit{SOHO}/EIT and LASCO - SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}
+\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}.},
+\item \textit{STEREO}/EUVI and COR1/2 - STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}
+\item \textit{Hinode}/XRT - XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
+\item \textit{PROBA2}/SWAP - PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}
+\item \textit{SDO}/AIA and HMI - HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
+\item \textit{IRIS} - IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L} SJI (slit-jaw imager) frames.           
+\end{itemize}
 
@@
 \caption{Example of the \texttt{AIAMap} specialisation of 
-\texttt{GenericMap}. First, a map is created from an \textit{SDO}/AIA FITS file. In this case, a demonstration file contained within the SunPy repository is used. A cutout
+\texttt{GenericMap}. First, a map is created from a sample \textit{SDO}/AIA FITS file. In this case, a demonstration file contained within the SunPy repository is used. A cutout
 of the full map is then created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}

### 2014-08-28 2-3-Spectra.tex
created code text files
spectra data source references
edits from full read thru

@@
 \href{http://www.e-callisto.org/}{e-Callisto}
-solar radio spectrometer network and \textit{STEREO}/SWAVES spectrograms.
+solar radio spectrometer network \citep{2009EM&P..104..277B} and \textit{STEREO}/SWAVES spectrograms \citep{2008SSRv..136..487B}.
 
 Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram}
-object retrieves spectrogram data in the time range specified taken at
-the observatory of interest.  When the data is requested using the
+object retrieves spectrogram data in the time range specified.  
+When the data is requested using the
 \texttt{from\_range()} function, the object merges all the downloaded
@@
 a constant background over time for each frequency channel.
-% RJH: Which subtraction method?  If the specifics are irrelevant, cut it.
-% RJH: is this better?
-%ji to DPS - what is the linearisation that is happening here?
-%ji- the linearisation consist in the frequency axis being linear and the 
-% data being streched with it.  The frequency normally are not evenly spaced
-%ays: I deleted the phrase "based on the values closer to the average" because I don't understand what that means
 
 \begin{listing}[H]
-\pythoncode{spectra.py}
+\pythoncode{pycode_spectra.txt}
 \begin{center}

### 2014-08-28 2-Data_Types.tex
edits from full read thru

--- 2014-08-27 2-Data_Types.tex
@@
 classes is to provide the same core data type to the SunPy user
-regardless of the differences in source data.  For example, if two
-different instruments use different time formats to describe the
-observation time of their images, the corresponding SunPy \texttt{Map}
-object for each of them expresses the observation time in the same
-way.  This simplifies the workflow for the user when handling data
-from multiple sources.
+regardless of the differences in source data.  This simplifies 
+the workflow for the user when handling data from multiple sources.
 
@@
 enable analysis and visualisation. For each of these classes, the data is
-stored in the \texttt{data} attribute, while the metadata should be stored 
-in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
-fully implemented). 
-% schriste - change this until all fixed
+stored in the \texttt{data} attribute, while the metadata is stored 
+in the \texttt{meta} attribute\footnote{Note, that currently only \texttt{Map} and \texttt{LightCurve} have this feature 
+fully implemented}. 
 It is possible to instantiate the
@@
 include visualisation methods that are tailored to each data type. 
-These visualisation methods all currently utilise the \texttt{matplotlib} 
+These visualisation methods all utilise the \texttt{matplotlib} 
 package and are designed in such a way that they integrate well with 

### 2014-08-28 3-1-VSO.tex
Missing comma after e.g.
edits from full read thru

@@
 
-The Virtual Solar Observatory (\href{http://virtualsolar.org}{VSO}) provides a 
-single, standard query interface to solar data from different archives 
+The Virtual Solar Observatory (\url{http://virtualsolar.org}{VSO}) provides a 
+single, standard query interface to solar data from many different archives 
 around the world \citep{hill2009}.
@@
 Listing~\ref{code:vso_query_simple} also shows how to download the data using
-the constructed query. The path to which the data files will be downloaded us defined using custom tokens
-which reference the file metadata (e.g. instrument, detector, filename). This provides
+the constructed query. The path to which the data files will be downloaded is defined using custom tokens
+which reference the file metadata (e.g., instrument, detector, filename). This provides
 users the ability to organize their data into subdirectories on download.

### 2014-08-28 3-2-HEK.tex
edits from full read thru

@@
 wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK) \citep{hek2012}.  Entries are generated both by 
+in the Heliophysics Event Knowledgebase (HEK) \citep{hurlburt2012}.  Entries are generated both by
 automated algorithms and human observers.  Some of the information in the HEK 
@@
 provides an homogeneous and well-described interface to a large amount of 
-feature and event information of interest to the solar physics community. SunPy 
+feature and event information. SunPy 
 accesses this information through the \texttt{hek} module.  The \texttt{hek} module makes use of the 
@@
 The example in Listing~\ref{code:hek:frm} repeats the previous 
-HEK query (see Listing \ref{code:hek:simple}}, with an additional filter enabled to return only those events that have the FRM `SSW Latest Events'.  
+HEK query (see Listing \ref{code:hek:simple}}, with an additional filter enabled 
+to return only those events that have the FRM `SSW Latest Events'.  
 Multiple comparisons can be made by including more comma-separated
@@
 and \texttt{or}). The ability to use comparison and logical operators on HEK attributes allows 
-the construction of queries of almost arbitrary complexity.
+the construction of queries of arbitrary complexity.
 For the query in Listing \ref{code:hek:or} returns
@@
 download observational data. The \texttt{H2VClient} module makes this
-much easier by providing a translation layer between HEK query results
-and VSO queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.
+east by providing a translation layer between HEK query results
+and VSO data queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.
 \begin{listing}[H]

### 2014-08-28 3-4-Helioviewer.tex
edits from full read thru

@@
 SunPy provides the ability to download images hosted by the
-Helioviewer Project (\href{http://helioviewer.org}{http://helioviewer.org}).  
+Helioviewer Project (\url{http://helioviewer.org}).  
 The aim of the Helioviewer Project is to enable
@@
 applications that allow users to browse images and create movies of the Sun taken 
-by a variety of instruments: \href{http://www.helioviewer.org}{Helioviewer.org}, a 
-Google Maps-like web application, and \href{http://www.jhelioviewer.org}{JHelioviewer}, 
+by a variety of instruments: \url{http://www.helioviewer.org}, a 
+Google Maps-like web application, and \url{http://www.jhelioviewer.org}, 
 a movie streaming desktop application. In order to manage all of this data, the Helioviewer
@@
 other pieces of software. The first, 
-\href{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open-source
+\url{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open-source
 library for reading and writing JPEG2000 files.  The other package 
 required is 
-\href{https://github.com/quintusdias/glymur}{\texttt{glymur}}, an
+\url{https://github.com/quintusdias/glymur}{\texttt{glymur}}, an
 interface between Python and the OpenJPEG libraries (note that these

### 2014-08-28 5-Dev.tex
edits from full read thru

@@
 meetings.
+
+In order to enable the long-term development of SunPy, a formal organizational
+structure has been defined. The management of SunPy is the responsibility of 
+the SunPy board, a group of elected members of the community. The board elects
+a lead developer whose is responsible for the day to day development of SunPy.
+SunPy also makes use of Python-style Enhancement proposals which can be proposed
+by the community and are voted on by the board. These proposals set the overal
+direction of SunPy's development.

### 2014-08-28 3-2-HEK.tex
bug fixes

@@
 The example in Listing~\ref{code:hek:frm} repeats the previous 
-HEK query (see Listing \ref{code:hek:simple}}, with an additional filter enabled 
+HEK query (see Listing \ref{code:hek:simple}), with an additional filter enabled 
 to return only those events that have the FRM `SSW Latest Events'.  

### 2014-08-28 2-3-Spectra.tex
more bug fixes, and finishes addressing #80

@@
 and convenient visualization and sampling of the data.
-Currently, the \texttt{Spectrogram} class supports radio spectrograms from the 
-\href{http://www.e-callisto.org/}{e-Callisto}
+Currently, the \texttt{Spectrogram} class supports radio spectrograms from the e-Callisto (
+\url{http://www.e-callisto.org/})
 solar radio spectrometer network \citep{2009EM&P..104..277B} and \textit{STEREO}/SWAVES spectrograms \citep{2008SSRv..136..487B}.
@@
   removes the background signal.  The data requested -- `BIR' -- is
-  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
+  the code name of the Rosse Observatory \url{http://www.rosseobservatory.ie}
   at Birr Castle in Ireland.}

### 2014-08-28 3-3-HELIO.tex
more bug fixes, and finishes addressing #80

--- 2014-08-26 3-3-HELIO.tex
@@
 catalogues, in this case the ones detected automatically 
-by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht2009}.}
+by the Computer Aided CME Tracking feature recognition algorithm CACTus (\url{http://sidc.oma.be/cactus/}) \citep{robbrecht_automated_2009}.}
 \label{code:helio}

### 2014-08-28 3-5-Database.tex
more bug fixes, and finishes addressing #80

@@
 The \texttt{database} subpackage can make use of any database software supported by
-{\texttt{SQLAlchemy} (\href{http://www.sqlalchemy.org}{http://www.sqlalchemy.org}). This library was chosen
+{\texttt{SQLAlchemy} (\url{http://www.sqlalchemy.org}). This library was chosen
 since it supports many SQL dialects. 

### 2014-08-28 3-3-HELIO.tex
fixes based on comments

@@
 catalogues, in this case the ones detected automatically 
-by the Computer Aided CME Tracking feature recognition algorithm CACTus (\url{http://sidc.oma.be/cactus/}) \citep{robbrecht_automated_2009}.}
+by the by the Computer Aided CME Tracking feature recognition algorithm
+\citep[CACTus - \url{http://sidc.oma.be/cactus/};][]{robbrecht_automated_2009}.}
 \label{code:helio}

### 2014-08-28 3-4-Helioviewer.tex
fixes based on comments

@@
 Reading JPEG2000 file into a SunPy session requires installing two
-other pieces of software. The first, 
-\url{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open-source
+other pieces of software. The first, OpenJPEG
+(\url{http://www.openjpeg.org}), is an open-source
 library for reading and writing JPEG2000 files.  The other package 
-required is 
-\url{https://github.com/quintusdias/glymur}{\texttt{glymur}}, an
+required is Glymur (
+\url{https://github.com/quintusdias/glymur}), an
 interface between Python and the OpenJPEG libraries (note that these

### 2014-08-28 1-Introduction.tex

--- 2014-08-27 1-Introduction.tex
@@
 (for example, the large solar flare of 23 July 2002 has Astrophysical
-Journal Letters volume 595, dedicated to the analysis of this flare).
-In this workflow, data from many different instruments are obtained.
-These data are typically in many different storage formats (for
+Journal Letters volume 595, dedicated to its analysis).
+In this workflow, an event is investigated in depth which requires 
+data from many different instruments.
+These data are typically provided in many different formats (for
 example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
 binary files), and contain many different types of data (such as
-images, lightcurves and spectra).  The repositories these data reside
+images, lightcurves and spectra).  In addition, the repositories these data reside
 in can have different access methods.  This workflow is characterized
@@
 capabilities, an overview of the project's development model, community aspects of the
-project, and future plans. The latest release of SunPy, version 0.4,
+project, and future plans. The latest release of SunPy, version 0.5,
 can be downloaded from \url{http://sunpy.org} or can be

### 2014-08-28 2-1-Map.tex
bug fixes

@@
 to be subclassed. Each subclass of \texttt{GenericMap} can register 
-with the \texttt{Map} creation function, which will then automatically return an instance
+with the \texttt{Map} creation factory, which will then automatically return an instance
 of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
@@
 \item \textit{SOHO}/EIT and LASCO - SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}
-\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}.},
+\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L},
 \item \textit{STEREO}/EUVI and COR1/2 - STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}

### 2014-08-28 3-1-VSO.tex

@@
 
-The Virtual Solar Observatory (\url{http://virtualsolar.org}{VSO}) provides a 
+The Virtual Solar Observatory (VSO, \url{http://virtualsolar.org}) provides a 
 single, standard query interface to solar data from many different archives 

### 2014-08-28 6-Future.tex

@@
 and 
-calibration routines, and contains full (WCS) coordinate information. 
+calibration routines, and contains valid metadata. 
 The plan for SunPy is to continue development within this 
@@
 \texttt{MapCube} 
-along one spatial coordinate, a \texttt{LightCurve} of intensity along the 
+along one spatial location, a \texttt{LightCurve} of intensity along the 
 time range of 
@@
 Astropy project \citep{theastropycollaboration2013} is ongoing.
-%schriste - shortened this bit as it was a bit vague and gave the impression that we may be subsumed by astropy

### 2014-08-28 abstract.tex

@@
 \begin{abstract}
-This paper presents version 0.4 of SunPy, a community-developed Python package 
+This paper presents SunPy (version 0.5), a community-developed Python package 
 for solar physics.
@@
 SunPy is a data-analysis environment specialising in providing the software 
-necessary to analyse solar and heliospheric datasets in Python. 
+necessary to analyse solar and heliospheric data in Python. 
 SunPy is open-source software (BSD licence) and has an open and transparent 

### 2014-08-28 authors.tex

@@
 Michael Malocha$^{11}$, %10
-John Evans$^{12}$,%10 %No affil
+John Evans$^{12}$, %10 %No affil
 Ankit Agrawal$^{13}$, %8
@@
 
-$^{17}$Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
-Bogotá, D.C., Colombia
+$^{17}$Observatorio Astron\'omico Nacional, Universidad Nacional de Colombia, 
+Bogot\'a, D.C., Colombia
 

### 2014-08-28 1-Introduction.tex
fixes to the FITS citation

@@
 These data are typically provided in many different formats (for
-example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
+example, FITS (Flexible Image Transport System, \citealt{refId0}), CSV, or
 binary files), and contain many different types of data (such as

### 2014-08-28 2-Data_Types.tex
remove duplicate line in Sec. 2
added full stop to foot note, Sec 2.

@@
 classes is to provide the same core data type to the SunPy user
-regardless of the differences in source data.  This simplifies 
-the workflow for the user when handling data from multiple sources.
+regardless of the differences in source data.  For example, if two
+different instruments use different time formats to describe the
+observation time of their images, the corresponding SunPy \texttt{Map}
+object for each of them expresses the observation time in the same
+way.  This simplifies the workflow for the user when handling data
+from multiple sources.
 
@@
 in the \texttt{meta} attribute\footnote{Note, that currently only \texttt{Map} and \texttt{LightCurve} have this feature 
-fully implemented}. 
+fully implemented.}. 
 It is possible to instantiate the

### 2014-08-28 reply_referee.txt

@@
 
-4)
+4) In the example on p.11, the term ‘coronagraphs’ was included here by mistake. Instead, the query result ‘lasco_query’ should have been referred to. The listing has been corrected.
 
@@
 
-6)
+6) We agree with the referee that more Python-like idioms should be used in the code listing examples.
+Code snippets such as lasco_query.num_records() (e.g.
+Listing 6) have hence been replaced with len(lasco_query.records) throughout the manuscript.
 
-7)
+7) We have clarified the construction of the file paths in Listing 6 by adding more description to the Listing caption.
+We have also endeavored to clarify the code listings throughout the manuscript, as the referee has suggested.
 
@@
 
-9)
+9) We agree with the referee that full descriptions of the allowed attrs should be easily available for HEK and VSO.
+Unfortunately this feature is not yet available within SunPy.
+However, we plan to address this in the near future.
 

### 2014-08-28 2-1-Map.tex
cleaned up map instrument list

@@
 \begin{itemize}
-\item \textit{Yohkoh}/SXT - SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T},
-\item \textit{SOHO}/EIT and LASCO - SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}
-\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L},
-\item \textit{STEREO}/EUVI and COR1/2 - STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}
-\item \textit{Hinode}/XRT - XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
-\item \textit{PROBA2}/SWAP - PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}
-\item \textit{SDO}/AIA and HMI - HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
-\item \textit{IRIS} - IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L} SJI (slit-jaw imager) frames.           
+\item \textit{Yohkoh} Solar X-ray Telescope (SXT; \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
+\item Solar and Heliospheric Observatory (\textit{SOHO}; \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
+\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO; \citealp{1995SoPh..162..357B})
+\item \textit{RHESSI} - Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
+\item Solar TErrestrial RElations Observatory (\textit{STEREO}; \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI; \citep{2004SPIE.5171..111W})
+\item \textit{STEREO} CORonagraph 1/2 (COR 1/2; \citealp{2002AdSpR..29.2017H})
+\item \textit{Hinode} XRT - X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
+\item PRojects for On Board Autonomy 2 (\textit{PROBA2}; \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
+\item \textit{SDO} AIA and HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
+\item Interface Region Imaging Spectrograph (\textit{IRIS}; \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
 \end{itemize}

### 2014-08-28 3-2-HEK.tex
HEK reference cleaned up

@@
 wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK) \citep{hurlburt2012}.  Entries are generated both by
+in the Heliophysics Event Knowledgebase (HEK, \citealp{hurlburt2012}).  Entries are generated both by
 automated algorithms and human observers.  Some of the information in the HEK 
@@
 download observational data. The \texttt{H2VClient} module makes this
-east by providing a translation layer between HEK query results
+easier by providing a translation layer between HEK query results
 and VSO data queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.

### 2014-08-28 1-Introduction.tex
proofreading edits.

--- 2014-08-28 1-Introduction.tex
@@
 
-Science is driven by the analysis of data of an ever-growing variety and 
+Science is driven by the analysis of data of ever-growing variety and 
 complexity. Advances in sensor technology, combined with the availability of 
@@
 powerful, and easy-to-learn high-level programming language. Additionally, Python is 
-widely used outside of scientific fields in areas like `big data' analytics, web 
-development, and educational environments. For example, \texttt{pandas} was 
+widely used outside of scientific fields in areas such as `big data' analytics, web 
+development, and educational environments. For example, \texttt{pandas} \citep{mckinney2010, mckinney2012} was 
 originally developed for quantitative analysis of financial data and has since 
@@
 such as array manipulation, core numerical algorithms, and visualisation, respectively.
-Building upon these foundations, packages such as \texttt{astropy} (astronomy)
-\citep{theastropycollaboration2013}, \texttt{pandas} (time-series)
-\citep{mckinney2010, mckinney2012}, and \texttt{scikit-image} (image processing)
-\citep{vanderwalt2014} provide more domain-specific functionality.
+Building upon these foundations, packages such as \texttt{astropy}
+\citep[astronomy;][]{theastropycollaboration2013}, \texttt{pandas} (time-series), and \texttt{scikit-image} 
+\citep[image processing;][]{vanderwalt2014} provide more domain-specific functionality.
 
@@
 data from many different instruments.
-These data are typically provided in many different formats (for
-example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
-binary files), and contain many different types of data (such as
+These data are typically provided in many different formats - for
+example, FITS \citep[Flexible Image Transport System,][]{refId0}, CSV, or
+binary files - and contain many different types of data (such as
 images, lightcurves and spectra).  In addition, the repositories these data reside
@@
 the need for an environment in which obtaining and performing common
-solar-physics operations on these data is as simple and intuitive as
+solar physics operations on these data is as simple and intuitive as
 possible.  SunPy is designed to be a clean, simple-to-use, and

### 2014-08-28 2-1-Map.tex
cleaned up HMI listing in 2-1
proofreading edits.

--- 2014-08-28 2-1-Map.tex
@@
 The \texttt{Map} class also provides a convenient interface for loading data 
-from a variety of sources, including from FITS (Flexible Image Transport System) 
-files, the standard format for storing image data in solar physics and astrophysics community. 
+from a variety of sources, including from FITS files, the standard format for storing image data in solar physics and astrophysics community. 
 An example of creating a \texttt{Map} object from a FITS file is shown in 
@@
 \item \textit{SOHO}/EIT and LASCO - SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}
-\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L},
+\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
 \item \textit{STEREO}/EUVI and COR1/2 - STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}

### 2014-08-28 3-2-HEK.tex
HEK text cleaned up a bit

@@
 For the query in Listing \ref{code:hek:or} returns
-returns flares with helioprojective x coordinates west of 50 arcseconds or 
-those that have a peak flux above 1000.0 in units defined by the FRM.
+returns flares with helio-projective $x$-coordinates west of 50 arcseconds or 
+those that have a peak flux above 1000.0 (in units defined by the FRM).
 

### 2014-08-28 3-2-HEK.tex
HEK text cleaned up a bit

@@
 \texttt{hek.attrs.EventType("FL")} or as \texttt{hek.attrs.FL}. 
-
 HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in that many 
@@
 \end{listing}
-All FRMs report the required feature attributes, but the optional attributes 
-are FRM dependent.  If a FRM does not have one of the optional attributes, 
-\texttt{None} is returned by the \texttt{hek} module.
+All FRMs report their required feature attributes (as defined by the
+HEK), but the optional attributes are FRM dependent\footnote{See
+  \url{http://www.lmsal.com/hek/VOEvent_Spec.html} for a list of
+  features and their attributes.}.  If a FRM does not have one of the
+optional attributes, \texttt{None} is returned by the \texttt{hek}
+module.
 
-Frequently after users have found events of interest the next step is to 
+After users have found events of interest the next step is to 
 download observational data. The \texttt{H2VClient} module makes this

### 2014-08-28 3-4-Helioviewer.tex
helioviewer section cleaned up

@@
 SunPy provides the ability to download images hosted by the
-Helioviewer Project (\url{http://helioviewer.org}).  
+Helioviewer Project (\url{http://wiki.helioviewer.org}).  
 The aim of the Helioviewer Project is to enable
@@
 Google Maps-like web application, and \url{http://www.jhelioviewer.org}, 
-a movie streaming desktop application. In order to manage all of this data, the Helioviewer
-project maintains archives of all of its data in JPEG2000 format (for further
-details on the Helioviewer Project, see \citealt{muller2009}). The
+a movie streaming desktop application. The Helioviewer
+project maintains archives of all its image data in JPEG2000 format (\citealt{muller2009}). The
 JPEG2000 files are typically highly compressed compared to the source
@@
 observatory $\rightarrow$ instrument $\rightarrow$ detector
-$\rightarrow$ measurement, where '$\rightarrow$' means 'provides
-(possibly multiple)'.  
+$\rightarrow$ measurement, where ``$\rightarrow$'' means ``provides a''.  
 %schriste - say what?!

### 2014-08-28 3-2-HEK.tex
more proofreading edits.

--- 2014-08-28 3-2-HEK.tex
@@
 wavelengths. Observations and metadata concerning these phenomena are collected 
-in the Heliophysics Event Knowledgebase (HEK, \citealp{hurlburt2012}).  Entries are generated both by
+in the Heliophysics Event Knowledgebase (HEK) \citep{hurlburt2012}.  Entries are generated both by
 automated algorithms and human observers.  Some of the information in the HEK 
@@
 the construction of queries of arbitrary complexity.
-For the query in Listing \ref{code:hek:or} returns
+The query in Listing \ref{code:hek:or} returns
 returns flares with helioprojective x coordinates west of 50 arcseconds or 

### 2014-08-28 2-1-Map.tex

--- 2014-08-28 2-1-Map.tex
@@
 \begin{itemize}
-\item \textit{Yohkoh} Solar X-ray Telescope (SXT; \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
-\item Solar and Heliospheric Observatory (\textit{SOHO}; \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
-\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO; \citealp{1995SoPh..162..357B})
+\item \textit{Yohkoh} Solar X-ray Telescope (SXT, \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
+\item Solar and Heliospheric Observatory (\textit{SOHO}, \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
+\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO, \citealp{1995SoPh..162..357B})
 \item \textit{RHESSI} - Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
-\item Solar TErrestrial RElations Observatory (\textit{STEREO}; \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI; \citep{2004SPIE.5171..111W})
-\item \textit{STEREO} CORonagraph 1/2 (COR 1/2; \citealp{2002AdSpR..29.2017H})
+\item Solar TErrestrial RElations Observatory (\textit{STEREO}, \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI, \citep{2004SPIE.5171..111W})
+\item \textit{STEREO} CORonagraph 1/2 (COR 1/2, \citealp{2002AdSpR..29.2017H})
 \item \textit{Hinode} XRT - X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
-\item PRojects for On Board Autonomy 2 (\textit{PROBA2}; \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
-\item \textit{SDO} AIA and HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
-\item Interface Region Imaging Spectrograph (\textit{IRIS}; \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
+\item PRojects for On Board Autonomy 2 (\textit{PROBA2}, \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
+\item \textit{SDO} AIA and Helioseismic Magnetic Imager, (HMI, \citealp{2012SoPh..275..207S})
+\item Interface Region Imaging Spectrograph (\textit{IRIS}, \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
 \end{itemize}

### 2014-08-28 3-1-VSO.tex

@@
 
-Listing~\ref{code:vso_query_simple} shows an example of how to query and download data using
+Listing~\ref{code:vso_query_simple} shows an example of how to query and download data
 from the VSO using the \texttt{vso} module.
@@
 attribute object is a constraint on a parameter of the data set, such as the
-time, instrument, or wavelength.
+time of the observation, instrument, or wavelength.
 Listing~\ref{code:vso_query_simple} also shows how to download the data using

### 2014-08-28 reply_referee.txt
response to referee 1 point 2
Finish up the ref response.

@@
 
-2)
+2) We have added appropriate references to the Introduction for the software packages that are mentioned in the text (e.g. Astropy, scipy, pandas) in accordance with the referee’s suggestion.
 
-3)
+3) The SunPy database holds data for any supported (and probably a few unsupported) instruments, performing a query without specifying an instrument will return all records in the database matching those criteria, for all data for all instruments.
+The example has been clarified.
 
@@
 
-5)
+5) Different data providers such as the VSO and the HEK have different interfaces and different available search options, which made it much simpler to implement these as separate hierarchies.
+There has been some work done over this summer to create a unified search interface to different providers.
+This feature will hopefully appear in SunPy 0.6 towards the end of the year.
 
@@
 7) We have clarified the construction of the file paths in Listing 6 by adding more description to the Listing caption.
-We have also endeavored to clarify the code listings throughout the manuscript, as the referee has suggested.
+We have also endeavoured to clarify the code listings throughout the manuscript, as the referee has suggested.
 
-8)
+8) There is no real reason why show() was chosen over __str__. We have taken this suggestion on board and will be changing the functionality in SunPy in the future.
 
@@
 10) We agree with the distinction made by the referee - we clarify the text to refer to 'database software supported by SQLAlchemy' in Section 3.5.
-
-7)

### 2014-08-28 2-2-Lightcurve.tex
edits from full read thru
more proofreading edits.
Change the location of the pandas citation.

@@
 data.  The main engine behind the \texttt{LightCurve} class is
-the {\texttt{pandas}} data-analysis library.  
+the {\texttt{pandas}} data analysis library.  
 \texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
@@
 of functionality for manipulating and analysing time-series data,
-making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
+making it an ideal basis for \texttt{LightCurve}.  \texttt{LightCurve}
 assumes that the input data are time-ordered list(s) of numbers, and each
@@
   CSV files is currently implemented -- see
-  \url{http://lasp.colorado.edu/home/eve/data/}} (EVE, \citealt{2012SoPh..275..115W}). \texttt{LightCurve}
+  \url{http://lasp.colorado.edu/home/eve/data/}} (EVE, \citealt{2012SoPh..275..115W}). 
+\texttt{LightCurve}
 also supports a number of solar summary indices - such as average
@@
 its corresponding specific data format in its constructor and parse
-that file type.
+that file type. A more general download interface is currently in development.
 
